---
title: "Turning Points Codebook"
author: 
  - name: "Maria L. Schweer-Collins, PhD"
    email: "mschweer@uoregon.edu"
    affiliations:
      - name: 'University of Oregon'
        city: 'Eugene'
        state: 'OR'
  - name: "Jonathan A. Pedroza, PhD"
    email: "cpppedroza@gmail.com"
format: 
  pdf:
    toc: true
    toc-depth: 3
    toc-title: Contents
    number-sections: true
    number-depth: 3
    colorlinks: true
bibliography: C:/Users/cpppe/Desktop/github_projects/TurningPoints4Women/tpw_references.bib
---

```{r, include = FALSE}
library(tidyverse)
library(here)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE)

theme_set(theme_light())

data <- read_csv('C:/Users/cpppe/Desktop/github_projects/TurningPoints4Women/do_not_push/data_77included.csv') 

complete <- read_csv('C:/Users/cpppe/Desktop/github_projects/TurningPoints4Women/do_not_push/data_calculated.csv')

source('C:/Users/cpppe/Desktop/github_projects/TurningPoints4Women/functions/codebook_fun.R')
```

### Missing Data Rule

-   For scales with [10 or more items]{.underline}, a composite score (average/total) is computed for **TC** that have less than [20%]{.underline} of the items from that measure missing

-   For scales with [7 to 9 items]{.underline}, a composite score (average/total) is computed for **TC** that have less than [30%]{.underline} of the items from that measure missing

-   For scales with [3 to 6 items]{.underline}, a composite score (average/total) is computed for **TC** that have less than [33%]{.underline} of the items from that measure missing

-   For scales with [only 2 items]{.underline}, composite scores (average/total) are calculated on a [case by case basis]{.underline}

# Mental Health

## BSI

### BSI Description

-   Variables for BSI scale

    -   `bsi1`, `bsi2`, `bsi3`, `bsi4`, `bsi5`, `bsi6`, `bsi7`, `bsi8`, `bsi9`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi14`, `bsi15`, `bsi16`, `bsi17`, `bsi18`, `bsi19`

    -   Variable Scale

        -   0 - "Not at all"

        -   1 - "A little bit"

        -   2 - "Moderately"

        -   3 - "Quite a bit"

        -   4 - "Very much"

-   Total scores should range from 0 to 76

-   Revere Scoring

    -   N/A

-   Subscales

    -   Somatization: `bsi2`, `bsi3`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi15`

    -   Anxiety: `bsi1`, `bsi5`, `bsi9`, `bsi16`, `bsi17`, `bsi18`

    -   Depression: `bsi4`, `bsi6`, `bsi7`, `bsi8`, `bsi14`, `bsi19`

-   Missing Data Rule:

    -   N/A

-   Reference: @derogatis1983brief

    -   [Link here](https://www.cambridge.org/core/journals/psychological-medicine/article/abs/brief-symptom-inventory-an-introductory-report/307F805810B165ED58581E355F24329F)

    -   [DOI here](https://doi.org/10.1017/S0033291700048017)

### BSI Missing Data

```{r bsi missing data, warning = FALSE, message = FALSE}
data %>%
  select(
    id:bsi19
  ) %>% 
  pct_miss_fun(
    id = 'id',
    n_items = 19
  )
```

### BSI Scale & Subscale Distributions

```{r bsi distributions}
complete %>%
  composite_hist(
    x = bsi_total
  ) +
  labs(title = 'Distribution of Total Scores for BSI Measure')

complete %>%
  composite_hist(x = bsi_soma_total) +
  labs(title = 'Distribution for BSI Somatization Subscale')

complete %>%
  composite_hist(x = bsi_anx_total) +
  labs(title = 'Distribution for BSI Anxiety Subscale')

complete %>%
  composite_hist(x = bsi_dep_total) +
  labs(title = 'Distribution for BSI Depression Subscale')
```

### BSI Internal Reliability

```{r bsi alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
bsi_alpha <-
  complete %>%
  select(bsi1:bsi19) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_som <-
  complete %>%
  select(bsi2:bsi3,
         bsi10:bsi13,
         bsi15) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_anx <-
  complete %>%
  select(bsi1, bsi5, bsi9, bsi16:bsi18) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_dep <-
  complete %>%
  select(bsi4, bsi6:bsi8, bsi14, bsi19) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_table <- tibble(
  Scale = c('BSI',
            'BSI - Somatization',
            'BSI - Anxiety',
            'BSI - Depression'),
  Alpha = c(round(bsi_alpha$total$raw_alpha, 3),
            round(bsi_alpha_som$total$raw_alpha, 3),
            round(bsi_alpha_anx$total$raw_alpha, 3),
            round(bsi_alpha_dep$total$raw_alpha, 3))
)

bsi_alpha_table %>%
  gt::gt() %>%
  gt::tab_header(
    title = 'Alpha Values for BSI Entire Scale & Subscales'
  )
```

## CESD

### CESD Description

-   Variables for CESD scale

    -   `c1`, `c2`, `c3`, `c4`, `c5`, `c6`, `c7`, `c8`, `c9`, `c10`, `c11`, `c12`, `c13`, `c14`, `c15`, `c16`, `c17`, `c18`, `c19`, `c20`

    -   Variable Scale

        -   0 - "Rarely or none of the time"

        -   1 - "Some or a little of the time"

        -   2 - "Occasionally or a moderate amount of time"

        -   3 - "Most or all of the time"

-   Total scores should range from `0` to `60`

-   Revere Scoring

    -   Items `c4`, `c8`, `c12`, and `c16` are reverse scored

-   Variables For Other Items

    -   `c21`, `c22`, `c23`, `c24`

        -   if response is `No` to item `c21`, then TC moved on to item `c24`

    -   Variable Scale

        -   0 - No

        -   1 - Yes

        -   2 - Declined to Answer

-   Subscales

    -   Positive Affect

        -   `c4_r`, `c8_r`, `c12_r`, `c16_r`

    -   Depressive Symptoms

        -   `c1`, `c2`, `c3`, `c5`, `c6`, `c7`, `c9`, `c10`, `c11`, `c13`, `c14`, `c15`, `c17`, `c18`, `c19`, `c20`

-   Missing Data Rule:

    -   N/A

-   Reference: @radloff1977ces

    -   [Link here](https://journals.sagepub.com/doi/abs/10.1177/014662167700100306)

    -   [DOI here](https://doi.org/10.1177%2F014662167700100306)

-   Additional References:

    -   Cutoff Information: @henry2018determining

        -   [Link here](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4)

        -   [DOI here](https://doi.org/10.1016/j.jad.2018.02.071)

    -   Items for Potential Subscales: @canady2009measurement

        -   [Link here](https://connect.springerpub.com/content/sgrjnm/17/2/91.abstract)

        -   [DOI here](10.1891/1061-3749.17.2.91)

### CESD Missing Data

```{r}
data %>%
  select(id,
         c1:c20,
         c4_r:c16_r) %>%
  pct_miss_fun(
    id = 'id',
    n_items = 20
  ) %>%
  gt::gt() %>%
  gt::tab_header(
    title = 'Missing Data',
    subtitle = 'By Each Participant'
  )
```

Missing data for suicidal ideation, plan, and attempt items.

```{r}
data %>%
  select(id,
         c21:c24) %>%
  pct_miss_fun(
    id = 'id',
    n_items = 20
  ) %>%
  gt::gt() %>%
  gt::tab_header(
    title = 'Missing Data',
    subtitle = 'By Each Participant'
  )
```

### CESD Scale & Suscale Distributions

```{r}
complete %>%
  composite_hist(cesd_total) +
  labs(
    title = 'CESD Total Score Distribution'
    )

complete %>%
  composite_hist(
    cesd_dep_symp_total
    ) +
  labs(
    title = 'Total Score Distribution',
       subtitle = 'Depressive Symptoms Subscale'
    )

complete %>%
  composite_hist(
    cesd_pos_aff_total,
    bins = 10
    ) +
  labs(
    title = 'Total Score Distribution',
       subtitle = 'Depressive Symptoms Subscale'
    )
```

### CESD Cutoffs

```{r}
complete %>%
  cutoff_plot(
    x = cesd_total,
    cutoff = 16,
    cutoff_other = 23
  ) +
  labs(
    title = 'Cutoff Scores for CESD Total Scores',
    caption = 'Cutoffs are 16 and/or 23\nSee references for literature on cutoff scores.'
  )
```

### CESD Internal Reliability

```{r}
cesd_alpha <-
  complete %>%
  select(c1:c16_r) %>%
  psych::alpha(check.keys = TRUE)

cesd_dep_alpha <-
  complete %>%
  select(c1:c20) %>%
  psych::alpha(check.keys = TRUE)

cesd_pos_aff_alpha <-
  complete %>%
  select(c4_r, c8_r, c12_r, c16_r) %>%
  psych::alpha(check.keys = TRUE)


cesd_alpha_table <- tibble(
  Scale = c('CESD', 'CESD - Depressive Symptoms',
            'CESD - Positive Affect'),
  Alpha = c(round(cesd_alpha$total$raw_alpha, 3),
            round(cesd_dep_alpha$total$raw_alpha, 3),
            round(cesd_pos_aff_alpha$total$raw_alpha, 3)
  )
)

cesd_alpha_table %>%
  gt::gt() %>%
  gt::tab_header(
    title = 'Alpha Values for CESD Entire Scale & Subscales'
  )
```

# COVID-19

## CIQ

### CIQ Description

-   Variables for BSI COVID-19 items

    -   `ciq1`, `ciq2`, `ciq3`

    -   Variable Scale

        -   1 - "Not true of me at all"

        -   2

        -   3

        -   4

        -   5

        -   6

        -   7 - "Very true of me"

-   Total score should range from 3 to 21

-   Reverse Scoring

    -   item `ciq3` should be reverse scored

-   Reference: @conway2020social

    -   [Link here](https://psyarxiv.com/z2x9a/download?format=pdf)

### CIQ Missing Data

```{r, warning = FALSE, message = FALSE}
data %>%
  select(id,
         ciq1:ciq3_r) %>%
  pct_miss_fun(
    id = 'id',
    n_items = 3
  )
```

### CIQ Scale Distribution

```{r}
complete %>%
  composite_hist(
    x = ciq_psych_total,
    bins = 10
    ) +
  labs(title = 'Distribution for CIQ Psychological Scale')
```

### CIQ Internal Reliability

```{r}
ciq_alpha <-
  complete %>%
  select(ciq1, ciq2, ciq3_r) %>%
  psych::alpha(check.keys = TRUE)

ciq_alpha_table <- tibble(
  Scale = 'CIQ - Psychological Scale',
  Alpha = round(ciq_alpha$total$raw_alpha, 3)
)
  
ciq_alpha_table %>%
 gt::gt() %>%
  gt::tab_header(
    title = 'Alpha Values for CIQ - Psychological Scale'
  )
```

# Substance Use

## DAST

### DAST Description

-   Variables for DAST scale

    -   `d00`, `d1a`, `d2a`, `d2b`, `d3`, `d4`, `d5`, `d6`, `d7`, `d8`, `d9`, `d10`, `d11`, `d12`, `d13`, `d14`, `d15`, `d16`, `d17`, `d18`, `d19`, `d20`

    -   Variable scale

        -   1 - "Yes"

        -   0 - "No"

    -   Total scores should range from `0` to `20`

    -   Reverse scoring

        -   Items `d4` and `d5` are reverse coded

        -   both were renamed to `d4_r` and `d5_r` respectively

    -   `d2a` and `d2b` are skip logic questions based on responses for `d1a`

        -   `d1a = 1` moved on to respond to `d2a`

        -   `d1a = 0` or `d1a = -77` moved on to respond to `d2b`

-   Subscales

    -   No subscales were created for this measure as there was a lack of evidence supporting a subscale structure

-   Missing Data Rule:

    -   Applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses)

-   Reference: @gavin1989diagnostic

    -   [Link here](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1360-0443.1989.tb03463.x)

    -   [DOI here](https://doi.org/10.1111/j.1360-0443.1989.tb03463.x)

### DAST Missing Data

```{r}
data %>%
  select(
    id,
    d1a:d3,
    d6:d5_r
         ) %>%
  pct_miss_fun(
    id = 'id',
    n_items = 21
  ) %>% 
  gt::gt() %>% 
  gt::tab_header(
    title = 'DAST Missing Data',
    subtitle = 'By Participant'
  )
  
```

### DAST Scale & Subscale Distributions

```{r}
complete %>%
  composite_hist(
    x = dast_total
  ) +
  labs(
    title = 'Distribution of Total Scores for DAST Measure'
  )
```

### DAST Severity

```{r}
complete %>%
  severity_plot(
  x = dast_total,
  bins = 20,
  low_xmin = 1,
  low_xmax = 5.5,
  medium_xmin = 5.5,
  medium_xmax = 10.5,
  large_xmin = 10.5,
  large_xmax = 15.5,
  critical_xmin = 15.5,
  critical_xmax = 20) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 3,
    y = -1.5,
    label = 'Low'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 8,
    y = -1.5,
    label = 'Intermediate'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 13,
    y = -1.5,
    label = 'Substantial'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 18,
    y = -1.5,
    label = 'Severe'
  ) +
  labs(
    title = 'Severity Categories',
    subtitle = 'Based on DAST',
    caption = 'Cutoffs are:\nLow = 1-5,\nIntermediate = 6-10,\nSubstantial = 11-15,\nSevere = 16-20'
  )
```

### DAST Internal Reliability

```{r}
dast_alpha <-
  complete %>%
  select(
    d1a:d3,
    d6:d5_r
         ) %>%
  mutate(
    d2 = coalesce(d2a, d2b)
  ) %>% 
  select(-d2a, -d2b) %>% 
  drop_na(d2) %>% 
  psych::alpha(check.keys = TRUE)


dast_alpha_table <-
  tibble(
  Scale = 'DAST',
  Alpha = round(dast_alpha$total$raw_alpha, 3)
)

dast_alpha_table %>%
  gt::gt() %>%
  gt::tab_header(
    title = 'Alpha Values for DAST Scale'
  )

```

# Child Abuse

## BCAP

### BCAP Description

-   Variables for the BCAP measure

    -   `q1`,`q2`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q9`, `q10`, `q11`, `q12`, `q13`, `q14`, `q15`, `q16`, `q17`, `q18`, `q19`, `q20`, `q21`, `q22`, `q23`, `q24`, `q25`, `q26`, `q27`, `q28`, `q29`, `q30`, `q31`, `q32`, `q33`, `q34`
    -   Variable Scale
        -   1 - "Agree"

        -   0 - "Disagree"

        -   -77 - "Decline to respond"
    -   Total scores should range from 0 to 24
        -   total scale score is the BCAP risk scale with all the items that are not part of the lie and random responding subscales

        -   `q1`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q10`, `q11`, `q12`, `q13`, `q14`, `q16`, `q17`, `q19`, `q20`, `q22`, `q23`, `q24`, `q25`, `q27`, `q29`, `q30`, `q31`, `q32`, `q33`
    -   Reverse coding
        -   Items `q1`, `q2`, `q23`, and `q29` should be reverse coded

-   Subscales

    -   Happiness (reverse coded)

        -   `q1`, `q23`, `q29`

    -   Feelings of persecution

        -   `q3`, `q25`, `q33`

    -   Loneliness

        -   `q5`, `q12`, `q22`, `q31`

    -   Family conflict

        -   `q6`, `q13`, `q17`

    -   Rigidity

        -   `q7`, `q14`, `q20`, `q32`

    -   Distress

        -   `q8`, `q11`, `q16`, `q19`, `q27`

    -   Poverty

        -   `q10`, `q30`

-   Additional subscales to remove invalid cases

    -   Lie

        -   `q4`, `q9`, `q15`, `q21`, `q26`, `q34`

    -   Random responding

        -   `q2`, `q18`, `q28`

-   Missing Data Rule:

    -   Applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses)

-   Reference: @ondersma2005brief

    -   [Link here](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug)

    -   [DOI here](https://doi.org/10.1207/s15374424jccp3402_9)

### BCAP Missing Data

```{r}
data %>%
  select(
    id,
    q3:q22,
    q24:q28,
    q30:q29_r
         ) %>% 
    pct_miss_fun(
      id = 'id', 
      n_items = 34 
    ) %>%
  gt::gt() %>% 
  gt::tab_header(
    title = 'BCAP Missing Data',
    subtitle = 'By Participant'
  )
```

### BCAP Scale & Subscale Distributions

```{r}
complete %>%
  composite_hist(
    x = bcap_risk_total
  ) +
  labs(
    title = 'Distribution of Total Scores for BCAP Risk Scale'
  )

complete %>% 
  composite_hist(
    x = bcap_happy_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Happiness Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_feel_pers_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Feelings of Persecution Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_lonely_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Loneliness Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_fam_conf_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Family Conflict Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_rigid_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Rigidity Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_distress_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Distress Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_poverty_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Poverty Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_lie_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Lying Subscale'
  )

complete %>% 
  composite_hist(
    x = bcap_random_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Random Responding Subscale'
  )
```

### BCAP Cutoffs

```{r}
complete %>%
  cutoff_plot(
    x = bcap_risk_total,
    cutoff = 9,
    cutoff_other = 12
  ) +
  labs(
    title = 'Cutoff Values for BCAP Scale',
    caption = 'Cutoffs are 9 and 12\nSee references for literature on cutoff scores.'
  )

complete %>% 
  cutoff_plot(
    x = bcap_lie_total,
    cutoff = 4
  ) +
  labs(
    title = 'Cutoff Values for BCAP Lie Subscale',
    caption = 'If 4 or more (score of 4) items are endorsed,\ncase may be invalid'
  )

complete %>% 
  cutoff_plot(
    x = bcap_random_total,
    cutoff = 0
  ) +
  labs(
    title = 'Cutoff Values for BCAP Random Responding Subscale',
    caption = 'If any of these items are endorsed (score > 0),\ncase may be invalid'
  )
```

### BCAP Internal Reliability

```{r}
bcap_alpha <- 
  complete %>% 
  select(
    q1_r,
    q2_r,
    q3:q22,
    q23_r,
    q24:q28,
    q29_r,
    q30:q34
  ) %>% 
  psych::alpha(check.keys = TRUE)

bcap_risk_alpha <-
  complete %>%
  select(
    q1_r,
    q3,
    q5:q8,
    q10:q14,
    q16:q17,
    q19:q20,
    q22,
    q23_r,
    q24:q25,
    q27,
    q29_r,
    q30:q33
    ) %>%
  psych::alpha(check.keys = TRUE)

bcap_happy_alpha <- 
  complete %>% 
  select(q1_r, q23_r, q29_r) %>% 
  psych::alpha(check.keys = TRUE)

bcap_feel_pers_alpha <- 
  complete %>% 
  select(q3, q25, q33) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lonely_alpha <- 
  complete %>% 
  select(q5, q12, q22, q31) %>% 
  psych::alpha(check.keys = TRUE)

bcap_fam_conf_alpha <- 
  complete %>% 
  select(q6, q13, q17) %>% 
  psych::alpha(check.keys = TRUE)

bcap_rigid_alpha <-
  complete %>% 
  select(q7, q14, q20, q32) %>% 
  psych::alpha(check.keys = TRUE)

bcap_distress_alpha <- 
  complete %>% 
  select(q8, q11, q16, q19, q27) %>% 
  psych::alpha(check.keys = TRUE)

bcap_poverty_alpha <- 
  complete %>% 
  select(q10, q30) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lie_alpha <-
  complete %>% 
  select(q4, q9, q15, q21, q26, q34) %>% 
  psych::alpha(check.keys = TRUE)

bcap_random_alpha <-
  complete %>% 
  select(q2_r, q19, q28) %>% 
  psych::alpha(check.keys = TRUE)

bcap_alpha_table <-
  tibble(
    Scale = c('BCAP Complete Scale', 'BCAP Risk Scale',
              'Happiness Subscale', 'Feelings of Persecution Subscale',
              'Loneliness Subscale', 'Family Conflict Subscale',
              'Rigidity Subscale', 'Distress Subscale',
              'Poverty Subscale',
              'Lying Subscale', 'Random Responding Subscale'),
    Alpha = c(round(bcap_alpha$total$raw_alpha, 3),
              round(bcap_risk_alpha$total$raw_alpha, 3),
              round(bcap_happy_alpha$total$raw_alpha, 3),
              round(bcap_feel_pers_alpha$total$raw_alpha, 3),
              round(bcap_lonely_alpha$total$raw_alpha, 3),
              round(bcap_fam_conf_alpha$total$raw_alpha, 3), 
              round(bcap_rigid_alpha$total$raw_alpha, 3), 
              round(bcap_distress_alpha$total$raw_alpha, 3),
              round(bcap_poverty_alpha$total$raw_alpha, 3), 
              round(bcap_lie_alpha$total$raw_alpha, 3),
              round(bcap_random_alpha$total$raw_alpha, 3))
  )

bcap_alpha_table %>%
  gt::gt() %>%
  gt::tab_header(
    title = 'Alpha Values for BCAP Scale & Subscales'
  )

```

# Partner Relationships

## DYADC

### DYADC Description

-   Variables for DYADC scale

    -   `e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`, `e14`, `e15`, `e16`, `e17`, `e18`, `e19`, `e20`, `e21`, `e22`, `e23`, `e24`, `e25`, `e26`, `e27`, `e28`, `e29`, `e30`, `e31`, `e32`

-   Variable Scale

    -   For items `e1` to `e15`

        -   5 - "Always Agree"

        -   4 - "Almost Always Agree"

        -   3 - "Occasionally Disagree"

        -   2 - "Frequently Disagree"

        -   1 - "Almost Always Disagree"

        -   0 - "Always Disagree"

        -   -77 - "Declined to Respond"

    -   Items `e16` to `e22`, except `e18` and `e19` are reverse scored

        -   0 - "All the time"

        -   1 - "Most of the time"

        -   2 - "More often than not"

        -   3 - "Occasionally"

        -   4 - "Rarely"

        -   5 - "Never"

        -   -77 -"Declined to Respond"

    -   Items `e23` and `e24` are both on the following scale

        -   4 - "Every day"

        -   3 - "Almost every day"

        -   2 - "Occasionally"

        -   1 - "Rarely"

        -   0 - "Never"

        -   -77 - "Declined to Respond"

    -   Items `e25` to `e28`

        -   0 - "Never"

        -   1 - "Less than once a month"

        -   2 - "Once or twice a month"

        -   3 - "Once or twice a week"

        -   4 - "Once a day"

        -   5 - "More often"

        -   -77 - "Declined to Respond"

    -   Items `e29` and `e30`

        -   0 - "Yes"

        -   1 - "No"

    -   `e31`

        -   0 - "Extremely Unhappy"

        -   1 - "Fairly Unhappy"

        -   2 - "A Little Unhappy"

        -   3 - "Happy"

        -   4 - "Very Happy"

        -   5 - "Extremely Happy"

        -   6 - "Perfect"

        -   -77 - "Declined to Respond"

    -   `e32`

        -   5 - "I want desperately for my relationship to succeed, and would go to almost any length to see that it does."

        -   4 - "I want very much for my relationship to succeed, and will do all I can to see that it does."

        -   3 - "I want very much for my relationship to succeed, and will do my fair share to see that it does."

        -   2 - "It would be nice if my relationship succeeded, but I can't do much more than I'm doing now to help it succeed."

        -   1 - "It would be nice if it succeeded, but I refuse to do any more than I am doing now to keep the relationship going."

        -   0 - "My relationship can never succeed, and there is no more that I can do to keep the relationship going."

        -   -77 - "Declined to Respond"

-   Total scores should range from 0 to 151

-   Reverse Coding

    -   `e18` and `e19` are reverse coded

-   Subscales

    -   Dyadic Consensus

        -   `e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`

    -   Affective Expression

        -   `e4`, `e6`, `e29`, `e30`

    -   Dyadic Satisfaction

        -   `e16`, `e17`, `e18`, `e19`, `e20`, `e21`, `e22`, `e23`, `e31`, `e32`

    -   Dyadic Cohesion

        -   `e24`, `e25`, `e26`, `e27`, `e28`

-   Missing Data Rule:

    -   Applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses)

-   Reference: @spanier1976measuring

    -   [Link here](https://www.jstor.org/stable/350547)

    -   [DOI here](https://doi.org/10.2307/350547)

### DYADC Missing Data

```{r}
data %>%
  select(
    id,
    e1:e32
  ) %>% 
  pct_miss_fun(
    id = 'id',
    n_items = 32
  ) %>%
  gt::gt() %>% 
  gt::tab_header(
    title = 'DYADC Missing Data',
    subtitle = 'By Participant'
  )
```

### DYADC Scale & Subscale Distributions

```{r}
complete %>%
  composite_hist(
    x = dyadc_total
  ) +
  labs(
    title = 'Distribution for DYADC Scale'
  )

complete %>%
  composite_hist(
    x = dyadc_con_total
  ) +
  labs(
    title = 'Distribution for DYADC Consensus Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_aff_exp_total,
    bins = 10
  ) +
  labs(
    title = 'Distribution for DYADC Affectional Expression Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_satis_total
  ) +
  labs(
    title = 'Distribution for DYADC Satisfaction Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_cohes_total
  ) +
  labs(
    title = 'Distribution for DYADC Cohesion Subscale'
  )
```

### DYADC Cutoffs

```{r}
complete %>%
  cutoff_plot(
    x = dyadc_total,
    cutoff = 92,
    cutoff_other = 107
  ) +
  labs(
    title = 'Cutoff Values for DYADC Scale',
    caption = 'Cutoffs are 92 and 107\nSee references for literature on cutoff scores.'
  )
```

### DYADC Internal Reliability

```{r}
dyadc_alpha <-
  complete %>% 
  select(
    e1:e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_con_alpha <-
  complete %>% 
  select(
    e1:e13
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_aff_exp_alpha <-
  complete %>% 
  select(
    e4, e6, e29, e30
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_satis_alpha <-
  complete %>% 
  select(
    e16:e23,
    e31,
    e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_cohes_alpha <-
  complete %>% 
  select(
    e24:e28
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_alpha_table <- 
  tibble(
    Scale = c('DYADC',
              'DYADC - Consensus',
              'DYADC - Affectional Expression',
              'DYADC - Satisfaction',
              'DYADC - Cohesion'
      
    ),
    Alpha = c(round(dyadc_alpha$total$raw_alpha, 3),
              round(dyadc_con_alpha$total$raw_alpha, 3),
              round(dyadc_aff_exp_alpha$total$raw_alpha, 3),
              round(dyadc_satis_alpha$total$raw_alpha, 3),
              round(dyadc_cohes_alpha$total$raw_alpha, 3))
  )

dyadc_alpha_table %>% 
  gt::gt() %>% 
  gt::tab_header(
    title = 'Alpha Values for DYADC Scale & Subscales'
  )
```

## CTS2S

### CTS2S Description

-   Variables in CTS2S

    -   `ct1`, `ct2`, `ct3`, `ct4`, `ct5`, `ct6`, `ct7`, `ct8`, `ct9`, `ct10`, `ct11`, `ct12`, `ct13`, `ct14`, `ct15`, `ct16`, `ct17`, `ct18`, `ct19`, `ct20`

-   Variable Scale

    -   1 - "Once in the past year"

    -   2 - "Twice in the past year"

    -   3 - "3-5 times in the past year"

    -   4 - "6-10 times in the past year"

    -   5 - "11-20 times in the past year"

    -   6 - "More than 20 times in the past year"

    -   7 - "Not in the past year, but it did happen before"

    -   8 - "This has never happened"

    -   -77 - "Declined to Respond"

-   Subscales (Individual/Participant/TC)

    -   Psychological Aggression

        -   `ct3`, `ct13`

    -   Physical Injury

        -   `ct5`, `ct15`

    -   Assault

        -   `ct9`, `ct11`

    -   Sexual Cohesion

        -   `ct17`, `ct19`

    -   Negotiation

        -   `ct1`, `ct7`

-   Subscales (Partner)

    -   Psychological Aggression

        -   `ct4`, `ct14`

    -   Physical Injury

        -   `ct6`, `ct16`

    -   Assault

        -   `ct10`, `ct12`

    -   Sexual Cohesion

        -   `ct18`, `ct20`

    -   Negotiation

        -   `ct2`, `ct8`

-   CTS2S should not have a calculated total/average composite score

-   CTS2S has three different ways of scoring (Prevalence, Severity, Mutuality)

    -   Prevalence

        -   assessed for both individual/participant/TC and partner

        -   assessed by whether any behavior within each subscale occurred in the past year

    -   Severity

        -   assessed for both individual/participant/TC and partner

        -   assessed as either no instance of the behavior, minor instance of the behavior, or severe instance of the behavior for each subscale

        -   0 - "No"

        -   1 - "Minor"

        -   2 - "Severe"

    -   Mutuality

        -   assessed by combining responses from both individual/participant/TC and partner

        -   assessed as either none, male/partner only, female/individual/participant/TC only, both

        -   0 - "None"

        -   1 - "Partner only"

        -   2 - "Individual/Participant/TC only"

        -   3 - "Both"

-   Missing Data Rule:

    -   Applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses)

-   Reference: @straus2004short

    -   [Link here](https://connect.springerpub.com/content/sgrvv/19/5/507.abstract)

    -   [DOI here](10.1891/vivi.19.5.507.63686)

### CTS2S Missing Data

```{r}
data %>%
  select(
    id,
    ct1:ct20
  ) %>% 
  pct_miss_fun(
    id = 'id',
    n_items = 20
  ) %>%
  gt::gt() %>% 
  gt::tab_header(
    title = 'CTS2S Missing Data',
    subtitle = 'By Participant'
  )
```

### CTS2S Severity Distributions (Individual \[TC\])

```{r}
complete %>%
  mutate(
    cts_psy_agg_ind_sev = case_when(
      cts_psy_agg_ind_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_ind_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_ind_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_ind_sev = as.factor(cts_psy_agg_ind_sev),
    cts_psy_agg_ind_sev = relevel(cts_psy_agg_ind_sev, 'No Psychological Aggression')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_ind_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Individual (TC) Psychological Aggression Severity',
       x = '')

complete %>%
  mutate(
    cts_injury_ind_sev = case_when(
      cts_injury_ind_sev == 0 ~ 'No Injury',
      cts_injury_ind_sev == 1 ~ 'Minor Injury',
      cts_injury_ind_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_ind_sev = as.factor(cts_injury_ind_sev),
    cts_injury_ind_sev = relevel(cts_injury_ind_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_ind_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Individual (TC) Physical Injury Severity',
       x = '')

complete %>%
  mutate(
    cts_assault_ind_sev = case_when(
      cts_assault_ind_sev == 0 ~ 'No Assault',
      cts_assault_ind_sev == 1 ~ 'Minor Assault',
      cts_assault_ind_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_ind_sev = as.factor(cts_assault_ind_sev),
    cts_assault_ind_sev = relevel(cts_assault_ind_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_ind_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Individual (TC) Assault Severity',
       x = '')

complete %>%
  mutate(
    cts_sex_ind_sev = case_when(
      cts_sex_ind_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_ind_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_ind_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_ind_sev = as.factor(cts_sex_ind_sev),
    cts_sex_ind_sev = relevel(cts_sex_ind_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_ind_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Individual (TC) Sexual Cohesion Severity',
       x = '')
```

### CTS2S Severity Distributions (Partner)

```{r}
complete %>%
  mutate(
    cts_psy_agg_part_sev = case_when(
      cts_psy_agg_part_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_part_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_part_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_part_sev = as.factor(cts_psy_agg_part_sev),
    cts_psy_agg_part_sev = relevel(cts_psy_agg_part_sev, 'No Psychological Aggression')
    ) %>%
  ggplot(
    aes(
      cts_psy_agg_part_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Partner Psychological Aggression Severity',
       x = '')

complete %>%
  mutate(
    cts_injury_part_sev = case_when(
      cts_injury_part_sev == 0 ~ 'No Injury',
      cts_injury_part_sev == 1 ~ 'Minor Injury',
      cts_injury_part_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_part_sev = as.factor(cts_injury_part_sev),
    cts_injury_part_sev = relevel(cts_injury_part_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_part_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Partner Physical Injury Severity',
       x = '')

complete %>%
  mutate(
    cts_assault_part_sev = case_when(
      cts_assault_part_sev == 0 ~ 'No Assault',
      cts_assault_part_sev == 1 ~ 'Minor Assault',
      cts_assault_part_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_part_sev = as.factor(cts_assault_part_sev),
    cts_assault_part_sev = relevel(cts_assault_part_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_part_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Partner Assault Severity',
       x = '')

complete %>%
  mutate(
    cts_sex_part_sev = case_when(
      cts_sex_part_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_part_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_part_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_part_sev = as.factor(cts_sex_part_sev),
    cts_sex_part_sev = relevel(cts_sex_part_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_part_sev
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Partner Sexual Cohesion Severity',
       x = '')
```

### CTS2S Prevalence Distributions

```{r}
complete %>%
  pivot_longer(
    cols = c(cts_psy_agg_ind_prev, cts_psy_agg_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_psy_agg_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_psy_agg_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Psychological Aggression Prevalence')

complete %>%
  pivot_longer(
    cols = c(cts_injury_ind_prev, cts_injury_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_injury_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_injury_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Physical Injury Prevalence')

complete %>%
  pivot_longer(
    cols = c(cts_assault_ind_prev, cts_assault_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_assault_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_assault_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Assault Prevalence')

complete %>%
  pivot_longer(
    cols = c(cts_sex_ind_prev, cts_sex_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_sex_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_sex_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Sexual Cohesion Prevalence')
```

### CTS2S Mutuality Distributions

```{r}
complete %>%
  mutate(
    cts_psy_agg_mutual = case_when(
      cts_psy_agg_mutual == 0 ~ 'Neither',
      cts_psy_agg_mutual == 1 ~ 'Male Only',
      cts_psy_agg_mutual == 2 ~ 'Female Only',
      cts_psy_agg_mutual == 3 ~ 'Both'
    ),
    cts_psy_agg_mutual = as.factor(cts_psy_agg_mutual),
    cts_psy_agg_mutual = relevel(cts_psy_agg_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_mutual
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Mutual Psychological Aggression')

complete %>%
  mutate(
    cts_injury_mutual = case_when(
      cts_injury_mutual == 0 ~ 'Neither',
      cts_injury_mutual == 1 ~ 'Male Only',
      cts_injury_mutual == 2 ~ 'Female Only',
      cts_injury_mutual == 3 ~ 'Both'
    ),
    cts_injury_mutual = as.factor(cts_injury_mutual),
    cts_injury_mutual = relevel(cts_injury_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_injury_mutual
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Mutual Injury')

complete %>%
  mutate(
    cts_assault_mutual = case_when(
      cts_assault_mutual == 0 ~ 'Neither',
      cts_assault_mutual == 1 ~ 'Male Only',
      cts_assault_mutual == 2 ~ 'Female Only',
      cts_assault_mutual == 3 ~ 'Both'
    ),
    cts_assault_mutual = as.factor(cts_assault_mutual),
    cts_assault_mutual = relevel(cts_assault_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_assault_mutual
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Mutual Assault')

complete %>%
  mutate(
    cts_sex_mutual = case_when(
      cts_sex_mutual == 0 ~ 'Neither',
      cts_sex_mutual == 1 ~ 'Male Only',
      cts_sex_mutual == 2 ~ 'Female Only',
      cts_sex_mutual == 3 ~ 'Both'
    ),
    cts_sex_mutual = as.factor(cts_sex_mutual),
    cts_sex_mutual = relevel(cts_sex_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_sex_mutual
    )
  ) +
  geom_bar() +
  labs(title = 'Distribution of Mutual Sexual Cohesion')
```

### CTS2S Internal Reliability

-   authors describe that internal reliability is not appropriate for the `CTS2S` measure.

# References
