 For scales with [10 or more items]{.underline}, a composite score
    (average/total) is computed for each participant that have less than
    [20%]{.underline} of the items from that measure missing

-   For scales with [7 to 9 items]{.underline}, a composite score
    (average/total) is computed for each participant that have less than
    [30%]{.underline} of the items from that measure missing

-   For scales with [3 to 6 items]{.underline}, a composite score
    (average/total) is computed for each participant that have less than
    [33%]{.underline} of the items from that measure missing

-   For scales with [only 2 items]{.underline}, composite scores
    (average/total) are calculated on a [case by case basis]{.underline}



## Sexual History Survey - Sex

### Sex Description

The SEX is a *insert*.

For the present study, 30 items from the SEX were collected in order to
#TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[\@cloitre2018international](https://onlinelibrary.wiley.com/doi/full/10.1111/acps.12956?casa_token=K4GIoIIYOkwAAAAA%3ABuaGU3cOQZwsFiM78FxHp_PHTQXDc72xABnVp8nlMCYRCHzf4c0oOMropyrzVjdClA3pFA-m01heootZ);
[DOI](https://doi.org/10.1111/acps.12956)

### sex Variables

#### Value Labels and Survey Items

All SEX variables are presented below. Variable without value are open
end questions.

```{r sex-var-prep}
# Pull question wording from qualtrics data
sex_word <- qualtrics %>% 
  select(S1:S48)%>%
  slice(1)


#create table with variable name, description, and notes
sex_word_long <- sex_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         value = case_when(var_name == "s1" ~ "1 = Yes
                                                  \n2 = No
                                                  \n3 = Decline",
                           var_name == "s1a" ~ "1 = cisgender female
                                                \n2 = female
                                                \n3 = cisgender male
                                                \n4 = male
                                                \n5 = trans female
                                                \n6 = tras male
                                                \n7 = non-binary
                                                \n8 = self-identify",
                           var_name %in% c("s3", "s4", "s6", "s13", "s22", "s23", "s26", "s35", "s38", "s39", "s40", "s44", "s45") ~ "1 = Yes
                                                              \n2 = No
                                                              \n3 = Decline",
                           var_name == "s9" ~ "1 = a great deal
                           \n2 = quite a lot
                           \n3 = some
                           \n4 = not much
                           \n5 = very little
                           \n6 = Decline",
                           var_name == "s10" ~ "1 = heterosexual
                           \n2 = gay_lesbian
                           \n3 = bisexual
                           \n4 = other
                           \n5 = Decline",
                           var_name == "s11" ~ "1 = Never,
                           \n2 ~ Rarely
                                 \n3 = Sometimes
                                 \n4 = Often
                                 \n5 = Very Often
                                 \n6 = Decline",
                           var_name == "s12" ~ "1 = Very Comfortable
                                 \n2 = Somewhat Comfortable
                                 \n3 = Neutral
                                 \n4 = Somewhat",
                           var_name == "s14" ~ "1 = Friend
                                 \n2 = Romantic Partner
                                 \n3 = Sister/Brother
                                 \n4 = Other Relative
                                 \n5 = Counselor/Teacher/Doctor
                                 \n6 = Parent
                                 \n7 = Other
                                 \n8 = Decline",
                           var_name == "s16" ~ "1 = Never
                                 \n2 = Rarely
                                 \n3 = Sometimes
                                 \n4 = Often
                                 \n5 = Very Often
                                 \n6 = Decline",
                           var_name %in% c("s17", "s18", "s19") ~ "1 = Very Comfortable
                                 \n2 = Somewhat Comfortable
                                 \n3 = Neutral
                                 \n4 = Somewhat uncomfortable
                                 \n5 = Very uncomfortable
                                 \n6 = Decline",
                           var_name == "s20" ~ "1 = Very confident
                                 \n2 = Somewhat confident
                                 \n3 = A little confident
                                 \n4 = Not at all confident
                                 \n5 = Decline",
                           var_name == "s21" ~ "1 = Always or almost always
                                 \n2 = Often
                                 \n3 = About  half the time
                                 \n4 = Occasionally
                                 \n5 = Never or almost never
                                 \n6 = Decline",
                           var_name == "s24" ~ "1 = Yes, I had a std (positive diagnosis)
                                 \n2 = No STD (negative diagnosis)
                                 \n3 = Don't know yet; waiting for results
                                 \n4 = Decline",
                           var_name == "s28" ~ "1 = Yes
                                 \n2 = No
                                 \n3 = Decline
                                 \n4 = Pregnant prior to last 6 months; knew pregnant prior to 6 month period",
                           var_name == "s29" ~ "1 = Went to dr; positive diagnosis
                                 \n2 = Went to dr; negative diagnosis
                                 \n3 = Went to dr; don't know
                                 \n4 = Took home test; positive
                                 \n5 = Took home test; negative
                                 \n6 = Took home test; don't know
                                 \n7 = Did nothing; period started
                                 \n8 = Did nothing, don't know
                                 \n9 = Decline",
                           var_name == "s33" ~ "1 = Always or almost always
                                 \n2 = Often
                                 \n3 = About half the time
                                 \n4 = Occasionally
                                 \n5 = Never or almost never
                                 \n6 = Decline",
                           var_name == "s34" ~ "1 = Never 0%
                                 \n2 = Rarely 1-15%
                                 \n3 = Occasionally 15-40%
                                 \n4 = About half the time 40-60%
                                 \n5 = Usually 60-85%
                                 \n6 = Most of the time 85-99%
                                 \n7 = Every single time 100%
                                 \n8 = Decline",
                           var_name == "s36" ~ "1 = Always or almost always
                                 \n2 = Often
                                 \n3 = About half the time
                                 \n4 = Occasionally
                                 \n5 = Never or almost never
                                 \n6 = Decline",
                           var_name == "s37" ~ "1 = Always or almost always
                                 \n2 = Often
                                 \n3 = About half the time
                                 \n4 = Occasionally
                                 \n5 = Never or almost never
                                 \n6 = Decline",
                           var_name == "s43" ~ "1 = Never 0%
                                 \n2 = Rarely 1-15%
                                 \n3 = Occasionally 15-40%
                                 \n4 = About half the time 40-60%
                                 \n5 = Usually 60-85%
                                 \n6 = Most of the time 85-99%
                                 \n7 = Every single time 100%
                                 \n8 = Decline
                                 \n9 = Don't know
                                 \n10 = Not using birth control; currently pregnant",
                           var_name == "s46" ~ "1 = Yes, had oral sex without dental dam
                                 \n2 = No, oral sex and always used dental dam
                                 \n3 = Decline",
                           TRUE ~ as.character("")
         ),
         notes = as.character("")
         
  ) %>%
  mutate(description = ifelse(var_name == "s2", "When did you start seeing your current partner? ",
         ifelse(var_name == "s2a", "02a. How long, not counting time when you were broken up, have you and your partner been together? __ __ years",
                              ifelse(var_name == "s2b", "	02b. __ __ months",
                                     ifelse(var_name == "s2c", "02c. __ __ days",
                                            ifelse(var_name == "s10", "Do you feel that you are: ",
                                                   ifelse(var_name == "s10_4_text", "Do you feel that you are:",
                                                          ifelse(var_name == "s13", "Do you have anyone else, not including your closest friends, that you talk to when you have a question or concern regarding birth control or safe sex practices?",
                                                                 ifelse(var_name == "s14", "Is that person a friend, relative, partner, or someone else?",
                                                                        ifelse(var_name == "s14_8_text", "Is that person a friend, relative, partner, or someone else?",
                                                                               ifelse(var_name == "s18", "How comfortable do you feel discussing the use of birth control or contraceptives to prevent pregnancy with someone you might have sex with?",
                                                                                      ifelse(var_name == "s28", "Were there any times during the last 6 months that you thought you might be pregnant? (Assessor select the 4th option \"I became pregnant prior to this last 6 months...\" if the participant was recently or is currently pregnant)",
                                                                                             ifelse(var_name == "s29", "What happened?",
                                                                                                    ifelse(var_name == "s30", "How many times, in the last six months, have you had sexual relations? __ __ __ times",
                                                                                                           ifelse(var_name == "s38", "In the last 6 months, have you had sexual relations with someone who injects drugs? ",
                                                                                                                  ifelse(var_name == "s43", "In the last 6 months, when you've had intercourse with a male partner, what percentage of the time did you or your partner USE a birth control method specifically to prevent pregnancy?", description
                                                                                                                         ))))))))))))))))

  



```

```{r sex-var-table, results ='asis'}
# Create the gt table object and apply generic theme
sex_gt_table <- gt(sex_word_long)

# Table-specific formatting (col width, names)
sex_gt_table <- sex_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(sex_gt_table)


```

## pregnancy childbirth trauma question

### CINT Description

The CINT is TODO: insert.

All <TODO:insert> items from the

TThe missing data rule was applied. Calculations were completed only
with participants that had less than 20% missing data (this includes
`-77` responses)

Reference:
[\@saxbe_birth_2018](https://psycnet.apa.org/doiLanding?doi=10.1037%2Ffam0000365);
[DOI](https://doi.org/10.1037/fam0000365)

### CINT Variables

#### Value Labels

All CINT survey items response options are below.

pct0, pct1, pct2a, pct2b, pct2c, pct2d, pct3a, pct3b, pct3c, pct3d

```{r CINT-label-table, results = 'asis'}

cint_label_df <- data.frame(
  value = c("1", "0"),
  label = c("Yes",
            "No")
) %>% 
  t() %>% 
  as.data.frame()

cint_label_df <- setNames(cint_label_df[-1, ], unlist(cint_label_df[1, ]))


#create table
cint_label_table <- cint_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(cint_label_table)


```

#### Survey Items

All CINT survey items are presented in the following table:

```{r cint-var-prep}
# Pull question wording from qualtrics data
cint_word <- qualtrics %>% 
  select(PCT0:PCT3e) %>% 
  slice(1)

#create table with variable name, description, and notes

cint_word_long <- cint_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate_all(~gsub("READ:", "", .)) %>%
  mutate(description = str_replace(description, "^\\d[a-z]+\\.\\s*|^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")
         ) %>%
  mutate(description = if_else(var_name == "pct0", "Has TC reported any pregnancies?",
                               if_else(var_name == "pct2e", "During which pregnancy or pregnancies did this occur? ",
                                       if_else(var_name == "pct3e", "During which pregnancy or pregnancies did this occur? ", description))))
  



```

```{r cint-var-table, results ='asis'}
# Create the gt table object and apply generic theme
cint_gt_table <- gt(cint_word_long)

# Table-specific formatting (col width, names)
cint_gt_table <- cint_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(250),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(cint_gt_table)

```

#### Scale and Subscales

Information on the aggregated scale and subscale variables are below.
Total and subscale variables were constructed by summing corresponding
items.

```{r cint-alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
cint_alpha <-
  complete_rnd2 %>%
  select( pct1, pct2a, pct2b, pct2c, pct2d, pct3a, pct3b, pct3c, pct3d) %>% #TODO: Shaina, could you double check if the calculation is right
   filter(complete.cases(.)) %>%
  psych::alpha(check.keys = TRUE)

cint_alpha_Preg <-
  complete_rnd2 %>%
  select( pct1, pct2a, pct2b, pct2c, pct2d) %>% #TODO: Shaina, could you double check if the calculation is right
   filter(complete.cases(.)) %>%
  psych::alpha(check.keys = TRUE)

cint_alpha_Child <-
  complete_rnd2 %>%
  select( pct1, pct3a, pct3b, pct3c, pct3d) %>% #TODO: Shaina, could you double check if the calculation is right
   filter(complete.cases(.)) %>%
  psych::alpha(check.keys = TRUE)
```

TODO: the Preg & Child sub-scale will need calculate in cleaning script

```{r cint-scale-table, results = 'asis'}
# Create the table as a data frame
# TODO: should the calculation use revers score?
cint_scale_df <- data.frame(
  var_name = c("cint_total", "", ""), # TODO: the scale need to be calculated in cleaning file
  scale = c("Total Score (9)","Pregnancy Trauma (3)","Childbirth Trauma (3)"),
  scale_construction = c( "`pct1`, `pct2a`, `pct2b`, `pct2c`, `pct2d`, `pct3a`, `pct3b`, `pct3c`, `pct3d`", "`pct1`, `pct2a`, `pct2b`, `pct2c`, `pct2d`", "`pct1`,`pct3a`, `pct3b`, `pct3c`, `pct3d`"),
  scale_range = c("","",""),
  alpha = c(round(cint_alpha$total$raw_alpha, 3),
            round(cint_alpha_Preg$total$raw_alpha, 3),
            round(cint_alpha_Child$total$raw_alpha, 3)
            )
)

# Create the gt table object
cint_scale_table <- gt(cint_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme()

# Print the table
print(cint_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r cint-mean-items}
# Create subset of cint items
data_subset_cint <- complete_rnd2 %>%
  select( pct1, pct2a, pct2b, pct2c, pct2d, pct3a, pct3b, pct3c, pct3d)

# Calculate the summary statistics for each variable
summary_data_cint <- lapply(data_subset_cint, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- sprintf("%.2f", round(sd(x, na.rm = TRUE), 2))
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_df_cint <- as.data.frame(summary_data_cint) %>% 
  rbind(names(summary_data_cint)) %>% 
  t() %>% 
  as.data.frame() %>% 
  select(`5`, everything())

# Create the gt table
cint_tbl <- summary_df_cint %>%
  gt() %>%
  cols_label(`5` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(2:5 ~ px(160)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
cint_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r cint-calculation, class.source='fold', echo = FALSE}
cint <- complete_rnd2 %>%
  select(
    id,
    pct0:pct3e
  ) %>%
  mutate(
    pct0 = case_when(
      pct0 == 1 ~ "Yes",
      pct0 == 2 ~ "No",
      TRUE ~ NA_character_
    ),
    across(
      c(
        pct1:pct2d,
        pct3a:pct3d
      ),
      ~case_when(
        .x == 1 ~ 1,
        .x == 2 ~ 0,
        .x == 3 ~ -77,
        TRUE ~ NA_real_
      )
    )
  )

cint_calc <- cint %>%
  mutate(
    across(
        -c(id, pct0, pct1, pct2e, pct3e),
        ~case_when(
          .x == -77 ~ NA_real_,
          TRUE ~ .x
        )
    )
  )

cint_miss <- cint_calc %>%
  pct_miss_fun(
    id = c(
      "id",
      "pct0",
      "pct1",
      "pct2e",
      "pct3e"
    ),
    n_items = 8
  )

# cint_miss %>%
#   gt::gt() %>%
#   gt::tab_header(
#     title = "Missing Data",
#     subtitle = "By Each Participant"
#   )

cint_remove <- cint_miss %>% filter(miss_pct >= 30) %>% pull(id)

cint_complete <- cint_calc %>%
  composite_total_avg_fun(
    id = c(
      "id",
      "pct0",
      "pct1",
      "pct2e",
      "pct3e"
    ),
    max_value = 1,
    n_items = 8
  ) %>%
  distinct(
    across(
      .cols = everything()
    )
  ) %>%
  select(
    -mean_values
  ) %>%
  rename(
    cint_total = sum_values
    ) %>%
  mutate(
    across(
      c(
        cint_total
      ),
      ~case_when(
        id %in% cint_remove ~ NA_real_,
        TRUE ~ .x
      )
    )
  )
```

```{r cint-distributions, class.source='fold', echo = FALSE}
cint_complete %>%
  composite_hist(
    x = cint_total,
    bins = 10
  ) +
  labs(
    title = "Distribution of Total Scores for the CINT"
  )
```
