---
title: "Turning Points Codebook"
 author: 
   - name: "Maria L. Schweer-Collins, PhD (corresponding author)"
     email: "mschweer@uoregon.edu"
#     affiliations:
#       - name: 'University of Oregon'
#         city: 'Eugene'
#         state: 'OR'
   - name: "Shaina Trevino, PhD"
#     email: "strevino@uoregon.edu"
   - name: "Jonathan A. Pedroza, PhD"
#     email: "cpppedroza@gmail.com"
   - name: "Min Zhang"
#     email: "mzhang8@uoregon.edu"
date: ""
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    self_contained: yes
    number_sections: no
    #html#toc_title: Contents
    #number_sections: true
    #html#number_depth: 3
    #qmd#colorlinks: true
    #keep_tex: yes
    #pdf#latex_engine: pdflatex
    #error#includes: 
      #error#in_header: styles.css
#pdf#geometry: landscape
bibliography: tpw_references.bib
editor_options: 
  markdown: 
    wrap: 72
---
<!-- TOC highlight color -->
<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #246B69;
}


<!-- To have nice indentation in toc float -->
.tocify-header {
  text-indent: initial;
}

.tocify-subheader > .tocify-item {
  text-indent: initial;
  padding-left: 2em;
}

</style>
TODO: double check codebook_fun.r composite_total_avg_fun

```{r setup, include = FALSE}
library(tidyverse)
library(here)
library(gt)
library(ggplot2)
library(scales)
library(ggpubr)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE)

theme_set(theme_light())

#import included survey items
# data <- read_csv(here("do_not_push", "tpw_data_77included.csv"))

#import df of calculated survey items
#complete_rnd2 <- read_csv(here("do_not_push", "round_two_measures_data_calc.csv"))

#import telephone survey data 
complete <- read_csv(here("do_not_push","tpw_archive_calc.csv"))

#import raw qualtrics data for parsing question text
qualtrics <- read_csv(here("do_not_push", "tpw_raw_qualtrics_5-30-23.csv"))

source(here("functions", "codebook_fun.R"))
```

```{r plot-style, echo=FALSE}
# Color palettes 
 Two_color = c("#246B69", "#604C41")

# Histogram style 
# hist_style <- geom_histogram(bins=20, color = "white", fill = "#246B69", alpha = 0.7)


bar_style <- geom_bar(color = "white", fill = "#246B69", alpha = 0.7)

THEME <-     theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),legend.key = element_rect(fill = "White", colour = "transparent"),plot.title = element_text(size= 13),
    )
```

```{r cutoff-plot-function}
#re-work JP cutoff function due to error "cant use `{{` in non-quoting function
cutoff_plot2 <- function(data,
                        x,
                        cutoff = 0,
                        cutoff_color = '#324B4A',
                        cutoff_other = NULL,
                        cutoff_other_color = '#95B1AF',
                        cutoff_other2 = NULL,
                        cutoff_other2_color = '#546085',
                        bins = 20) {

  library(magrittr)
  library(dplyr)
  library(ggplot2)

  x <- enquo(x)

  if (is.null(cutoff_other)) {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = '#246B69',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 20),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  } else if (is.null(cutoff_other2)) {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = '#246B69',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other,
                 color = cutoff_other_color,
                 linetype = 3,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 13),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  } else {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = 'black',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other,
                 color = cutoff_other_color,
                 linetype = 3,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other2,
                 color = cutoff_other2_color,
                 linetype = 4,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 13),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  }
}

# gt-theme-general
apply_tbl_theme <- function(table) {
  table %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_fill(color = "#246B69", alpha = .7)),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white")%>% 
  tab_options(table.align = "left")
}

#theme for value label tables
apply_labtab_theme <- function(table) {
  table %>% 
  cols_align(columns = everything(), align = "center") %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_fill(color = "#246B69", alpha = .7)),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white") %>% 
  tab_options(table.align = "left")
}
  
```
# CRediT author statement

**Schweer-Collins** conceptualization; software; validation; data curation (specifically checking code for data cleaning and codebook creation, managed data archival) project administration; supervision; funding acquisition; **Trevino** software; validation; data curation (specifically developing codebook, functions, and protocols, data cleaning, codebook creation; data archival); supervision; **Pedroza** software; data curation (specifically making functions used in codebook, data retrieval from Qualtrics; cleaning; codebook creation, visualization); **Zhang** software; validation; data curation (specifically making functions used in codebook, primary responsibility for data retrieval from Qualtrics; data cleaning, codebook creation, visualization)

# Overview

<MARIA>INSERT BRIEF INFO ON STUDY, SAMPLE, AND AIMS

*Additional info to possibly include: global missing data info, links to
supplemental materials, any disclaimers/info we think data users need to
know to use these data accurately*

<SHAINA>INSERT BRIEF DESCRIPTION OF DATA/CODEBOOK LAYOUT/FILE STRUCTURE
(can complete once we have more sections and overall structure)

### Missing Data

-   Truly missing = `NA` (blank in file or -99): The question should
    have been asked of the respondent, but for a reason other than those
    listed below, no answer was given or recorded.

    This -99 is also given in the case of a computed subscale or total
    score or other summary when the percentage of missing data is
    outside what is allowable for missing data rules

-   Not Applicable = -55: The subject was never asked a question for
    some reason (conditional question)

-   Don't Know = -66: The subject was unable to answer a question,
    either because he or she had no opinion or because the required
    information was not available (could not recall).

-   Refusal/No Answer = -77: The subject explicitly refused to answer a
    question or did not answer it when he or she should have.

-   No Match = -88: This situation arises when data are drawn from
    different sources (for example, a survey questionnaire and an
    administrative database), and information from one source cannot be
    located.

-   Processing Error = -44: For some reason, there is no answer to the
    question, although the subject provided one. This can result from
    interviewer error, incorrect coding, machine failure, or other
    problems

### Missing Data Rule

For summary or subscale scores that are computed with individual items,
any of the above reasons are included in computing the percent of
missing data. The following missing data rules are below and follow procedures used throughout the history of this longitudinal study.

-   For scales with [10 or more items]{.underline}, a composite score
    (average/total) is computed for each participant that have less than
    [20%]{.underline} of the items from that measure missing

-   For scales with [7 to 9 items]{.underline}, a composite score
    (average/total) is computed for each participant that have less than
    [30%]{.underline} of the items from that measure missing

-   For scales with [3 to 6 items]{.underline}, a composite score
    (average/total) is computed for each participant that have less than
    [33%]{.underline} of the items from that measure missing

-   For scales with [only 2 items]{.underline}, composite scores
    (average/total) are calculated on a [case by case basis]{.underline}



# Mental Health Measures

## Brief Symptom Inventory (BSI)

### BSI Description

The Brief Symptom Inventory (BSI) is designed to reflect psychological symptom patterns of psychiatric and medical patients. The BSI instrument is especially appropriate in clinical situations where debilitation results in reduced attention and endurance, in research with limited interview schedules, and in outpatient clinics where testing procedures demand brevity. The BSI instrument is also frequently used in measuring patient progress during treatment or in the assessment of treatment outcome.

*For the present study, 19 items from the BSI were collected in order to
calculate the **Somatization**, **Anxiety**, and **Depression** raw subscales.

  +**Somatization** reflects distress arising from perceptions of bodily dysfunction.
  +**Anxiety** reflects general signs such as nervousness and tension are included in the Anxiety dimension, as are panic attacks and feelings of terror.
  +**Depression** reflects symptoms of dysphoric mood and affect are represented as are lack of motivation and loss of interest in life.

*Item numbers in this data set may not match original item numbers from
the BSI. Please reference this guide to see match with original BSI (original BSI item number in *italics*): 01 = *01*, 02 = *02*, 03 = *07*, 04 = *09*, 05 = *12*, 06 = *16*, 07 = *17*, 08 = *18*, 09 = *19*, 10 = *23*, 11 = *29*, 12 = *30*, 13 = *33*, 14 = *35*, 15 = *37*, 16 = *38*, 17 = *45*, 18 = *49*, 19 = *50* 

*No items need to be reverse scored. 

***Higher** scores indicate **more** severe
psychological symptoms.

*The missing data rule was not applied since there are no missing data
among BSI variables.

Reference:
[@derogatis1983brief](https://www.cambridge.org/core/journals/psychological-medicine/article/abs/brief-symptom-inventory-an-introductory-report/307F805810B165ED58581E355F24329F);

### BSI Variables

#### Value Labels

All BSI variables have the same response options.

```{r BSI-label-table, results = 'asis'}

bsi_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("Not at all",
            "A little bit",
            "Moderately",
            "Quite a bit",
            "Very much")
) %>% 
  t() %>% 
  as.data.frame()

bsi_label_df <- setNames(bsi_label_df[-1, ], unlist(bsi_label_df[1, ]))


#create table
bsi_label_table <- bsi_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme()

# Print the table
print(bsi_label_table)


```

#### Survey Items

BSI survey items are presented in the following table:

**STEM**: *During the past week, how much were you bothered by...*

```{r BSI-var-prep}
# Pull question wording from Qualtrics data
bsi_word <- qualtrics %>% 
  select(starts_with("BSI")) %>% 
  slice(1)

#create table with variable name, description, and notes
bsi_word_long <- bsi_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         description = str_replace(description, "During the past week,", ""),
         description = str_replace(description, regex("how much were you bothered by", ignore_case = TRUE), ""),
         var_name = str_to_lower(var_name), 
          notes = case_when(var_name == "bsi4" ~ "This item was not asked for TC who were incarcerated while assessment were conducted",
                           TRUE ~ as.character(""))) %>% 
  slice(1:19)

```

```{r BSI-var-table, results ='asis'}
# Create the gt table object and apply generic theme
my_gt_table <- gt(bsi_word_long)

# Table-specific formatting (col width, names)
my_gt_table <- my_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(description ~ px(300),
             var_name ~ px(100)
             ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(my_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were constructed by summing included items.

```{r bsi alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
bsi_alpha <-
  complete %>%
  select(bsi1:bsi19) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_som <-
  complete %>%
  select(bsi2:bsi3,
         bsi10:bsi13,
         bsi15) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_anx <-
  complete %>%
  select(bsi1, bsi5, bsi9, bsi16:bsi18) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_dep <-
  complete %>%
  select(bsi4, bsi6:bsi8, bsi14, bsi19) %>%
  psych::alpha(check.keys = TRUE)

```

```{r BSI-scale-table, results = 'asis'}
# Create the table as a data frame
bsi_scale_df <- data.frame(
  var_name = c("bsi_total", "bsi_soma", "bsi_anx", "bsi_dep"),
  scale = c("Total Score (19)", "Somatization (7)", "Anxiety (6)", "Depression (6)"),
  scale_construction = c("`bsi1`, `bsi2`, `bsi3`, `bsi4`, `bsi5`, `bsi6`, `bsi7`, `bsi8`, `bsi9`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi14`, `bsi15`, `bsi16`, `bsi17`, `bsi18`, `bsi19`",
                           "`bsi2`, `bsi3`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi15`",
                           "`bsi1`, `bsi5`, `bsi9`, `bsi16`, `bsi17`, `bsi18`",
                           "`bsi4`, `bsi6`, `bsi7`, `bsi8`, `bsi14`, `bsi19`"),
  scale_range = c("0-76", "0-28", "0-24", "0-24"),
  alpha = c(round(bsi_alpha$total$raw_alpha, 3), 
            round(bsi_alpha_som$total$raw_alpha, 3), 
            round(bsi_alpha_anx$total$raw_alpha, 3), 
            round(bsi_alpha_dep$total$raw_alpha, 3))
)

# Create the gt table object
bsi_scale_table <- gt(bsi_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale_construction ~ pct(100)) %>% 
  apply_tbl_theme() 

# Print the table
print(bsi_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale raw score:

```{r bsi-mean-items}
# Create subset of BSI items
data_subset <- complete %>%
  select(bsi1:bsi19, bsi_total, bsi_soma, bsi_anx, bsi_dep)

# Calculate the summary statistics for each variable
summary_data <- lapply(data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_data <- as.data.frame(summary_data)

# Set items as first row
summary_data <- rbind(names(summary_data), summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
tbl <- summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ pct(100)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r bsi-distributions, class.source='fold', echo = FALSE}
p_bsi_total <- complete %>%
  composite_hist(x = bsi_total) 

p_bsi_soma <- complete %>%
  composite_hist(x = bsi_soma) 

p_bsi_anx <- complete %>%
  composite_hist(x = bsi_anx) 

p_bsi_dep <- complete %>%
  composite_hist(x = bsi_dep) 

ggarrange(p_bsi_total, p_bsi_soma + rremove("ylab"), 
          p_bsi_anx, p_bsi_dep + rremove("ylab")) %>%
  annotate_figure(top = text_grob( "Distribution for BSI Subscals \n(x-axis and y-axis are in different scales)"))
```

#### Clinical cutoff

TODO: Maria/Shaina, please confirm weather we need this section or not.

```{r bsi-clinical}
complete %>%
  cutoff_plot2(
    x = bsi_total,
    cutoff = 0
  ) +
  labs(title = 'Cutoff Value for BSI Measure')
```


## Center for Epidemiologic Studies Depression Scale (CES-D)

### CES-D Description

The Center for Epidemiological Studies – Depression Scale (CES-D) is a self-report measure with 20 items comprising six scales reflecting major dimensions of depression: depressed mood, feelings of guilt and worthlessness, feelings of helplessness and hopelessness, psychomotor retardation, loss of appetite, and sleep disturbance.

*All 20 items from the CES-D were collected and two subscales were
calculated: **positive affect** and **depressive symptoms**. Four items (`c4`, `c8`, `c12`, and `c16`) should be reverse scored which is noted in the variable table below and the reverse scored variables are provided
(`c4_r`, `c8_r`, `c12_r`, and `c16_r`). 

***Higher** scores indicate the presence of **more** depression symptoms.

*Four additional variables (`c21`-`c24`) were included in this section to
assess suicidality. Variables `c22` and `c23` are only applicable if
participants responded "Yes" to `c21`.

*The missing data rule was not applied since all participants had less
than 20% missing data. Missing data for each variable is presented in
the descriptive statistics table below.

Reference:
[@radloff1977ces](https://journals.sagepub.com/doi/abs/10.1177/014662167700100306);


-   Additional References:

    -   Cutoff Information:
        [@henry2018determining](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4);
        [DOI](https://doi.org/10.1016/j.jad.2018.02.071)

    -   Items for Potential Subscales:
        [@canady2009measurement](https://connect.springerpub.com/content/sgrjnm/17/2/91.abstract);
        [DOI](10.1891/1061-3749.17.2.91)

### CES-D Variables

#### Value Labels

All CES-D survey items (`c1`-`c20`) have the same response options.

```{r CESD-label-table, results = 'asis'}

cesd_label_df <- data.frame(
  value = c("0", "1", "2", "3"),
  label = c("Rarely or none of the time",
            "Some or a little of the time",
            "Occasionally or a moderate amount of time",
            "Most or all of the time")
) %>% 
  t() %>% 
  as.data.frame()

cesd_label_df <- setNames(cesd_label_df[-1, ], unlist(cesd_label_df[1, ]))


#create table
cesd_label_table <- cesd_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme()

# Print the table
print(cesd_label_table)


```

Additional variables on suicidality (`c21`-`c24`) share the same
response options.

```{r CESD-label-table2, results = 'asis'}

cesd2_label_df <- data.frame(
  value = c("0", "1"),
  label = c("No",
            "Yes")
) %>% 
  t() %>% 
  as.data.frame()

cesd2_label_df <- setNames(cesd2_label_df[-1, ], unlist(cesd2_label_df[1, ]))


#create table
cesd2_label_table <- cesd2_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme() 

# Print the table
print(cesd2_label_table)


```

#### Survey Items

All CES-D survey items are presented in the following table:

```{r CESD-var-prep}
# Pull question wording from qualtrics data
cesd_word <- qualtrics %>% 
  select(C1:C24) %>% 
  slice(1)

#create table with variable name, description, and notes
cesd_word_long <- cesd_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         #description = case_when(var_name == "c21" ~ "In the past 6 months, have you ever thought about killing yourself?"),
         notes = case_when(var_name == "c4" ~ "This item should be reverse scored. `c4_r` is reverse scored",
                           var_name == "c8" ~ "This item should be reverse scored. `c8_r` is reverse scored",
                           var_name == "c12" ~ "This item should be reverse scored. `c12_r` is reverse scored",
                           var_name == "c16" ~ "This item should be reverse scored. `c16_r` is reverse scored",
                           
                           var_name %in% c("c22", "c23") ~ "Skipped if answered No for `c21`. \nThis item was not asked for TC who were incarcerated while assessment were conducted",
                           var_name %in% c("c21","c24") ~ "This item was not asked for TC who were incarcerated while assessment were conducted",
                           TRUE ~ as.character(""))) %>%
  mutate(description = if_else(var_name == "c21", "In the past 6 months, have you ever thought about killing yourself?", description))
  

```

```{r CESD-var-table, results ='asis'}
# Create the gt table object and apply generic theme
cesd_gt_table <- gt(cesd_word_long)

# Table-specific formatting (col width, names)
cesd_gt_table <- cesd_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(250),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(cesd_gt_table)

```

#### Scale and Subscales

Information on the aggregated scale and subscale variables are below.
Total and subscale variables were constructed by summing corresponding
items.

```{r cesd-alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
#TODO: After Maria confirm if the items are right this one, Min will need edits either this one or cleanning script. 
cesd_alpha <-
  complete %>%
  select(c1:c3,c4_r,c5:c7,c8_r,c9:c11, c12_r,c13:c15,c16_r,c17:c20) %>%
  psych::alpha(check.keys = TRUE)

cesd_dep_alpha <- # I think this should include all scores? -- may need to edit cleaning script
  complete %>%
  select(c1:c3,c5:c6, c9:c11,c13:c15,c17:c20) %>%
  psych::alpha(check.keys = TRUE)

cesd_pos_aff_alpha <-
  complete %>%
  select(c4_r, c8_r, c12_r, c16_r) %>%
  psych::alpha(check.keys = TRUE)


cesd_alpha_table <- tibble(
  Scale = c('CESD', 'CESD - Depressive Symptoms',
            'CESD - Positive Affect'),
  Alpha = c(round(cesd_alpha$total$raw_alpha, 3),
            round(cesd_dep_alpha$total$raw_alpha, 3),
            round(cesd_pos_aff_alpha$total$raw_alpha, 3)
  )
)
```

```{r CESD-scale-table, results = 'asis'}
# Create the table as a data frame
# TODO: should the calculation use revers score?
#TODO: Total range should be changed since we change the scale starting from 1
cesd_scale_df <- data.frame(
  var_name = c("cesd_total", "cesd_dep_symp_total", "cesd_pos_aff_total"),
  scale = c("Total Score (20)", "Depression (16)", "Positive Affect (4)"),
  scale_construction = c("`c1`, `c2`, `c3`, `c4_r`, `c5`, `c6`, `c7`, `c8_r`, `c9`, `c10`, `c11`, `c12_r`, `c13`, `c14`, `c15`, `c16_r`, `c17`, `c18`, `c19`, `c20`",
                           "`c1`, `c2`, `c3`, `c5`, `c6`, 
                         #`c7`, 
                         `c9`, `c10`, `c11`, `c13`, `c14`, `c15`, `c17`, `c18`, `c19`, `c20`",
                           "`c4_r`, `c8_r`, `c12_r`, `c16_r`"),
  scale_range = c("0-80", "0-64", "0-16"),
  alpha = c(round(cesd_alpha$total$raw_alpha, 3), round(cesd_dep_alpha$total$raw_alpha, 3), round(cesd_pos_aff_alpha$total$raw_alpha, 3))
)

# Create the gt table object
cesd_scale_table <- gt(cesd_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale_construction ~ pct(100)) %>% 
  apply_tbl_theme()

# Print the table
print(cesd_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r cesd-mean-items}
# Create subset of CESD items
data_subset_cesd <- complete %>%
  select(c1:c24, cesd_total, cesd_dep_symp, cesd_pos_aff)

# Calculate the summary statistics for each variable
summary_data_cesd <- lapply(data_subset_cesd, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- sprintf("%.2f", round(sd(x, na.rm = TRUE), 2))
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_df_cesd <- as.data.frame(summary_data_cesd) %>% 
  rbind(names(summary_data_cesd)) %>% 
  t() %>% 
  as.data.frame() %>% 
  select(`5`, everything())

# Create the gt table
cesd_tbl <- summary_df_cesd %>%
  gt() %>%
  cols_label(`5` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(`5` ~ px(170)) %>%
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
cesd_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r cesd-distributions, class.source='fold', echo = FALSE}
p_cesd_total <- complete %>%
  composite_hist(cesd_total) +
  labs(
    title = 'CESD Total Score Distribution'
    )

p_cesd_dep_symp <- complete %>%
  composite_hist(
    cesd_dep_symp
    ) +
  labs(
    title = 'Depressive Symptoms Subscale Distribution'
    )

p_cesd_pos_aff <- complete %>%
  composite_hist(
    cesd_pos_aff,
    bins = 10
    ) +
  labs(
    title = 'Positive Affect Subscale Distribution'
    )

ggarrange(p_cesd_total, p_cesd_dep_symp + rremove("ylab"), 
          p_cesd_pos_aff) %>%
  annotate_figure(top = text_grob( "Distribution for CESD Subscals \n(x-axis and y-axis are in different scales)"))

```

#### Clinical Categories

The distribution for CES-D scores alongside clinical cutoffs are
presented below.

The clinical cutoff score of 16 or above is generally accepted (MARIA add cite); however a cutoff score of 23 or above has been found to be more valid in samples of [insert; MARIA add cite]

Reference:
[@henry2018determining](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4);
[DOI](https://doi.org/10.1016/j.jad.2018.02.071)

```{r cesd-clinical}
complete %>%
  cutoff_plot2(
    x = cesd_total,
    cutoff = 16,
    cutoff_other = 23
  ) +
  labs(
    title = 'Cutoff Scores for CESD Total Scores',
    caption = 'Cutoffs are 16 and/or 23\nSee references for literature on cutoff scores.', 
    y = "Number of Participants"
  ) +
  geom_text(aes(x = 16, y = 16.5, label = "cutoff1", vjust = -.25, hjust = 1.2)) + ###MARIA INSERT CUTOFF LABEL
  geom_text(aes(x = 16, y = 16.5, label = "cutoff2", vjust = -.25, hjust = -1.8))  ##MARIA INSERT CUTOFF LABEL
```



## Coronavirus Impacts Questionnaire (CIQ)

### CIQ Description

The CIQ is self-report survey used to assess the financial, resource,
and psychological impacts of the COVID-19 pandemic.

*For the present study, 3 items from the CIQ were collected in order to
construct the psychological impacts scale. We made this decision because data collection launched in the COVID-19 pandemic, whereas prior waves occurred before the onset of the COVID-19 pandemic.

*`ciq1` need to be reverse scored. 

***Higher**scores indicate **greater** psychological impacts of COVID-19.

*The missing data rule was not applied since there is no missing data
among CIQ variables.

Reference: [@conway2020social](https://psyarxiv.com/z2x9a/)

### CIQ Variables

#### Value Labels

All CIQ variables have the same response options.

```{r ciq-label-table, results = 'asis'}

ciq_label_df <- data.frame(
  value = seq(1:7),
  label = c("Not true of me at all",
            "2",
            "3",
            "4",
            "5",
            "6",
            "Very true of me")) %>% 
  t() %>% 
  as.data.frame()

ciq_label_df <- setNames(ciq_label_df[-1, ], unlist(ciq_label_df[1, ]))


#create table
ciq_label_table <- ciq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme()

# Print the table
print(ciq_label_table)


```

#### Survey Items

All CIQ survey items are presented in the following table:

```{r ciq-var-prep}
# Pull question wording from qualtrics data
# ciq is from BIS question 20-22
# TODO: Check range of possible values 
ciq_word <- qualtrics %>% 
  select(starts_with("BSI")) %>% 
  slice(1)

#create table with variable name, description, and notes
ciq_word_long <- ciq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name),
         notes = case_when(var_name == "bsi22" ~ "This item should be reverse scored. `ciq3_r` is reverse scored",
                           TRUE ~ as.character("")
                           )) %>% 
  mutate(description = if_else(var_name == "bsi20", "I have become depressed because of the Coronavirus (COVID-19).", description)) %>%
  mutate(var_name = case_when(var_name == "bsi20" ~ "ciq1",
                              var_name == "bsi21" ~ "ciq2",
                              var_name == "bsi22" ~ "ciq3",
                              TRUE ~ var_name)) %>% 
  slice(20:22)

```

```{r ciq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
ciq_gt_table <- gt(ciq_word_long)

# Table-specific formatting (col width, names)
ciq_gt_table <- ciq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
   tab_options(table.width = pct(100))%>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(ciq_gt_table)

#WHEN RENDERING WITH PDF USE: 
#ciq_gt_table
```

#### Scale and Subscales

Information on the the subscale and associated variables are below.
The subscale was constructed by averaging the included items.

```{r ciq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
ciq_alpha <-
  complete %>%
  select(ciq1,ciq2,ciq3_r) %>%
  psych::alpha(check.keys = TRUE)

```

```{r ciq-scale-table, results = 'asis'}
# Create the table as a data frame
ciq_scale_df <- data.frame(
  var_name = c("ciq_psych_total"),
  scale = c("Total Score (3)"),
  scale_construction = c("`ciq1`, `ciq2`, `ciq3_r`"),
  scale_range = c("3-21"),
  alpha = c(round(ciq_alpha$total$raw_alpha, 3))
)

# Create the gt table object
ciq_scale_table <- gt(ciq_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(var_name ~ pct(25),
             scale ~ pct(25),
             scale_construction ~ pct(25)
             ) %>% 
   tab_options(table.width = pct(100))%>%
  apply_tbl_theme() 

# Print the table
print(ciq_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and the psychological impacts subscale:

```{r ciq-mean-items}
# subset items
ciq_data_subset <- complete %>%
  select(ciq1:ciq2, ciq3, ciq_psych_total)

# Calculate the summary statistics for each variable
ciq_summary_data <- lapply(ciq_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
ciq_summary_data <- as.data.frame(ciq_summary_data)

# Set items as first row
ciq_summary_data <- rbind(names(ciq_summary_data), ciq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
ciq_tbl <- ciq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ pct(100)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
ciq_tbl

```

#### Distributions

The distribution for the total score is presented below:

```{r csi-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(
    x = ciq_psych_total,
    bins = 10
    ) +
  labs(title = 'Distribution for CIQ Psychological Scale')
```


## The Drug Abuse Screening Test (DAST)

### DAST Description

<MIN/SHAINA>TODO: ROW DATA INCORRECTLY CLEANED, WILL NEED RE_CLEAN!

<SHAINA> TODO: CHECK AFTER DATA IS CLEANED

The DAST is a self-report instrument used to assess problems related to
substance use.

For the present study, 22 items from the DAST were collected and a total
score was constructed. No subscales were created for this measure as
there was a lack of evidence supporting a subscale structure.

Two items (`d4` and `d5`) should to be reverse scored which is noted in
the variable table below and the reverse scored variables are provided
(`d4_r` and `d5_r`). Higher scores indicate more problems related to
substance use.

<TODO: Maria please check if you like this sentences here> 
TC who are incarcerated while assessment was done weren't asked for this survey. 

<SHAINA> TODO: CONFIRM THIS IS CORRECT AND IF SHOULD BE APPLIED IN
TABLES BELOW - specify -77 The missing data rule was applied.
Calculations were completed only with participants that had less than
20% missing data (this includes `-77` responses)

Reference:
[@gavin1989diagnostic](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1360-0443.1989.tb03463.x);[DOI](https://doi.org/10.1111/j.1360-0443.1989.tb03463.x)

### DAST Variables

#### Value Labels

All The Drug Abuse Screening Test variables have the same response
options.

```{r DAST-label-table, results = 'asis'}

dast_label_df <- data.frame(
  value = c(1,0),
  label = c("Yes",
            "No")) %>% 
  t() %>% 
  as.data.frame()

dast_label_df <- setNames(dast_label_df[-1, ], unlist(dast_label_df[1, ]))


#create table
dast_label_table <- dast_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(dast_label_table)


```

<MARIA> TODO: CONFIRM THIS TABLE SHOULD BE INCLUDED AND WHAT VARIABLES
THEY APPLY TO Re-coded total value label `dast_total_r`

```{r DAST-label-table-total, results = 'asis'}
dast_label_total <- data.frame(
  value = seq(0,4),
  label = c("None",
            "Low",
            "Intermediate (likely meets DSM criteria)",
            "Substantial",
            "Severe")) %>% 
  t() %>% 
  as.data.frame()

dast_label_total <- setNames(dast_label_total[-1, ], unlist(dast_label_total[1, ]))


#create table
dast_label_table_total <- dast_label_total %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(c(1:5) ~ px(151)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(dast_label_table_total)


```

#### Survey Items

All DAST survey items are presented in the following table:

This questionnaire deals with certain drug use and social behavior patterns. Please answer each of the items truthfully by stating Yes or No to me, thinking about the past 6 months.

```{r DAST-var-prep}
# Pull question wording from qualtrics data
dast_word <- qualtrics %>% 
  select(starts_with("D")) %>% 
  rename(dast_screen = D00) %>%
  slice(1)

#create table with variable name, description, and notes
dast_word_long <- dast_word %>% 
  select(-D2A) %>%
  rename(d2 = D2B) %>%
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         description = case_when(var_name == "d2" ~ "Have you misused prescription drugs in the last 6 months?",
                                 TRUE ~ description),
         var_name = str_to_lower(var_name),
         notes = case_when(var_name == "d4" ~ "This item should be reverse scored. `d4_r` is reverse scored",
                           var_name == "d5" ~ "This item should be reverse scored. `d4_r` is reverse scored",
                           TRUE ~ as.character("")
                           )
         ) %>% 
  mutate(description = if_else(var_name == "dast_screen", "Is TC currently pregnant?", description)) %>%
  slice(4:25)

```

```{r dast-var-table, results ='asis'}
# Create the gt table object and apply generic theme
dast_gt_table <- gt(dast_word_long)

# Table-specific formatting (col width, names)
dast_gt_table <- dast_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())
 

# Print the table
print(dast_gt_table)

#WHEN RENDERING WITH PDF USE: 
#dast_gt_table
```

#### Scale and Subscales

Information on the total score is below. The total score was constructed
by summing all items.

```{r dast alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
dast_alpha <-
  complete %>%
  select(d1a:d3, d6:d5_r) %>%
  mutate(d2 = coalesce(d2a, d2b)) %>% 
  select(-d2a, -d2b) %>% 
  drop_na(d2) %>% 
  psych::alpha(check.keys = TRUE)

```

<MIN> DATA CLEANING TODO: need check the total

```{r DAST-scale-table, results = 'asis'}
# Create the table as a data frame
dast_scale_df <- data.frame(
  var_name = c("dast_total"),
  scale = c("Total Score (20)"),
  scale_construction = c(" `d1a`, `d2`, `d3`, `d4_r`, `d5_r`, `d6`, `d7`, `d8`, `d9`, `d10`, `d11`, `d12`, `d13`, `d14`, `d15`, `d16`, `d17`, `d18`, `d19`, `d20`"),
  scale_range = c("0-20"),
  alpha = c(round(dast_alpha$total$raw_alpha, 3))
)

# Create the gt table object
dast_scale_table <- gt(dast_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(150),
             scale_construction ~ pct(50)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme() 

# Print the table
print(dast_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and the total
score.

For binary items:

```{r dast-binary-desc}
# Create subset of DAST items
dast_data_subset_binary <- complete %>%
  select(d1a:d20)

# Calculate the dichotomous summary statistics for each variable
dast_summary_data_binary <- lapply(dast_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dast_summary_data_binary <- as.data.frame(dast_summary_data_binary)

# Set items as first row
dast_summary_data_binary <- rbind(names(dast_summary_data_binary), dast_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dast_tbl_binary <- dast_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "No", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Yes", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
dast_tbl_binary


```

For the total score:

```{r dast-cont-desc}
# Create subset of DAST items
dast_data_subset <- complete %>%
  select(dast_total)

# Calculate the dichotomous summary statistics for each variable
dast_summary_data <- lapply(dast_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dast_summary_data <- as.data.frame(dast_summary_data) 

# Set items as first row
dast_summary_data <- rbind(names(dast_summary_data),dast_summary_data) %>% 
  t() %>% 
  as.data.frame() %>%
  mutate(Mean = if_else(Mean == "NaN", "NA", Mean)) %>%
  mutate(Range = if_else(Range == "Inf--Inf", "NA", Range))

 



# Create the gt table
dast_tbl <- dast_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
dast_tbl

```

#### Distributions

The distribution for the total score is presented below:

<#TODO: Maria, should I use reversed total score for this distributions?>
```{r}
complete %>%
  composite_hist(dast_total) +
  labs(
    title = 'DAST Total Score Distribution'
    )
```

#### Clinical Categories

The distribution for the total score alongside clinical severity
categories are presented below.

<MARIA>INSERT MORE INFO ON SEVERITY CUTOFF SCORES - what do they
categorize?, how should they be used

Reference: <SHAINA/MARIA> INSERT REFERENCE FOR DAST SCORES - MARIA, WHAT
IS REFERENCE?

```{r dast-distributions, class.source='fold', echo = FALSE}
complete %>%
  severity_plot(
  x = dast_total,
  bins = 20,
  low_xmin = 0,
  low_xmax = 5.5,
  medium_xmin = 5.5,
  medium_xmax = 10.5,
  large_xmin = 10.5,
  large_xmax = 15.5,
  critical_xmin = 15.5,
  critical_xmax = 20) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 3,
    y = -1.5,
    label = 'Low'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 8,
    y = -1.5,
    label = 'Intermediate'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 13,
    y = -1.5,
    label = 'Substantial'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 18,
    y = -1.5,
    label = 'Severe'
  ) +
  labs(
    title = 'Severity Categories',
    subtitle = 'Based on DAST',
    caption = 'Cutoffs are:\nLow = 1-5,\nIntermediate = 6-10,\nSubstantial = 11-15,\nSevere = 16-20',
    y = 'Number of Participants'
  )
```




## Conflict Tactics Scales (CTS)

### CTS Description

The CTS is a self-report measure used to assess tactics used when there
is conflict in a relationship.

For the present study, all 20 items from the CTS short form were
collected, and all scales (Negotiation, Physical Assault, and
Psychological Aggression) and supplemental scales (Assault and Sexual
Coercion) were calculated.

Authors describe that internal reliability is not appropriate for the
CTS measure. CTS should not have a calculated total/average composite
score. Instead, CTS has three different ways of scoring (Prevalence,
Severity, Mutuality).

No items need to be reverse scored. <MARIA> TODO: How to word
directionality with current values/labels. (e.g., Higher scores indicate
..."

<SHAINA> TODO: CONFIRM & CHECK CALC CODE The missing data rule was
applied. Calculations were completed only with participants that had
less than 20% missing data (this includes `-77` responses)

Reference:
[@straus2004short](https://connect.springerpub.com/content/sgrvv/19/5/507.abstract);
[DOI](10.1891/vivi.19.5.507.63686)

### CTS Variables

#### Value Labels

All CTS variables have the same response options.

```{r CTS-label-table, results = 'asis'}

CTS_label_df <- data.frame(
  value = c( "1", "2", "3", "4", "5", "6", "7", "8"),
  label = c("This has never happened",
            "Once in the past year",
            "Twice in the past year",
            "3-5 times in the past year",
            "6-10 times in the past year",
            "11-20 times in the past year",
            "More than 20 times in the past year", 
            "Not in the past year, but it did happen before"
            )
) %>% 
  t() %>% 
  as.data.frame()

CTS_label_df <- setNames(CTS_label_df[-1, ], unlist(CTS_label_df[1, ]))


#create table
CTS_label_table <- CTS_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(100)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(CTS_label_table)


```

#### Survey Items

All CTS survey items are presented in the following table:
Incarcerated TC weren't administered for this survey

```{r CTS-var-prep}
# Pull question wording from Qualtrics data
CTS_word <- qualtrics %>% 
  select(starts_with("CT"), -CT0, -CT000) %>% 
  slice(1)

#create table with variable name, description, and notes
CTS_word_long <- CTS_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  mutate(notes = if_else(var_name == "cts screen", "If TC answered No for this question the rest of survey will be skipped", notes),
    description = if_else(var_name == "ct0", "Have you lived with any other children, under the age of 17, since the time of your last interview? Only think about children who you or your partner was responsible for parenting. Please do not include any children listed in the other sections or children that you have reported before.", 
                               if_else(var_name == "ct000", "How many new children are you parenting since your last interview on (last interview date)?",
                                       if_else(var_name ==  "cts screen", "Have you been in a (romantic) relationship in the past year?",
                                               if_else(var_name == "cts parent screen", "Have you parented a child (under 18) in the past year?", description))))
  ) %>%
  slice(1:26)

```

Incarcerated TC weren't administered for this survey

Please indicate how many times you did each of these things in the past year, and how many times you partner did them in the past year. 

```{r CTS-var-table, results ='asis'}
# Create the gt table object and apply generic theme
my_gt_table <- gt(CTS_word_long)

# Table-specific formatting (col width, names)
my_gt_table <- my_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(my_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on total score and subscale variables are below. Prevalence
scales are calculated ... <MARIA> INSERT INFO ON COMPOSITE SCORE
CREATION. Severity scores are calculated ... <MARIA> INSERT INFO ON
COMPOSITE SCORE CREATION. Mutuatlity scores are created by ... <MARIA>
INSERT INFO ON COMPOSITE SCORE CREATION

<SHAINA/MIN> TODO: NEED fill Range once we understand how composite
scores were created

```{r CTS-scale-table, results = 'asis'}
# Create the table as a data frame
CTS_scale_df <- data.frame(
  var_name = c("cts_psy_agg_ind_sev", "cts_injury_ind_sev", "cts_assault_ind_sev",   "cts_sex_ind_sev",       #TC   severity 
                "cts_psy_agg_part_sev","cts_injury_part_sev", "cts_assault_part_sev","cts_sex_part_sev",      #Partner severity 

                "cts_psy_agg_ind_prev", "cts_injury_ind_prev", "cts_assault_ind_prev", "cts_sex_ind_prev", 
                "cts_psy_agg_part_prev", "cts_injury_part_prev", "cts_assault_part_prev", "cts_sex_part_prev",
               
                "cts_psy_agg_mutual", "cts_injury_mutual", "cts_assault_mutual", "cts_sex_mutual",
               
                "cts_negotiate_ind",    "cts_negotiate_part"),

  scale = c("TC Psychological Aggression (2)", "TC Physical Injury (2)", "TC Assault (2)", "TC Sexual Cohesion (2)",
            "Partner Psychological Aggression (2)", "Partner Physical Injury (2)", "Partner Assault (2)", "Partner Sexual Cohesion (2)",

            "TC Psychological Aggression (2)", "TC Physical Injury (2)", "TC Assault (2)", "TC Sexual Cohesion (2)",
            "Partner Psychological Aggression (2)", "Partner Physical Injury (2)", "Partner Assault (2)", "Partner Sexual Cohesion (2)",
            
            "Psychological Aggression (4)", "Physical Injury (4)", "Assaul (4)t", "Sexual Cohesion (4)",
            
            "TC Negotiation (2)", "Partner Negotiation (2)"
            ),
  score_method = c("Severity", "Severity", "Severity", "Severity",
                   "Severity", "Severity", "Severity", "Severity",
                   "Prevalence", "Prevalence", "Prevalence", "Prevalence", 
                   "Prevalence", "Prevalence", "Prevalence", "Prevalence", 
                   "Mutuality", "Mutuality", "Mutuality", "Mutuality",
                   "", ""
                   ),

  scale_construction = c("`ct3`, `ct13`", "`ct5`, `ct15`", "`ct9`, `ct11`", "`ct17`, `ct19`", 
                         "`ct4`, `ct14`", "`ct6`, `ct16`", "`ct10`, `ct12`", "`ct18`, `ct20`", 
                         
                         "`ct3`, `ct13`", "`ct5`, `ct15`", "`ct9`, `ct11`", "`ct17`, `ct19`", 
                         "`ct4`, `ct14`", "`ct6`, `ct16`", "`ct10`, `ct12`", "`ct18`, `ct20`",
                         
                         "`ct3`, `ct13`, `ct4`, `ct14`","`ct5`, `ct15`, `ct6`, `ct16`",
                         "`ct9`, `ct11`, `ct10`, `ct12`", "`ct17`, `ct19`, `ct18`, `ct20`",
                         
                         "`ct1`, `ct7`", "`ct2`, `ct8`"
                         
                         ),
  scale_range = c("", "", "", "", "", "", "", "", "", "",
                  "", "", "", "", "", "", "", "", "", "", 
                  "", "")
  )


# Create the gt table object
CTS_scale_table <- gt(CTS_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            score_method = "Score Method",
            scale_construction = "Scale Construction",
            scale_range = "Range*") %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale ~ px(200)) %>% 
  apply_tbl_theme() 

# Print the table
print(CTS_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and subscale
score:

```{r CTS-mean-items}
# Create subset of CTS items
cts_data_subset <- complete %>%
  select(ct1:ct20, starts_with("cts"))

# Calculate the summary statistics for each variable
cts_summary_data <- lapply(cts_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert cts2_summary_data to a data frame
cts_summary_data <- as.data.frame(cts_summary_data)

# Set items as first row
cts_summary_data <- rbind(names(cts_summary_data), cts_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
cts_tbl <- cts_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(`1` ~ pct(27)) %>%
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
    fmt_missing(
        columns = c("Mean","SD","Range", "Missing")
        # missing_text = "missing"
  )%>%
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

   
# Render the table
cts_tbl

```

#### Distributions

Distributions are presented below for each subscale
<Maria> I'd like your input on how to abbriviate the x axix and title. 

##### Severity distributions

```{r CTS-Severity-TC-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
p_cts_psy_agg_ind_sev <- complete %>%
  mutate(
    cts_psy_agg_ind_sev = case_when(
      cts_psy_agg_ind_sev == 0 ~ 'No Psychological Aggression',  #TODO: <Maria> Can I short this to No Psy. Aggre. etc... 
      cts_psy_agg_ind_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_ind_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_ind_sev = as.factor(cts_psy_agg_ind_sev),
    cts_psy_agg_ind_sev = relevel(cts_psy_agg_ind_sev, 'No Psychological Aggression')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10),guide = guide_axis(n.dodge=3)) +
  labs(title = 'Individual (TC) Psychological Aggression Severity',
       y = "Number of Participants") + 
  THEME


# Psychical Injury 
p_cts_injury_ind_sev <- complete %>%
  mutate(
    cts_injury_ind_sev = case_when(
      cts_injury_ind_sev == 0 ~ 'No Injury',
      cts_injury_ind_sev == 1 ~ 'Minor Injury',
      cts_injury_ind_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_ind_sev = as.factor(cts_injury_ind_sev),
    cts_injury_ind_sev = relevel(cts_injury_ind_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Individual (TC) Physical Injury Severity',
       y = "Number of Participants") + 
  THEME

# Assault 
p_cts_assault_ind_sev <- complete %>%
  mutate(
    cts_assault_ind_sev = case_when(
      cts_assault_ind_sev == 0 ~ 'No Assault',
      cts_assault_ind_sev == 1 ~ 'Minor Assault',
      cts_assault_ind_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_ind_sev = as.factor(cts_assault_ind_sev),
    cts_assault_ind_sev = relevel(cts_assault_ind_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Individual (TC) Assault Severity',
       y = 'Number of Participants') +
  THEME

# Sexual Cohesion
p_cts_sex_ind_sev <- complete %>%
  mutate(
    cts_sex_ind_sev = case_when(
      cts_sex_ind_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_ind_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_ind_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_ind_sev = as.factor(cts_sex_ind_sev),
    cts_sex_ind_sev = relevel(cts_sex_ind_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Individual (TC) Sexual Cohesion Severity',
       y = "Number of Participants") + 
  THEME

#TODO: <Min FIX the x axis overlap>
ggarrange(p_cts_psy_agg_ind_sev, p_cts_injury_ind_sev + rremove("ylab"), 
          p_cts_assault_ind_sev, p_cts_sex_ind_sev + rremove("ylab")) %>%
  annotate_figure(top = text_grob( "Distribution for CTS Individual (TC) Serverity \n(x-axis and y-axis are in different scales)"))
```



```{r CTS-Severity-Partner-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
p_cts_psy_agg_part_sev <- complete %>%
  mutate(
    cts_psy_agg_part_sev = case_when(
      cts_psy_agg_part_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_part_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_part_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_part_sev = as.factor(cts_psy_agg_part_sev),
    cts_psy_agg_part_sev = relevel(cts_psy_agg_part_sev, 'No Psychological Aggression')
    ) %>%
  ggplot(
    aes(
      cts_psy_agg_part_sev
    )
  ) +
  bar_style +
   scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Partner Psychological Aggression Severity',
       y = "Number of Participants") + 
  THEME +
  theme(axis.text.x = element_text(angle = -45))

# Physical Injury
p_cts_injury_part_sev <- complete %>%
  mutate(
    cts_injury_part_sev = case_when(
      cts_injury_part_sev == 0 ~ 'No Injury',
      cts_injury_part_sev == 1 ~ 'Minor Injury',
      cts_injury_part_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_part_sev = as.factor(cts_injury_part_sev),
    cts_injury_part_sev = relevel(cts_injury_part_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_part_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Partner Physical Injury Severity',
       y = "Number of Participants") + 
  THEME


# Assault
p_cts_assault_part_sev <- complete %>%
  mutate(
    cts_assault_part_sev = case_when(
      cts_assault_part_sev == 0 ~ 'No Assault',
      cts_assault_part_sev == 1 ~ 'Minor Assault',
      cts_assault_part_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_part_sev = as.factor(cts_assault_part_sev),
    cts_assault_part_sev = relevel(cts_assault_part_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_part_sev
    )
  ) +
  bar_style +
    scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Partner Assault Severity',
       y = "Number of Participants") + 
  THEME

# Sexual Cohesion
p_cts_sex_part_sev <- complete %>%
  mutate(
    cts_sex_part_sev = case_when(
      cts_sex_part_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_part_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_part_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_part_sev = as.factor(cts_sex_part_sev),
    cts_sex_part_sev = relevel(cts_sex_part_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_part_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Partner Sexual Cohesion Severity',
       y = "Number of Participants") + 
  THEME

# TODO: Min fix x axis overlap 
ggarrange(p_cts_psy_agg_part_sev, p_cts_injury_part_sev + rremove("ylab"), 
          p_cts_assault_part_sev, p_cts_sex_part_sev + rremove("ylab")) %>%
  annotate_figure(top = text_grob( "Distribution for CTS Partner Serverity \n(x-axis and y-axis are in different scales)"))
```

##### Prevalence distributions

<MIN> TODO NA was removed when generating following Prevalence plot
MZ note: I think NA was removed when colculate the prevalence score. 

```{r CTS-Prevalence-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
p_cts_psy_agg_pre <- complete %>%
  pivot_longer(
    cols = c(cts_psy_agg_ind_prev, cts_psy_agg_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_psy_agg_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_psy_agg_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Psychological Aggression Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Physical Injury
p_cts_inj_pre <- complete %>%
  pivot_longer(
    cols = c(cts_injury_ind_prev, cts_injury_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_injury_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_injury_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Physical Injury Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Assault
p_cts_ass_pre <- complete %>%
  pivot_longer(
    cols = c(cts_assault_ind_prev, cts_assault_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_assault_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_assault_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Assault Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Sexual Cohesion
p_cts_sex_pre <- complete %>%
  pivot_longer(
    cols = c(cts_sex_ind_prev, cts_sex_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_sex_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_sex_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Sexual Cohesion Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

ggarrange(p_cts_psy_agg_pre + rremove("legend"), p_cts_inj_pre + rremove("ylab"), 
          p_cts_ass_pre + rremove("legend"), p_cts_sex_pre + rremove("ylab")) %>%
  annotate_figure(top = text_grob( "Distribution for CTS Prevalence \n(x-axis and y-axis are in different scales)"))
```



##### Mutuality distributions

```{r CTS-Mutuality-distributions, class.source='fold', echo = FALSE}

# Psychological Aggression 
p_cts_psy_mut <- complete %>%
  mutate(
    cts_psy_agg_mutual = case_when(
      cts_psy_agg_mutual == 0 ~ 'Neither',
      cts_psy_agg_mutual == 1 ~ 'Male',
      cts_psy_agg_mutual == 2 ~ 'Female',
      cts_psy_agg_mutual == 3 ~ 'Both'
    ),
    cts_psy_agg_mutual = as.factor(cts_psy_agg_mutual),
    cts_psy_agg_mutual = relevel(cts_psy_agg_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_mutual
    )
  ) +
  bar_style +
  labs(title = 'Mutual Psychological Aggression',
       y = "Number of Participants") +
  THEME



# Physical Injury
p_cts_ing_mut <- complete %>%
  mutate(
    cts_injury_mutual = case_when(
      cts_injury_mutual == 0 ~ 'Neither',
      cts_injury_mutual == 1 ~ 'Male',
      cts_injury_mutual == 2 ~ 'Female',
      cts_injury_mutual == 3 ~ 'Both'
    ),
    cts_injury_mutual = as.factor(cts_injury_mutual),
    cts_injury_mutual = relevel(cts_injury_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_injury_mutual
    )
  ) +
  bar_style +
  labs(title = 'Mutual Physical Injury',
       y = "Number of Participants") +
  THEME


# Assault
p_cts_ass_mut <- complete %>%
  mutate(
    cts_assault_mutual = case_when(
      cts_assault_mutual == 0 ~ 'Neither',
      cts_assault_mutual == 1 ~ 'Male',
      cts_assault_mutual == 2 ~ 'Female',
      cts_assault_mutual == 3 ~ 'Both'
    ),
    cts_assault_mutual = as.factor(cts_assault_mutual),
    cts_assault_mutual = relevel(cts_assault_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_assault_mutual
    )
  ) +
  bar_style +
  labs(title = 'Mutual Assault',
       y = "Number of Participants") +
  THEME

# Sexual Cohesion
p_cts_sex_mut <- complete %>%
  mutate(
    cts_sex_mutual = case_when(
      cts_sex_mutual == 0 ~ 'Neither',
      cts_sex_mutual == 1 ~ 'Male',
      cts_sex_mutual == 2 ~ 'Female',
      cts_sex_mutual == 3 ~ 'Both'
    ),
    cts_sex_mutual = as.factor(cts_sex_mutual),
    cts_sex_mutual = relevel(cts_sex_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_sex_mutual
    )
  ) +
  bar_style +
  labs(title = 'Mutual Sexual Cohesion',
       y = "Number of Participants") +
  THEME

ggarrange(p_cts_psy_mut, p_cts_ing_mut + rremove("ylab"), 
          p_cts_ass_mut, p_cts_sex_mut + rremove("ylab")) %>%
  annotate_figure(top = text_grob( "Distribution for CTS Mutual Subscale \n(x-axis and y-axis are in different scales)"))
```


##### Negotiation distributions

```{r CTS-Negotiation-distributions, class.source='fold', echo = FALSE}
p_cts_neg <- complete %>% 
  composite_hist(
    cts_negotiate_ind,
    bins = 10
  ) +
  labs(title = 'Individual (TC) Negotiation Subscale',
       #subtitle = 'Individual (TC)'
       )

p_cts_part <- complete %>% 
  composite_hist(
    cts_negotiate_part,
    bins = 10
  ) +
  labs(title = 'Partner Negotiation Subscale',
      # subtitle = 'Partner'
       )

ggarrange(p_cts_neg, p_cts_part + rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for CTS Negotiation Subscale \n(x-axis and y-axis are in different scales)"))
```




## Brief Child Abuse Potential Inventory (BCAP)

### BCAP Description

The BCAP is a self-report inventory used to assess parental child abuse
risk.

For the present study, <SHAINA> CONFIRM 34 items from the BCAP were
collected and <SHAINA/MARIA> CONFIRM all 9 subscales were computed:
Happiness, Feelings of Persecution, Loneliness, Family Conflict,
Rigidity, Distress, Financial Insecurity, Lie, and Random Responding.

Four items (`q1`, `q2`, `q23`, and `q29`) should be reverse scored which
is noted in the variable table below and the reverse scored variables
are provided (`q1_r`, `q2_r`, `q23_r`, and `q29_r`). Higher scores on
the BCAP indicates increased risk.

<SHAINA> CONFIRM\> The missing data rule was applied. Calculations were
completed only with participants that had less than 20% missing data
(this includes `-77` responses).

Reference:
[@ondersma2005brief](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug);
[DOI](https://doi.org/10.1207/s15374424jccp3402_9)

### BCAP Variables

#### Value Labels

All BCAP variables have the same response options.

```{r BCAP-label-table, results = 'asis'}

bcap_label_df <- data.frame(
  value = c("0", "1"),
  label = c("Disagree",
            "Agree")
) %>% 
  t() %>% 
  as.data.frame()

bcap_label_df <- setNames(bcap_label_df[-1, ], unlist(bcap_label_df[1, ]))


#create table
bcap_label_table <- bcap_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(bcap_label_table)


```

#### Survey Items

All BCAP survey items are presented in the following table:

```{r bcap-var-prep}
# Pull question wording from qualtrics data
bcap_word <- qualtrics %>% 
  select(starts_with("q")) %>% 
  slice(1)

#create table with variable name, description, and notes
bcap_word_long <- bcap_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = case_when(var_name == "q1" ~ "This item should be reverse scored. `q1_r` is reverse scored",
                           var_name == "q2" ~ "This item should be reverse scored. `q2_r` is reverse scored",
                           var_name == "q23" ~ "This item should be reverse scored. `q23_r` is reverse scored",
                           var_name == "q29" ~ "This item should be reverse scored. `q29_r` is reverse scored",
                           
                           var_name %in% c("c22", "c23") ~ "Skipped if `c21` = No",
                           TRUE ~ as.character(""))) %>%
  slice(1:34)


```

```{r bcap-var-table, results ='asis'}
# Create the gt table object and apply generic theme
bcap_gt_table <- gt(bcap_word_long)

# Table-specific formatting (col width, names)
bcap_gt_table <- bcap_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(250),
             var_name ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  #tab_options(table.width = pct(100))%>%
  #cols_width(var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(bcap_gt_table)

#WHEN RENDERING WITH PDF USE: 
#bcap_gt_table
```

#### Scale and Subscales

Information on the total score and subscale variables are below.
<SHAINA/MARIA> INSERT Variables were constructed by ...

```{r bcap alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
# Total
bcap_alpha <- 
  complete %>% 
  select(
    q1_r,
    q2_r,
    q3:q22,
    q23_r,
    q24:q28,
    q29_r,
    q30:q34
  ) %>% 
  psych::alpha(check.keys = TRUE)

bcap_risk_alpha <-
  complete %>%
  select(
    q1_r,
    q3,
    q5:q8,
    q10:q14,
    q16:q17,
    q19:q20,
    q22,
    q23_r,
    q24:q25,
    q27,
    q29_r,
    q30:q33
    ) %>%
  psych::alpha(check.keys = TRUE)

bcap_happy_alpha <- 
  complete %>% 
  select(q1_r, q23_r, q29_r) %>% 
  psych::alpha(check.keys = TRUE)

bcap_feel_pers_alpha <- 
  complete %>% 
  select(q3, q25, q33) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lonely_alpha <- 
  complete %>% 
  select(q5, q12, q22, q31) %>% 
  psych::alpha(check.keys = TRUE)

bcap_fam_conf_alpha <- 
  complete %>% 
  select(q6, q13, q17) %>% 
  psych::alpha(check.keys = TRUE)

bcap_rigid_alpha <-
  complete %>% 
  select(q7, q14, q20, q32) %>% 
  psych::alpha(check.keys = TRUE)

bcap_distress_alpha <- 
  complete %>% 
  select(q8, q11, q16, q19, q27) %>% 
  psych::alpha(check.keys = TRUE)

bcap_poverty_alpha <- 
  complete %>% 
  select(q10, q30) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lie_alpha <-
  complete %>% 
  select(q4, q9, q15, q21, q26, q34) %>% 
  psych::alpha(check.keys = TRUE)

bcap_random_alpha <-
  complete %>% 
  select(q2_r, q19, q28) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r bcap-scale-table, results = 'asis'}
# Create the table as a data frame
bcap_scale_df <- data.frame(
  var_name = c("bcap_total", "bcap_risk", "bcap_happy", "bcap_feel_pers", "bcap_lonely", "bcap_fam_conf", "bcap_rigid","bcap_distress", "bcap_poverty", "bcap_lie", "bcap_random"),
  scale = c("BCAP complete Scale (34)", "BCAP Risk Scale (26)", "Happiness (3)", "Feelings of persecution", "Loneliness (4)", "Family conflict (3)", "Rigidity (4)", "Distress (5)", "Financial Insecurity (2)", "Lie (6)", "Random responding (3)"),
  scale_construction = c("`q1_r`,`q2_r`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q9`, `q10`, `q11`, `q12`, `q13`, `q14`, `q15`, `q16`, `q17`, `q18`, `q19`, `q20`, `q21`, `q22`, `q23_r`, `q24`, `q25`, `q26`, `q27`, `q28`, `q29_r`, `q30`, `q31`, `q32`, `q33`, `q34`", 
                         "`q1_r`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q10`, `q11`, `q12`, `q13`, `q14`, `q16`, `q17`, `q19`, `q20`, `q22`, `q23_r`, `q24`, `q25`, `q27`, `q29_r`, `q30`, `q31`, `q32`, `q33`", 
                         "`q1_r`, `q23_r`, `q29_r`", 
                         "`q3`, `q25`, `q33`", 
                         "`q5`, `q12`, `q22`, `q31`", 
                         "`q6`, `q13`, `q17`", 
                         "`q7`, `q14`, `q20`, `q32`", 
                         "`q8`, `q11`, `q16`, `q19`, `q27`", 
                         "`q10`, `q30`", 
                         "`q4`, `q9`, `q15`, `q21`, `q26`, `q34`,", 
                         "`q2`, `q18`, `q28`"),
  scale_range = c("0-24","","","","","","","","","", ""), #TODO fill in range 
   alpha = c(round(bcap_alpha$total$raw_alpha, 3),
              round(bcap_risk_alpha$total$raw_alpha, 3),
              round(bcap_happy_alpha$total$raw_alpha, 3),
              round(bcap_feel_pers_alpha$total$raw_alpha, 3),
              round(bcap_lonely_alpha$total$raw_alpha, 3),
              round(bcap_fam_conf_alpha$total$raw_alpha, 3), 
              round(bcap_rigid_alpha$total$raw_alpha, 3), 
              round(bcap_distress_alpha$total$raw_alpha, 3),
              round(bcap_poverty_alpha$total$raw_alpha, 3), 
              round(bcap_lie_alpha$total$raw_alpha, 3),
              round(bcap_random_alpha$total$raw_alpha, 3))
)

# Create the gt table object
bcap_scale_table <- gt(bcap_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale_construction ~ px(135)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme() 

# Print the table
print(bcap_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score.

For binary items:

```{r bcap-binary-desc}

# Create subset of BCAP items
bcap_data_subset_binary <- complete %>%
  select(q1_r,
         q2_r,
         q3:q22,
         q23_r,
         q24:q28,
         q29_r,
         q30:q34)

# Calculate the dichotomous summary statistics for each variable
bcap_summary_data_binary <- lapply(bcap_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
bcap_summary_data_binary <- as.data.frame(bcap_summary_data_binary)

# Set items as first row
bcap_summary_data_binary <- rbind(names(bcap_summary_data_binary), bcap_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
bcap_tbl_binary <- bcap_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "Disagree", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Agree", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
bcap_tbl_binary
```

For continuous total and subscale scores:

```{r bcap-mean-items}
# Create subset of bcap items
bcap_data_subset <- complete %>%
  select(
    bcap_risk, bcap_happy, bcap_feel_pers, bcap_lonely, bcap_fam_conf, bcap_rigid, bcap_distress, bcap_poverty, bcap_lie, bcap_random)

# Calculate the summary statistics for each variable
bcap_summary_data <- lapply(bcap_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
bcap_summary_data <- as.data.frame(bcap_summary_data)

# Set items as first row
bcap_summary_data <- rbind(names(bcap_summary_data), bcap_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
bcap_tbl <- bcap_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(1 ~ px(165),2:5 ~ px(115)) %>%
    tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
bcap_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r bcap-distributions, class.source='fold', echo = FALSE}
#Risk 
p_bcap_risk <- complete %>%
  composite_hist(
    x = bcap_risk
  ) +
  labs(
    title = 'Risk'
  )

# Happiness 
p_bcap_happy <- complete %>% 
  composite_hist(
    x = bcap_happy,
    bins = 5
  ) +
  labs(
    title = 'Happiness'
  )

# Feelings
p_bcap_pers <- complete %>% 
  composite_hist(
    x = bcap_feel_pers,
    bins = 5
  ) +
  labs(
    title = 'Feelings of Persecution'
  )

# Loneliness
p_bacp_lonely <- complete %>% 
  composite_hist(
    x = bcap_lonely,
    bins = 5
  ) +
  labs(
    title = 'Loneliness'
  )

# Family Conflict
p_bcap_fam_c<-complete %>% 
  composite_hist(
    x = bcap_fam_conf,
    bins = 5
  ) +
  labs(
    title = 'Family Conflict'
  )

# Rigidity
p_bcap_rig <- complete %>% 
  composite_hist(
    x = bcap_rigid,
    bins = 5
  ) +
  labs(
    title = 'Rigidity'
  )

# Distress
p_bcap_dis <- complete %>% 
  composite_hist(
    x = bcap_distress,
    bins = 5
  ) +
  labs(
    title = 'Distress'
  )

# Poverty
p_bcap_prov <- complete %>% 
  composite_hist(
    x = bcap_poverty,
    bins = 5
  ) +
  labs(
    title = 'Poverty'
  )

# Lying
p_bcap_lie <- complete %>% 
  composite_hist(
    x = bcap_lie,
    bins = 5
  ) +
  labs(
    title = 'Lying'
  )
    
# Random Responding 
p_bcap_rand <- complete %>% 
  composite_hist(
    x = bcap_random,
    bins = 5
  ) +
  labs(
    title = 'Random Responding'
  ) 

ggarrange(p_bcap_risk, p_bcap_happy + rremove("ylab"),
          p_bcap_pers+ rremove("ylab"), p_bacp_lonely+ rremove("ylab"),
          p_bcap_fam_c, p_bcap_rig+ rremove("ylab"),
          p_bcap_dis+ rremove("ylab"), p_bcap_dis+ rremove("ylab"),
          p_bcap_prov, p_bcap_lie+ rremove("ylab"),
          p_bcap_rand+ rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for bcap Subscale \n(x-axis and y-axis are in different scales)"))
```

####Clinical Cutoff TODO: Maria/Shaina, please confirm weather we need
this section or not.

```{r}
p_bcap_risk_clin <- complete %>%
  cutoff_plot2(
    x = bcap_risk,
    cutoff = 9,
    cutoff_other = 12
  ) +
  labs(
    title = 'Risk',
    y = "Number of Participant",
    caption = 'Cutoffs are 9 and 12\nSee references for literature on cutoff scores.'
  )

p_bcap_lie_clin <- complete %>% 
  cutoff_plot2(
    x = bcap_lie,
    cutoff = 4
  ) +
  labs(
    title = 'Lie',
    y = "Number of Participant",
    caption = 'If 4 or more (score of 4) items are endorsed,\ncase may be invalid'
  )

p_bcap_rand_clin <- complete %>% 
  cutoff_plot2(
    x = bcap_random,
    cutoff = 0
  ) +
  labs(
    title = 'Random Responding',
    caption = 'If any of these items are endorsed (score > 0),\ncase may be invalid'
  )

ggarrange(p_bcap_risk_clin, p_bcap_lie_clin+ rremove("ylab"), p_bcap_rand_clin 

          ) %>%
  annotate_figure(top = text_grob( "Cutoff Values for BCAP Subscale \n(x-axis and y-axis are in different scales)"))
```



## Dyadic Adjustment Scale (DAS)

### DAS Description

The DAS is a self-report measure used to assess dyadic adjustment
(e.g., interpersonal tensions, dyadic satisfaction, dyadic functioning).

*For the present study, all 32 items from the DYADC were collected, and
the total score and all subscales are included: Consensus, Affective
Expression, Satisfaction, and Cohesion.

*Two items `e18` and `e19` should be reverse scored which is noted in the
variable table below and the reverse scored variables are provided
(`e18_r` and `e19_r`). 

***Higher** scores indicate **more** positive dyadic (couple) adjustment.

<SHAINA> CONFIRM The missing data rule was Applied. Calculations were
completed only with participants that had less than 20% missing data
(this includes `-77` responses)

Reference:
[@ondersma2005brief](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug);
[DOI](https://doi.org/10.1207/s15374424jccp3402_9) <SHIANA> EXPLAIN WHAT
2ND REF IS FOR Reference:
[@spanier1976measuring](https://www.jstor.org/stable/350547);[DOI](https://doi.org/10.2307/350547)

### DAS Variables

#### Value Labels

The DAS has multiple response options, value labels for each variable
can be found in the survey items table below.

#### Survey Items

All DAS survey items are presented in the following table:

```{r dyadc-var-prep}
# Pull question wording from qualtrics data
dyadc_word <- qualtrics %>% 
  select(starts_with("E")) %>%
  slice(1) %>%
  select(-(1:2))

#create table with variable name, description, and notes
dyadc_word_long <- dyadc_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         value = case_when(row_number() <= 15  ~ "0 = Always Disagree 
                                                 \n1 = Almost Always Disagree
                                                 \n2 = Frequently Disagree
                                                 \n3 = Occasionally Disagree
                                                 \n4 = Almost Always Agree
                                                 \n5 = Always Agree",
                           row_number() %in% c(16, 17, 20:22) ~ "0 = All the time 
                                                 \n1 = Most of the time
                                                 \n2 = More often than not
                                                 \n3 = Occasionally
                                                 \n4 = Rarely
                                                 \n5 = Never",
                           row_number() %in% c(18,19) ~ "0 = Never
                                                 \n1 = Rarely
                                                \n2 = Occasionally
                                                 \n3 = More often than not
                                                 \n4 = Most of the time
                                                 \n5 = All the time ",
                           between(row_number(), 23, 24 ) ~ "0 = Never
                                                 \n1 = Rarely
                                                 \n2 = Occasionally
                                                 \n3 = Almost every day
                                                 \n4 = Every day",
                           between(row_number(), 25,28) ~ "0 = Never
                                                 \n1 = Less than once a month
                                                 \n2 = Once or twice a month
                                                 \n3 = Once or twice a week
                                                 \n4 = Once a day
                                                 \n5 = More often",
                           row_number() %in% c(29,30) ~ "0 = Yes
                                                 \n1 = No",
                           row_number() %in% c(31) ~ "0 = Extremely Unhappy
                                                 \n1 = Fairly Unhappy
                                                 \n2 = A Little Unhappy
                                                 \n3 = Happy
                                                 \n4 = Very Happy
                                                 \n5 = Extremely Happy
                                                 \n6 = Perfect",
                           row_number() >= 32 ~ "0 =	My relationship can never succeed, and there is no more that I can do to keep the relationship going.
                                                 \n1 =	It would be nice if it succeeded, but I refuse to do any more than I am doing now to keep the relationship going.
                                                 \n2 =	It would be nice if my relationship succeeded, but I can’t do much more than I’m doing now to help it succeed.
                                                 \n3 =	I want very much for my relationship to succeed, and will do my fair share to see that it does.
                                                 \n4 =	I want very much for my relationship to succeed, and will do all I can to see that it does.
                                                 \n5 =	I want desperately for my relationship to succeed, and would go to almost any length to see that it does."
                           ),
         notes = case_when(var_name == "e18" ~ "This item should be reverse scored. `e18_r` is reverse scored",
                           var_name == "e19" ~ "This item should be reverse scored. `e19_r` is reverse scored",
                           TRUE ~ as.character(""))
         ) %>%
   mutate(description = if_else(var_name == "e31", " Please indicate the number that best describes the degree of happiness in your relationship.",
                               if_else(var_name == "e32", "Which of the following statements best describes how you feel about the future of your relationship? Please indicate only one answer", description))) %>%
  slice(1:32)


```

Questions in this survey were not asked for participants who were incarcerated at the time of survey administration.

```{r dyadc-var-table, results ='asis'}
# Create the gt table object and apply generic theme
dyadc_gt_table <- gt(dyadc_word_long)

# Table-specific formatting (col width, names)
dyadc_gt_table <- dyadc_gt_table %>% 
  apply_tbl_theme() %>% 
  tab_row_group(label = "Please indicate if items below were problems in your relationships in the past few weeks.", 
                rows = 29:32,
                id = "set4") %>%
  tab_row_group(label = "Thinking about the past 6 months,how often do you…", 
                rows = 25:28,
                id = "set3") %>%
  tab_row_group(label = "In the past 6 months, how often. . .", 
                rows = 23:24,
                id = "set2") %>%
  tab_row_group(label = "Thinking about the past 6 months, how often do you. . . ", 
                rows = 1:22,
                id = "set1")%>%
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1", alpha = 0.2),
                         cell_borders(sides = c("left", "right", "top", "bottom"))),
            locations = cells_row_groups(groups = c("set1", "set2", "set3", "set4"))) %>%
  cols_width(notes ~ px(150),
             var_name ~ px(100),
             value ~ px(225)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(dyadc_gt_table)

#WHEN RENDERING WITH PDF USE: 
#dyadc_gt_table


```

#### Scale and Subscales

Information on total score and subscale variables are below.
<SHAINA/MARIA> INSERT Variables were constructed by ...

```{r dyadc alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
dyadc_alpha <-
  complete %>% 
  select(
    e1:e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_con_alpha <-
  complete %>% 
  select(
    e1:e13
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_aff_exp_alpha <-
  complete %>% 
  select(
    e4, e6, e29, e30
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_satis_alpha <-
  complete %>% 
  select(
    e16:e23,
    e31,
    e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_cohes_alpha <-
  complete %>% 
  select(
    e24:e28
  ) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r dyadc-scale-table, results = 'asis'}
# Create the table as a data frame
dyadc_scale_df <- data.frame(
  var_name = c("dyadc_total", "dyadc_con", "dyadc_aff_exp", "dyadc_satis", "dyadc_cohes"),
  scale = c("DYADC Total score (32) ", "Consensus (13)", "Affective Expression (4)", "Satisfaction (10)", "Cohesion (5)"),
  scale_construction = c("`e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`, `e14`, `e15`, `e16`, `e17`, `e18_r`, `e19_r`, `e20`, `e21`, `e22`, `e23`, `e24`, `e25`, `e26`, `e27`, `e28`, `e29`, `e30`, `e31`, `e32`", 
                         "`e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`", 
                         "`e4`, `e6`, `e29`, `e30`", 
                         "`e16`, `e17`, `e18_r`, `e19_r`, `e20`, `e21`, `e22`, `e23`, `e31`, `e32`", "`e24`, `e25`, `e26`, `e27`, `e28`"),
  scale_range = c("0-151","","","",""), #TODO fill in range 
   alpha = c(round(dyadc_alpha$total$raw_alpha, 3),
              round(dyadc_con_alpha$total$raw_alpha, 3),
              round(dyadc_aff_exp_alpha$total$raw_alpha, 3),
              round(dyadc_satis_alpha$total$raw_alpha, 3),
              round(dyadc_cohes_alpha$total$raw_alpha, 3))
  )

# Create the gt table object
dyadc_scale_table <- gt(dyadc_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale ~ px(135)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme() 

# Print the table
print(dyadc_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score.

For continuous items:

```{r dyadc-mean-items}
# Create subset of dyadc items
dyadc_data_subset <- complete %>%
  select(e1:e28, e31:e32, dyadc_total,
         dyadc_con, ,dyadc_aff_exp,
         dyadc_satis, dyadc_cohes)  


# Calculate the summary statistics for each variable
dyadc_summary_data <- lapply(dyadc_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dyadc_summary_data <- as.data.frame(dyadc_summary_data)

# Set items as first row
dyadc_summary_data <- rbind(names(dyadc_summary_data), dyadc_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dyadc_tbl <- dyadc_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(1 ~ px(165),2:5 ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme()

# Render the table
dyadc_tbl

```

For binary items:

```{r dyadc-binary-desc}

# Create subset of BCAP items
dyadc_data_subset_binary <- complete %>%
  select(e29, e30)

# Calculate the dichotomous summary statistics for each variable
dyadc_summary_data_binary <- lapply(dyadc_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dyadc_summary_data_binary <- as.data.frame(dyadc_summary_data_binary)

# Set items as first row
dyadc_summary_data_binary <- rbind(names(dyadc_summary_data_binary), dyadc_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dyadc_tbl_binary <- dyadc_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "No", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Yes", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) %>%
  tab_options(table.width = pct(100))

# Render the table
dyadc_tbl_binary
```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r dyadc-distributions, class.source='fold', echo = FALSE}
p_dyadc_total <- complete %>%
  composite_hist(
    x = dyadc_total
  ) +
  labs(
    title = 'DYADC Total Score'
  )

p_dyadc_con <- complete %>%
  composite_hist(
    x = dyadc_con
  ) +
  labs(
    title = 'Consensus'
  )

p_dyadc_aff_e <- complete %>%
  composite_hist(
    x = dyadc_aff_exp,
    bins = 10
  ) +
  labs(
    title = 'Affectional Expression'
  )

p_dyadc_satis <- complete %>%
  composite_hist(
    x = dyadc_satis
  ) +
  labs(
    title = 'Satisfaction'
  )

p_dyadc_choes <- complete %>%
  composite_hist(
    x = dyadc_cohes
  ) +
  labs(
    title = 'Cohesion'
  )

ggarrange(p_dyadc_total, p_dyadc_con + rremove("ylab"),
          p_dyadc_aff_e+ rremove("ylab"), p_dyadc_satis,
          p_dyadc_choes + rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for DYADC Total and Subscale \n(x-axis and y-axis are in different scales)"))
```

#### Clinical Categories

The distribution for the total score alongside clinical cutoffs are
presented below. Cutoffs for a distressed couple (below 98) or for a satisfied and happy couple (at or above 114.8) are cited in the original Spanier, 1976 article. Other cutoffs may be established.


Reference for Cutoffs: [@spanier1976measuring](https://www.jstor.org/stable/350547);[DOI](https://doi.org/10.2307/350547)

```{r dyadc-cutoff, class.source='fold', echo = FALSE}
complete %>%
  cutoff_plot2(
    x = dyadc_total,
    cutoff = 98,
    cutoff_other = 114.8
  ) +
  labs(
    title = 'Cutoff Values for DAS Scale',
    caption = 'Cutoffs are 92 and 107\nSee references for literature on cutoff scores.'
  )+
  geom_text(aes(x = 16, y = 16.5, label = "Distressed\n Couple\n Below Cutoff", vjust = -.25, hjust = -6)) +
  geom_text(aes(x = 16, y = 16.5, label = "Happy\n or Satisfied\n Couple\n Above Cutoff", vjust = -.25, hjust = -9.25))
```



## Attachment Relationships Questionnaire (ARQ)

### ARQ Description

The ARQ is a self-report measure used to categorize attachment styles in
adulthood. <MARIA> CONFIRM THIS IS CORRECT

For the present study, all 5 items from the ARQ were collected in order
to construct four attachment styles (secure, fearful, preoccupied, and
dismissing).

No items need to be reverse scored. Participants self-select one
attachment style that best describes them in the first question `rq1`,
then rate their agreement with each attachment style for `rqa` - `rqd`.
Higher ratings indicate more agreement with the statement.

The missing data rule is applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@bartholomew1991attachment](https://psycnet.apa.org/record/1991-33075-001);[DOI](https://doi.org/10.1037/0022-3514.61.2.226)

### ARQ Variables

#### Value Labels

Response options for `rq1`

```{r ARQ-label-table, results = 'asis'}

arq_label_df <- data.frame(
  value = c("A", "B", "C", "D"),
  label = c("It is easy for me to become emotionally close to others. I am comfortable dependingon them and having them depend on me. I don't worry about being alone or havingothers not accept me.",
            "I am uncomfortable getting close to others. I want emotionally close relationships, but Ifind it difficult to trust others completely, or to depend on them. I worry that I will be hurt ifI allow myself to become too close to others.",
            "I want to be completely emotionally intimate with others, but I often find that others arereluctant to get as close as I would like. I am uncomfortable being without closerelationships, but I sometimes worry that others don't value me as much as I value them.",
            "I am comfortable without close emotional relationships. It is very important to me tofeel independent and self-sufficient, and I prefer not to depend on others or have othersdepend on me.")
) %>% 
  t() %>% 
  as.data.frame()


arq_label_df <- setNames(arq_label_df[-1, ], unlist(arq_label_df[1, ]))


#create table
arq_label_table <- arq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ pct(100)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(arq_label_table)


```

Response option for `rqa`, `rqb`, `rqc`, `rqd`.

```{r ARQ-label-table-2, results = 'asis'}

arq_label_df <- data.frame(
  value = c("1", "2", "3", "4", "5", "6", "7"),
  label = c("Disagree Strongly",
            "",
            "",
            "Neutral/Mixed",
            "",
            "",
            "Agree Strongly")
) %>% 
  t() %>% 
  as.data.frame()


arq_label_df <- setNames(arq_label_df[-1, ], unlist(arq_label_df[1, ]))


#create table
arq_label_table <- arq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(arq_label_table)


```

#### Survey Items

All ARQ survey items are presented in the following table

```{r ARQ-var-prep}
# Pull question wording from qualtrics data
arq_word <- qualtrics %>% 
  select(RQ1,RQA, RQB, RQC, RQD) %>% 
  slice(1)

#create table with variable name, description, and notes
arq_word_long <- arq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  mutate(description = if_else(var_name == "rq1", "Please tell me which one style best describes you or is the closest to the way you are.", description))

```

```{r arq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
arq_gt_table <- gt(arq_word_long)

# Table-specific formatting (col width, names)
arq_gt_table <- arq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(arq_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on constructed attachment groups is presented below. The
highest rating for attachment style was used to classify participants
into one of four attachment groups (secure, dismissing, preoccupied,
fearful). Model of the self (i.e., attachment anxiety) was calculated by
summing secure and dismissing ratings then subtracting the sum of
preoccupied and fearful items. Model of the other (i.e., attachment
avoidance) was constructed by summing secure and preoccupied items and
subtracting the sum of dismissing and fearful items. Higher scores on
attachment models indicate more positive attachment models. <MARIA>
CONFIRM THIS IS CORRECT

<SHAINA/MARIA> CONFIRM ALPHA IS NEEDED

```{r arq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
arq_alpha <-
  complete %>%
  select(rqa,	rqb, rqc, rqd) %>%
  psych::alpha(check.keys = TRUE)
```

```{r arq-subscales}
#DATA CLEANING CODE - create arq categories
vars_to_check <- c("rqa", "rqb", "rqc", "rqd")

arq_subscale <- complete %>% 
  mutate(max_var = apply(.[vars_to_check], 1, function(row) vars_to_check[which.max(row)])) %>% 
  mutate(arq_group = case_when(max_var == "rqa" ~ "Secure",
                               max_var == "rqb" ~ "Fearful",
                               max_var == "rqc" ~ "Preoccupied",
                               max_var == "rqd" ~ "Dismissive",
                               TRUE ~ NA_character_),
         arq_model_self = rowSums(data.frame(rqa, rqd), na.rm = TRUE) - rowSums(data.frame(rqc, rqb), na.rm = TRUE),
    arq_model_other = rowSums(data.frame(rqa, rqc), na.rm = TRUE) - rowSums(data.frame(rqd, rqb), na.rm = TRUE)) %>%
  mutate_at(vars(arq_model_self, arq_model_other), ~ if_else(is.na(arq_group), NA_real_, .)) %>% 
  select(-max_var) 

#missing ratings: 50, 116, and 123

```

```{r ARQ-scale-table, results = 'asis'}
# Create the table as a data frame
arq_scale_df <- data.frame(
  var_name = c("arq_group", "arq_model_self", "arq_model_other"),
  scale = c("Attachment Group", "Model of Self", "Model of Other"),
  scale_construction = c("Highest rating among `rqa`, `rqb`, `rqc`, `rqd`", "(`rqa` + `rqd`) - (`rqc` + `rqb`)", "(`rqa` + `rqc`) - (`rqd` + `rqb`)"))

# Create the gt table object
arq_scale_table <- gt(arq_scale_df) %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale Name", 
            scale_construction = "Scale Construction") %>% 
  tab_options(table.width = pct(100))%>%
  #tab_options(table.border.bottom.style = "hidden") %>% 
  apply_tbl_theme() 

# Print the table
print(arq_scale_table)
```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and
total/subscale score

```{r ARQ-mean-items}
# Create subset of BSI items
arq_data_subset <- complete %>%
  select(rq1,rqa,	rqb, rqc, rqd)

# Calculate the summary statistics for each variable
arq_summary_data <- lapply(arq_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
arq_summary_data <- as.data.frame(arq_summary_data)

# Set items as first row
arq_summary_data <- rbind(names(arq_summary_data), arq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
arq_tbl <- arq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme()

# Render the table
arq_tbl

```

#### Distributions

Distributions are presented for the total score and each subscale *TODO:
JP's graphs are count on x axis*

```{r ARQ-distributions, class.source='fold', echo = FALSE}
p_rq1 <- complete %>%
  select(rq1) %>%
  mutate(
    across(
      .cols = rq1,
      .fns = ~case_when(
        .x == "A" ~ 1,
        .x == "B" ~ 2,
        .x == "C" ~ 3,
        .x == "D" ~ 4,
        TRUE ~ NA_real_
      )
    )
    ) %>%
  composite_hist(x = rq1, bins = 4) +
  scale_x_continuous(breaks=c(1,2,3,4),
    #breaks=c("1","2","3","4"),
        labels=c("A","B", "C", "D")) +
  labs(title = 'rq1') 

p_rqa <- complete %>%
  composite_hist(x = rqa, bins = 10) +
  labs(title = 'rqa')

p_rqb <- complete %>%
  composite_hist(x = rqb, bins = 10) +
  labs(title = 'rqb')

p_rqc<-complete %>%
  composite_hist(x = rqc, bins = 10) +
  labs(title = 'rqc')

p_rqd<-complete %>%
  composite_hist(x = rqd, bins = 10) +
  labs(title = 'rqd')

ggarrange(p_rq1, p_rqa + rremove("ylab"),
          p_rqb+ rremove("ylab"), p_rqc,
          p_rqd + rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for ARQ \n(x-axis and y-axis are in different scales)"))
```



## Posttraumatic Risk Seeking Scale (PRSS)

### PRSS Description

The PRSS is a 5-item questionnaire designed to measure *insert text*

For the present study, 5 items from the PRSS were collected in order to
*TODO: insert text here*

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@kerig2019linking](https://onlinelibrary.wiley.com/doi/abs/10.1111/cpsp.12280);
[DOI](https://doi.org/10.1111/cpsp.12280)

### PRSS Variables

#### Value Labels

All PRSS variables have the same response options.

```{r PRSS-label-table, results = 'asis'}

prss_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("None of the time",
            "A little of the time",
            "Some of the time",
            "Much of the time",
            "Most of the time")) %>% 
  t() %>% 
  as.data.frame()

prss_label_df <- setNames(prss_label_df[-1, ], unlist(prss_label_df[1, ]))


#create table
prss_label_table <- prss_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(150)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(prss_label_table)


```

#### Survey Items

PRSS survey items are presented in the following table:

```{r prss-var-prep}
# Pull question wording from Qualtrics data
prss_word <- qualtrics %>% 
  select(starts_with("ps")) %>% 
  slice(1)

#create table with variable name, description, and notes
prss_word_long <- prss_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character(""))%>%
  slice(9:13)

```

```{r prss-var-table, results ='asis'}
# Create the gt table object and apply generic theme
# this sould be ps9-ps13
prss_gt_table <- gt(prss_word_long)

# Table-specific formatting (col width, names)
prss_gt_table <- prss_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(prss_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were constructed by summing included items.

```{r prss alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
prss_alpha <-
  complete %>%
  select(ps9:ps13) %>%  
  psych::alpha(check.keys = TRUE)
```

```{r PRSS-scale-table, results = 'asis'}
# Create subset of prss items
prss_data_subset <- complete %>%
  select(ps9:ps13, prss_total)


# Create the table as a data frame
prss_scale_df <- data.frame(
  var_name = c("prss_total"),
  scale = c("PRSS Total score (5) "),
  scale_construction = c("`ps9`, `ps10`, `ps11`, `ps12`, `ps13`"),
  scale_range = c("0-16"), #TODO maria double check range 
   alpha = c(round(prss_alpha$total$raw_alpha, 3))
  )

# Create the gt table object
prss_scale_df <- gt(prss_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale ~ px(135)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme() 

# Print the table
print(prss_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r prss-mean-items}

# Calculate the summary statistics for each variable
prss_summary_data <- lapply(prss_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
prss_summary_data <- as.data.frame(prss_summary_data)

# Set items as first row
prss_summary_data <- rbind(names(prss_summary_data), prss_summary_data) %>% 
  t() %>% 
  as.data.frame() 

# Create the gt table
prss_tbl <- prss_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme()

# Render the table
prss_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r PRSS-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(
    x = prss_avg
  ) +
  labs(title = "Distribution of Average Scores for the PRSS")


```


## Stigma & Shame Questionnaire (SSQ)

### SSQ Description

The SSQ is a 8-item questionnaire designed to measure *insert*.

For the present study, 8 items from the SSQ were collected in order to
#TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@feiring2005persistence](https://journals.sagepub.com/doi/abs/10.1177/1077559505276686);
[DOI](https://doi.org/10.1177/1077559505276686)

### SSQ Variables

#### Value Labels

All SSQ variables have the same response options.

```{r SSQ-label-table, results = 'asis'}

ssq_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("None of the time",
            "A little of the time",
            "Some of the time",
            "Much of the time",
            "Most of the time")) %>% 
  t() %>% 
  as.data.frame()

ssq_label_df <- setNames(ssq_label_df[-1, ], unlist(ssq_label_df[1, ]))


#create table
ssq_label_table <- ssq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(ssq_label_table)


```

#### Survey Items

SSQ survey items are presented in the following table:

```{r ssq-var-prep}
# Pull question wording from qualtrics data
ssq_word <- qualtrics %>% 
  select(starts_with("ps")) %>% 
  slice(1)

#create table with variable name, description, and notes
ssq_word_long <- ssq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  slice(1:8)


```

```{r ssq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
ssq_gt_table <- gt(ssq_word_long)

# Table-specific formatting (col width, names)
ssq_gt_table <- ssq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(ssq_gt_table)


```


#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were constructed by summing included items.

```{r ssq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
ssq_abuse_shame_alpha <- complete %>% 
  select(
    ps1:ps4
  ) %>% 
  psych::alpha(check.keys = TRUE)

ssq_alpha <- complete %>% 
  select(
    ps1:ps8
  ) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r SSQ-scale-table, results = 'asis'}
# Create subset of ssq items
ssq_data_subset <-
  complete %>%
  select(ps1:ps8, starts_with("ssq"))

# Create the table as a data frame
ssq_scale_df <- data.frame(
  var_name = c("ssq_total", "ssq_abuse_shame"),
  scale = c("SSQ Total score (8)", "Abuse-related Shame (4)"),
  scale_construction = c("`ps1`, `ps2`, `ps3`, `ps4`,`ps5`, `ps6`, `ps7`, `ps8`",
                         "`ps1`, `ps2`, `ps3`, `ps4`"),
  scale_range = c("",""), #TODO fill in range 
  alpha = c(round(ssq_alpha$total$raw_alpha, 3),
            round(ssq_abuse_shame_alpha$total$raw_alpha, 3))
)

# Create the gt table object
ssq_scale_df <- gt(ssq_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(ssq_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r ssq-mean-items}
# Calculate the summary statistics for each variable
ssq_summary_data <- lapply(ssq_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
ssq_summary_data <- as.data.frame(ssq_summary_data)

# Set items as first row
ssq_summary_data <- rbind(names(ssq_summary_data), ssq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
ssq_tbl <- ssq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  #cols_width(everything() ~ px(115)) %>%
  
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
ssq_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r ssq-distributions, class.source='fold', echo = FALSE}
ssq_data_subset %>%
  composite_hist(
    x = ssq_total
  ) +
  labs(title = "Distribution of Total Scores for the Stigma & Shame Questionnaire")

```

#### Clinical Categories

The distribution for the total score alongside clinical cutoffs are
presented below.

<MARIA>INSERT MORE INFO ON CUTOFF SCORES - what are they (what should
plot labels be)?, how should they be used

Reference: <SHAINA/MARIA> INSERT REFERENCE FOR DYADC CUTOFF SCORES

```{r ssq-cutoff, class.source='fold', echo = FALSE}

p_ssq_total_clin <- ssq_data_subset %>% 
  cutoff_plot2(
    x = ssq_total,
    cutoff = 16
  ) +
  labs(
    title = "Total",
    caption = "Cutoff is 16\nSee reference for literature on cutoff score."
  )

p_ssq_abuse_shame_clin <- ssq_data_subset %>% 
  cutoff_plot2(
    x = ssq_abuse_shame,
    cutoff = 3
  ) +
  labs(
    title = "Abuse-related Shame",
    caption = "Cutoff is 3\nSee reference for literature on cutoff score."
  )

ggarrange(p_ssq_total_clin, p_ssq_abuse_shame_clin + rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for SSQ Clinical Cut-off \n(x-axis and y-axis are in different scales)"))
```


## Elliott Delinquency Scale (EDS) Friends/Peers report

### EDS Description

The EDS is a 39-item questionnaire designed to measure *insert*.

For the present study, 39 items from the EDS were collected in order to
#TODO: insert text here

All 39 items need to be reverse scored. *TODO: need change text here
Higher scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@feiring2005persistence](https://journals.sagepub.com/doi/abs/10.1177/1077559505276686);
[DOI](https://doi.org/10.1177/1077559505276686)

### EDS Variables

#### Value Labels

All EDS variables have the same response options.

```{r EDS-label-table, results = 'asis'}

eds_label_df <- data.frame(
  value = c("4", "3", "2", "1", "0", "0 "),
  label = c("All",
            "Most",
            "Some",
            "Very Few",
            "None",
            "Does not apply")) %>% 
  t() %>% 
  as.data.frame()

eds_label_df <- setNames(eds_label_df[-1, ], unlist(eds_label_df[1, ]))


#create table
eds_label_table <- eds_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(150)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(eds_label_table)


```

#### Survey Items

EDS survey items are presented in the following table:

```{r eds-var-prep}
# Pull question wording from qualtrics data
eds_word <- qualtrics %>% 
  select(starts_with("elf")) %>% 
  slice(1)

#create table with variable name, description, and notes
eds_word_long <- eds_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name),
          notes = ("")
          # notes = paste0("This item should be reverse scored. `", var_name, "_c` is reverse scored")
           ) %>% 
  slice(1:39)
# TODO: need double check reverse code variable name, it's inconsistant with other measure's reverse score name 

```

```{r eds-var-table, results ='asis'}
# Create the gt table object and apply generic theme
eds_gt_table <- gt(eds_word_long)

# Table-specific formatting (col width, names)
eds_gt_table <- eds_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())


# Print the table
print(eds_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were c onstructed by summing included items.


#Calculate internal reliability

```{r eds alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
eds <-
  complete %>%
  select(
    matches(
      "^elf"
    )
  )
#Calculate internal reliability 
eds_alpha <- complete %>% 
  select(elf1:elf39) %>%
  drop_na() %>%  # TODO: Shaina: I don't know why does including NA doesn't work for the alpha function. 
    psych::alpha(check.keys = TRUE)

```

TODO: all revers coded column is 0, need to double check, I used
non-revers coded score for now

```{r EDS-scale-table, results = 'asis'}


# Create the table as a data frame
eds_scale_df <- data.frame(
  var_name = c("eds_total"),
  scale = c("EDS Total score (39)"),
  scale_construction = c("`elf1`, `elf2`, `elf3`, `elf4`, `elf5`, `elf6`, `elf7`, 
  `elf8`, `elf9`, `elf10`, `elf11`, `elf12`, `elf13`, `elf14`, `elf15`, `elf16`, 
  `elf17`, `elf18`, `elf19`, `elf20`, `elf21`, `elf22`, `elf23`, `elf24`, `elf25`, 
  `elf26`, `elf27`, `elf28`, `elf29`, `elf30`, `elf31`, `elf32`, `elf33`, `elf34`, 
                         `elf35`, `elf36`, `elf37`, `elf38`, `elf39`"),
  scale_range = c("39-159"), #TODO fill in range 
  alpha = c(round(eds_alpha$total$raw_alpha, 3))
)

# Create the gt table object
eds_scale_df <- gt(eds_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(eds_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r eds-mean-items}
# Calculate the summary statistics for each variable
eds_summary_data <- lapply(eds, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
eds_summary_data <- as.data.frame(eds_summary_data)

# Set items as first row
eds_summary_data <- rbind(names(eds_summary_data), eds_summary_data) %>% 
  t() %>% 
  as.data.frame()


# Create the gt table
eds_tbl <- eds_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
 #cols_width(everything() ~ px(115)) %>%
    tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
eds_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r eds-distributions, class.source='fold', echo = FALSE}

eds %>%
  composite_hist(
    x = elf_total
  ) +
  labs(title = "Distribution of Total Scores for the Stigma & Shame Questionnaire")

```



## Elliott Delinquency Scale Self Report (ELL)

### ELL Description

The Ell is a 39-item questionnaire designed to measure *insert*.

For the present study, 39 items from the ELL were collected in order to
#TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@feiring2005persistence](https://journals.sagepub.com/doi/abs/10.1177/1077559505276686);
[DOI](https://doi.org/10.1177/1077559505276686)

### ELL Variables

#### Value Labels

Variable Scale (for variables that end with a) and for any item that has
been done 10 or more times.
TODO: Shaina: please review text above as I altered JP's text.

```{r ELL-label-table, results = 'asis'}
ell_label_df <- data.frame(
  value = c("1", "2", "3", "4", "5", "6"),
  label = c("Once a month",
            "Once every 2-3 weeks",
            "Once a week",
            "2-3 times a dday",
            "Once a day",
            "2-3 times a day")) %>% 
  t() %>% 
  as.data.frame()

ell_label_df <- setNames(ell_label_df[-1, ], unlist(ell_label_df[1, ]))


#create table
ell_label_table <- ell_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(ell_label_table)


```

#### Survey Items

ELL survey items are presented in the following table. Variables are not ending with a are open ended. Vairable end with a only been ask for item that has been done 10 or more times. 

```{r ell-var-prep}
# Pull question wording from qualtrics data
ell_word <- qualtrics %>% 
  select(starts_with("ell"))%>%
  slice(1)

#create table with variable name, description, and notes
ell_word_long <- ell_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  mutate(description = gsub("ASSESSOR NOTE.*","",description))# %>%
  # slice(1:78)

```

```{r ell-var-table, results ='asis'}
# Create the gt table object and apply generic theme
ell_gt_table <- gt(ell_word_long)

# Table-specific formatting (col width, names)
ell_gt_table <- ell_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels()) 

# Print the table
print(ell_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were c onstructed by summing included items.

```{r ell df, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
ell <-
  complete %>%
  select(
    starts_with("ell"),
    -c(matches("aa$"))
  ) %>%
  # rename(
  #   ell35a  = x35a
  # ) %>%
  mutate(
    across(
      matches("a$"),
      ~case_when(
        .x == 7 ~ -77,
        .x == 8 ~ NA_real_,
        is.na(.x) ~ NA_real_,
        TRUE ~ .x
      )
    )
  )

ell_calc <-
  ell %>%
  select(
    matches("a$")
  ) %>%
  mutate(
    across(
      #.cols = -id,
      .fns = ~case_when(
        .x == -77 ~ NA_real_,
        TRUE ~ .x
      )
    ),
    across(
      .names = "{.col}a"
    ),
    across(
      c(
        matches("a$"),
        matches("aa$")
      ),
      ~case_when(
        .x == 1 ~ 0,
        .x == 2 ~ 1,
        .x == 3 ~ 2,
        .x == 4 ~ 3,
        .x == 5 ~ 4,
        .x == 6 ~ 5,
        .x == 7 ~ -77,
        .x == 8 ~ NA_real_,
        TRUE ~ NA_real_
      )
    ),
    across(
      c(
        matches("aa$")
      ),
      ~case_when(
        .x >= 4 ~ 4,
        TRUE ~ .x
      )
    )
  )

ell_count_calc <-
  ell %>%
  select(
   # id,
    matches("\\d$")
  ) %>%
  mutate(
    across(
     # -id,
      .cols = everything(),
      ~case_when(
        .x == 0 ~ 0,
        .x > 0 ~ 1,
        #.x < 0 ~ NA,
        #TRUE ~ .x
      )
    )
  )


```

```{r ell calculation, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# ell_complete <-
#   ell_calc %>%
#   subscale_create(
#     total_only = TRUE,
#     scale1 = c(
#       "ell4a", "ell5a", "ell6a", "ell8a", "ell9a",
#       "ell10a", "ell11a", "ell14a", "ell16a", "ell20a",
#       "ell21a", "ell22a", "ell24a", "ell25a", "ell27a", "ell29a",
#       "ell31a", "ell32a", "ell33a", "ell38a", "ell39a"
#     ),
#     scale2 = c(
#       "ell4aa", "ell5aa", "ell6aa", "ell8aa", "ell9aa",
#       "ell10aa", "ell11aa", "ell14aa", "ell16aa", "ell20aa",
#       "ell21aa", "ell22aa", "ell24aa", "ell25aa", "ell27aa", "ell29aa",
#       "ell31aa", "ell32aa", "ell33aa", "ell38aa", "ell39aa"
#     )
#   ) %>%
#   rename(
#     ell_raw_total = total1,
#     ell_censor_total = total2
#   )
# 
# 
# ell_count_complete <-
#   ell_count_calc %>%
#   composite_total_avg_fun(
#     id = c(
#       'id', "ell1", "ell2", "ell3", "ell7",
#       "ell12", "ell13", "ell15", "ell17", "ell18",
#       "ell19", "ell23", "ell26", "ell28", "ell30",
#       "ell34", "ell35", "ell36", "ell37"
#     ),
#     max_value = 1,
#     n_items = 21
#   ) %>%
#   distinct(
#     across(
#       .cols = everything()
#     )
#   ) %>%
#   rename(
#     ell_count_total = sum_values,
#     ell_count_avg = mean_values
#   ) %>%
#   mutate(
#     across(
#       c(
#         ell_count_total,
#         ell_count_avg
#       ),
#       ~case_when(
#       #  id %in% ell_count_remove ~ NA_real_,
#         TRUE ~ .x
#       )
#     )
#   )
```

```{r ell alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
#TODO: Shaina: JP doesn't include alpha in his script. Please review and delet if not needed


```

```{r ELL-scale-table, results = 'asis'}
# Create the table as a data frame
ell_scale_df <- data.frame(
  var_name = c("ell_raw_total"),
  scale = c("ELL score (Raw) (21)", "ELL Total (Censored) (21)", "ELL Total (Binary Count Data) (18)"),
  scale_construction = c(" `ell4a`, `ell5a`, `ell6a`, `ell8a`, `ell9a`,
      `ell10a`, `ell11a`, `ell14a`, `ell16a`, `ell20a`,
      `ell21a`, `ell22a`, `ell24a`, `ell25a`, `ell27a`, `ell29a`,
      `ell31a`, `ell32a`, `ell33a`, `ell38a`, `ell39a`", 
      " `ell4aa`, `ell5aa`,`ell6aa`, `ell8aa`, `ell9aa`,
      `ell10aa`, `ell11aa`, `ell14aa`, `ell16aa`, `ell20aa`,
      `ell21aa`, `ell22aa`, `ell24aa`, `ell25aa`, `ell27aa`, `ell29aa`,
      `ell31aa`, `ell32aa`, `ell33aa`, `ell38aa`, `ell39aa`",
      "`ell1`, `ell2`, `ell3`, `ell7`,
      `ell12`, `ell13`, `ell15`, `ell17`, `ell18`,
      `ell19`, `ell23`, `ell26`, `ell28`, `ell30`,
      `ell34`, `ell35`, `ell36`, `ell37`"),
  scale_range = c("","","") #TODO fill in range 
  #alpha = c(round(eds_alpha$total$raw_alpha, 3))
)

# Create the gt table object
ell_scale_df <- gt(ell_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             # alpha = "Alpha"
             ) %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_tbl_theme() 

# Print the table
print(ell_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r ell-mean-items}
# Calculate the summary statistics for each variable
ell_summary_data <- lapply(ell, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
ell_summary_data <- as.data.frame(ell_summary_data)

# Set items as first row
ell_summary_data <- rbind(names(ell_summary_data), ell_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
ell_tbl <- ell_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  #cols_width(everything() ~ px(115)) %>%
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
ell_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r ell-distributions, class.source='fold', echo = FALSE}
# ell_complete %>%
#   composite_hist(
#     x = ell_raw_total
#   ) +
#   labs(title = 'Distribution of Total Scores for \nElliott Self Delinquency Scale (Raw)')

# ell_complete %>%
#   composite_hist(
#     x = ell_censor_total
#   ) +
#   labs(title = 'Distribution of Total Scores for \nElliott Self Delinquency Scale (Censored)')
# 
# ell_count_complete %>%
#   composite_hist(
#     x = ell_count_total
#   ) +
#   labs(title = "Distribution of Total Scores for \nElliott Self Delinquency Scale (Binary Count Data)")
```

    

## Mental Health Contimuun - SF (MHC-SF)

### MHC Description

The MHC is a 14-item questionnaire designed to measure *insert*.

For the present study, 14 items from the MHC were collected in order to
#TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was not applied. 

Reference: [@keyes2009brief]
[@lamers2011evaluating](https://onlinelibrary.wiley.com/doi/abs/10.1002/jclp.20741);
[DOI](https://doi.org/10.1002/jclp.20741)

### MHC Variables

#### Value Labels

All MHC variables have the same response options.

```{r MHC-label-table, results = 'asis'}

mhc_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4", "5"),
  label = c("Never",
            "Once or Twice",
            "About Once A Week",
            "About 2 or 3 Times A Week",
            "Almost Every Day",
            "Every Day")) %>% 
  t() %>% 
  as.data.frame()

mhc_label_df <- setNames(mhc_label_df[-1, ], unlist(mhc_label_df[1, ]))


#create table
mhc_label_table <- mhc_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()

# Print the table
print(mhc_label_table)


```

#### Survey Items

MHC survey items are presented in the following table:

```{r mhc-var-prep}
# Pull question wording from qualtrics data
mhc_word <- qualtrics %>% 
  select(starts_with("h"))%>%
  slice(1)

#create table with variable name, description, and notes
mhc_word_long <- mhc_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) 
```

```{r elf-var-table, results ='asis'}
# Create the gt table object and apply generic theme
mhc_gt_table <- gt(mhc_word_long)

# Table-specific formatting (col width, names)
mhc_gt_table <- mhc_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(mhc_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were c onstructed by summing included items.

```{r mhc df, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
mhc_complete <-
  complete %>%
  select(
  #  id,

    matches("^h"), 
    mhc_total,mhc_pa,mhc_swb, mhc_pwb
  )

```


```{r mhc alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
mhc_alpha <-
  mhc_complete %>%
  select(h1:h3) %>%
  psych::alpha(check.keys = TRUE)


mhc_pa_alpha <-
  mhc_complete %>%
  select(h1:h3) %>%
  psych::alpha(check.keys = TRUE)

mhc_swb_alpha <-
  mhc_complete %>%
  select(h4:h8) %>%
  psych::alpha(check.keys = TRUE)

mhc_pwb_alpha <-
  mhc_complete %>%
  select(h9:h14) %>%
  psych::alpha(check.keys = TRUE)
```

```{r MHC-scale-table, results = 'asis'}
# Create the table as a data frame
mhc_scale_df <- data.frame(
  var_name = c("mhc_raw_total", "mhc_pa_total", "mhc_swb_total", "mhc_pwb_total"),
  scale = c("MHC Total score (14)", "Positive Affect (3)", "Social Well-being (4)", "Psychological well-being (6)"),
  scale_construction = c(" `h1`, `h2`, `h3`, `h4`, `h5`, `h6`, `h7`, `h8`, `h9`, `h10`, `h11`, `h12`, `h13`, `h14`",
                         "`h1`, `h2`,`h3`", "`h4`, `h5`, `h6`, `h7`, `h8`", "`h9`, `h10`, `h11`, `h12`, `h13`, `h14`"
                         ),
  scale_range = c(""), #TODO fill in range 
  alpha = c(round(mhc_alpha$total$raw_alpha, 3),
            round(mhc_pa_alpha$total$raw_alpha, 3),
            round(mhc_swb_alpha$total$raw_alpha, 3),
            round(mhc_pwb_alpha$total$raw_alpha, 3))
)

# Create the gt table object
mhc_scale_df <- gt(mhc_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             # alpha = "Alpha"
             ) %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(mhc_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r mhc-mean-items}
# Calculate the summary statistics for each variable
mhc_summary_data <- lapply(mhc_complete, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
mhc_summary_data <- as.data.frame(mhc_summary_data)

# Set items as first row
mhc_summary_data <- rbind(names(mhc_summary_data), mhc_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
mhc_tbl <- mhc_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  tab_options(table.width = pct(100))%>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
mhc_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r mhc-distributions, class.source='fold', echo = FALSE}

p_mhc_total <- mhc_complete %>%
  composite_hist(
    x = mhc_total
  ) +
  labs(title = 'Total Scores')

p_mhc_swb <- mhc_complete %>%
  composite_hist(
    x = mhc_pa
  ) +
  labs(title = 'Positive Affect Subscale')

p_mhc_swb <- mhc_complete %>%
  composite_hist(
    x = mhc_swb
  ) +
  labs(title = 'Social Well-being Subscale')

p_mhc_pwb <- mhc_complete %>%
  composite_hist(
    x = mhc_pwb
  ) +
  labs(title = 'Psychological Well-being Subscale')

ggarrange(p_mhc_total, p_mhc_swb + rremove("ylab"), 
          p_mhc_swb, p_mhc_pwb + rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for MHC-SF total and subscale \n(x-axis and y-axis are in different scales)"))
```


## Flourishing Index

### FLO Description

The Flourishing Index is a 12-item questionnaire designed to measure
*insert*.

For the present study, 12 items from the Flourishing Index were
collected in order to #TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@vanderweele2017promotion](https://www.pnas.org/doi/abs/10.1073/pnas.1702996114);
[DOI](https://doi.org/10.1073/pnas.1702996114)

### Flourishing Index Variables

#### Value Labels

All Flourishing Index variables have the same response options.

```{r flo-label-table, results = 'asis'}

flo_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
  label = c("Not Satisfied At All","","","", "","","","","","","Completely Satisfied"),
  label2 = c("Extremely unhappy","","","", "","","","","","","Extremely Happy"),
  label3 = c("Poor","","","", "","","","","","","Excellent"),
  label4 = c("Not at all worthwhile","","","", "","","","","","","Completely Worthwhile"),
  label5 = c("Strongly Disagree","","","", "","","","","","","Strongly Agree"),
  label6 = c("Not true of me","","","", "","","","","","","Completely true of me"),
  label7 = c("Worry all of the time","","","", "","","","","","","Do not ever worry")
  ) %>% 
  t() %>% 
  as.data.frame()

flo_label_df <- setNames(flo_label_df[-1, ], unlist(flo_label_df[1, ]))


#create table
flo_label_table <- flo_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>%
  tab_options(table.width = pct(100))%>%
  apply_labtab_theme()


# Print the table
print(flo_label_table)


```
#### Survey Items

ALL Flourishing Index variables have the same response options.

```{r flo-var-prep}
# Pull question wording from qualtrics data
flo_word <- qualtrics %>% 
  select(I1:I12)%>%
  slice(1)

#create table with variable name, description, and notes
flo_word_long <- flo_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  slice(1:12)
```

```{r flo-var-table, results ='asis'}
# Create the gt table object and apply generic theme
flo_gt_table <- gt(flo_word_long)

# Table-specific formatting (col width, names)
flo_gt_table <- flo_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(flo_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were constructed by summing included items.
```{r  flo, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
flo_complete <- complete %>%
  select(i1:i12, flo_total)
```

```{r flo alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
flo_alpha <- flo_complete %>% 
  select(i1:i12) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r flo-scale-table, results = 'asis'}
# Create the table as a data frame
flo_scale_df <- data.frame(
  var_name = c("flo_total"),
  scale = c("FLO Total score (12)"),
  scale_construction = c(" `i1`, `i2`, `i3`, `i4`, `i5`, `i6`, `i7`, `i8`, `i9`, `i10`, `i11`, `i12`"),
  scale_range = c(""), #TODO fill in range 
  alpha = c(round(flo_alpha$total$raw_alpha, 3))
)

# Create the gt table object
flo_scale_df <- gt(flo_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             # alpha = "Alpha"
             ) %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(flo_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r flo-mean-items}
# Calculate the summary statistics for each variable
flo_summary_data <- lapply(flo_complete, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
flo_summary_data <- as.data.frame(flo_summary_data)

# Set items as first row
flo_summary_data <- rbind(names(flo_summary_data), flo_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
flo_tbl <- flo_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ pct(100)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
flo_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r flo-distributions, class.source='fold', echo = FALSE}
flo_complete %>%
  composite_hist(
    x = flo_total
  ) +
  labs(title = 'Distribution of Total Scores for Flourishing Index')
```



## International Trauma Questionnaire - ITQ

### ITQ Description

The ITQ is a 9-item questionnaire designed to measure *insert*.

For the present study, 9 items from the ITQ were collected in order to
#TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 33% or less missing data (this includes -77 responses)

Reference:
[@cloitre2018international](https://onlinelibrary.wiley.com/doi/full/10.1111/acps.12956?casa_token=K4GIoIIYOkwAAAAA%3ABuaGU3cOQZwsFiM78FxHp_PHTQXDc72xABnVp8nlMCYRCHzf4c0oOMropyrzVjdClA3pFA-m01heootZ);
[DOI](https://doi.org/10.1111/acps.12956)

### ITQ Variables

#### Value Labels

All ITQ variables have the same response options.

```{r itq-label-table, results = 'asis'}
itq_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("Not at All",
            "A Little Bit",
            "Moderately",
            "Quite a Bit",
            "Extremely")) %>% 
  t() %>% 
  as.data.frame()

itq_label_df <- setNames(itq_label_df[-1, ], unlist(itq_label_df[1, ]))


#create table
itq_label_table <- itq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme()

# Print the table
print(itq_label_table)


```

#### Survey Items

All ITQ variables have the same response options.

```{r itq-var-prep}
# Pull question wording from qualtrics data
itq_word <- qualtrics %>% 
  select(starts_with("itq"))%>%
  slice(1)

#create table with variable name, description, and notes
itq_word_long <- itq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  slice(1:9)
```

```{r itq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
itq_gt_table <- gt(itq_word_long)

# Table-specific formatting (col width, names)
itq_gt_table <- itq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(itq_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were constructed by summing included items.

```{r itq df, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
itq_complete <- complete %>%
  select(
    starts_with("itq") 
    )
```

```{r itq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
itq_alpha <- itq_complete %>% 
  select(itq1:itq9) %>% 
  psych::alpha(check.keys = TRUE)
```



```{r itq-scale-table, results = 'asis'}
# Create the table as a data frame
itq_scale_df <- data.frame(
  var_name = c("Affective Dysregulation Subscale (2)", "Negative Self-Concept Subscale (2)", 
               "Disturbances in Relationships Subscale (2)", "DSO (6)"),
  scale = c("itq_ad_total", "itq_nsc_total", "itq_dr_total", "itq_dso"),
  scale_construction = c("`itq1`, `itq2`", "`itq3`, `itq4`", "`itq5`,`itq6`", 
                         "`itq1`, `itq2`, `itq3`, `itq4`, `itq5`,`itq6`"),
  scale_range = c("","","",""), #TODO fill in range 
  alpha = c("","","","")
)

# Create the gt table object
itq_scale_df <- gt(itq_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             # alpha = "Alpha"
             ) %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(itq_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:

```{r itq-mean-items}
# Calculate the summary statistics for each variable
itq_summary_data <- lapply(itq_complete, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
itq_summary_data <- as.data.frame(itq_summary_data)

# Set items as first row
itq_summary_data <- rbind(names(itq_summary_data), itq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
itq_tbl <- itq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ pct(100)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
itq_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r itq-distributions, class.source='fold', echo = FALSE}
p_itq_ad_total <- itq_complete %>%
  composite_hist(
    x = itq_ad_total,
    bins = 15
  ) +
  labs(title = "Affective Dysregulation Subscale")

p_itq_nsc_total <- itq_complete %>%
  composite_hist(
    x = itq_nsc_total,
    bins = 15
  ) +
  labs(title = "Negative Self-Concept Subscale")

p_itq_dr_total <- itq_complete %>%
  composite_hist(
    x = itq_dr_total,
    bins = 15
  ) +
  labs(title = "Relationships Subscale")


p_itq_dso <- itq_complete %>%
  composite_hist(
    x = itq_dso,
    bins = 15
  ) +
  labs(title = "DSO Subscale")

ggarrange(p_itq_ad_total, p_itq_nsc_total + rremove("ylab"),
          p_itq_dr_total, p_itq_dso + rremove("ylab")
          ) %>%
  annotate_figure(top = text_grob( "Distribution for ITQ Subscale \n(x-axis and y-axis are in different scales)"))

```


## IBQ

### IBQ Description

The IBQis a 10-item questionnaire designed to measure *insert*.

For the present study, 10 items from the IBQ were collected in order to
#TODO: insert text here

No items need to be reverse scored. *TODO: need change text here Higher
scores indicate more severe mental health symptoms.*

The missing data rule was applied. Calculations were completed for
participants with 20% or less missing data (this includes -77 responses)

Reference:
<TODO: Maria, please add reference> 

### IBQ Variables

#### Value Labels

IBQ variables response options for ibp1 - ibq9.

```{r ibq-label-table, results = 'asis'}
ibq_label_df <- data.frame(
  value = c("0", "1"),
  label = c("No",
            "Yes")) %>% 
  t() %>% 
  as.data.frame()

ibq_label_df <- setNames(ibq_label_df[-1, ], unlist(ibq_label_df[1, ]))


#create table
ibq_label_table <- ibq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme()

# Print the table
print(ibq_label_table)
```

<TODO: Maria, Please review this table>
```{r ibq-label-table2, results = 'asis'}
ibq_label_df2 <- data.frame(
  #value = c("0", "1"),
  label = c("School/University/College",
            "Juvenile Justice",
            "Legal System",
            "Police",
            "Medical or Mental Health Clinic",
            "Church",
            "Foster Care",
            "Child Welfare",
            "Other, please describe:",
            "Decline to Answer")) %>% 
  t() %>% 
  as.data.frame()


ibq_label_df2 <- setNames(ibq_label_df2[-1, ], unlist(ibq_label_df2[1, ]))


#create table
ibq_label_table2 <- ibq_label_df2 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ pct(100)) %>% 
  apply_labtab_theme()

# Print the table
print(ibq_label_table2)
```

#### Survey Items

All IBQ variables have the same response options.

```{r ibq-var-prep}
# Pull question wording from qualtrics data
ibq_word <- qualtrics %>% 
  select(starts_with("ibq"))%>%
  slice(1)

#create table with variable name, description, and notes
ibq_word_long <- ibq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>%
  mutate(description = if_else(var_name == "ibq10", "Please indicate all types of institutions involved.", description)) %>%
  slice(1:10)
```

```{r ibq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
ibq_gt_table <- gt(ibq_word_long)

# Table-specific formatting (col width, names)
ibq_gt_table <- ibq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_options(table.width = pct(100))%>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(ibq_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below.
Variables were constructed by summing included items.

```{r ibq df, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
ibq_complete <- complete %>%
  select(
    starts_with("ibq") 
    )
```

```{r ibq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
ibq_alpha <- ibq_complete %>% 
  select(ibq1:ibq9) %>% 
  psych::alpha(check.keys = TRUE)
```



```{r ibq-scale-table, results = 'asis'}
# Create the table as a data frame
ibq_scale_df <- data.frame(
  var_name = c("IBQ Total Score(7)"),
  scale = c("ibq_total"),
  scale_construction = c("`ibq1`, `ibq2`, `ibq3`, `ibq4`, `ibq5`,`ibq6`, `ibp7`"),
  scale_range = c("0-7"), #TODO fill in range 
  alpha = c("")
)

# Create the gt table object
ibq_scale_df <- gt(ibq_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             # alpha = "Alpha"
             ) %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(ibq_scale_df)


```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and
subscale score:
<TODO: Maria: please review this table and see if there are anything you want me remove from this table>
```{r ibq-mean-items}
# Calculate the summary statistics for each variable
ibq_summary_data <- lapply(ibq_complete, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
ibq_summary_data <- as.data.frame(ibq_summary_data)

# Set items as first row
ibq_summary_data <- rbind(names(ibq_summary_data), ibq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
ibq_tbl <- ibq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ pct(100)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
ibq_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r ibq-distributions, class.source='fold', echo = FALSE}
ibq_complete %>%
  composite_hist(
    x = ibq_total,
    bins = 15
  ) +
  labs(title = "Distribution for IBQ Total Score ")

```


