---
title: "Turning Points Codebook"
# author: 
#   - name: "Maria L. Schweer-Collins, PhD"
#     email: "mschweer@uoregon.edu"
#     affiliations:
#       - name: 'University of Oregon'
#         city: 'Eugene'
#         state: 'OR'
#   - name: "Shaina Trevino, PhD"
#     email: "strevino@uoregon.edu"
#   - name: "Jonathan A. Pedroza, PhD"
#     email: "cpppedroza@gmail.com"
#   - name: "Min Zhang"
date: "2023-07-31"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    #html#toc_title: Contents
    #number_sections: true
    #html#number_depth: 3
    #qmd#colorlinks: true
    #keep_tex: yes
    #pdf#latex_engine: pdflatex
    #error#includes: 
      #error#in_header: styles.css
#pdf#geometry: landscape
bibliography: tpw_references.bib
---

TODO: double check codebook_fun.r composite_total_avg_fun

```{r setup, include = FALSE}
library(tidyverse)
library(here)
library(gt)
library(ggplot2)
library(scales)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE)

theme_set(theme_light())

#import included survey items
data <- read_csv(here("do_not_push", "tpw_data_77included.csv"))

#import df of calculated survey items
complete_rnd2 <- read_csv(here("do_not_push", "round_two_measures_data_calc.csv"))

#import first "complete" file
complete <- read_csv(here("do_not_push","tpw_data_calculated.csv"))

#import raw qualtrics data for parsing question text
qualtrics <- read_csv(here("do_not_push", "tpw_raw_qualtrics_5-30-23.csv"))

source(here("functions", "codebook_fun.R"))
```

```{r plot-style, echo=FALSE}
# Color palettes 
 Two_color = c("#246B69", "#604C41")

# Histogram style 
# hist_style <- geom_histogram(bins=20, color = "white", fill = "#246B69", alpha = 0.7)


bar_style <- geom_bar(color = "white", fill = "#246B69", alpha = 0.7)

THEME <-     theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),legend.key = element_rect(fill = "White", colour = "transparent"),plot.title = element_text(size= 13),
    )
```

# Overview

*<MARIA>INSERT BRIEF INFO ON STUDY, SAMPLE, AND AIMS*

*Additional info to possibly include: global missing data info, links to supplemental materials, any disclaimers/info we think data users need to know to use these data accurately*

*<SHAINA>INSERT BRIEF DESCRIPTION OF DATA/CODEBOOK LAYOUT/FILE STRUCTURE (can complete once we have more sections and overall structure)*

### Missing Data Rule

-   For scales with [10 or more items]{.underline}, a composite score (average/total) is computed for each participant that have less than [20%]{.underline} of the items from that measure missing

-   For scales with [7 to 9 items]{.underline}, a composite score (average/total) is computed for each participant that have less than [30%]{.underline} of the items from that measure missing

-   For scales with [3 to 6 items]{.underline}, a composite score (average/total) is computed for each participant that have less than [33%]{.underline} of the items from that measure missing

-   For scales with [only 2 items]{.underline}, composite scores (average/total) are calculated on a [case by case basis]{.underline}

*<MARIA>INSERT REFERENCE LINK (from JP?)*

# Mental Health Measures

*<MARIA>INSERT BRIEF DESCRIPTION ABOUT CONSTRUCT DOMAIN (why distinct from others)*

## Brief Symptom Inventory (BSI)

### BSI Description

The BSI is a brief self-report scale used to assess psychological symptoms in adolescents and adults.

For the present study, 19 items from the BSI were collected in order to calculate the Somatization, Anxiety, and Depression subscales. 

Item numbers in this data set may not match original item numbers from the BSI exactly *<MARIA> is this correct - what other info do we need to include about mismatch between ours and original measure?*

No items need to be reverse scored. Higher scores indicate more severe mental health symptoms. 

The missing data rule was not applied since there are no missing data among BSI variables. 

Reference: [@derogatis1983brief](https://www.cambridge.org/core/journals/psychological-medicine/article/abs/brief-symptom-inventory-an-introductory-report/307F805810B165ED58581E355F24329F); [DOI](https://doi.org/10.1017/S0033291700048017)

### BSI Variables

#### Value Labels

All BSI variables have the same response options.

```{r gt-theme-general}

apply_tbl_theme <- function(table) {
  table %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_fill(color = "#9BB6D1")),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white")%>% 
  tab_options(table.align = "left")
}

#theme for value label tables
apply_labtab_theme <- function(table) {
  table %>% 
  cols_align(columns = everything(), align = "center") %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_fill(color = "#9BB6D1")),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white") %>% 
  tab_options(table.align = "left")
}
  
```

```{r BSI-label-table, results = 'asis'}

bsi_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("Not at all",
            "A little bit",
            "Moderately",
            "Quite a bit",
            "Very much")
) %>% 
  t() %>% 
  as.data.frame()

bsi_label_df <- setNames(bsi_label_df[-1, ], unlist(bsi_label_df[1, ]))


#create table
bsi_label_table <- bsi_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(bsi_label_table)


```


#### Survey Items

BSI survey items are presented in the following table:

```{r BSI-var-prep}
# Pull question wording from qualtrics data
bsi_word <- qualtrics %>% 
  select(starts_with("BSI")) %>% 
  slice(1)

#create table with variable name, description, and notes
bsi_word_long <- bsi_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  slice(1:19)

```


```{r BSI-var-table, results ='asis'}
# Create the gt table object and apply generic theme
my_gt_table <- gt(bsi_word_long)

# Table-specific formatting (col width, names)
my_gt_table <- my_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(my_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```


#### Scale and Subscales

Information on the total score and subscale variables are below. Variables were constructed by summing included items. 

```{r bsi alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
bsi_alpha <-
  complete %>%
  select(bsi1:bsi19) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_som <-
  complete %>%
  select(bsi2:bsi3,
         bsi10:bsi13,
         bsi15) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_anx <-
  complete %>%
  select(bsi1, bsi5, bsi9, bsi16:bsi18) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_dep <-
  complete %>%
  select(bsi4, bsi6:bsi8, bsi14, bsi19) %>%
  psych::alpha(check.keys = TRUE)

```

```{r BSI-scale-table, results = 'asis'}
# Create the table as a data frame
bsi_scale_df <- data.frame(
  var_name = c("bsi_total", "bsi_soma_total", "bsi_anx_total", "bsi_dep_total"),
  scale = c("Total Score (19)", "Somatization (7)", "Anxiety (6)", "Depression (6)"),
  scale_construction = c("`bsi1`, `bsi2`, `bsi3`, `bsi4`, `bsi5`, `bsi6`, `bsi7`, `bsi8`, `bsi9`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi14`, `bsi15`, `bsi16`, `bsi17`, `bsi18`, `bsi19`",
                           "`bsi2`, `bsi3`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi15`",
                           "`bsi1`, `bsi5`, `bsi9`, `bsi16`, `bsi17`, `bsi18`",
                           "`bsi4`, `bsi6`, `bsi7`, `bsi8`, `bsi14`, `bsi19`"),
  scale_range = c("0-76", "0-28", "0-24", "0-24"),
  alpha = c(round(bsi_alpha$total$raw_alpha, 3), round(bsi_alpha_som$total$raw_alpha, 3), round(bsi_alpha_anx$total$raw_alpha, 3), round(bsi_alpha_dep$total$raw_alpha, 3))
)

# Create the gt table object
bsi_scale_table <- gt(bsi_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(bsi_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score:

```{r bsi-mean-items}
# Create subset of BSI items
data_subset <- complete %>%
  select(bsi1:bsi19, bsi_total, bsi_soma_total, bsi_anx_total, bsi_dep_total)

# Calculate the summary statistics for each variable
summary_data <- lapply(data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_data <- as.data.frame(summary_data)

# Set items as first row
summary_data <- rbind(names(summary_data), summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
tbl <- summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
tbl

```


#### Distributions

Distributions are presented below for the total score and each subscale:

```{r bsi-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(x = bsi_total) +
  labs(title = 'Distribution of Total Scores for BSI Measure')


complete %>%
  composite_hist(x = bsi_soma_total) +
  labs(title = 'Distribution for BSI Somatization Subscale')

complete %>%
  composite_hist(x = bsi_anx_total) +
  labs(title = 'Distribution for BSI Anxiety Subscale')

complete %>%
  composite_hist(x = bsi_dep_total) +
  labs(title = 'Distribution for BSI Depression Subscale')

```


## Center for Epidemiologic Studies Depression Scale (CES-D)

### CES-D Description

The CES-D is self-report scale used to assess major dimensions of depression. 

All 20 items from the CES-D were collected and two subscales were calculated: positive affect and depressive symptoms. Four items (`c4`, `c8`, `c12`, and `c16`) should be reverse scored which is noted in the variable table below and the reverse scored variables are provided (`c4_r`, `c8_r`, `c12_r`, and `c16_r`). Higher scores indicate the presence of more symptoms.

Four additional variables (`c21`-`c24`) were included in this section to assess suicidality. Variables `c22` and `c23` are only applicable if participants responded "Yes" to `c21`.  

The missing data rule was not applied since all participants had less than 20% missing data. Missing data for each variable is presented in the descriptive statistics table below. 

Reference: [@radloff1977ces](https://journals.sagepub.com/doi/abs/10.1177/014662167700100306); [DOI](https://doi.org/10.1177%2F014662167700100306)

-   Additional References:

    -   Cutoff Information:  [@henry2018determining](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4); [DOI](https://doi.org/10.1016/j.jad.2018.02.071)

    -   Items for Potential Subscales:  [@canady2009measurement](https://connect.springerpub.com/content/sgrjnm/17/2/91.abstract); [DOI](10.1891/1061-3749.17.2.91)
    
### CES-D Variables

#### Value Labels

All CES-D survey items (`c1`-`c20`) have the same response options.

```{r CESD-label-table, results = 'asis'}

cesd_label_df <- data.frame(
  value = c("0", "1", "2", "3"),
  label = c("Rarely or none of the time",
            "Some or a little of the time",
            "Occasionally or a moderate amount of time",
            "Most or all of the time")
) %>% 
  t() %>% 
  as.data.frame()

cesd_label_df <- setNames(cesd_label_df[-1, ], unlist(cesd_label_df[1, ]))


#create table
cesd_label_table <- cesd_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(cesd_label_table)


```

Additional variables on suicidality (`c21`-`c24`) share the same response options.
    
```{r CESD-label-table2, results = 'asis'}

cesd2_label_df <- data.frame(
  value = c("0", "1", "2"),
  label = c("No",
            "Yes",
            "Declined to Answer")
) %>% 
  t() %>% 
  as.data.frame()

cesd2_label_df <- setNames(cesd2_label_df[-1, ], unlist(cesd2_label_df[1, ]))


#create table
cesd2_label_table <- cesd2_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(150)) %>% 
  apply_labtab_theme() 

# Print the table
print(cesd2_label_table)


```

#### Survey Items

All CES-D survey items are presented in the following table:

```{r CESD-var-prep}
# Pull question wording from qualtrics data
cesd_word <- qualtrics %>% 
  select(C1:C24) %>% 
  slice(1)

#create table with variable name, description, and notes
cesd_word_long <- cesd_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         #description = case_when(var_name == "c21" ~ "In the past 6 months, have you ever thought about killing yourself?"),
         notes = case_when(var_name == "c4" ~ "This item should be reverse scored. `c4_r` is reverse scored",
                           var_name == "c8" ~ "This item should be reverse scored. `c8_r` is reverse scored",
                           var_name == "c12" ~ "This item should be reverse scored. `c12_r` is reverse scored",
                           var_name == "c16" ~ "This item should be reverse scored. `c16_r` is reverse scored",
                           
                           var_name %in% c("c22", "c23") ~ "Skipped if `c21` = No",
                           TRUE ~ as.character(""))) %>%
  mutate(description = if_else(var_name == "c21", "In the past 6 months, have you ever thought about killing yourself?", description))
  

```


```{r CESD-var-table, results ='asis'}
# Create the gt table object and apply generic theme
cesd_gt_table <- gt(cesd_word_long)

# Table-specific formatting (col width, names)
cesd_gt_table <- cesd_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(250),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(cesd_gt_table)

```


#### Scale and Subscales

Information on the aggregated scale and subscale variables are below. Total and subscale variables were constructed by summing corresponding items. 

```{r cesd-alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
cesd_alpha <-
  complete %>%
  select(c1:c16_r) %>%
  psych::alpha(check.keys = TRUE)

cesd_dep_alpha <-
  complete %>%
  select(c1:c20) %>%
  psych::alpha(check.keys = TRUE)

cesd_pos_aff_alpha <-
  complete %>%
  select(c4_r, c8_r, c12_r, c16_r) %>%
  psych::alpha(check.keys = TRUE)


cesd_alpha_table <- tibble(
  Scale = c('CESD', 'CESD - Depressive Symptoms',
            'CESD - Positive Affect'),
  Alpha = c(round(cesd_alpha$total$raw_alpha, 3),
            round(cesd_dep_alpha$total$raw_alpha, 3),
            round(cesd_pos_aff_alpha$total$raw_alpha, 3)
  )
)
```

```{r CESD-scale-table, results = 'asis'}
# Create the table as a data frame
# TODO: should the calculation use revers score?
cesd_scale_df <- data.frame(
  var_name = c("cesd_total", "cesd_dep_symp_total", "cesd_pos_aff_total"),
  scale = c("Total Score (20)", "Depression (16)", "Positive Affect (4)"),
  scale_construction = c("`c1`, `c2`, `c3`, `c4`, `c5`, `c6`, `c7`, `c8`, `c9`, `c10`, `c11`, `c12`, `c13`, `c14`, `c15`, `c16`, `c17`, `c18`, `c19`, `c20`",
                           "`c1`, `c2`, `c3`, `c5`, `c6`, `c7`, `c9`, `c10`, `c11`, `c13`, `c14`, `c15`, `c17`, `c18`, `c19`, `c20`",
                           "`c4_r`, `c8_r`, `c12_r`, `c16_r`"),
  scale_range = c("0-60", "0-48", "0-12"),
  alpha = c(round(cesd_alpha$total$raw_alpha, 3), round(cesd_dep_alpha$total$raw_alpha, 3), round(cesd_pos_aff_alpha$total$raw_alpha, 3))
)

# Create the gt table object
cesd_scale_table <- gt(cesd_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme()

# Print the table
print(cesd_scale_table)

```


### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score:

```{r cesd-mean-items}
# Create subset of CESD items
data_subset_cesd <- complete %>%
  select(c1:c3, c4, c5:c7, c8, c9:c11, c12, c13:c15, c16, c17:c20, cesd_total, cesd_dep_symp_total, cesd_pos_aff_total)

# Calculate the summary statistics for each variable
summary_data_cesd <- lapply(data_subset_cesd, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- sprintf("%.2f", round(sd(x, na.rm = TRUE), 2))
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_df_cesd <- as.data.frame(summary_data_cesd) %>% 
  rbind(names(summary_data_cesd)) %>% 
  t() %>% 
  as.data.frame() %>% 
  select(`5`, everything())

# Create the gt table
cesd_tbl <- summary_df_cesd %>%
  gt() %>%
  cols_label(`5` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(2:5 ~ px(160)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
cesd_tbl

```
    
#### Distributions

Distributions are presented below for the total score and each subscale:

```{r cesd-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(cesd_total) +
  labs(
    title = 'CESD Total Score Distribution'
    )

complete %>%
  composite_hist(
    cesd_dep_symp_total
    ) +
  labs(
    title = 'Depressive Symptoms Subscale Distribution'
    )

complete %>%
  composite_hist(
    cesd_pos_aff_total,
    bins = 10
    ) +
  labs(
    title = 'Positive Affect Subscale Distribution'
    )
```

#### Clinical Categories

The distribution for CES-D scores alongside clinical cutoffs are presented below.

*<MARIA>INSERT MORE INFO ON 16/23 CUTOFF SCORES - what are they (what should plot labels be)?, how should they be used*

Reference: [@henry2018determining](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4); [DOI](https://doi.org/10.1016/j.jad.2018.02.071)

```{r cutoff-plot-function}
#re-work JP cutoff function due to error "cant use `{{` in non-quoting function
cutoff_plot2 <- function(data,
                        x,
                        cutoff = 0,
                        cutoff_color = '#324B4A',
                        cutoff_other = NULL,
                        cutoff_other_color = '#95B1AF',
                        cutoff_other2 = NULL,
                        cutoff_other2_color = '#546085',
                        bins = 20) {

  library(magrittr)
  library(dplyr)
  library(ggplot2)

  x <- enquo(x)

  if (is.null(cutoff_other)) {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = '#246B69',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 20),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  } else if (is.null(cutoff_other2)) {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = '#246B69',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other,
                 color = cutoff_other_color,
                 linetype = 3,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 13),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  } else {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = 'black',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other,
                 color = cutoff_other_color,
                 linetype = 3,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other2,
                 color = cutoff_other2_color,
                 linetype = 4,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 13),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  }
}
```


```{r cesd-clinical}
complete %>%
  cutoff_plot2(
    x = cesd_total,
    cutoff = 16,
    cutoff_other = 23
  ) +
  labs(
    title = 'Cutoff Scores for CESD Total Scores',
    caption = 'Cutoffs are 16 and/or 23\nSee references for literature on cutoff scores.', 
    y = "Number of Participants"
  ) +
  geom_text(aes(x = 16, y = 16.5, label = "cutoff1", vjust = -.25, hjust = 1.2)) + ###MARIA INSERT CUTOFF LABEL
  geom_text(aes(x = 16, y = 16.5, label = "cutoff2", vjust = -.25, hjust = -1.8))  ##MARIA INSERT CUTOFF LABEL
```


## Coronavirus Impacts Questionnaire (CIQ)

### CIQ Description

The CIQ is self-report survey used to assess the financial, resource, and psychological impacts of COVID-19. 
  
For the present study, 3 items from the CIQ were collected in order to construct the psychological impacts scale.

`ciq1` need to be reverse scored. Higher scores indicate increased psychological impacts of COVID-19. 

The missing data rule was not applied since there is no missing data among CIQ variables. 

Reference: [@conway2020social](https://psyarxiv.com/z2x9a/)


### CIQ Variables

#### Value Labels

All CIQ variables have the same response options.

```{r ciq-label-table, results = 'asis'}

ciq_label_df <- data.frame(
  value = seq(1:7),
  label = c("Not true of me at all",
            "",
            "",
            "",
            "",
            "",
            "Very true of me")) %>% 
  t() %>% 
  as.data.frame()

ciq_label_df <- setNames(ciq_label_df[-1, ], unlist(ciq_label_df[1, ]))


#create table
ciq_label_table <- ciq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(c(1,7) ~ px(180),
             2:6 ~ px(79)) %>% 
  apply_labtab_theme()

# Print the table
print(ciq_label_table)


```

#### Survey Items

All CIQ survey items are presented in the following table:

```{r ciq-var-prep}
# Pull question wording from qualtrics data
# ciq is from BIS question 20-22
ciq_word <- qualtrics %>% 
  select(starts_with("BSI")) %>% 
  slice(1)

#create table with variable name, description, and notes
ciq_word_long <- ciq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name),
         notes = case_when(var_name == "bsi22" ~ "This item should be reverse scored. `ciq3_r` is reverse scored",
                           TRUE ~ as.character("")
                           )) %>% 
  mutate(description = if_else(var_name == "bsi20", "I have become depressed because of the Coronavirus (COVID-19).", description)) %>%
  mutate(var_name = case_when(var_name == "bsi20" ~ "ciq1",
                              var_name == "bsi21" ~ "ciq2",
                              var_name == "bsi22" ~ "ciq3",
                              TRUE ~ var_name)) %>% 
  slice(20:22)

```


```{r ciq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
ciq_gt_table <- gt(ciq_word_long)

# Table-specific formatting (col width, names)
ciq_gt_table <- ciq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(ciq_gt_table)

#WHEN RENDERING WITH PDF USE: 
#ciq_gt_table
```


#### Scale and Subscales

Information on the total score and subscale variables are below. Variables were constructed by summing included items. 


```{r ciq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
ciq_alpha <-
  complete %>%
  select(ciq1:ciq3_r) %>%
  psych::alpha(check.keys = TRUE)

```

```{r ciq-scale-table, results = 'asis'}
# Create the table as a data frame
ciq_scale_df <- data.frame(
  var_name = c("ciq_psych_total"),
  scale = c("Total Score (3)"),
  scale_construction = c("`ciq1`, `ciq2`, `ciq3_r`"),
  scale_range = c("3-21"),
  alpha = c(round(ciq_alpha$total$raw_alpha, 3))
)

# Create the gt table object
ciq_scale_table <- gt(ciq_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(151)) %>% 
  apply_tbl_theme() 

# Print the table
print(ciq_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and the total score:

```{r ciq-mean-items}
# Create subset of BSI items
ciq_data_subset <- complete %>%
  select(ciq1:ciq2, ciq3, ciq_psych_total)

# Calculate the summary statistics for each variable
ciq_summary_data <- lapply(ciq_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
ciq_summary_data <- as.data.frame(ciq_summary_data)

# Set items as first row
ciq_summary_data <- rbind(names(ciq_summary_data), ciq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
ciq_tbl <- ciq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(130)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
ciq_tbl

```


#### Distributions

The distribution for the total score is presented below:

```{r csi-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(
    x = ciq_psych_total,
    bins = 10
    ) +
  labs(title = 'Distribution for CIQ Psychological Scale')
```


## The Drug Abuse Screening Test (DAST)

### DAST Description

*<MIN/SHAINA>TODO: ROW DATA INCORRECTLY CLEANED, WILL NEED RE_CLEAN!*

```{r dast re-code}
# This session should go together with the data cleaning 

# re-code total score 
# RECODE AWH8DAST (0 = 0) (1 THRU 5 = 1) (6 THRU 10 = 2) (11 THRU 15 = 3) (16 THRU 20 = 4) INTO AWHPDASC
# VALUE LABELS AWHPDASC
# 0 'None'
# 1 'Low'
# 2 'Intermediate (likely meets DSM criteria)'
# 3 'Substantial'
# 4 'Severe'.

complete$dast_total_r <- case_match(complete$dast_total,
                1:5 ~ 1,
                6:10 ~ 2,
                11:15 ~ 3,
                16:20 ~ 4, .default = complete$dast_total)

complete <- complete %>%
  mutate(dast_total_r = case_when(
    dast_total == 0 ~ 0,
    dast_total %in% 1:5 ~ 1,
    dast_total %in% 6:10 ~ 2,
    dast_total %in% 11:15 ~ 3,
    dast_total %in% 16:20 ~ 4,
    TRUE ~ NA_integer_
  ))

```

*<SHAINA> TODO: CHECK AFTER DATA IS CLEANED*

The DAST is a self-report instrument used to assess problems related to substance use.
  
For the present study, 22 items from the DAST were collected and a total score was constructed. No subscales were created for this measure as there was a lack of evidence supporting a subscale structure.  

Two items (`d4` and `d5`) should to be reverse scored which is noted in the variable table below and the reverse scored variables are provided (`d4_r` and `d5_r`). Higher scores indicate more problems related to substance use.

*<SHAINA> TODO: CONFIRM THIS IS CORRECT AND IF SHOULD BE APPLIED IN TABLES BELOW - specify -77* The missing data rule was applied. Calculations were completed only with participants that had less than 20% missing data (this includes `-77` responses) 

Reference: [@gavin1989diagnostic](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1360-0443.1989.tb03463.x);[DOI](https://doi.org/10.1111/j.1360-0443.1989.tb03463.x)


### DAST Variables

#### Value Labels

All The Drug Abuse Screening Test variables have the same response options.

```{r DAST-label-table, results = 'asis'}

dast_label_df <- data.frame(
  value = c(0,1),
  label = c("Yes ",
            "No")) %>% 
  t() %>% 
  as.data.frame()

dast_label_df <- setNames(dast_label_df[-1, ], unlist(dast_label_df[1, ]))


#create table
dast_label_table <- dast_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(c(1,2) ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(dast_label_table)


```

*<MARIA> TODO: CONFIRM THIS TABLE SHOULD BE INCLUDED AND WHAT VARIABLES THEY APPLY TO*
Recoded total value label 

```{r DAST-label-table-total, results = 'asis'}

dast_label_total <- data.frame(
  value = seq(0,4),
  label = c("None",
            "Low",
            "Intermediate (likely meets DSM criteria)",
            "Substantial",
            "Severe")) %>% 
  t() %>% 
  as.data.frame()

dast_label_total <- setNames(dast_label_total[-1, ], unlist(dast_label_total[1, ]))


#create table
dast_label_table_total <- dast_label_total %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(c(1:5) ~ px(151)) %>% 
  apply_labtab_theme()

# Print the table
print(dast_label_table_total)


```

#### Survey Items

All DAST survey items are presented in the following table:

```{r DAST-var-prep}
# Pull question wording from qualtrics data
dast_word <- qualtrics %>% 
  select(starts_with("D")) %>% 
  slice(1)

#create table with variable name, description, and notes
dast_word_long <- dast_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name),
         notes = case_when(var_name == "d4" ~ "This item should be reverse scored. `d4_r` is reverse scored",
                           var_name == "d5" ~ "This item should be reverse scored. `d4_r` is reverse scored",
                           TRUE ~ as.character("")
                           )
         ) %>% 
  mutate(description = if_else(var_name == "d00", "Is TC currently pregnant?", description)) %>%
  slice(4:25)

```



```{r dast-var-table, results ='asis'}
# Create the gt table object and apply generic theme
dast_gt_table <- gt(dast_word_long)

# Table-specific formatting (col width, names)
dast_gt_table <- dast_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())
 

# Print the table
print(dast_gt_table)

#WHEN RENDERING WITH PDF USE: 
#dast_gt_table
```


#### Scale and Subscales

Information on the total score is below. The total score was constructed by summing all items. 

```{r dast alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
dast_alpha <-
  complete %>%
  select(d1a:d3, d6:d5_r) %>%
  mutate(d2 = coalesce(d2a, d2b)) %>% 
  select(-d2a, -d2b) %>% 
  drop_na(d2) %>% 
  psych::alpha(check.keys = TRUE)

```

*<MIN> DATA CLEANING TODO: need check the total *

```{r DAST-scale-table, results = 'asis'}
# Create the table as a data frame
dast_scale_df <- data.frame(
  var_name = c("dast_total"),
  scale = c("Total Score (22)"),
  scale_construction = c("`d00`, `d1a`, `d2a`, `d2b`, `d3`, `d4_r`, `d5_r`, `d6`, `d7`, `d8`, `d9`, `d10`, `d11`, `d12`, `d13`, `d14`, `d15`, `d16`, `d17`, `d18`, `d19`, `d20`"),
  scale_range = c("0-20"),
  alpha = c(round(dast_alpha$total$raw_alpha, 3))
)

# Create the gt table object
dast_scale_table <- gt(dast_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(dast_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and the total score.

For binary items: 

```{r dast-binary-desc}
# Create subset of DAST items
dast_data_subset_binary <- complete %>%
  select(d1a:d3, d6:d5_r)

# Calculate the dichotomous summary statistics for each variable
dast_summary_data_binary <- lapply(dast_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dast_summary_data_binary <- as.data.frame(dast_summary_data_binary)

# Set items as first row
dast_summary_data_binary <- rbind(names(dast_summary_data_binary), dast_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dast_tbl_binary <- dast_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "No", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Yes", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
dast_tbl_binary


```

For the total score: 

```{r dast-cont-desc}
# Create subset of DAST items
dast_data_subset <- complete %>%
  select(dast_total)

# Calculate the dichotomous summary statistics for each variable
dast_summary_data <- lapply(dast_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dast_summary_data <- as.data.frame(dast_summary_data) 

# Set items as first row
dast_summary_data <- rbind(names(dast_summary_data),dast_summary_data) %>% 
  t() %>% 
  as.data.frame() %>%
  mutate(Mean = if_else(Mean == "NaN", "NA", Mean)) %>%
  mutate(Range = if_else(Range == "Inf--Inf", "NA", Range))

 



# Create the gt table
dast_tbl <- dast_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
dast_tbl

```


#### Distributions

The distribution for the total score is presented below:

*<MIN> TODO: ADD DISTRIBUTION PLOT FOR TOTAL DAST SCORE HERE*

#### Clinical Categories

The distribution for the total score alongside clinical severity categories are presented below.

*<MARIA>INSERT MORE INFO ON SEVERITY CUTOFF SCORES - what do they categorize?, how should they be used*

Reference: *<SHAINA/MARIA> INSERT REFERENCE FOR DAST SCORES - MARIA, WHAT IS REFERENCE?*

```{r dast-distributions, class.source='fold', echo = FALSE}
complete %>%
  severity_plot(
  x = dast_total,
  bins = 20,
  low_xmin = 0,
  low_xmax = 5.5,
  medium_xmin = 5.5,
  medium_xmax = 10.5,
  large_xmin = 10.5,
  large_xmax = 15.5,
  critical_xmin = 15.5,
  critical_xmax = 20) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 3,
    y = -1.5,
    label = 'Low'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 8,
    y = -1.5,
    label = 'Intermediate'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 13,
    y = -1.5,
    label = 'Substantial'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 18,
    y = -1.5,
    label = 'Severe'
  ) +
  labs(
    title = 'Severity Categories',
    subtitle = 'Based on DAST',
    caption = 'Cutoffs are:\nLow = 1-5,\nIntermediate = 6-10,\nSubstantial = 11-15,\nSevere = 16-20',
    y = 'Number of Participants'
  )
```


## Conflict Tactics Scales (CTS)

### CTS Description

The CTS is a self-report measure used to assess tactics used when there is conflict in a relationship.

For the present study, all 20 items from the CTS short form were collected, and all scales (Negotiation, Physical Assault, and Psychological Aggression) and supplemental scales (Assault and Sexual Coercion) were calculated. 

Authors describe that internal reliability is not appropriate for the CTS measure. CTS should not have a calculated total/average composite score. Instead, CTS has three different ways of scoring (Prevalence, Severity, Mutuality). 

No items need to be reverse scored. *<MARIA> TODO: How to word directionality with current values/labels. (e.g., Higher scores indicate ..." *

*<SHAINA> TODO: CONFIRM & CHECK CALC CODE* The missing data rule was applied. Calculations were completed only with participants that had less than 20% missing data (this includes `-77` responses)

Reference: [@straus2004short](https://connect.springerpub.com/content/sgrvv/19/5/507.abstract); [DOI](10.1891/vivi.19.5.507.63686)

### CTS Variables

#### Value Labels

All CTS variables have the same response options.

```{r CTS-label-table, results = 'asis'}

CTS_label_df <- data.frame(
  value = c( "1", "2", "3", "4", "5", "6", "7", "8"),
  label = c("Once in the past year",
            "Twice in the past year",
            "3-5 times in the past year",
            "6-10 times in the past year",
            "11-20 times in the past year",
            "More than 20 times in the past year", 
            "Not in the past year, but it did happen before", 
            "This has never happened")
) %>% 
  t() %>% 
  as.data.frame()

CTS_label_df <- setNames(CTS_label_df[-1, ], unlist(CTS_label_df[1, ]))


#create table
CTS_label_table <- CTS_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(100)) %>% 
  apply_labtab_theme()

# Print the table
print(CTS_label_table)


```

#### Survey Items

All CTS survey items are presented in the following table:

```{r CTS-var-prep}
# Pull question wording from qualtrics data
CTS_word <- qualtrics %>% 
  select(starts_with("CT")) %>% 
  slice(1)

#create table with variable name, description, and notes
CTS_word_long <- CTS_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  mutate(description = if_else(var_name == "ct0", "Have you lived with any other children, under the age of 17, since the time of your last interview? Only think about children who you or your partner was responsible for parenting. Please do not include any children listed in the other sections or children that you have reported before.", 
                               if_else(var_name == "ct000", "How many new children are you parenting since your last interview on (last interview date)?",
                                       if_else(var_name ==  "cts screen", "Have you been in a (romantic) relationship in the past year?",
                                               if_else(var_name == "cts parent screen", "Have you parented a child (under 18) in the past year?", description))))
  ) %>%
  slice(1:26)

```


```{r CTS-var-table, results ='asis'}
# Create the gt table object and apply generic theme
my_gt_table <- gt(CTS_word_long)

# Table-specific formatting (col width, names)
my_gt_table <- my_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(my_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on total score and subscale variables are below. Prevalence scales are calculated ... *<MARIA> INSERT INFO ON COMPOSITE SCORE CREATION*. Severity scores are calculated ... *<MARIA> INSERT INFO ON COMPOSITE SCORE CREATION*. Mutuatlity scores are created by ... *<MARIA> INSERT INFO ON COMPOSITE SCORE CREATION* 

*<SHAINA/MIN> TODO: NEED fill Range once we understand how composite scores were created*

```{r CTS-scale-table, results = 'asis'}
# Create the table as a data frame
CTS_scale_df <- data.frame(
  var_name = c("cts_psy_agg_ind_sev", "cts_injury_ind_sev", "cts_assault_ind_sev",   "cts_sex_ind_sev",       #TC   severity 
                "cts_psy_agg_part_sev","cts_injury_part_sev", "cts_assault_part_sev","cts_sex_part_sev",      #Partner serverity 

                "cts_psy_agg_ind_prev", "cts_injury_ind_prev", "cts_assault_ind_prev", "cts_sex_ind_prev", 
                "cts_psy_agg_part_prev", "cts_injury_part_prev", "cts_assault_part_prev", "cts_sex_part_prev",
               
                "cts_psy_agg_mutual", "cts_injury_mutual", "cts_assault_mutual", "cts_sex_mutual",
               
                "cts_negotiate_ind",    "cts_negotiate_part"),

  scale = c("TC Psychological Aggression (2)", "TC Physical Injury (2)", "TC Assault (2)", "TC Sexual Cohesion (2)",
            "Partner Psychological Aggression (2)", "Partner Physical Injury (2)", "Partner Assault (2)", "Partner Sexual Cohesion (2)",

            "TC Psychological Aggression (2)", "TC Physical Injury (2)", "TC Assault (2)", "TC Sexual Cohesion (2)",
            "Partner Psychological Aggression (2)", "Partner Physical Injury (2)", "Partner Assault (2)", "Partner Sexual Cohesion (2)",
            
            "Psychological Aggression (4)", "Physical Injury (4)", "Assaul (4)t", "Sexual Cohesion (4)",
            
            "TC Negotiation (2)", "Partner Negotiation (2)"
            ),
  score_method = c("Severity", "Severity", "Severity", "Severity",
                   "Severity", "Severity", "Severity", "Severity",
                   "Prevalence", "Prevalence", "Prevalence", "Prevalence", 
                   "Prevalence", "Prevalence", "Prevalence", "Prevalence", 
                   "Mutuality", "Mutuality", "Mutuality", "Mutuality",
                   "", ""
                   ),

  scale_construction = c("`ct3`, `ct13`", "`ct5`, `ct15`", "`ct9`, `ct11`", "`ct17`, `ct19`", 
                         "`ct4`, `ct14`", "`ct6`, `ct16`", "`ct10`, `ct12`", "`ct18`, `ct20`", 
                         
                         "`ct3`, `ct13`", "`ct5`, `ct15`", "`ct9`, `ct11`", "`ct17`, `ct19`", 
                         "`ct4`, `ct14`", "`ct6`, `ct16`", "`ct10`, `ct12`", "`ct18`, `ct20`",
                         
                         "`ct3`, `ct13`, `ct4`, `ct14`","`ct5`, `ct15`, `ct6`, `ct16`",
                         "`ct9`, `ct11`, `ct10`, `ct12`", "`ct17`, `ct19`, `ct18`, `ct20`",
                         
                         "`ct1`, `ct7`", "`ct2`, `ct8`"
                         
                         ),
  scale_range = c("", "", "", "", "", "", "", "", "", "",
                  "", "", "", "", "", "", "", "", "", "", 
                  "", "")
  )


# Create the gt table object
CTS_scale_table <- gt(CTS_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            score_method = "Score Method",
            scale_construction = "Scale Construction",
            scale_range = "Range*") %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale ~ px(200)) %>% 
  apply_tbl_theme() 

# Print the table
print(CTS_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and subscale score:

```{r CTS-mean-items}
# Create subset of CTS items
cts_data_subset <- complete %>%
  select(ct1:ct20, starts_with("cts"))

# Calculate the summary statistics for each variable
cts_summary_data <- lapply(cts_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert cts2_summary_data to a data frame
cts_summary_data <- as.data.frame(cts_summary_data)

# Set items as first row
cts_summary_data <- rbind(names(cts_summary_data), cts_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
cts_tbl <- cts_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(
    c(2,3,5) ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

   
# Render the table
cts_tbl

```

#### Distributions

Distributions are presented below for each subscale

##### Severity distributions 

```{r CTS-Severity-TC-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
complete %>%
  mutate(
    cts_psy_agg_ind_sev = case_when(
      cts_psy_agg_ind_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_ind_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_ind_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_ind_sev = as.factor(cts_psy_agg_ind_sev),
    cts_psy_agg_ind_sev = relevel(cts_psy_agg_ind_sev, 'No Psychological Aggression')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Individual (TC) Psychological Aggression Severity',
       y = "Number of Participants") + 
  THEME


# Psychical Injury 
complete %>%
  mutate(
    cts_injury_ind_sev = case_when(
      cts_injury_ind_sev == 0 ~ 'No Injury',
      cts_injury_ind_sev == 1 ~ 'Minor Injury',
      cts_injury_ind_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_ind_sev = as.factor(cts_injury_ind_sev),
    cts_injury_ind_sev = relevel(cts_injury_ind_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_ind_sev
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Individual (TC) Physical Injury Severity',
       y = "Number of Participants") + 
  THEME

# Assault 
complete %>%
  mutate(
    cts_assault_ind_sev = case_when(
      cts_assault_ind_sev == 0 ~ 'No Assault',
      cts_assault_ind_sev == 1 ~ 'Minor Assault',
      cts_assault_ind_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_ind_sev = as.factor(cts_assault_ind_sev),
    cts_assault_ind_sev = relevel(cts_assault_ind_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_ind_sev
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Individual (TC) Assault Severity',
       y = 'Number of Participants') +
  THEME

# Sexual Cohesion
complete %>%
  mutate(
    cts_sex_ind_sev = case_when(
      cts_sex_ind_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_ind_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_ind_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_ind_sev = as.factor(cts_sex_ind_sev),
    cts_sex_ind_sev = relevel(cts_sex_ind_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Individual (TC) Sexual Cohesion Severity',
       y = "Number of Participants") + 
  THEME

```


```{r CTS-Severity-Partner-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
complete %>%
  mutate(
    cts_psy_agg_part_sev = case_when(
      cts_psy_agg_part_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_part_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_part_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_part_sev = as.factor(cts_psy_agg_part_sev),
    cts_psy_agg_part_sev = relevel(cts_psy_agg_part_sev, 'No Psychological Aggression')
    ) %>%
  ggplot(
    aes(
      cts_psy_agg_part_sev
    )
  ) +
  bar_style +
   scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Partner Psychological Aggression Severity',
       y = "Number of Participants") + 
  THEME

# Physical Injury
complete %>%
  mutate(
    cts_injury_part_sev = case_when(
      cts_injury_part_sev == 0 ~ 'No Injury',
      cts_injury_part_sev == 1 ~ 'Minor Injury',
      cts_injury_part_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_part_sev = as.factor(cts_injury_part_sev),
    cts_injury_part_sev = relevel(cts_injury_part_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_part_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Partner Physical Injury Severity',
       y = "Number of Participants") + 
  THEME


# Assault
complete %>%
  mutate(
    cts_assault_part_sev = case_when(
      cts_assault_part_sev == 0 ~ 'No Assault',
      cts_assault_part_sev == 1 ~ 'Minor Assault',
      cts_assault_part_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_part_sev = as.factor(cts_assault_part_sev),
    cts_assault_part_sev = relevel(cts_assault_part_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_part_sev
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Partner Assault Severity',
       y = "Number of Participants") + 
  THEME

# Sexual Cohesion
complete %>%
  mutate(
    cts_sex_part_sev = case_when(
      cts_sex_part_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_part_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_part_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_part_sev = as.factor(cts_sex_part_sev),
    cts_sex_part_sev = relevel(cts_sex_part_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_part_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Partner Sexual Cohesion Severity',
       y = "Number of Participants") + 
  THEME
```

##### Prevalence distributions

*<MIN> TODO NA was removed when generating following Prevalence plot*

```{r CTS-Prevalence-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
complete %>%
  pivot_longer(
    cols = c(cts_psy_agg_ind_prev, cts_psy_agg_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_psy_agg_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_psy_agg_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Psychological Aggression Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Physical Injury
complete %>%
  pivot_longer(
    cols = c(cts_injury_ind_prev, cts_injury_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_injury_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_injury_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Physical Injury Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Assault
complete %>%
  pivot_longer(
    cols = c(cts_assault_ind_prev, cts_assault_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_assault_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_assault_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Assault Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Sexual Cohesion
complete %>%
  pivot_longer(
    cols = c(cts_sex_ind_prev, cts_sex_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_sex_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_sex_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Sexual Cohesion Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME
```

##### Mutuality distributions

```{r CTS-Mutuality-distributions, class.source='fold', echo = FALSE}

# Psychological Aggression 
complete %>%
  mutate(
    cts_psy_agg_mutual = case_when(
      cts_psy_agg_mutual == 0 ~ 'Neither',
      cts_psy_agg_mutual == 1 ~ 'Male Only',
      cts_psy_agg_mutual == 2 ~ 'Female Only',
      cts_psy_agg_mutual == 3 ~ 'Both'
    ),
    cts_psy_agg_mutual = as.factor(cts_psy_agg_mutual),
    cts_psy_agg_mutual = relevel(cts_psy_agg_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Psychological Aggression',
       y = "Number of Participants") +
  THEME



# Physical Injury
complete %>%
  mutate(
    cts_injury_mutual = case_when(
      cts_injury_mutual == 0 ~ 'Neither',
      cts_injury_mutual == 1 ~ 'Male Only',
      cts_injury_mutual == 2 ~ 'Female Only',
      cts_injury_mutual == 3 ~ 'Both'
    ),
    cts_injury_mutual = as.factor(cts_injury_mutual),
    cts_injury_mutual = relevel(cts_injury_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_injury_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Injury',
       y = "Number of Participants") +
  THEME


# Assault
complete %>%
  mutate(
    cts_assault_mutual = case_when(
      cts_assault_mutual == 0 ~ 'Neither',
      cts_assault_mutual == 1 ~ 'Male Only',
      cts_assault_mutual == 2 ~ 'Female Only',
      cts_assault_mutual == 3 ~ 'Both'
    ),
    cts_assault_mutual = as.factor(cts_assault_mutual),
    cts_assault_mutual = relevel(cts_assault_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_assault_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Assault',
       y = "Number of Participants") +
  THEME

# Sexual Cohesion
complete %>%
  mutate(
    cts_sex_mutual = case_when(
      cts_sex_mutual == 0 ~ 'Neither',
      cts_sex_mutual == 1 ~ 'Male Only',
      cts_sex_mutual == 2 ~ 'Female Only',
      cts_sex_mutual == 3 ~ 'Both'
    ),
    cts_sex_mutual = as.factor(cts_sex_mutual),
    cts_sex_mutual = relevel(cts_sex_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_sex_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Sexual Cohesion',
       y = "Number of Participants") +
  THEME
```


## Brief Child Abuse Potential Inventory (BCAP)

### BCAP Description

The BCAP is a self-report inventory used to assess parental child abuse risk.

For the present study, *<SHAINA> CONFIRM* 34 items from the BCAP were collected and *<SHAINA/MARIA> CONFIRM* all 9 subscales were computed: Happiness, Feelings of Persecution, Loneliness, Family Conflict, Rigidity, Distress, Financial Insecurity, Lie, and Random Responding. 

Four items (`q1`, `q2`, `q23`, and `q29`) should be reverse scored which is noted in the variable table below and the reverse scored variables are provided (`q1_r`, `q2_r`, `q23_r`, and `q29_r`). Higher scores on the BCAP indicates increased risk. 

*<SHAINA> CONFIRM>* The missing data rule was applied. Calculations were completed only with participants that had less than 20% missing data (this includes `-77` responses).

Reference: [@ondersma2005brief](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug); 
[DOI](https://doi.org/10.1207/s15374424jccp3402_9)

### BCAP Variables

#### Value Labels

All BCAP variables have the same response options.

```{r BCAP-label-table, results = 'asis'}

bcap_label_df <- data.frame(
  value = c("0", "1"),
  label = c("Disagree",
            "Agree")
) %>% 
  t() %>% 
  as.data.frame()

bcap_label_df <- setNames(bcap_label_df[-1, ], unlist(bcap_label_df[1, ]))


#create table
bcap_label_table <- bcap_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(bcap_label_table)


```

#### Survey Items

All BCAP survey items are presented in the following table:

```{r bcap-var-prep}
# Pull question wording from qualtrics data
bcap_word <- qualtrics %>% 
  select(starts_with("q")) %>% 
  slice(1)

#create table with variable name, description, and notes
bcap_word_long <- bcap_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = case_when(var_name == "q1" ~ "This item should be reverse scored. `q1_r` is reverse scored",
                           var_name == "q2" ~ "This item should be reverse scored. `q2_r` is reverse scored",
                           var_name == "q23" ~ "This item should be reverse scored. `q23_r` is reverse scored",
                           var_name == "q29" ~ "This item should be reverse scored. `q29_r` is reverse scored",
                           
                           var_name %in% c("c22", "c23") ~ "Skipped if `c21` = No",
                           TRUE ~ as.character(""))) %>%
  slice(1:34)


```


```{r bcap-var-table, results ='asis'}
# Create the gt table object and apply generic theme
bcap_gt_table <- gt(bcap_word_long)

# Table-specific formatting (col width, names)
bcap_gt_table <- bcap_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(bcap_gt_table)

#WHEN RENDERING WITH PDF USE: 
#bcap_gt_table
```

#### Scale and Subscales

Information on the total score and subscale variables are below. *<SHAINA/MARIA> INSERT Variables were constructed by ... *

```{r bcap alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
# Total
bcap_alpha <- 
  complete %>% 
  select(
    q1_r,
    q2_r,
    q3:q22,
    q23_r,
    q24:q28,
    q29_r,
    q30:q34
  ) %>% 
  psych::alpha(check.keys = TRUE)

bcap_risk_alpha <-
  complete %>%
  select(
    q1_r,
    q3,
    q5:q8,
    q10:q14,
    q16:q17,
    q19:q20,
    q22,
    q23_r,
    q24:q25,
    q27,
    q29_r,
    q30:q33
    ) %>%
  psych::alpha(check.keys = TRUE)

bcap_happy_alpha <- 
  complete %>% 
  select(q1_r, q23_r, q29_r) %>% 
  psych::alpha(check.keys = TRUE)

bcap_feel_pers_alpha <- 
  complete %>% 
  select(q3, q25, q33) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lonely_alpha <- 
  complete %>% 
  select(q5, q12, q22, q31) %>% 
  psych::alpha(check.keys = TRUE)

bcap_fam_conf_alpha <- 
  complete %>% 
  select(q6, q13, q17) %>% 
  psych::alpha(check.keys = TRUE)

bcap_rigid_alpha <-
  complete %>% 
  select(q7, q14, q20, q32) %>% 
  psych::alpha(check.keys = TRUE)

bcap_distress_alpha <- 
  complete %>% 
  select(q8, q11, q16, q19, q27) %>% 
  psych::alpha(check.keys = TRUE)

bcap_poverty_alpha <- 
  complete %>% 
  select(q10, q30) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lie_alpha <-
  complete %>% 
  select(q4, q9, q15, q21, q26, q34) %>% 
  psych::alpha(check.keys = TRUE)

bcap_random_alpha <-
  complete %>% 
  select(q2_r, q19, q28) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r bcap-scale-table, results = 'asis'}
# Create the table as a data frame
bcap_scale_df <- data.frame(
  var_name = c("bcap_total", "bcap_risk", "bcap_happy_total", "bcap_feel_pers_total", "bcap_lonely_total", "bcap_fam_conf_total", "bcap_rigid_total","bcap_distress_total", "bcap_poverty_total", "bcap_lie_total", "bcap_random_total"),
  scale = c("BCAP complete Scale (34)", "BCAP Risk Scale (26)", "Happiness (3)", "Feelings of persecution", "Loneliness (4)", "Family conflict (3)", "Rigidity (4)", "Distress (5)", "Financial Insecurity (2)", "Lie (6)", "Random responding (3)"),
  scale_construction = c("`q1_r`,`q2_r`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q9`, `q10`, `q11`, `q12`, `q13`, `q14`, `q15`, `q16`, `q17`, `q18`, `q19`, `q20`, `q21`, `q22`, `q23_r`, `q24`, `q25`, `q26`, `q27`, `q28`, `q29_r`, `q30`, `q31`, `q32`, `q33`, `q34`", 
                         "`q1_r`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q10`, `q11`, `q12`, `q13`, `q14`, `q16`, `q17`, `q19`, `q20`, `q22`, `q23_r`, `q24`, `q25`, `q27`, `q29_r`, `q30`, `q31`, `q32`, `q33`", 
                         "`q1_r`, `q23_r`, `q29_r`", 
                         "`q3`, `q25`, `q33`", 
                         "`q5`, `q12`, `q22`, `q31`", 
                         "`q6`, `q13`, `q17`", 
                         "`q7`, `q14`, `q20`, `q32`", 
                         "`q8`, `q11`, `q16`, `q19`, `q27`", 
                         "`q10`, `q30`", 
                         "`q4`, `q9`, `q15`, `q21`, `q26`, `q34`,", 
                         "`q2`, `q18`, `q28`"),
  scale_range = c("","","","","","","","","","", ""), #TODO fill in range 
   alpha = c(round(bcap_alpha$total$raw_alpha, 3),
              round(bcap_risk_alpha$total$raw_alpha, 3),
              round(bcap_happy_alpha$total$raw_alpha, 3),
              round(bcap_feel_pers_alpha$total$raw_alpha, 3),
              round(bcap_lonely_alpha$total$raw_alpha, 3),
              round(bcap_fam_conf_alpha$total$raw_alpha, 3), 
              round(bcap_rigid_alpha$total$raw_alpha, 3), 
              round(bcap_distress_alpha$total$raw_alpha, 3),
              round(bcap_poverty_alpha$total$raw_alpha, 3), 
              round(bcap_lie_alpha$total$raw_alpha, 3),
              round(bcap_random_alpha$total$raw_alpha, 3))
)

# Create the gt table object
bcap_scale_table <- gt(bcap_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(bcap_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score.

For binary items: 

```{r bcap-binary-desc}

# Create subset of BCAP items
bcap_data_subset_binary <- complete %>%
  select(q1_r,
         q2_r,
         q3:q22,
         q23_r,
         q24:q28,
         q29_r,
         q30:q34)

# Calculate the dichotomous summary statistics for each variable
bcap_summary_data_binary <- lapply(bcap_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
bcap_summary_data_binary <- as.data.frame(bcap_summary_data_binary)

# Set items as first row
bcap_summary_data_binary <- rbind(names(bcap_summary_data_binary), bcap_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
bcap_tbl_binary <- bcap_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "Disagree", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Agree", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
bcap_tbl_binary
```

For continuous total and subscale scores: 

```{r bcap-mean-items}
# Create subset of bcap items
bcap_data_subset <- complete %>%
  select(
    bcap_risk_total, bcap_happy_total, bcap_feel_pers_total, bcap_lonely_total, bcap_fam_conf_total, bcap_rigid_total, bcap_distress_total, bcap_poverty_total, bcap_lie_total, bcap_random_total)

# Calculate the summary statistics for each variable
bcap_summary_data <- lapply(bcap_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
bcap_summary_data <- as.data.frame(bcap_summary_data)

# Set items as first row
bcap_summary_data <- rbind(names(bcap_summary_data), bcap_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
bcap_tbl <- bcap_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(1 ~ px(165),2:5 ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
bcap_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r bcap-distributions, class.source='fold', echo = FALSE}
#Risk 
complete %>%
  composite_hist(
    x = bcap_risk_total
  ) +
  labs(
    title = 'Distribution of Total Scores for BCAP Risk Scale'
  )

# Happiness 
complete %>% 
  composite_hist(
    x = bcap_happy_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Happiness Subscale'
  )

# Feelings
complete %>% 
  composite_hist(
    x = bcap_feel_pers_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Feelings of Persecution Subscale'
  )

# Loneliness
complete %>% 
  composite_hist(
    x = bcap_lonely_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Loneliness Subscale'
  )

# Family Conflict
complete %>% 
  composite_hist(
    x = bcap_fam_conf_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Family Conflict Subscale'
  )

# Rigidity
complete %>% 
  composite_hist(
    x = bcap_rigid_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Rigidity Subscale'
  )

# Distress
complete %>% 
  composite_hist(
    x = bcap_distress_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Distress Subscale'
  )

# Poverty
complete %>% 
  composite_hist(
    x = bcap_poverty_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Poverty Subscale'
  )

# Lying
complete %>% 
  composite_hist(
    x = bcap_lie_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Lying Subscale'
  )
    
# Random Responding 
complete %>% 
  composite_hist(
    x = bcap_random_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Random Responding Subscale'
  ) 
```

## Dyadic Adjustment Scale (DYADC)

### DYADC Description

The DYADC is a self-report measure used to assess dyadic adjustment (e.g., interpersonal tensions, dyadic satisfaction, dyadic functioning). 

For the present study, all 32 items from the DYADC were collected, and the total score and all subscales are included: Consensus, Affective Expression, Satisfaction, and Cohesion.

Two items `e18` and `e19` should be reverse scored which is noted in the variable table below and the reverse scored variables are provided (`e18_r` and `e19_r`). Higher scores indicate more positive dyadic adjustment.

*<SHAINA> CONFIRM* The missing data rule was Applied. Calculations were completed only with participants that had less than 20% missing data (this includes `-77` responses) 

Reference: [@ondersma2005brief](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug); 
[DOI](https://doi.org/10.1207/s15374424jccp3402_9)
*<SHIANA> EXPLAIN WHAT 2ND REF IS FOR* Reference: [@spanier1976measuring](https://www.jstor.org/stable/350547);[DOI](https://doi.org/10.2307/350547)

### DYADC Variables

#### Value Labels

The DYADC has multiple response options, value labels for each variable can be found in the survey items table below. 

#### Survey Items

All DYADC survey items are presented in the following table:

```{r dyadc-var-prep}
# Pull question wording from qualtrics data
dyadc_word <- qualtrics %>% 
  select(starts_with("E")) %>%
  slice(1) %>%
  select(-(1:2))

#create table with variable name, description, and notes
dyadc_word_long <- dyadc_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         value = case_when(row_number() <= 15  ~ "0 = Always Disagree 
                                                 \n1 = Almost Always Disagree
                                                 \n2 = Frequently Disagree
                                                 \n3 = Occasionally Disagree
                                                 \n4 = Almost Always Agree
                                                 \n5 = Always Agree",
                           row_number() %in% c(16, 17, 20:22) ~ "0 = All the time 
                                                 \n1 = Most of the time
                                                 \n2 = More often than not
                                                 \n3 = Occasionally
                                                 \n4 = Rarely
                                                 \n5 = Never",
                           row_number() %in% c(18,19) ~ "0 = Never
                                                 \n1 = Rarely
                                                \n2 = Occasionally
                                                 \n3 = More often than not
                                                 \n4 = Most of the time
                                                 \n5 = All the time ",
                           between(row_number(), 23, 24 ) ~ "0 = Never
                                                 \n1 = Rarely
                                                 \n2 = Occasionally
                                                 \n3 = Almost every day
                                                 \n4 = Every day",
                           between(row_number(), 25,28) ~ "0 = Never
                                                 \n1 = Less than once a month
                                                 \n2 = Once or twice a month
                                                 \n3 = Once or twice a week
                                                 \n4 = Once a day
                                                 \n5 = More often",
                           row_number() %in% c(29,30) ~ "0 = Yes
                                                 \n1 = No",
                           row_number() %in% c(31) ~ "0 = Extremely Unhappy
                                                 \n1 = Fairly Unhappy
                                                 \n2 = A Little Unhappy
                                                 \n3 = Happy
                                                 \n4 = Very Happy
                                                 \n5 = Extremely Happy
                                                 \n6 = Perfect",
                           row_number() >= 32 ~ "0 =	My relationship can never succeed, and there is no more that I can do to keep the relationship going.
                                                 \n1 =	It would be nice if it succeeded, but I refuse to do any more than I am doing now to keep the relationship going.
                                                 \n2 =	It would be nice if my relationship succeeded, but I cant do much more than Im doing now to help it succeed.
                                                 \n3 =	I want very much for my relationship to succeed, and will do my fair share to see that it does.
                                                 \n4 =	I want very much for my relationship to succeed, and will do all I can to see that it does.
                                                 \n5 =	I want desperately for my relationship to succeed, and would go to almost any length to see that it does."
                           ),
         notes = case_when(var_name == "e18" ~ "This item should be reverse scored. `e18_r` is reverse scored",
                           var_name == "e19" ~ "This item should be reverse scored. `e19_r` is reverse scored",
                           TRUE ~ as.character(""))
         ) %>%
   mutate(description = if_else(var_name == "e31", " Please indicate the number that best describes the degree of happiness in your relationship.",
                               if_else(var_name == "e32", "Which of the following statements best describes how you feel about the future of your relationship? Please indicate only one answer", description))) %>%
  slice(1:32)


```


```{r dyadc-var-table, results ='asis'}
# Create the gt table object and apply generic theme
dyadc_gt_table <- gt(dyadc_word_long)

# Table-specific formatting (col width, names)
dyadc_gt_table <- dyadc_gt_table %>% 
  apply_tbl_theme() %>% 
  tab_row_group(label = "Please indicate if items below were problems in your relationships in the past few weeks.", 
                rows = 29:32,
                id = "set4") %>%
  tab_row_group(label = "Thinking about the past 6 months,how often do you", 
                rows = 25:28,
                id = "set3") %>%
  tab_row_group(label = "In the past 6 months, how often. . .", 
                rows = 23:24,
                id = "set2") %>%
  tab_row_group(label = "Thinking about the past 6 months, how often do you. . . ", 
                rows = 1:22,
                id = "set1")%>%
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1", alpha = 0.2),
                         cell_borders(sides = c("left", "right", "top", "bottom"))),
            locations = cells_row_groups(groups = c("set1", "set2", "set3", "set4"))) %>%
  cols_width(notes ~ px(150),
             var_name ~ px(100),
             value ~ px(225)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(dyadc_gt_table)

#WHEN RENDERING WITH PDF USE: 
#dyadc_gt_table


```

#### Scale and Subscales

Information on total score and subscale variables are below. *<SHAINA/MARIA> INSERT Variables were constructed by ...*

```{r dyadc alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
dyadc_alpha <-
  complete %>% 
  select(
    e1:e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_con_alpha <-
  complete %>% 
  select(
    e1:e13
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_aff_exp_alpha <-
  complete %>% 
  select(
    e4, e6, e29, e30
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_satis_alpha <-
  complete %>% 
  select(
    e16:e23,
    e31,
    e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_cohes_alpha <-
  complete %>% 
  select(
    e24:e28
  ) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r dyadc-scale-table, results = 'asis'}
# Create the table as a data frame
dyadc_scale_df <- data.frame(
  var_name = c("dyadc_total", "dyadc_con_total", "dyadc_aff_exp_total", "dyadc_satis_total", "dyadc_cohes_total"),
  scale = c("DYADC Total score (32) ", "Consensus (13)", "Affective Expression (4)", "Satisfaction (10)", "Cohesion (5)"),
  scale_construction = c("`e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`, `e14`, `e15`, `e16`, `e17`, `e18_r`, `e19_r`, `e20`, `e21`, `e22`, `e23`, `e24`, `e25`, `e26`, `e27`, `e28`, `e29`, `e30`, `e31`, `e32`", 
                         "`e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`", 
                         "`e4`, `e6`, `e29`, `e30`", 
                         "`e16`, `e17`, `e18_r`, `e19_r`, `e20`, `e21`, `e22`, `e23`, `e31`, `e32`", "`e24`, `e25`, `e26`, `e27`, `e28`"),
  scale_range = c("","","","",""), #TODO fill in range 
   alpha = c(round(dyadc_alpha$total$raw_alpha, 3),
              round(dyadc_con_alpha$total$raw_alpha, 3),
              round(dyadc_aff_exp_alpha$total$raw_alpha, 3),
              round(dyadc_satis_alpha$total$raw_alpha, 3),
              round(dyadc_cohes_alpha$total$raw_alpha, 3))
  )

# Create the gt table object
dyadc_scale_table <- gt(dyadc_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(dyadc_scale_table)

```
### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score.

For continuous items: 

```{r dyadc-mean-items}
# Create subset of dyadc items
dyadc_data_subset <- complete %>%
  select(e1:e28, e31:e32, dyadc_total,
         dyadc_con_total, ,dyadc_aff_exp_total,
         dyadc_satis_total, dyadc_cohes_total)  


# Calculate the summary statistics for each variable
dyadc_summary_data <- lapply(dyadc_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dyadc_summary_data <- as.data.frame(dyadc_summary_data)

# Set items as first row
dyadc_summary_data <- rbind(names(dyadc_summary_data), dyadc_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dyadc_tbl <- dyadc_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(1 ~ px(165),2:5 ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
dyadc_tbl

```

For binary items:

```{r dyadc-binary-desc}

# Create subset of BCAP items
dyadc_data_subset_binary <- complete %>%
  select(e29, e30)

# Calculate the dichotomous summary statistics for each variable
dyadc_summary_data_binary <- lapply(dyadc_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dyadc_summary_data_binary <- as.data.frame(dyadc_summary_data_binary)

# Set items as first row
dyadc_summary_data_binary <- rbind(names(dyadc_summary_data_binary), dyadc_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dyadc_tbl_binary <- dyadc_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "No", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Yes", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
dyadc_tbl_binary
```

#### Distributions

Distributions are presented below for the total score and each subscale:

```{r dyadc-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(
    x = dyadc_total
  ) +
  labs(
    title = 'Distribution for DYADC Scale'
  )

complete %>%
  composite_hist(
    x = dyadc_con_total
  ) +
  labs(
    title = 'Distribution for DYADC Consensus Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_aff_exp_total,
    bins = 10
  ) +
  labs(
    title = 'Distribution for DYADC Affectional Expression Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_satis_total
  ) +
  labs(
    title = 'Distribution for DYADC Satisfaction Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_cohes_total
  ) +
  labs(
    title = 'Distribution for DYADC Cohesion Subscale'
  )
```

#### Clinical Categories

The distribution for the total score alongside clinical cutoffs are presented below.

*<MARIA>INSERT MORE INFO ON CUTOFF SCORES - what are they (what should plot labels be)?, how should they be used*

Reference: *<SHAINA/MARIA> INSERT REFERENCE FOR DYADC CUTOFF SCORES*

```{r dyadc-cutoff, class.source='fold', echo = FALSE}
complete %>%
  cutoff_plot2(
    x = dyadc_total,
    cutoff = 92,
    cutoff_other = 107
  ) +
  labs(
    title = 'Cutoff Values for DYADC Scale',
    caption = 'Cutoffs are 92 and 107\nSee references for literature on cutoff scores.'
  )+
  geom_text(aes(x = 16, y = 16.5, label = "cutoff1", vjust = -.25, hjust = -6)) +
  geom_text(aes(x = 16, y = 16.5, label = "cutoff2", vjust = -.25, hjust = -9.25))
```

## Attachment Relationships Questionnaire (ARQ)

### ARQ Description

The ARQ is a self-report measure used to categorize attachment styles in adulthood. *<MARIA> CONFIRM THIS IS CORRECT*
  
For the present study, all 5 items from the ARQ were collected in order to construct four attachment styles (secure, fearful, preoccupied, and dismissing).

No items need to be reverse scored. Participants self-select one attachment style that best describes them in the first question `rq1`, then rate their agreement with each attachment style for `rqa` - `rqd`. Higher ratings indicate more agreement with the statement. 

The missing data rule is applied. Calculations were completed for participants with 33% or less missing data (this includes -77 responses) 

Reference: [@bartholomew1991attachment](https://psycnet.apa.org/record/1991-33075-001);[DOI](https://doi.org/10.1037/0022-3514.61.2.226)

### ARQ Variables

#### Value Labels

ARQ variables have the multiple response options

```{r ARQ-label-table, results = 'asis'}

arq_label_df <- data.frame(
  value = c("A", "B", "C", "D"),
  label = c("It is easy for me to become emotionally close to others. I am comfortable dependingon them and having them depend on me. I don't worry about being alone or havingothers not accept me.",
            "I am uncomfortable getting close to others. I want emotionally close relationships, but Ifind it difficult to trust others completely, or to depend on them. I worry that I will be hurt ifI allow myself to become too close to others.",
            "I want to be completely emotionally intimate with others, but I often find that others arereluctant to get as close as I would like. I am uncomfortable being without closerelationships, but I sometimes worry that others don't value me as much as I value them.",
            "I am comfortable without close emotional relationships. It is very important to me tofeel independent and self-sufficient, and I prefer not to depend on others or have othersdepend on me.")
) %>% 
  t() %>% 
  as.data.frame()


arq_label_df <- setNames(arq_label_df[-1, ], unlist(arq_label_df[1, ]))


#create table
arq_label_table <- arq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(arq_label_table)


```

```{r ARQ-label-table-2, results = 'asis'}

arq_label_df <- data.frame(
  value = c("1", "2", "3", "4", "5", "6", "7"),
  label = c("Disagree Strongly",
            "",
            "",
            "Neutral/Mixed",
            "",
            "",
            "Agree Strongly")
) %>% 
  t() %>% 
  as.data.frame()


arq_label_df <- setNames(arq_label_df[-1, ], unlist(arq_label_df[1, ]))


#create table
arq_label_table <- arq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(arq_label_table)


```
#### Survey Items

All ARQ survey items are presented in the following table

```{r ARQ-var-prep}
# Pull question wording from qualtrics data
 

#create table with variable name, description, and notes
arq_word_long <- arq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  mutate(description = if_else(var_name == "rq1", "Please tell me which one style best describes you or is the closest to the way you are. A. It is easy for me to become emotionally close to others. I am comfortable depending on them and having them depend on me. I dont worry about being alone or having others not accept me. B. I am uncomfortable getting close to others. I want emotionally close relationships, but I find it difficult to trust others completely, or to depend on them. I worry that I will be hurt if I allow myself to become too close to others. C. I want to be completely emotionally intimate with others, but I often find that others are reluctant to get as close as I would like. I am uncomfortable being without close relationships, but I sometimes worry that others dont value me as much as I value them. D. I am comfortable without close emotional relationships. It is very important to me to feel independent and self-sufficient, and I prefer not to depend on others or have others depend on me.", description))

```


```{r arq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
arq_gt_table <- gt(arq_word_long)

# Table-specific formatting (col width, names)
arq_gt_table <- arq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(arq_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```


#### Scale and Subscales

Information on constructed attachment groups is presented below. The highest rating for attachment style was used to classify participants into one of four attachment groups (secure, dismissing, preoccupied, fearful). Model of the self (i.e., attachment anxiety) was calculated by summing secure and dismissing ratings then subtracting the sum of preoccupied and fearful items. Model of the other (i.e., attachment avoidance) was constructed by summing secure and preoccupied items and subtracting the sum of dismissing and fearful items. Higher scores on attachment models indicate more positive attachment models. *<MARIA> CONFIRM THIS IS CORRECT*

*<SHAINA/MARIA> CONFIRM ALPHA IS NEEDED*

```{r arq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
arq_alpha <-
  complete_rnd2 %>%
  select(rq1,rqa,	rqb, rqc, rqd) %>%
  psych::alpha(check.keys = TRUE)
```

```{r arq-subscales}
#DATA CLEANING CODE - create arq categories
vars_to_check <- c("rqa", "rqb", "rqc", "rqd")

arq_subscale <- complete_rnd2 %>% 
  mutate(max_var = apply(.[vars_to_check], 1, function(row) vars_to_check[which.max(row)])) %>% 
  mutate(arq_group = case_when(max_var == "rqa" ~ "Secure",
                               max_var == "rqb" ~ "Fearful",
                               max_var == "rqc" ~ "Preoccupied",
                               max_var == "rqd" ~ "Dismissive",
                               TRUE ~ NA_character_),
         arq_model_self = rowSums(data.frame(rqa, rqd), na.rm = TRUE) - rowSums(data.frame(rqc, rqb), na.rm = TRUE),
    arq_model_other = rowSums(data.frame(rqa, rqc), na.rm = TRUE) - rowSums(data.frame(rqd, rqb), na.rm = TRUE)) %>%
  mutate_at(vars(arq_model_self, arq_model_other), ~ if_else(is.na(arq_group), NA_real_, .)) %>% 
  select(-max_var) 

#missing ratings: 50, 116, and 123

```

```{r ARQ-scale-table, results = 'asis'}
# Create the table as a data frame
arq_scale_df <- data.frame(
  var_name = c("arq_group", "arq_model_self", "arq_model_other"),
  scale = c("Attachment Group", "Model of Self", "Model of Other"),
  scale_construction = c("Highest rating among `rqa`, `rqb`, `rqc`, `rqd`", "(`rqa` + `rqd`) - (`rqc` + `rqb`)", "(`rqa` + `rqc`) - (`rqd` + `rqb`)"))

# Create the gt table object
arq_scale_table <- gt(arq_scale_df) %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale Name", 
            scale_construction = "Scale Construction") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  apply_tbl_theme() 

# Print the table
print(arq_scale_table)
```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

```{r ARQ-mean-items}
# Create subset of BSI items
arq_data_subset <- complete_rnd2 %>%
  select(rq1,rqa,	rqb, rqc, rqd)

# Calculate the summary statistics for each variable
arq_summary_data <- lapply(arq_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
arq_summary_data <- as.data.frame(arq_summary_data)

# Set items as first row
arq_summary_data <- rbind(names(arq_summary_data), arq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
arq_tbl <- arq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
arq_tbl

```

#### Distributions

Distributions are presented for the total score and each subscale
*TODO: JP's graphs are count on x axis *
```{r ARQ-distributions, class.source='fold', echo = FALSE}
complete_rnd2 %>%
  composite_hist(x = rq1, bins = 4) +
  labs(title = 'Distribution of rq1') #TODO: Shaina could you decide on #of bins?

complete_rnd2 %>%
  composite_hist(x = rqa, bins = 10) +
  labs(title = 'Distribution of rqa')

complete_rnd2 %>%
  composite_hist(x = rqb, bins = 10) +
  labs(title = 'Distribution of rqb')

complete_rnd2 %>%
  composite_hist(x = rqc, bins = 10) +
  labs(title = 'Distribution of rqc')

complete_rnd2 %>%
  composite_hist(x = rqd, bins = 10) +
  labs(title = 'Distribution of rqd')
```


## Posttraumatic Risk Seeking Scale (PRSS)

### PRSS Description

The PRSS is a 5-item questionnaire designed to measure *insert text*

For the present study, 5 items from the PRSS were collected in order to *TODO: insert text here*

  No items need to be reverse scored. *TODO: need change text here Higher scores indicate more severe mental health symptoms. *

The missing data rule was applied. Calculations were completed for participants with 33% or less missing data (this includes -77 responses)

Reference: [@kerig2019linking](https://onlinelibrary.wiley.com/doi/abs/10.1111/cpsp.12280); [DOI](https://doi.org/10.1111/cpsp.12280)

### PRSS Variables

#### Value Labels

All PRSS variables have the same response options.


```{r PRSS-label-table, results = 'asis'}

prss_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("None of the time",
            "A little of the time",
            "Some of the time",
            "Much of the time",
            "Most of the time")) %>% 
  t() %>% 
  as.data.frame()

prss_label_df <- setNames(prss_label_df[-1, ], unlist(prss_label_df[1, ]))


#create table
prss_label_table <- prss_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(150)) %>% 
  apply_labtab_theme()

# Print the table
print(prss_label_table)


```

#### Survey Items

PRSS survey items are presented in the following table:
  
```{r prss-var-prep}
# Pull question wording from Qualtrics data
prss_word <- qualtrics %>% 
  select(starts_with("ps")) %>% 
  slice(1)

#create table with variable name, description, and notes
prss_word_long <- prss_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character(""))%>%
  slice(9:13)

```


```{r prss-var-table, results ='asis'}
# Create the gt table object and apply generic theme
# this sould be ps9-ps13
prss_gt_table <- gt(prss_word_long)

# Table-specific formatting (col width, names)
prss_gt_table <- prss_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(prss_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on the total score and subscale variables are below. Variables were constructed by summing included items. 

```{r prss alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
prss_alpha <-
  complete_rnd2 %>%
  select(ps9:ps13) %>%  
  psych::alpha(check.keys = TRUE)
```

```{r PRSS-scale-table, results = 'asis'}
# Create subset of prss items
prss_data_subset <- complete_rnd2 %>%
  select(ps9:ps13, id)

# Calculate total and average
prss_data_subset <-
  prss_data_subset %>%
  composite_total_avg_fun(
    id = 'id',
    max_value = 13,
    n_items = 5
  ) %>%
  distinct(
    across(
      .cols = everything()
    )
  ) %>%
  rename(
    prss_total = sum_values,
    prss_avg = mean_values
  ) 
  # mutate(
  #   across(
  #     c(
  #       prss_total,
  #       prss_avg
  #     ),
  #     ~case_when(
  #       id %in% prss_remove ~ NA_real_,
  #       TRUE ~ .x
  #     )
  #   )
  # )

# Create the table as a data frame
prss_scale_df <- data.frame(
  var_name = c("prss_total"),
  scale = c("PRSS Total score (5) "),
  scale_construction = c("`ps9`, `ps10`, `ps11`, `ps12`, `ps13`"),
  scale_range = c(""), #TODO fill in range 
   alpha = c(round(prss_alpha$total$raw_alpha, 3))
  )

# Create the gt table object
prss_scale_df <- gt(prss_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(prss_scale_df)


```
### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score:
  
```{r prss-mean-items}

# Calculate the summary statistics for each variable
prss_summary_data <- lapply(prss_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
prss_summary_data <- as.data.frame(prss_summary_data)%>%select(-c(id))

# Set items as first row
prss_summary_data <- rbind(names(prss_summary_data), prss_summary_data) %>% 
  t() %>% 
  as.data.frame() 

# Create the gt table
prss_tbl <- prss_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
prss_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:
  
```{r PRSS-distributions, class.source='fold', echo = FALSE}
prss_data_subset %>%
  composite_hist(
    x = prss_avg
  ) +
  labs(title = "Distribution of Average Scores for the PRSS")


```

## Stigma & Shame Questionnaire (SSQ)

### SSQ Description

The SSQ is a 8-item questionnaire designed to measure *insert*.

For the present study, 8 items from the SSQ were collected in order to #TODO: insert text here

  No items need to be reverse scored. *TODO: need change text here Higher scores indicate more severe mental health symptoms. *

The missing data rule was applied. Calculations were completed for participants with 33% or less missing data (this includes -77 responses)

Reference: [ @feiring2005persistence](https://journals.sagepub.com/doi/abs/10.1177/1077559505276686); [DOI](https://doi.org/10.1177/1077559505276686)


### SSQ Variables

#### Value Labels

All SSQ variables have the same response options.


```{r SSQ-label-table, results = 'asis'}

ssq_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("None of the time",
            "A little of the time",
            "Some of the time",
            "Much of the time",
            "Most of the time")) %>% 
  t() %>% 
  as.data.frame()

ssq_label_df <- setNames(ssq_label_df[-1, ], unlist(ssq_label_df[1, ]))


#create table
ssq_label_table <- ssq_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(ssq_label_table)


```

#### Survey Items

SSQ survey items are presented in the following table:
  
```{r ssq-var-prep}
# Pull question wording from qualtrics data
ssq_word <- qualtrics %>% 
  select(starts_with("ps")) %>% 
  slice(1)

#create table with variable name, description, and notes
ssq_word_long <- ssq_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  slice(1:8)


```


```{r ssq-var-table, results ='asis'}
# Create the gt table object and apply generic theme
ssq_gt_table <- gt(ssq_word_long)

# Table-specific formatting (col width, names)
ssq_gt_table <- ssq_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(ssq_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below. Variables were constructed by summing included items. 

```{r ssq alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
ssq_abuse_shame_alpha <- complete_rnd2 %>% 
  select(
    ps1:ps4
  ) %>% 
  psych::alpha(check.keys = TRUE)

ssq_alpha <- complete_rnd2 %>% 
  select(
    ps1:ps8
  ) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r SSQ-scale-table, results = 'asis'}
# Create subset of ssq items
ssq_data_subset <-
  complete_rnd2 %>%
  select(id,
         ps1:ps8) %>%
  subscale_create(
    total_only = TRUE,
    scale1 = c("ps1", "ps2", "ps3", "ps4"),
    scale1_nitems = 4,
    scale2 = c("ps1", "ps2", "ps3", "ps4",
               "ps5", "ps6", "ps7", "ps8"),
    scale2_nitems = 8
  ) %>%
  rename(
    ssq_abuse_shame = total1,
    ssq_total = total2
  ) %>%
  mutate(
    across(
      c(ssq_abuse_shame, ssq_total)), #, ~case_when(id %in% ssq_remove ~ NA_real_, TRUE ~ .x)),
    ssq_total_cutoff = case_when(
      ssq_total >= 16 ~ "high shame",
      ssq_total <= 15 ~ "low shame"
    )
  )

# Create the table as a data frame
ssq_scale_df <- data.frame(
  var_name = c("ssq_total", "ssq_abuse_shame"),
  scale = c("SSQ Total score (8)", "Abuse-related Shame (4)"),
  scale_construction = c("`ps1`, `ps2`, `ps3`, `ps4`,`ps5`, `ps6`, `ps7`, `ps8`",
                         "`ps1`, `ps2`, `ps3`, `ps4`"),
  scale_range = c("",""), #TODO fill in range 
  alpha = c(round(ssq_alpha$total$raw_alpha, 3),
            round(ssq_abuse_shame_alpha$total$raw_alpha, 3))
)

# Create the gt table object
ssq_scale_df <- gt(ssq_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(ssq_scale_df)


```
### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score:
  
```{r ssq-mean-items}
# Calculate the summary statistics for each variable
ssq_summary_data <- lapply(ssq_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
ssq_summary_data <- as.data.frame(ssq_summary_data)%>%select(-c(id))

# Set items as first row
ssq_summary_data <- rbind(names(ssq_summary_data), ssq_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
ssq_tbl <- ssq_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
ssq_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:
  
```{r ssq-distributions, class.source='fold', echo = FALSE}
ssq_data_subset %>%
  composite_hist(
    x = ssq_total
  ) +
  labs(title = "Distribution of Total Scores for the Stigma & Shame Questionnaire")

```

#### Clinical Categories

The distribution for the total score alongside clinical cutoffs are presented below.

*<MARIA>INSERT MORE INFO ON CUTOFF SCORES - what are they (what should plot labels be)?, how should they be used*
  
  Reference: *<SHAINA/MARIA> INSERT REFERENCE FOR DYADC CUTOFF SCORES*
  
```{r ssq-cutoff, class.source='fold', echo = FALSE}

ssq_data_subset %>% 
  cutoff_plot2(
    x = ssq_total,
    cutoff = 16
  ) +
  labs(
    title = "Cutoff Scores for SSQ Total Scores",
    caption = "Cutoff is 16\nSee reference for literature on cutoff score."
  )

ssq_data_subset %>% 
  cutoff_plot2(
    x = ssq_abuse_shame,
    cutoff = 3
  ) +
  labs(
    title = "Cutoff Scores for SSQ Abuse-related Shame Scores",
    caption = "Cutoff is 3\nSee reference for literature on cutoff score."
  )
```


## Elliott Delinquency Scale (EDS) Friends/Peers report

### EDS Description

The EDS is a 39-item questionnaire designed to measure *insert*.

For the present study, 39 items from the EDS were collected in order to #TODO: insert text here

All 39 items need to be reverse scored. *TODO: need change text here Higher scores indicate more severe mental health symptoms. *
  
The missing data rule was applied. Calculations were completed for participants with 33% or less missing data (this includes -77 responses)

Reference: [ @feiring2005persistence](https://journals.sagepub.com/doi/abs/10.1177/1077559505276686); [DOI](https://doi.org/10.1177/1077559505276686)


### EDS Variables

#### Value Labels

All EDS variables have the same response options.


```{r EDS-label-table, results = 'asis'}

eds_label_df <- data.frame(
  value = c("1", "2", "3", "4", "5", "6"),
  label = c("All",
            "Most",
            "Some",
            "Very Few",
            "None",
            "Does not apply")) %>% 
  t() %>% 
  as.data.frame()

eds_label_df <- setNames(eds_label_df[-1, ], unlist(eds_label_df[1, ]))


#create table
eds_label_table <- eds_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(150)) %>% 
  apply_labtab_theme()

# Print the table
print(eds_label_table)


```

#### Survey Items

EDS survey items are presented in the following table:
  
```{r eds-var-prep}
# Pull question wording from qualtrics data
eds_word <- qualtrics %>% 
  select(starts_with("elf")) %>% 
  slice(1)

#create table with variable name, description, and notes
eds_word_long <- eds_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = paste0("This item should be reverse scored. `", var_name, "_c` is reverse scored")
           ) %>% 
  slice(1:39)
# TODO: need double check reverse code variable name, it's inconsistant with other measure's reverse score name 

```


```{r eds-var-table, results ='asis'}
# Create the gt table object and apply generic theme
eds_gt_table <- gt(eds_word_long)

# Table-specific formatting (col width, names)
eds_gt_table <- eds_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(eds_gt_table)


```

#### Scale and Subscales

Information on the total score and subscale variables are below. Variables were c
onstructed by summing included items. 
```{r eds df, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
# TODO: this section might need move to data cleaning script
# reverse scoring 
eds <-
  complete_rnd2 %>%
  select(
    id,
    matches(
      "^elf"
    )
  ) %>% 
#TODO: need to colculate total and average 
composite_total_avg_fun(
  id = c(
    'id', "elf1_c", "elf2_c", "elf3_c", "elf7_c",
    "elf12_c", "elf13_c", "elf15_c", "elf17_c", "elf18_c",
    "elf19_c", "elf23_c", "elf26_c", "elf28_c", "elf30_c",
    "elf34_c", "elf35_c", "elf36_c", "elf37_c"
  ),
  max_value = 4,
  n_items = 21
) %>%
distinct(
  across(
    .cols = everything()
  )
) %>%
rename(
  elf_total = sum_values,
  elf_avg = mean_values)

```
#Calculate internal reliability 
```{r eds alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
eds_alpha <- eds %>% 
    select(matches("_c$")) %>% #TODO: this need to be changed based on df naming
    psych::alpha(check.keys = TRUE)

```
TODO: all revers coded column is 0, need to double check, I used non-revers coded score for now 
```{r EDS-scale-table, results = 'asis'}


# Create the table as a data frame
eds_scale_df <- data.frame(
  var_name = c("eds_total"),
  scale = c("EDS Total score (39)"),
  scale_construction = c("`elf1`, `elf2`, `elf3`, `elf4`, `elf5`, `elf6`, `elf7`, 
  `elf8`, `elf9`, `elf10`, `elf11`, `elf12`, `elf13`, `elf14`, `elf15`, `elf16`, 
  `elf17`, `elf18`, `elf19`, `elf20`, `elf21`, `elf22`, `elf23`, `elf24`, `elf25`, 
  `elf26`, `elf27`, `elf28`, `elf29`, `elf30`, `elf31`, `elf32`, `elf33`, `elf34`, 
                         `elf35`, `elf36`, `elf37`, `elf38`, `elf39`"),
  scale_range = c(""), #TODO fill in range 
  alpha = c(round(eds_alpha$total$raw_alpha, 3))
)

# Create the gt table object
eds_scale_df <- gt(eds_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(eds_scale_df)


```
### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item, total, and subscale score:
  
```{r eds-mean-items}
# Calculate the summary statistics for each variable
eds_summary_data <- lapply(eds, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
eds_summary_data <- as.data.frame(eds_summary_data)%>%select(-c(id))

# Set items as first row
eds_summary_data <- rbind(names(eds_summary_data), eds_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
eds_tbl <- eds_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
eds_tbl

```

#### Distributions

Distributions are presented below for the total score and each subscale:
  
```{r eds-distributions, class.source='fold', echo = FALSE}
#TODO: make sure total is colculated 
# eds %>%
#   composite_hist(
#     x = elf_total
#   ) +
#   labs(title = "Distribution of Total Scores for the Stigma & Shame Questionnaire")

```
