---
title: "TPW Codebook Draft"
author: "Shaina Trevino"
date: "2023-05-22"
output: 
  html_document:
    toc: true
    toc_depth: 3
    #html#toc_title: Contents
    number_sections: true
    #html#number_depth: 3
    #qmd#colorlinks: true
    #keep_tex: yes
    #pdf#latex_engine: pdflatex
    #error#includes: 
      #error#in_header: styles.css
#pdf#geometry: landscape
bibliography: tpw_references.bib
---



```{r, include = FALSE}
library(tidyverse)
library(here)
library(gt)
library(ggplot2)
library(scales)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE)

theme_set(theme_light())

#import included survey items
data <- read_csv(here("do_not_push", "tpw_data_77included.csv"))

#import df of calculated survey items
complete <- read_csv(here("do_not_push", "tpw_data_calculated.csv"))

#import raw qualtrics data for parsing question text
qualtrics <- read_csv(here("do_not_push", "tpw_raw_qualtrics_5-30-23.csv"))

source(here("functions", "codebook_fun.R"))
```

```{r plot style, echo=FALSE}
# Color palettes 
 Two_color = c("#246B69", "#604C41")

# Histogram style 
# hist_style <- geom_histogram(bins=20, color = "white", fill = "#246B69", alpha = 0.7)


bar_style <- geom_bar(color = "white", fill = "#246B69", alpha = 0.7)

THEME <-     theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),legend.key = element_rect(fill = "White", colour = "transparent"),plot.title = element_text(size= 13),
    )
```

# Overview

*INSERT BRIEF INFO ON STUDY, SAMPLE, AND AIMS*

*Additional info to possibly include: global missing data info, links to supplemental materials, any disclaimers/info we think data users need to know to use these data accurately*

*INSERT BRIEF DESCRIPTION OF DATA/CODEBOOK LAYOUT/FILE STRUCTURE (can complete once we have more sections and overall structure)*

### Missing Data Rule

-   For scales with [10 or more items]{.underline}, a composite score (average/total) is computed for each participant that have less than [20%]{.underline} of the items from that measure missing

-   For scales with [7 to 9 items]{.underline}, a composite score (average/total) is computed for each participant that have less than [30%]{.underline} of the items from that measure missing

-   For scales with [3 to 6 items]{.underline}, a composite score (average/total) is computed for each participant that have less than [33%]{.underline} of the items from that measure missing

-   For scales with [only 2 items]{.underline}, composite scores (average/total) are calculated on a [case by case basis]{.underline}

*INSERT REFERENCE LINK*

# Mental Health

*INSERT BRIEF DESCRIPTION ABOUT CONSTRUCT DOMAIN*

## Brief Symptom Inventory (BSI)

### BSI Description

The BSI is used to assess ... *INSERT TEXT DESCRIPTION ABOUT BSI MEASURE*

For the present study, 19 items from the BSI were collected in order to calculate the Somatization, Anxiety, and Depression subscales. 

Item numbers in this dataset may not match original item numbers from the BSI exactly (?)

No items need to be reverse scored. Higher scores indicate more severe mental health symptoms. 

The missing data rule was not applied since there is no missing data among BSI variables. 

Reference: [@derogatis1983brief](https://www.cambridge.org/core/journals/psychological-medicine/article/abs/brief-symptom-inventory-an-introductory-report/307F805810B165ED58581E355F24329F); [DOI](https://doi.org/10.1017/S0033291700048017)

### BSI Variables

#### Value Labels

All BSI variables have the same response options

```{r gt-theme-general}

apply_tbl_theme <- function(table) {
  table %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_fill(color = "#9BB6D1")),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white")%>% 
  tab_options(table.align = "left")
}

#theme for value label tables
apply_labtab_theme <- function(table) {
  table %>% 
  cols_align(columns = everything(), align = "center") %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1))),
            locations = cells_body(columns = everything())) %>% 
  tab_style(style = list(cell_borders(sides = "all", color = "black", weight = px(1)),
                         cell_fill(color = "#9BB6D1")),
            locations = cells_column_labels()) %>% 
  tab_options(column_labels.border.top.color = "black",
              column_labels.border.bottom.color = "black",
              table_body.border.bottom.color = "black",
              table.border.top.color = "white",
              heading.border.bottom.color = "black",
              table_body.hlines.color = "white") %>% 
  tab_options(table.align = "left")
}
  
```

```{r BSI-label-table, results = 'asis'}

bsi_label_df <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("Not at all",
            "A little bit",
            "Moderately",
            "Quite a bit",
            "Very much")
) %>% 
  t() %>% 
  as.data.frame()

bsi_label_df <- setNames(bsi_label_df[-1, ], unlist(bsi_label_df[1, ]))


#create table
bsi_label_table <- bsi_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(bsi_label_table)


```


#### Survey Items

All BSI survey items are presented in the following table

```{r BSI-var-prep}
# Pull question wording from qualtrics data
bsi_word <- qualtrics %>% 
  select(starts_with("BSI")) %>% 
  slice(1)

#create table with variable name, description, and notes
bsi_word_long <- bsi_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  slice(1:19)

```


```{r BSI-var-table, results ='asis'}
# Create the gt table object and apply generic theme
my_gt_table <- gt(bsi_word_long)

# Table-specific formatting (col width, names)
my_gt_table <- my_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(my_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```


#### Scale and Subscales

Information on total score and subscale variables are below. Variables were constructed by summing included items. 

```{r bsi alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
bsi_alpha <-
  complete %>%
  select(bsi1:bsi19) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_som <-
  complete %>%
  select(bsi2:bsi3,
         bsi10:bsi13,
         bsi15) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_anx <-
  complete %>%
  select(bsi1, bsi5, bsi9, bsi16:bsi18) %>%
  psych::alpha(check.keys = TRUE)

bsi_alpha_dep <-
  complete %>%
  select(bsi4, bsi6:bsi8, bsi14, bsi19) %>%
  psych::alpha(check.keys = TRUE)

```

```{r BSI-scale-table, results = 'asis'}
# Create the table as a data frame
bsi_scale_df <- data.frame(
  var_name = c("bsi_total", "bsi_soma_total", "bsi_anx_total", "bsi_dep_total"),
  scale = c("Total Score (19)", "Somatization (7)", "Anxiety (6)", "Depression (6)"),
  scale_construction = c("`bsi1`, `bsi2`, `bsi3`, `bsi4`, `bsi5`, `bsi6`, `bsi7`, `bsi8`, `bsi9`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi14`, `bsi15`, `bsi16`, `bsi17`, `bsi18`, `bsi19`",
                           "`bsi2`, `bsi3`, `bsi10`, `bsi11`, `bsi12`, `bsi13`, `bsi15`",
                           "`bsi1`, `bsi5`, `bsi9`, `bsi16`, `bsi17`, `bsi18`",
                           "`bsi4`, `bsi6`, `bsi7`, `bsi8`, `bsi14`, `bsi19`"),
  scale_range = c("0-76", "0-28", "0-24", "0-24"),
  alpha = c(round(bsi_alpha$total$raw_alpha, 3), round(bsi_alpha_som$total$raw_alpha, 3), round(bsi_alpha_anx$total$raw_alpha, 3), round(bsi_alpha_dep$total$raw_alpha, 3))
)

# Create the gt table object
bsi_scale_table <- gt(bsi_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(bsi_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

```{r bsi-mean-items}
# Create subset of BSI items
data_subset <- complete %>%
  select(bsi1:bsi19, bsi_total, bsi_soma_total, bsi_anx_total, bsi_dep_total)

# Calculate the summary statistics for each variable
summary_data <- lapply(data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_data <- as.data.frame(summary_data)

# Set items as first row
summary_data <- rbind(names(summary_data), summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
tbl <- summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
tbl

```


#### Distributions

Distributions are presented for the total score and each subscale

```{r bsi-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(x = bsi_total) +
  labs(title = 'Distribution of Total Scores for BSI Measure')


complete %>%
  composite_hist(x = bsi_soma_total) +
  labs(title = 'Distribution for BSI Somatization Subscale')

complete %>%
  composite_hist(x = bsi_anx_total) +
  labs(title = 'Distribution for BSI Anxiety Subscale')

complete %>%
  composite_hist(x = bsi_dep_total) +
  labs(title = 'Distribution for BSI Depression Subscale')

```


## Center for Epidemiologic Studies Depression Scale (CES-D)

### CES-D Description

The CES-D is used to assess ... *INSERT TEXT DESCRIPTION ABOUT CES-D MEASURE*

All 20 items from the CES-D were collected. Two subscales are included as variables, positive affect and depressive symptoms. Four items (`c4`, `c8`, `c12`, and `c16`) are/should be reverse scored which is noted in the variable table below. Higher scores indicate the presence of more symptoms.

Four additional variables (`c21`-`c24`) were included in this section to assess suicidality. Variables `c22` and `c23` are only applicable if participants responded "Yes" to `c21`.  

The missing data rule was not applied since all participants had less than 20% missing data. Missing data for each variable is presented in the summary information below. 

Reference: [@radloff1977ces](https://journals.sagepub.com/doi/abs/10.1177/014662167700100306); [DOI](https://doi.org/10.1177%2F014662167700100306)

-   Additional References:

    -   Cutoff Information:  [@henry2018determining](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4); [DOI](https://doi.org/10.1016/j.jad.2018.02.071)

    -   Items for Potential Subscales:  [@canady2009measurement](https://connect.springerpub.com/content/sgrjnm/17/2/91.abstract); [DOI](10.1891/1061-3749.17.2.91)
    
### CES-D Variables

#### Value Labels

All CES-D survey items (`c1`-`c20`) have the same response options

```{r CESD-label-table, results = 'asis'}

cesd_label_df <- data.frame(
  value = c("0", "1", "2", "3"),
  label = c("Rarely or none of the time",
            "Some or a little of the time",
            "Occasionally or a moderate amount of time",
            "Most or all of the time")
) %>% 
  t() %>% 
  as.data.frame()

cesd_label_df <- setNames(cesd_label_df[-1, ], unlist(cesd_label_df[1, ]))


#create table
cesd_label_table <- cesd_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(cesd_label_table)


```

Additional variables on suicidality (`c21`-`c24`) share the same response options
    
```{r CESD-label-table2, results = 'asis'}

cesd2_label_df <- data.frame(
  value = c("0", "1", "2"),
  label = c("No",
            "Yes",
            "Declined to Answer")
) %>% 
  t() %>% 
  as.data.frame()

cesd2_label_df <- setNames(cesd2_label_df[-1, ], unlist(cesd2_label_df[1, ]))


#create table
cesd2_label_table <- cesd2_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(150)) %>% 
  apply_labtab_theme() 

# Print the table
print(cesd2_label_table)


```

#### Survey Items

All CES-D survey items are presented in the following table

```{r CESD-var-prep}
# Pull question wording from qualtrics data
cesd_word <- qualtrics %>% 
  select(C1:C24) %>% 
  slice(1)

#create table with variable name, description, and notes
cesd_word_long <- cesd_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         #description = case_when(var_name == "c21" ~ "In the past 6 months, have you ever thought about killing yourself?"),
         notes = case_when(var_name == "c4" ~ "This item should be reverse scored. `c4_r` is reverse scored",
                           var_name == "c8" ~ "This item should be reverse scored. `c8_r` is reverse scored",
                           var_name == "c12" ~ "This item should be reverse scored. `c12_r` is reverse scored",
                           var_name == "c16" ~ "This item should be reverse scored. `c16_r` is reverse scored",
                           
                           var_name %in% c("c22", "c23") ~ "Skipped if `c21` = No",
                           TRUE ~ as.character(""))) %>%
  mutate(description = if_else(var_name == "c21", "In the past 6 months, have you ever thought about killing yourself?", description))
  

```


```{r CESD-var-table, results ='asis'}
# Create the gt table object and apply generic theme
cesd_gt_table <- gt(cesd_word_long)

# Table-specific formatting (col width, names)
cesd_gt_table <- cesd_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(250),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(cesd_gt_table)

```


#### Scale and Subscales

Information on aggregated scale and subscale variables are below. Total and subscale variables were constructed by summing corresponding items. 

```{r cesd-alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
cesd_alpha <-
  complete %>%
  select(c1:c16_r) %>%
  psych::alpha(check.keys = TRUE)

cesd_dep_alpha <-
  complete %>%
  select(c1:c20) %>%
  psych::alpha(check.keys = TRUE)

cesd_pos_aff_alpha <-
  complete %>%
  select(c4_r, c8_r, c12_r, c16_r) %>%
  psych::alpha(check.keys = TRUE)


cesd_alpha_table <- tibble(
  Scale = c('CESD', 'CESD - Depressive Symptoms',
            'CESD - Positive Affect'),
  Alpha = c(round(cesd_alpha$total$raw_alpha, 3),
            round(cesd_dep_alpha$total$raw_alpha, 3),
            round(cesd_pos_aff_alpha$total$raw_alpha, 3)
  )
)
```

```{r CESD-scale-table, results = 'asis'}
# Create the table as a data frame
cesd_scale_df <- data.frame(
  var_name = c("cesd_total", "cesd_dep_symp_total", "cesd_pos_aff_total"),
  scale = c("Total Score (20)", "Depression (16)", "Positive Affect (4)"),
  scale_construction = c("`c1`, `c2`, `c3`, `c4`, `c5`, `c6`, `c7`, `c8`, `c9`, `c10`, `c11`, `c12`, `c13`, `c14`, `c15`, `c16`, `c17`, `c18`, `c19`, `c20`",
                           "`c1`, `c2`, `c3`, `c5`, `c6`, `c7`, `c9`, `c10`, `c11`, `c13`, `c14`, `c15`, `c17`, `c18`, `c19`, `c20`",
                           "`c4_r`, `c8_r`, `c12_r`, `c16_r`"),
  scale_range = c("0-60", "0-48", "0-12"),
  alpha = c(round(cesd_alpha$total$raw_alpha, 3), round(cesd_dep_alpha$total$raw_alpha, 3), round(cesd_pos_aff_alpha$total$raw_alpha, 3))
)

# Create the gt table object
cesd_scale_table <- gt(cesd_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme()

# Print the table
print(cesd_scale_table)

```


### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

```{r cesd-mean-items}
# Create subset of CESD items
data_subset_cesd <- complete %>%
  select(c1:c3, c4, c5:c7, c8, c9:c11, c12, c13:c15, c16, c17:c20, cesd_total, cesd_dep_symp_total, cesd_pos_aff_total)

# Calculate the summary statistics for each variable
summary_data_cesd <- lapply(data_subset_cesd, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- sprintf("%.2f", round(sd(x, na.rm = TRUE), 2))
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
summary_df_cesd <- as.data.frame(summary_data_cesd) %>% 
  rbind(names(summary_data_cesd)) %>% 
  t() %>% 
  as.data.frame() %>% 
  select(`5`, everything())

# Create the gt table
cesd_tbl <- summary_df_cesd %>%
  gt() %>%
  cols_label(`5` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(2:5 ~ px(160)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
cesd_tbl

```
    
#### Distributions

Distributions are presented for the total score and each subscale

```{r cesd-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(cesd_total) +
  labs(
    title = 'CESD Total Score Distribution'
    )

complete %>%
  composite_hist(
    cesd_dep_symp_total
    ) +
  labs(
    title = 'Depressive Symptoms Subscale Distribution'
    )

complete %>%
  composite_hist(
    cesd_pos_aff_total,
    bins = 10
    ) +
  labs(
    title = 'Positive Affect Subscale Distribution'
    )
```

#### Clinical Categories

CES-D cutoff scores are presented below

*INSERT MORE INFO ON CUTOFF SCORES* - what are they, how many of them; how are they used

Reference: [@henry2018determining](https://www.sciencedirect.com/science/article/pii/S0165032717319274?casa_token=Aan1lg2Z8mUAAAAA:aun9j7DwQRQLhRqhbBJQfpPQG4fDv4yjN1WGHvzv-Hh9Pu58f7IhyGyPTDJmeAUZWonwmO7tfi4); [DOI](https://doi.org/10.1016/j.jad.2018.02.071)

```{r cutoff-plot-function}
#re-work JP cutoff function due to error "cant use `{{` in non-quoting function
cutoff_plot2 <- function(data,
                        x,
                        cutoff = 0,
                        cutoff_color = '#324B4A',
                        cutoff_other = NULL,
                        cutoff_other_color = '#95B1AF',
                        cutoff_other2 = NULL,
                        cutoff_other2_color = '#546085',
                        bins = 20) {

  library(magrittr)
  library(dplyr)
  library(ggplot2)

  x <- enquo(x)

  if (is.null(cutoff_other)) {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = '#246B69',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 20),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  } else if (is.null(cutoff_other2)) {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = '#246B69',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other,
                 color = cutoff_other_color,
                 linetype = 3,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 13),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  } else {
    data %>%
      ggplot(aes(!!x)) +
      geom_histogram(bins = bins,
                     color = 'white',
                     fill = 'black',
                     alpha = .7) +
      geom_vline(xintercept = cutoff,
                 color = cutoff_color,
                 linetype = 2,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other,
                 color = cutoff_other_color,
                 linetype = 3,
                 linewidth = 1.25) +
      geom_vline(xintercept = cutoff_other2,
                 color = cutoff_other2_color,
                 linetype = 4,
                 linewidth = 1.25)+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          panel.border = element_blank(),
          axis.line = element_line(colour = "black",size = .8),
          axis.text = element_text(size = 10), axis.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.key = element_rect(fill = "White",
                                    colour = "transparent"),
          plot.title = element_text(size= 13),
          #scale_x_discrete(guide = guide_axis(n.dodge=3))
    )
  }
}
```


```{r cesd-clinical}
complete %>%
  cutoff_plot2(
    x = cesd_total,
    cutoff = 16,
    cutoff_other = 23
  ) +
  labs(
    title = 'Cutoff Scores for CESD Total Scores',
    caption = 'Cutoffs are 16 and/or 23\nSee references for literature on cutoff scores.', 
    y = "Number of Participants"
  ) +
  geom_text(aes(x = 16, y = 16.5, label = "cutoff1", vjust = -.25, hjust = 1.2)) +
  geom_text(aes(x = 16, y = 16.5, label = "cutoff2", vjust = -.25, hjust = -1.8))
```


## Coronavirus Impacts Scale (Psychological Subscale)

### Coronavirus Impacts Scale Description

*TODO: NOTE FOR DATA CLEANINING: the variable name should be cis, codebook should be change accordingly *

The Coronavirus Impacts Scale is used to assess ... *TODO INSERT TEXT DESCRIPTION ABOUT Coronavirus Impacts Scale MEASURE*
  
For the present study, 3 items from the Coronavirus Impacts Scale (Psychological Subscale) were collected in order to *TODO INSERT TEXT*. 

`ciq1` need to be reverse scored. Higher scores indicate *TODO more severe mental health symptoms*. 

The missing data rule was not applied since there is no missing data among CIS variables. 

Reference: *TODO NEED REFERENCE *

### Coronavirus Impacts Scale Variables

#### Value Labels

All Coronavirus Impacts Scale variables have the same response options



```{r CIS-label-table, results = 'asis'}

cis_label_df <- data.frame(
  value = seq(1:7),
  label = c("Not true of me at all",
            "",
            "",
            "",
            "",
            "",
            "Very true of me")) %>% 
  t() %>% 
  as.data.frame()

cis_label_df <- setNames(cis_label_df[-1, ], unlist(cis_label_df[1, ]))


#create table
cis_label_table <- cis_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(c(1,7) ~ px(180),
             2:6 ~ px(79)) %>% 
  apply_labtab_theme()

# Print the table
print(cis_label_table)


```

#### Survey Items

All CIS survey items are presented in the following table

```{r CIS-var-prep}
# Pull question wording from qualtrics data
# CIS is from BIS question 20-22
cis_word <- qualtrics %>% 
  select(starts_with("BSI")) %>% 
  slice(1)

#create table with variable name, description, and notes
cis_word_long <- cis_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name),
         notes = case_when(var_name == "bsi22" ~ "This item should be reverse scored. `ciq3_r` is reverse scored",
                           TRUE ~ as.character("")
                           )) %>% 
  mutate(description = if_else(var_name == "bsi20", "I have become depressed because of the Coronavirus (COVID-19).", description)) %>%
  slice(20:22)




```

TODO: the variable name need to be change to ciq when make df 
```{r cis-var-table, results ='asis'}
# Create the gt table object and apply generic theme
cis_gt_table <- gt(cis_word_long)

# Table-specific formatting (col width, names)
cis_gt_table <- cis_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(cis_gt_table)

#WHEN RENDERING WITH PDF USE: 
#cis_gt_table
```


#### Scale and Subscales

Information on total score and subscale variables are below. Variables were constructed by summing included items. 


```{r cis alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
cis_alpha <-
  complete %>%
  select(ciq1:ciq3_r) %>%
  psych::alpha(check.keys = TRUE)

```

```{r CIS-scale-table, results = 'asis'}
# Create the table as a data frame
cis_scale_df <- data.frame(
  var_name = c("ciq_psych_total"),
  scale = c("Total Score (3)"),
  scale_construction = c("`ciq1`, `ciq2`, `ciq3_r`"),
  scale_range = c("3-21"),
  alpha = c(round(cis_alpha$total$raw_alpha, 3))
)

# Create the gt table object
cis_scale_table <- gt(cis_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(151)) %>% 
  apply_tbl_theme() 

# Print the table
print(cis_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

```{r cis-mean-items}
# Create subset of BSI items
cis_data_subset <- complete %>%
  select(ciq1:ciq2, ciq3, ciq_psych_total)

# Calculate the summary statistics for each variable
cis_summary_data <- lapply(cis_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
cis_summary_data <- as.data.frame(cis_summary_data)

# Set items as first row
cis_summary_data <- rbind(names(cis_summary_data), cis_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
cis_tbl <- cis_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(130)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
cis_tbl

```


#### Distributions

Distributions are presented for the total score and each subscale

```{r csi-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(
    x = ciq_psych_total,
    bins = 10
    ) +
  labs(title = 'Distribution for CIQ Psychological Scale')
```


## The Drug Abuse Screening Test (DAST)

### The Drug Abuse Screening Test Description

*TODO: ROW DATA INCORRECTLY CLEANED, WILL NEED RE_CLEAN!*
```{r dast re-code}
# This session should go together with the data cleaning 

# re-code total score 
# RECODE AWH8DAST (0 = 0) (1 THRU 5 = 1) (6 THRU 10 = 2) (11 THRU 15 = 3) (16 THRU 20 = 4) INTO AWHPDASC
# VALUE LABELS AWHPDASC
# 0 'None'
# 1 'Low'
# 2 'Intermediate (likely meets DSM criteria)'
# 3 'Substantial'
# 4 'Severe'.

complete$dast_total_r <- case_match(complete$dast_total,
                1:5 ~ 1,
                6:10 ~ 2,
                11:15 ~ 3,
                16:20 ~ 4, .default = complete$dast_total)

complete <- complete %>%
  mutate(dast_total_r = case_when(
    dast_total == 0 ~ 0,
    dast_total %in% 1:5 ~ 1,
    dast_total %in% 6:10 ~ 2,
    dast_total %in% 11:15 ~ 3,
    dast_total %in% 16:20 ~ 4,
    TRUE ~ NA_integer_
  ))

```

The The Drug Abuse Screening Test is used to assess ... *TODO INSERT TEXT DESCRIPTION ABOUT DAST*
  
For the present study, 22 items from the The Drug Abuse Screening Test (DAST) were collected in order to *TODO INSERT TEXT*. 

Two items (`d4` and `d5`) are/should to be reverse scored which is noted in the variable table below. *TODO Higher scores indicate more severe mental health symptoms. *

The missing data rule was applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses) 

Reference: [@gavin1989diagnostic](https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1360-0443.1989.tb03463.x);[DOI](https://doi.org/10.1111/j.1360-0443.1989.tb03463.x)


### DAST Variables

#### Value Labels

All The Drug Abuse Screening Test variables have the same response options



```{r DAST-label-table, results = 'asis'}

dast_label_df <- data.frame(
  value = c(0,1),
  label = c("Yes ",
            "No")) %>% 
  t() %>% 
  as.data.frame()

dast_label_df <- setNames(dast_label_df[-1, ], unlist(dast_label_df[1, ]))


#create table
dast_label_table <- dast_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(c(1,2) ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(dast_label_table)


```
Recoeded tatoal value lable 
```{r DAST-label-table-total, results = 'asis'}

dast_label_total <- data.frame(
  value = seq(0,4),
  label = c("None",
            "Low",
            "Intermediate (likely meets DSM criteria)",
            "Substantial",
            "Severe")) %>% 
  t() %>% 
  as.data.frame()

dast_label_total <- setNames(dast_label_total[-1, ], unlist(dast_label_total[1, ]))


#create table
dast_label_table_total <- dast_label_total %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(c(1:5) ~ px(151)) %>% 
  apply_labtab_theme()

# Print the table
print(dast_label_table_total)


```

#### Survey Items

All DAST survey items are presented in the following table

```{r DAST-var-prep}
# Pull question wording from qualtrics data
dast_word <- qualtrics %>% 
  select(starts_with("D")) %>% 
  slice(1)

#create table with variable name, description, and notes
dast_word_long <- dast_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name),
         notes = case_when(var_name == "d4" ~ "This item should be reverse scored. `d4_r` is reverse scored",
                           var_name == "d5" ~ "This item should be reverse scored. `d4_r` is reverse scored",
                           TRUE ~ as.character("")
                           )
         ) %>% 
  mutate(description = if_else(var_name == "d00", "Is TC currently pregnant?", description)) %>%
  slice(4:25)





```



```{r dast-var-table, results ='asis'}
# Create the gt table object and apply generic theme
dast_gt_table <- gt(dast_word_long)

# Table-specific formatting (col width, names)
dast_gt_table <- dast_gt_table %>% 
  cols_label(var_name = "Variable", 
             description = "Description",
             notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())
 

# Print the table
print(dast_gt_table)

#WHEN RENDERING WITH PDF USE: 
#dast_gt_table
```


#### Scale and Subscales

No subscales were created for this measure as there was a lack of evidence supporting a subscale structurek


```{r dast alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
dast_alpha <-
  complete %>%
  select(d1a:d3, d6:d5_r) %>%
  mutate(d2 = coalesce(d2a, d2b)) %>% 
  select(-d2a, -d2b) %>% 
  drop_na(d2) %>% 
  psych::alpha(check.keys = TRUE)

```

*TODO: need check the total *
```{r DAST-scale-table, results = 'asis'}
# Create the table as a data frame
dast_scale_df <- data.frame(
  var_name = c("dast_total"),
  scale = c("Total Score (22)"),
  scale_construction = c("`d00`, `d1a`, `d2a`, `d2b`, `d3`, `d4_r`, `d5_r`, `d6`, `d7`, `d8`, `d9`, `d10`, `d11`, `d12`, `d13`, `d14`, `d15`, `d16`, `d17`, `d18`, `d19`, `d20`"),
  scale_range = c("0-20"),
  alpha = c(round(dast_alpha$total$raw_alpha, 3))
)

# Create the gt table object
dast_scale_table <- gt(dast_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
             scale = "Scale (# of items)", 
             scale_construction = "Scale Construction",
             scale_range = "Range*",
             alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(dast_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

For binary items: 

```{r dast-binary-desc}
# Create subset of DAST items
dast_data_subset_binary <- complete %>%
  select(d1a:d3, d6:d5_r)

# Calculate the dichotomous summary statistics for each variable
dast_summary_data_binary <- lapply(dast_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dast_summary_data_binary <- as.data.frame(dast_summary_data_binary)

# Set items as first row
dast_summary_data_binary <- rbind(names(dast_summary_data_binary), dast_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dast_tbl_binary <- dast_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "No", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Yes", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
dast_tbl_binary


```

For total score: 

```{r dast-cont-desc}
# Create subset of DAST items
dast_data_subset <- complete %>%
  select(dast_total)

# Calculate the dichotomous summary statistics for each variable
dast_summary_data <- lapply(dast_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dast_summary_data <- as.data.frame(dast_summary_data) 

# Set items as first row
dast_summary_data <- rbind(names(dast_summary_data),dast_summary_data) %>% 
  t() %>% 
  as.data.frame() %>%
  mutate(Mean = if_else(Mean == "NaN", "NA", Mean)) %>%
  mutate(Range = if_else(Range == "Inf--Inf", "NA", Range))

 



# Create the gt table
dast_tbl <- dast_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
dast_tbl

```


#### Distributions

Distributions are presented for the total score and each subscale

```{r dast-distributions, class.source='fold', echo = FALSE}
complete %>%
  severity_plot(
  x = dast_total,
  bins = 20,
  low_xmin = 0,
  low_xmax = 5.5,
  medium_xmin = 5.5,
  medium_xmax = 10.5,
  large_xmin = 10.5,
  large_xmax = 15.5,
  critical_xmin = 15.5,
  critical_xmax = 20) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 3,
    y = -1.5,
    label = 'Low'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 8,
    y = -1.5,
    label = 'Intermediate'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 13,
    y = -1.5,
    label = 'Substantial'
  ) +
  annotate(
    geom = 'text',
    color = 'Black',
    x = 18,
    y = -1.5,
    label = 'Severe'
  ) +
  labs(
    title = 'Severity Categories',
    subtitle = 'Based on DAST',
    caption = 'Cutoffs are:\nLow = 1-5,\nIntermediate = 6-10,\nSubstantial = 11-15,\nSevere = 16-20',
    y = 'Number of Participants'
  )
```


## Conflict Tactics Scales (CTS2)

### Conflict Tactics Description

The Conflict Tactics is used to assess ... *TODO INSERT TEXT DESCRIPTION ABOUT Conflict Tactics MEASURE*

For the present study, 20 items from the Conflict Tactics were collected in order to calculate the Psychological Aggression, Physical Injury, Assault, Sexual Cohesion, Negotiation for TC and their partner respectively. 


No items need to be reverse scored. *TODO NEED REPLACE Higher scores indicate more severe mental health symptoms. *

The missing data rule was applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses)

Reference: [@straus2004short](https://connect.springerpub.com/content/sgrvv/19/5/507.abstract); [DOI](10.1891/vivi.19.5.507.63686)

### CTS2 Variables

#### Value Labels

All CTS2 variables have the same response options

```{r CTS2-label-table, results = 'asis'}

CTS2_label_df <- data.frame(
  value = c( "1", "2", "3", "4", "5", "6", "7", "8"),
  label = c("Once in the past year",
            "Twice in the past year",
            "3-5 times in the past year",
            "6-10 times in the past year",
            "11-20 times in the past year",
            "More than 20 times in the past year", 
            "Not in the past year, but it did happen before", 
            "This has never happened")
) %>% 
  t() %>% 
  as.data.frame()

CTS2_label_df <- setNames(CTS2_label_df[-1, ], unlist(CTS2_label_df[1, ]))


#create table
CTS2_label_table <- CTS2_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  #cols_width(everything() ~ px(100)) %>% 
  apply_labtab_theme()

# Print the table
print(CTS2_label_table)


```

#### Survey Items

All CTS2 survey items are presented in the following table

```{r CTS2-var-prep}
# Pull question wording from qualtrics data
CTS2_word <- qualtrics %>% 
  select(starts_with("CT")) %>% 
  slice(1)

#create table with variable name, description, and notes
CTS2_word_long <- CTS2_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         
         var_name = str_to_lower(var_name), 
         notes = as.character("")) %>% 
  mutate(description = if_else(var_name == "ct0", "Have you lived with any other children, under the age of 17, since the time of your last interview? Only think about children who you or your partner was responsible for parenting. Please do not include any children listed in the other sections or children that you have reported before.", 
                               if_else(var_name == "ct000", "How many new children are you parenting since your last interview on (last interview date)?",
                                       if_else(var_name ==  "cts screen", "Have you been in a (romantic) relationship in the past year?",
                                               if_else(var_name == "cts parent screen", "Have you parented a child (under 18) in the past year?", description))))
  ) %>%
  slice(1:26)

```


```{r CTS2-var-table, results ='asis'}
# Create the gt table object and apply generic theme
my_gt_table <- gt(CTS2_word_long)

# Table-specific formatting (col width, names)
my_gt_table <- my_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(notes ~ px(150),
             var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(my_gt_table)

#WHEN RENDERING WITH PDF USE: 
#my_gt_table
```

#### Scale and Subscales

Information on total score and subscale variables are below. Variables were constructed by summing included items. 
Authors describe that internal reliability is not appropriate for the `CTS2` measure. 
`CTS2` should not have a calculated total/average composite score
`CTS2` has three different ways of scoring (Prevalence, Severity, Mutuality)

*NEED fill Range*

```{r CTS2-scale-table, results = 'asis'}
# Create the table as a data frame
CTS2_scale_df <- data.frame(
  var_name = c("cts_psy_agg_ind_sev", "cts_injury_ind_sev", "cts_assault_ind_sev",   "cts_sex_ind_sev",       #TC   severity 
                "cts_psy_agg_part_sev","cts_injury_part_sev", "cts_assault_part_sev","cts_sex_part_sev",      #Partner serverity 

                "cts_psy_agg_ind_prev", "cts_injury_ind_prev", "cts_assault_ind_prev", "cts_sex_ind_prev", 
                "cts_psy_agg_part_prev", "cts_injury_part_prev", "cts_assault_part_prev", "cts_sex_part_prev",
               
                "cts_psy_agg_mutual", "cts_injury_mutual", "cts_assault_mutual", "cts_sex_mutual",
               
                "cts_negotiate_ind",    "cts_negotiate_part"),

  scale = c("TC Psychological Aggression (2)", "TC Physical Injury (2)", "TC Assault (2)", "TC Sexual Cohesion (2)",
            "Partner Psychological Aggression (2)", "Partner Physical Injury (2)", "Partner Assault (2)", "Partner Sexual Cohesion (2)",

            "TC Psychological Aggression (2)", "TC Physical Injury (2)", "TC Assault (2)", "TC Sexual Cohesion (2)",
            "Partner Psychological Aggression (2)", "Partner Physical Injury (2)", "Partner Assault (2)", "Partner Sexual Cohesion (2)",
            
            "Psychological Aggression (4)", "Physical Injury (4)", "Assaul (4)t", "Sexual Cohesion (4)",
            
            "TC Negotiation (2)", "Partner Negotiation (2)"
            ),
  score_method = c("Severity", "Severity", "Severity", "Severity",
                   "Severity", "Severity", "Severity", "Severity",
                   "Prevalence", "Prevalence", "Prevalence", "Prevalence", 
                   "Prevalence", "Prevalence", "Prevalence", "Prevalence", 
                   "Mutuality", "Mutuality", "Mutuality", "Mutuality",
                   "", ""
                   ),

  scale_construction = c("`ct3`, `ct13`", "`ct5`, `ct15`", "`ct9`, `ct11`", "`ct17`, `ct19`", 
                         "`ct4`, `ct14`", "`ct6`, `ct16`", "`ct10`, `ct12`", "`ct18`, `ct20`", 
                         
                         "`ct3`, `ct13`", "`ct5`, `ct15`", "`ct9`, `ct11`", "`ct17`, `ct19`", 
                         "`ct4`, `ct14`", "`ct6`, `ct16`", "`ct10`, `ct12`", "`ct18`, `ct20`",
                         
                         "`ct3`, `ct13`, `ct4`, `ct14`","`ct5`, `ct15`, `ct6`, `ct16`",
                         "`ct9`, `ct11`, `ct10`, `ct12`", "`ct17`, `ct19`, `ct18`, `ct20`",
                         
                         "`ct1`, `ct7`", "`ct2`, `ct8`"
                         
                         ),
  scale_range = c("", "", "", "", "", "", "", "", "", "",
                  "", "", "", "", "", "", "", "", "", "", 
                  "", "")
  )


# Create the gt table object
CTS2_scale_table <- gt(CTS2_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            score_method = "Score Method",
            scale_construction = "Scale Construction",
            scale_range = "Range*") %>% 
  tab_footnote(footnote = "*Range of possible values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  #cols_width(scale ~ px(200)) %>% 
  apply_tbl_theme() 

# Print the table
print(CTS2_scale_table)

```

### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and subscale score

```{r CTS2-mean-items}
# Create subset of CTS2 items
cts2_data_subset <- complete %>%
  select(ct1:ct20, starts_with("cts"))

# Calculate the summary statistics for each variable
cts2_summary_data <- lapply(cts2_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert cts2_summary_data to a data frame
cts2_summary_data <- as.data.frame(cts2_summary_data)

# Set items as first row
cts2_summary_data <- rbind(names(cts2_summary_data), cts2_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
cts2_tbl <- cts2_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(
    c(2,3,5) ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

   
# Render the table
cts2_tbl

```

#### Distributions

Distributions are presented for the total score and each subscale

##### Serverity distributions 
```{r CTS2-Severity-TC-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
complete %>%
  mutate(
    cts_psy_agg_ind_sev = case_when(
      cts_psy_agg_ind_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_ind_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_ind_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_ind_sev = as.factor(cts_psy_agg_ind_sev),
    cts_psy_agg_ind_sev = relevel(cts_psy_agg_ind_sev, 'No Psychological Aggression')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Individual (TC) Psychological Aggression Severity',
       y = "Number of Participants") + 
  THEME


# Psychical Injury 
complete %>%
  mutate(
    cts_injury_ind_sev = case_when(
      cts_injury_ind_sev == 0 ~ 'No Injury',
      cts_injury_ind_sev == 1 ~ 'Minor Injury',
      cts_injury_ind_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_ind_sev = as.factor(cts_injury_ind_sev),
    cts_injury_ind_sev = relevel(cts_injury_ind_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_ind_sev
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Individual (TC) Physical Injury Severity',
       y = "Number of Participants") + 
  THEME

# Assault 
complete %>%
  mutate(
    cts_assault_ind_sev = case_when(
      cts_assault_ind_sev == 0 ~ 'No Assault',
      cts_assault_ind_sev == 1 ~ 'Minor Assault',
      cts_assault_ind_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_ind_sev = as.factor(cts_assault_ind_sev),
    cts_assault_ind_sev = relevel(cts_assault_ind_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_ind_sev
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Individual (TC) Assault Severity',
       y = 'Number of Participants') +
  THEME

# Sexual Cohesion
complete %>%
  mutate(
    cts_sex_ind_sev = case_when(
      cts_sex_ind_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_ind_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_ind_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_ind_sev = as.factor(cts_sex_ind_sev),
    cts_sex_ind_sev = relevel(cts_sex_ind_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_ind_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Individual (TC) Sexual Cohesion Severity',
       y = "Number of Participants") + 
  THEME

```
```{r CTS2-Severity-Partner-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
complete %>%
  mutate(
    cts_psy_agg_part_sev = case_when(
      cts_psy_agg_part_sev == 0 ~ 'No Psychological Aggression',
      cts_psy_agg_part_sev == 1 ~ 'Minor Psychological Aggression',
      cts_psy_agg_part_sev == 2 ~ 'Severe Psychological Aggression'
    ),
    cts_psy_agg_part_sev = as.factor(cts_psy_agg_part_sev),
    cts_psy_agg_part_sev = relevel(cts_psy_agg_part_sev, 'No Psychological Aggression')
    ) %>%
  ggplot(
    aes(
      cts_psy_agg_part_sev
    )
  ) +
  bar_style +
   scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Partner Psychological Aggression Severity',
       y = "Number of Participants") + 
  THEME

# Physical Injury
complete %>%
  mutate(
    cts_injury_part_sev = case_when(
      cts_injury_part_sev == 0 ~ 'No Injury',
      cts_injury_part_sev == 1 ~ 'Minor Injury',
      cts_injury_part_sev == 2 ~ 'Severe Injury'
    ),
    cts_injury_part_sev = as.factor(cts_injury_part_sev),
    cts_injury_part_sev = relevel(cts_injury_part_sev, 'No Injury')
  ) %>%
  ggplot(
    aes(
      cts_injury_part_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Partner Physical Injury Severity',
       y = "Number of Participants") + 
  THEME


# Assault
complete %>%
  mutate(
    cts_assault_part_sev = case_when(
      cts_assault_part_sev == 0 ~ 'No Assault',
      cts_assault_part_sev == 1 ~ 'Minor Assault',
      cts_assault_part_sev == 2 ~ 'Severe Assault'
    ),
    cts_assault_part_sev = as.factor(cts_assault_part_sev),
    cts_assault_part_sev = relevel(cts_assault_part_sev, 'No Assault')
  ) %>%
  ggplot(
    aes(
      cts_assault_part_sev
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Partner Assault Severity',
       y = "Number of Participants") + 
  THEME

# Sexual Cohesion
complete %>%
  mutate(
    cts_sex_part_sev = case_when(
      cts_sex_part_sev == 0 ~ 'No Sexual Cohesion',
      cts_sex_part_sev == 1 ~ 'Minor Sexual Cohesion',
      cts_sex_part_sev == 2 ~ 'Severe Sexual Cohesion'
    ),
    cts_sex_part_sev = as.factor(cts_sex_part_sev),
    cts_sex_part_sev = relevel(cts_sex_part_sev, 'No Sexual Cohesion')
  ) %>%
  ggplot(
    aes(
      cts_sex_part_sev
    )
  ) +
  bar_style +
  scale_x_discrete(labels = label_wrap(10)) +
  labs(title = 'Distribution of Partner Sexual Cohesion Severity',
       y = "Number of Participants") + 
  THEME
```

##### Prevalence distributions
*TODO NA was removed when generating following Prevalence plot*
```{r CTS2-Prevalence-distributions, class.source='fold', echo = FALSE}
# Psychological Aggression 
complete %>%
  pivot_longer(
    cols = c(cts_psy_agg_ind_prev, cts_psy_agg_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_psy_agg_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_psy_agg_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Psychological Aggression Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Physical Injury
complete %>%
  pivot_longer(
    cols = c(cts_injury_ind_prev, cts_injury_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_injury_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_injury_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Physical Injury Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Assault
complete %>%
  pivot_longer(
    cols = c(cts_assault_ind_prev, cts_assault_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_assault_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_assault_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Assault Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME

# Sexual Cohesion
complete %>%
  pivot_longer(
    cols = c(cts_sex_ind_prev, cts_sex_part_prev),
    names_to = 'ind_part',
    values_to = 'prevalence'
  ) %>%
  mutate(
    ind_part = case_when(
      ind_part == 'cts_sex_ind_prev' ~ 'Individual (TC)',
      ind_part == 'cts_sex_part_prev' ~ 'Partner'
    )
  ) %>%
  group_by(ind_part) %>%
  mutate(
    sum_prev = sum(prevalence, na.rm = T)
  ) %>%
  ungroup() %>%
  ggplot(
    aes(
      ind_part, sum_prev
    )
  ) +
  geom_col(
    aes(fill = ind_part),
    position = 'dodge'
  ) +
  labs(title = 'Distribution of Sexual Cohesion Prevalence') +
  scale_fill_manual(values = Two_color) +
  THEME
```

##### Mutuality distributions
```{r CTS2-Mutuality-distributions, class.source='fold', echo = FALSE}

# Psychological Aggression 
complete %>%
  mutate(
    cts_psy_agg_mutual = case_when(
      cts_psy_agg_mutual == 0 ~ 'Neither',
      cts_psy_agg_mutual == 1 ~ 'Male Only',
      cts_psy_agg_mutual == 2 ~ 'Female Only',
      cts_psy_agg_mutual == 3 ~ 'Both'
    ),
    cts_psy_agg_mutual = as.factor(cts_psy_agg_mutual),
    cts_psy_agg_mutual = relevel(cts_psy_agg_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_psy_agg_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Psychological Aggression',
       y = "Number of Participants") +
  THEME



# Physical Injury
complete %>%
  mutate(
    cts_injury_mutual = case_when(
      cts_injury_mutual == 0 ~ 'Neither',
      cts_injury_mutual == 1 ~ 'Male Only',
      cts_injury_mutual == 2 ~ 'Female Only',
      cts_injury_mutual == 3 ~ 'Both'
    ),
    cts_injury_mutual = as.factor(cts_injury_mutual),
    cts_injury_mutual = relevel(cts_injury_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_injury_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Injury',
       y = "Number of Participants") +
  THEME


# Assault
complete %>%
  mutate(
    cts_assault_mutual = case_when(
      cts_assault_mutual == 0 ~ 'Neither',
      cts_assault_mutual == 1 ~ 'Male Only',
      cts_assault_mutual == 2 ~ 'Female Only',
      cts_assault_mutual == 3 ~ 'Both'
    ),
    cts_assault_mutual = as.factor(cts_assault_mutual),
    cts_assault_mutual = relevel(cts_assault_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_assault_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Assault',
       y = "Number of Participants") +
  THEME

# Sexual Cohesion
complete %>%
  mutate(
    cts_sex_mutual = case_when(
      cts_sex_mutual == 0 ~ 'Neither',
      cts_sex_mutual == 1 ~ 'Male Only',
      cts_sex_mutual == 2 ~ 'Female Only',
      cts_sex_mutual == 3 ~ 'Both'
    ),
    cts_sex_mutual = as.factor(cts_sex_mutual),
    cts_sex_mutual = relevel(cts_sex_mutual, 'Neither')
  ) %>%
  ggplot(
    aes(
      cts_sex_mutual
    )
  ) +
  bar_style +
  labs(title = 'Distribution of Mutual Sexual Cohesion',
       y = "Number of Participants") +
  THEME
```


## Child Abuse (BCAP)
TODO: change above name to actual scale name

### BCAP Description

The BCAP is used to assess ... *TODO INSERT TEXT DESCRIPTION ABOUT BSI MEASURE*

For the present study, 34 items from the BSI were collected in order to *TODO: INSERT TEXT  *

Four items (`q1`, `q2`, `q23`, and `q29`) are/should be reverse scored which is noted in the variable table below. *TODO: NEED CHANGE THE TEXT: Higher scores indicate more severe mental health symptoms. *

The missing data rule was Applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses) 

Reference: [@ondersma2005brief](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug); 
[DOI](https://doi.org/10.1207/s15374424jccp3402_9)

### Child Abuse (BCAP) Variables

#### Value Labels

All BCAP variables have the same response options

```{r BCAP-label-table, results = 'asis'}

bcap_label_df <- data.frame(
  value = c("0", "1"),
  label = c("Disagree",
            "Agree")
) %>% 
  t() %>% 
  as.data.frame()

bcap_label_df <- setNames(bcap_label_df[-1, ], unlist(bcap_label_df[1, ]))


#create table
bcap_label_table <- bcap_label_df %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(180)) %>% 
  apply_labtab_theme()

# Print the table
print(bcap_label_table)


```

#### Survey Items

All BCAP survey items are presented in the following table

```{r bcap-var-prep}
# Pull question wording from qualtrics data
bcap_word <- qualtrics %>% 
  select(starts_with("q")) %>% 
  slice(1)

#create table with variable name, description, and notes
bcap_word_long <- bcap_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         notes = case_when(var_name == "q1" ~ "This item should be reverse scored. `q1_r` is reverse scored",
                           var_name == "q2" ~ "This item should be reverse scored. `q2_r` is reverse scored",
                           var_name == "q23" ~ "This item should be reverse scored. `q23_r` is reverse scored",
                           var_name == "q29" ~ "This item should be reverse scored. `q29_r` is reverse scored",
                           
                           var_name %in% c("c22", "c23") ~ "Skipped if `c21` = No",
                           TRUE ~ as.character(""))) %>%
  slice(1:34)


```


```{r bcap-var-table, results ='asis'}
# Create the gt table object and apply generic theme
bcap_gt_table <- gt(bcap_word_long)

# Table-specific formatting (col width, names)
bcap_gt_table <- bcap_gt_table %>% 
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  apply_tbl_theme() %>% 
  cols_width(var_name ~ px(100)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(bcap_gt_table)

#WHEN RENDERING WITH PDF USE: 
#bcap_gt_table
```
#### Scale and Subscales

Information on total score and subscale variables are below. Variables were constructed by summing included items. 

```{r bcap alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
# Total
bcap_alpha <- 
  complete %>% 
  select(
    q1_r,
    q2_r,
    q3:q22,
    q23_r,
    q24:q28,
    q29_r,
    q30:q34
  ) %>% 
  psych::alpha(check.keys = TRUE)

bcap_risk_alpha <-
  complete %>%
  select(
    q1_r,
    q3,
    q5:q8,
    q10:q14,
    q16:q17,
    q19:q20,
    q22,
    q23_r,
    q24:q25,
    q27,
    q29_r,
    q30:q33
    ) %>%
  psych::alpha(check.keys = TRUE)

bcap_happy_alpha <- 
  complete %>% 
  select(q1_r, q23_r, q29_r) %>% 
  psych::alpha(check.keys = TRUE)

bcap_feel_pers_alpha <- 
  complete %>% 
  select(q3, q25, q33) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lonely_alpha <- 
  complete %>% 
  select(q5, q12, q22, q31) %>% 
  psych::alpha(check.keys = TRUE)

bcap_fam_conf_alpha <- 
  complete %>% 
  select(q6, q13, q17) %>% 
  psych::alpha(check.keys = TRUE)

bcap_rigid_alpha <-
  complete %>% 
  select(q7, q14, q20, q32) %>% 
  psych::alpha(check.keys = TRUE)

bcap_distress_alpha <- 
  complete %>% 
  select(q8, q11, q16, q19, q27) %>% 
  psych::alpha(check.keys = TRUE)

bcap_poverty_alpha <- 
  complete %>% 
  select(q10, q30) %>% 
  psych::alpha(check.keys = TRUE)

bcap_lie_alpha <-
  complete %>% 
  select(q4, q9, q15, q21, q26, q34) %>% 
  psych::alpha(check.keys = TRUE)

bcap_random_alpha <-
  complete %>% 
  select(q2_r, q19, q28) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r bcap-scale-table, results = 'asis'}
# Create the table as a data frame
bcap_scale_df <- data.frame(
  var_name = c("bcap_total", "bcap_risk", "bcap_happy_total", "bcap_feel_pers_total", "bcap_lonely_total", "bcap_fam_conf_total", "bcap_rigid_total","bcap_distress_total", "bcap_poverty_total", "bcap_lie_total", "bcap_random_total"),
  scale = c("BCAP complete Scale (34)", "BCAP Risk Scale (26)", "Happiness (3)", "Feelings of persecution", "Loneliness (4)", "Family conflict (3)", "Rigidity (4)", "Distress (5)", "Poverty (2)", "Lie (6)", "Random responding (3)"),
  scale_construction = c("`q1_r`,`q2_r`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q9`, `q10`, `q11`, `q12`, `q13`, `q14`, `q15`, `q16`, `q17`, `q18`, `q19`, `q20`, `q21`, `q22`, `q23_r`, `q24`, `q25`, `q26`, `q27`, `q28`, `q29_r`, `q30`, `q31`, `q32`, `q33`, `q34`", 
                         "`q1_r`, `q3`, `q4`, `q5`, `q6`, `q7`, `q8`, `q10`, `q11`, `q12`, `q13`, `q14`, `q16`, `q17`, `q19`, `q20`, `q22`, `q23_r`, `q24`, `q25`, `q27`, `q29_r`, `q30`, `q31`, `q32`, `q33`", 
                         "`q1_r`, `q23_r`, `q29_r`", 
                         "`q3`, `q25`, `q33`", 
                         "`q5`, `q12`, `q22`, `q31`", 
                         "`q6`, `q13`, `q17`", 
                         "`q7`, `q14`, `q20`, `q32`", 
                         "`q8`, `q11`, `q16`, `q19`, `q27`", 
                         "`q10`, `q30`", 
                         "`q4`, `q9`, `q15`, `q21`, `q26`, `q34`,", 
                         "`q2`, `q18`, `q28`"),
  scale_range = c("","","","","","","","","","", ""), #TODO fill in range 
   alpha = c(round(bcap_alpha$total$raw_alpha, 3),
              round(bcap_risk_alpha$total$raw_alpha, 3),
              round(bcap_happy_alpha$total$raw_alpha, 3),
              round(bcap_feel_pers_alpha$total$raw_alpha, 3),
              round(bcap_lonely_alpha$total$raw_alpha, 3),
              round(bcap_fam_conf_alpha$total$raw_alpha, 3), 
              round(bcap_rigid_alpha$total$raw_alpha, 3), 
              round(bcap_distress_alpha$total$raw_alpha, 3),
              round(bcap_poverty_alpha$total$raw_alpha, 3), 
              round(bcap_lie_alpha$total$raw_alpha, 3),
              round(bcap_random_alpha$total$raw_alpha, 3))
)

# Create the gt table object
bcap_scale_table <- gt(bcap_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(bcap_scale_table)

```
### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

For binary items
```{r bcap-binary-desc}

# Create subset of BCAP items
bcap_data_subset_binary <- complete %>%
  select(q1_r,
         q2_r,
         q3:q22,
         q23_r,
         q24:q28,
         q29_r,
         q30:q34)

# Calculate the dichotomous summary statistics for each variable
bcap_summary_data_binary <- lapply(bcap_data_subset_binary, function(x) {
  per_no <- paste0(round(sum(x == 0, na.rm = TRUE) / length(x) *100, 1), "%")
  per_yes <- paste0(round(sum(x == 1, na.rm = TRUE) / length(x) *100, 1), "%")
  num_no <- sum(x == 0, na.rm = TRUE)
  num_yes <-sum(x == 1, na.rm = TRUE)
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(per_no = per_no, per_yes = per_yes, num_no = num_no, num_yes = num_yes, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
bcap_summary_data_binary <- as.data.frame(bcap_summary_data_binary)

# Set items as first row
bcap_summary_data_binary <- rbind(names(bcap_summary_data_binary), bcap_summary_data_binary) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
bcap_tbl_binary <- bcap_summary_data_binary %>%
  gt() %>%
  cols_label(`1` = "Variable",
             num_no = "N",
             per_no = "%",
             num_yes = "N",
             per_yes = "%",
             Missing = "% Missing") %>% 
  cols_width(everything() ~ px(115),
             num_no ~ px(100),
             num_yes ~ px(100)) %>%
  cols_align(columns = c("per_no", "per_yes", "num_no", "num_yes", "Missing"), align = "center") %>% 
  tab_spanner(label = "Disagree", columns = c(num_no, per_no)) %>% 
  tab_spanner(label = "Agree", columns = c(num_yes, per_yes)) %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1")),
            locations = cells_column_spanners()) %>% 
  apply_tbl_theme() %>% 
  tab_style(style = list(cell_fill(color = colorspace::lighten("#9BB6D1", .4))),
            locations = cells_column_labels(columns = c(num_yes, num_no, per_yes, per_no))) 

# Render the table
bcap_tbl_binary
```

```{r bcap-mean-items}
# Create subset of bcap items
bcap_data_subset <- complete %>%
  select(
    bcap_risk_total, bcap_happy_total, bcap_feel_pers_total, bcap_lonely_total, bcap_fam_conf_total, bcap_rigid_total, bcap_distress_total, bcap_poverty_total, bcap_lie_total, bcap_random_total)

# Calculate the summary statistics for each variable
bcap_summary_data <- lapply(bcap_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
bcap_summary_data <- as.data.frame(bcap_summary_data)

# Set items as first row
bcap_summary_data <- rbind(names(bcap_summary_data), bcap_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
bcap_tbl <- bcap_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(1 ~ px(165),2:5 ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
bcap_tbl

```

#### Distributions

Distributions are presented for the total score and each subscale

```{r bcap-distributions, class.source='fold', echo = FALSE}
#Risk 
complete %>%
  composite_hist(
    x = bcap_risk_total
  ) +
  labs(
    title = 'Distribution of Total Scores for BCAP Risk Scale'
  )

# Happiness 
complete %>% 
  composite_hist(
    x = bcap_happy_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Happiness Subscale'
  )

# Feelings
complete %>% 
  composite_hist(
    x = bcap_feel_pers_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Feelings of Persecution Subscale'
  )

# Loneliness
complete %>% 
  composite_hist(
    x = bcap_lonely_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Loneliness Subscale'
  )

# Family Conflict
complete %>% 
  composite_hist(
    x = bcap_fam_conf_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Family Conflict Subscale'
  )

# Rigidity
complete %>% 
  composite_hist(
    x = bcap_rigid_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Rigidity Subscale'
  )

# Distress
complete %>% 
  composite_hist(
    x = bcap_distress_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Distress Subscale'
  )

# Poverty
complete %>% 
  composite_hist(
    x = bcap_poverty_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Poverty Subscale'
  )

# Lying
complete %>% 
  composite_hist(
    x = bcap_lie_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Lying Subscale'
  )
    
# Random Responding 
complete %>% 
  composite_hist(
    x = bcap_random_total,
    bins = 5
  ) +
  labs(
    title = 'Distribution For BCAP Random Responding Subscale'
  ) 
```

## Partner Relationships (DYADC)
<!-#TODO: change above name to actual scale name ->

### DYADC Description

The DYADC is used to assess ... #TODO: *INSERT TEXT DESCRIPTION ABOUT BSI MEASURE*

For the present study, 32 items from the BSI were collected in order to *TODO: INSERT TEXT  *

Two items `e18` and `e19` are/should be reverse scored which is noted in the variable table below. *TODO: NEED CHANGE THE TEXT: Higher scores indicate more severe mental health symptoms. *

The missing data rule was Applied. Calculations were completed only with participants that had less then 20% missing data (this includes `-77` responses) 

Reference: [@ondersma2005brief](https://www.tandfonline.com/doi/abs/10.1207/s15374424jccp3402_9?casa_token=ZIJ3j8CLmK0AAAAA:_ztEWiTg5FO0Y3Jb_fL-zTuyqSmH623f0Q91STiqNR3jYvQyPzUiTqLSW3E5_U4iAucWcpqvbHAUug); 
[DOI](https://doi.org/10.1207/s15374424jccp3402_9)
Reference: [@spanier1976measuring](https://www.jstor.org/stable/350547);[DOI](https://doi.org/10.2307/350547)

### DYADC Variables

#### Value Labels

Multiple response options applied for DYADC

Response options for items `e1` to `e15`.
```{r dyadc-label-table, results = 'asis'}

dyadc_label_df_1 <- data.frame(
  value = c("0", "1", "2", "3", "4", "5"),
  label = c("Always Disagree",
            "Almost Always Disagree",
            "Frequently Disagree", 
            "Occasionally Disagree",
            "Almost Always Agree", 
            "Always Agree")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_1 <- setNames(dyadc_label_df_1[-1, ], unlist(dyadc_label_df_1[1, ]))


#create table
dyadc_label_table_1 <- dyadc_label_df_1 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(151)) %>% 
  apply_labtab_theme()

# Print the table
print(dyadc_label_table_1)


```
Response options for items `e16` to `e22`, except `e18` and `e19` are reverse scored
```{r dyadc-label-table_2, results = 'asis'}

dyadc_label_df_2 <- data.frame(
  value = c("0", "1", "2", "3", "4", "5"),
  label = c("Never",
            "Rarely",
            "Occasionally", 
            "More often than not",
            "Most of the time", 
            "All the time")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_2 <- setNames(dyadc_label_df_2[-1, ], unlist(dyadc_label_df_2[1, ]))


#create table
dyadc_label_table_2 <- dyadc_label_df_2 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(151)) %>% 
  apply_labtab_theme()



# Print the table
print(dyadc_label_table_2)
```

Response options for items `e23` and `e24`
```{r dyadc-label-table_3, results = 'asis'}

dyadc_label_df_3 <- data.frame(
  value = c("0", "1", "2", "3", "4"),
  label = c("Never",
            "Rarely", 
            "Occasionally",
            "Almost every day", 
            "Every day")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_3 <- setNames(dyadc_label_df_3[-1, ], unlist(dyadc_label_df_3[1, ]))


#create table
dyadc_label_table_3 <- dyadc_label_df_3 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(151)) %>% 
  apply_labtab_theme()

# Print the table
print(dyadc_label_table_3)
```

Response options for items `e25` to `e28`
```{r dyadc-label-table_4, results = 'asis'}

dyadc_label_df_4 <- data.frame(
  value = c("0", "1", "2", "3", "4", "5"),
  label = c("Never",
            "Less than once a month", 
            "Once or twice a month",
            "Once or twice a week", 
            "Once a day",
            "More often")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_4 <- setNames(dyadc_label_df_4[-1, ], unlist(dyadc_label_df_4[1, ]))


#create table
dyadc_label_table_4 <- dyadc_label_df_4 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(151)) %>% 
  apply_labtab_theme()

# Print the table
print(dyadc_label_table_4)


```

Response options for items `e29` and `e30`
```{r dyadc-label-table_5, results = 'asis'}

dyadc_label_df_5 <- data.frame(
 value = c("0", "1"),
  label = c("Yes",
            "No")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_5 <- setNames(dyadc_label_df_5[-1, ], unlist(dyadc_label_df_5[1, ]))


#create table
dyadc_label_table_5 <- dyadc_label_df_5 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(100)) %>% 
  apply_labtab_theme()

# Print the table
print(dyadc_label_table_5)


```
Response options for items `e31`
```{r dyadc-label-table_6, results = 'asis'}

dyadc_label_df_6 <- data.frame(
  value = c("0", "1", "2", "3", "4", "5", "6"),
  label = c("Extremely Unhappy",
            "Fairly Unhappy", 
            "A Little Unhappy",
            "Happy",
            "Very Happy",
            "Extremely Happy",
            "Perfect")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_6 <- setNames(dyadc_label_df_6[-1, ], unlist(dyadc_label_df_6[1, ]))


#create table
dyadc_label_table_6 <- dyadc_label_df_6 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(129)) %>% 
  apply_labtab_theme()

# Print the table
print(dyadc_label_table_6)


```

Response options for items `e32`
```{r dyadc-label-table_7, results = 'asis'}

dyadc_label_df_7 <- data.frame(
  value = c("0", "1", "2", "3", "4", "5"),
  label = c("My relationship can never succeed, and there is no more that I can do to keep the relationship going.", 
            "It would be nice if it succeeded, but I refuse to do any more than I am doing now to keep the relationship going.",
            "It would be nice if my relationship succeeded, but I can't do much more than I'm doing now to help it succeed.",
            "I want very much for my relationship to succeed, and will do my fair share to see that it does.",
            "I want very much for my relationship to succeed, and will do all I can to see that it does.",
            "I want desperately for my relationship to succeed, and would go to almost any length to see that it does.")
) %>% 
  t() %>% 
  as.data.frame()

dyadc_label_df_7 <- setNames(dyadc_label_df_7[-1, ], unlist(dyadc_label_df_7[1, ]))


#create table
dyadc_label_table_7 <- dyadc_label_df_7 %>%
  gt() %>% 
  tab_options(table.border.top.width = 1, table.border.bottom.width = 1,
              table.border.left.width = 1, table.border.right.width = 1) %>% 
  cols_width(everything() ~ px(151)) %>% 
  apply_labtab_theme()

# Print the table
print(dyadc_label_table_7)


```
#### Survey Items

All dyadc survey items are presented in the following table

```{r dyadc-var-prep}
# Pull question wording from qualtrics data
dyadc_word <- qualtrics %>% 
  select(starts_with("E")) %>%
  slice(1) %>%
  select(-(1:2))

#create table with variable name, description, and notes
dyadc_word_long <- dyadc_word %>% 
  pivot_longer(cols = everything(), 
               names_to = "var_name",
               values_to = "description") %>% 
  mutate(description = str_replace(description, "^\\d+\\.\\s*", ""),
         var_name = str_to_lower(var_name), 
         value = case_when(row_number() <= 15  ~ "0 = Always Disagree 
                                                 \n1 = Almost Always Disagree
                                                 \n2 = Frequently Disagree
                                                 \n3 = Occasionally Disagree
                                                 \n4 = Almost Always Agree
                                                 \n5 = Always Agree",
                           row_number() %in% c(16, 17, 20:22) ~ "0 = All the time 
                                                 \n1 = Most of the time
                                                 \n2 = More often than not
                                                 \n3 = Occasionally
                                                 \n4 = Rarely
                                                 \n5 = Never",
                           row_number() %in% c(18,19) ~ "0 = Never
                                                 \n1 = Rarely
                                                \n2 = Occasionally
                                                 \n3 = More often than not
                                                 \n4 = Most of the time
                                                 \n5 = All the time ",
                           between(row_number(), 23, 24 ) ~ "0 = Never
                                                 \n1 = Rarely
                                                 \n2 = Occasionally
                                                 \n3 = Almost every day
                                                 \n4 = Every day",
                           between(row_number(), 25,28) ~ "0 = Never
                                                 \n1 = Less than once a month
                                                 \n2 = Once or twice a month
                                                 \n3 = Once or twice a week
                                                 \n4 = Once a day
                                                 \n5 = More often",
                           row_number() %in% c(29,30) ~ "0 = Yes
                                                 \n1 = No",
                           row_number() %in% c(31) ~ "0 = Extremely Unhappy
                                                 \n1 = Fairly Unhappy
                                                 \n2 = A Little Unhappy
                                                 \n3 = Happy
                                                 \n4 = Very Happy
                                                 \n5 = Extremely Happy
                                                 \n6 = Perfect",
                           row_number() >= 32 ~ "0 =	My relationship can never succeed, and there is no more that I can do to keep the relationship going.
                                                 \n1 =	It would be nice if it succeeded, but I refuse to do any more than I am doing now to keep the relationship going.
                                                 \n2 =	It would be nice if my relationship succeeded, but I cant do much more than Im doing now to help it succeed.
                                                 \n3 =	I want very much for my relationship to succeed, and will do my fair share to see that it does.
                                                 \n4 =	I want very much for my relationship to succeed, and will do all I can to see that it does.
                                                 \n5 =	I want desperately for my relationship to succeed, and would go to almost any length to see that it does."
                           ),
         notes = case_when(var_name == "e18" ~ "This item should be reverse scored. `e18_r` is reverse scored",
                           var_name == "e19" ~ "This item should be reverse scored. `e19_r` is reverse scored",
                           TRUE ~ as.character(""))
         ) %>%
   mutate(description = if_else(var_name == "e31", " Please indicate the number that best describes the degree of happiness in your relationship.",
                               if_else(var_name == "e32", "Which of the following statements best describes how you feel about the future of your relationship? Please indicate only one answer", description))) %>%
  slice(1:32)


```


```{r dyadc-var-table, results ='asis'}
# Create the gt table object and apply generic theme
dyadc_gt_table <- gt(dyadc_word_long)

# Table-specific formatting (col width, names)
dyadc_gt_table <- dyadc_gt_table %>% 
  apply_tbl_theme() %>% 
  tab_row_group(label = "Please indicate if items below were problems in your relationships in the past few weeks.", 
                rows = 29:32,
                id = "set4") %>%
  tab_row_group(label = "Thinking about the past 6 months,how often do you", 
                rows = 25:28,
                id = "set3") %>%
  tab_row_group(label = "In the past 6 months, how often. . .", 
                rows = 23:24,
                id = "set2") %>%
  tab_row_group(label = "Thinking about the past 6 months, how often do you. . . ", 
                rows = 1:22,
                id = "set1")%>%
  cols_label(var_name = "Variable", 
            description = "Description",
            notes = "Notes") %>% 
  tab_style(style = list(cell_fill(color = "#9BB6D1", alpha = 0.2),
                         cell_borders(sides = c("left", "right", "top", "bottom"))),
            locations = cells_row_groups(groups = c("set1", "set2", "set3", "set4"))) %>%
  cols_width(notes ~ px(150),
             var_name ~ px(100),
             value ~ px(225)) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_column_labels())

# Print the table
print(dyadc_gt_table)

#WHEN RENDERING WITH PDF USE: 
#dyadc_gt_table


```
#### Scale and Subscales

Information on total score and subscale variables are below. Variables were constructed by summing included items. 

```{r dyadc alpha, echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE}
#Calculate internal reliability 
dyadc_alpha <-
  complete %>% 
  select(
    e1:e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_con_alpha <-
  complete %>% 
  select(
    e1:e13
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_aff_exp_alpha <-
  complete %>% 
  select(
    e4, e6, e29, e30
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_satis_alpha <-
  complete %>% 
  select(
    e16:e23,
    e31,
    e32
  ) %>% 
  psych::alpha(check.keys = TRUE)

dyadc_cohes_alpha <-
  complete %>% 
  select(
    e24:e28
  ) %>% 
  psych::alpha(check.keys = TRUE)
```

```{r dyadc-scale-table, results = 'asis'}
# Create the table as a data frame
dyadc_scale_df <- data.frame(
  var_name = c("dyadc_total", "dyadc_con_total", "dyadc_aff_exp_total", "dyadc_satis_total", "dyadc_cohes_total"),
  scale = c("DYADC Total score (32) ", "Consensus (13)", "Affectional Expression (4)", "Satisfaction (10)", "Cohesion (5)"),
  scale_construction = c("`e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`, `e14`, `e15`, `e16`, `e17`, `e18_r`, `e19_r`, `e20`, `e21`, `e22`, `e23`, `e24`, `e25`, `e26`, `e27`, `e28`, `e29`, `e30`, `e31`, `e32`", 
                         "`e1`, `e2`, `e3`, `e4`, `e5`, `e6`, `e7`, `e8`, `e9`, `e10`, `e11`, `e12`, `e13`", 
                         "`e4`, `e6`, `e29`, `e30`", 
                         "`e16`, `e17`, `e18_r`, `e19_r`, `e20`, `e21`, `e22`, `e23`, `e31`, `e32`", "`e24`, `e25`, `e26`, `e27`, `e28`"),
  scale_range = c("","","","",""), #TODO fill in range 
   alpha = c(round(dyadc_alpha$total$raw_alpha, 3),
              round(dyadc_con_alpha$total$raw_alpha, 3),
              round(dyadc_aff_exp_alpha$total$raw_alpha, 3),
              round(dyadc_satis_alpha$total$raw_alpha, 3),
              round(dyadc_cohes_alpha$total$raw_alpha, 3))
  )

# Create the gt table object
dyadc_scale_table <- gt(dyadc_scale_df) %>%
  cols_align(columns = c("scale_range"), align = "center") %>% 
  cols_label(var_name = "Variable Name",
            scale = "Scale (# of items)", 
            scale_construction = "Scale Construction",
            scale_range = "Range*",
            alpha = "Alpha") %>% 
  tab_footnote(footnote = "*Range of possible values; `_r` Reverse scored variable") %>% 
  tab_options(table.border.bottom.style = "hidden") %>% 
  cols_width(scale ~ px(135)) %>% 
  apply_tbl_theme() 

# Print the table
print(dyadc_scale_table)

```
### Summary Statistics

#### Descriptive Statistics

Descriptive statistics are presented below for each item and total/subscale score

```{r dyadc-mean-items}
# Create subset of dyadc items
dyadc_data_subset <- complete %>%
  select(e1:e32, "dyadc_con_total")

# Calculate the summary statistics for each variable
dyadc_summary_data <- lapply(dyadc_data_subset, function(x) {
  mean_val <- sprintf("%.2f", round(mean(x, na.rm = TRUE), 2))
  sd_val <- round(sd(x, na.rm = TRUE), 2)
  range_val <- paste(min(x, na.rm = TRUE), max(x, na.rm = TRUE), sep = "-")
  miss_val <- round(mean(is.na(x)) * 100, 2)
  c(Mean = mean_val, SD = sd_val, Range = range_val, Missing = paste(miss_val, "%", sep = ""))
})

# Convert summary_data to a data frame
dyadc_summary_data <- as.data.frame(dyadc_summary_data)

# Set items as first row
dyadc_summary_data <- rbind(names(dyadc_summary_data), dyadc_summary_data) %>% 
  t() %>% 
  as.data.frame()

# Create the gt table
dyadc_tbl <- dyadc_summary_data %>%
  gt() %>%
  cols_label(`1` = "Variable",
             Range = "Range*",
             Missing = "% Missing") %>% 
  cols_width(1 ~ px(165),2:5 ~ px(115)) %>%
  cols_align(columns = c("Mean", "SD", "Range", "Missing"), align = "center") %>% 
  tab_footnote("*Range of data values") %>% 
  tab_options(table.border.bottom.style = "hidden") %>%
  apply_tbl_theme()

# Render the table
dyadc_tbl

```

#### Distributions

Distributions are presented for the total score and each subscale

```{r dyadc-distributions, class.source='fold', echo = FALSE}
complete %>%
  composite_hist(
    x = dyadc_total
  ) +
  labs(
    title = 'Distribution for DYADC Scale'
  )

complete %>%
  composite_hist(
    x = dyadc_con_total
  ) +
  labs(
    title = 'Distribution for DYADC Consensus Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_aff_exp_total,
    bins = 10
  ) +
  labs(
    title = 'Distribution for DYADC Affectional Expression Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_satis_total
  ) +
  labs(
    title = 'Distribution for DYADC Satisfaction Subscale'
  )

complete %>%
  composite_hist(
    x = dyadc_cohes_total
  ) +
  labs(
    title = 'Distribution for DYADC Cohesion Subscale'
  )
```

```{r dyadc-cutoff, class.source='fold', echo = FALSE}
complete %>%
  cutoff_plot2(
    x = dyadc_total,
    cutoff = 92,
    cutoff_other = 107
  ) +
  labs(
    title = 'Cutoff Values for DYADC Scale',
    caption = 'Cutoffs are 92 and 107\nSee references for literature on cutoff scores.'
  )
```
