---
title: "Biological Assessment Data Cleaning Script"
author: "Shaina Trevino"
date: "2023-09-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")

pacman::p_load(rio, here, tidyverse, lubridate)

```

## Import

```{r import}
#import raw data
raw_bio_df <- import(here("do_not_push", "Biological Assessment_final_raw_sample_data_NEVERDELETE.csv"), header = TRUE) %>% 
  janitor::clean_names()

#import pulse data

raw_pulse_df <- import(here("do_not_push", "HeartRate_coded.csv")) %>% 
  janitor::clean_names()

#import incarcerated data
incarcerated_df <- import(here("do_not_push", "tpw_incarcerated_bio.csv"), header = TRUE) %>% 
  janitor::clean_names()

```

## Tidy 

Tidy data for archiving 

1. Extract question text and variable name in separate df (for codebook) and remove from archived data

1. Remove variables that will not be archived (e.g., qualtrics info)

1. Re-order variables so questions that affect bio variables are together and presented first, the variables of interest are presented second (e.g., height, weight, lifestyle/covid questions)

1. Correct variable types for calculations

1. Rename variables based on construct name

1. Merge with pulse data and incarcerated data

1. Specify missing data

1. Check for data errors (data quality check of variables included in calculations) - impossible values
 
  * `pef` and `fev` values 0 for one participant (HR219) --> changed to NA
  * `pef` and `fev` values flipped for one participant (P821) --> swapped `pef` values with `fev` values
  * `pef3` for HR214 should not have decimal
  * `fev1a` for P866 is missing decimal
  * `fev1c` is missing decimals for participants P856, P844, and HR119
  * `b27` should be changed to NA for P803
  
1. Protect identifiability

  * remove exact covid and diagnosis dates
  * remove specific diagnosis names



```{r tidy}
#create function to clean and standardize time format
standardize_time <- function(time) {
  #remove any non-time-related characters and extra spaces
  time_clean <- str_trim(str_remove(time, "[^0-9:APMapm]"))
  time_parsed <- parse_date_time(time_clean, orders = c('HM', 'HMS', 'HMa', 'HMp', 'H'))
  #return NA if parsing fails, otherwise format
  if (all(is.na(time_parsed))) {
    NA_character_ 
  } else {
    format(time_parsed, '%I:%M %p')  
  }
}

#create function to convert military time to standard time
convert_to_standard_time <- function(time) {
  #parse the time with a default date
  time_parsed <- strptime(paste("1970-01-01", time), format = "%Y-%m-%d %H:%M")
  #format the time to 'HH:MM AM/PM' format
  format(time_parsed, "%I:%M %p")
}

#transform pulse data to merge
pulse_td <- raw_pulse_df %>% 
  select(family, pulse1, pulse2)

#transform incarcerated data to merge
incar_td <- incarcerated_df %>% 
  slice(-1) %>% 
  filter(recipient_first_name != "HR211") %>% #TODO: MARIA, confirm remove and not change to -99
  rename_with(~gsub("_\\d+", "", .x), starts_with("q")) %>% 
  mutate(start_date = format(ymd_hms(start_date), "%m/%d/%Y %H:%M"),
         end_date = format(ymd_hms(end_date), "%m/%d/%Y %H:%M")) %>% 
  mutate(q8 = "-55") %>% #TODO: MARIA, confirm -55 for incarcerated participants
  relocate(q8, .before = q9) %>% 
  select(-x7b_2, -x7b_3) %>% 
  select(start_date, end_date, recorded_date, recipient_first_name,
         starts_with("q"), starts_with("x"), starts_with("r")) %>% 
  rename(x6b = x6b_4009,
         x6b_2 = x6b_4010,
         x9a = x9a_4029,
         x7b = x7b_1) 

#select incarcerated variables in bio data to bind rows
bio_incarvars_td <- raw_bio_df %>% 
  select(start_date, end_date, recorded_date, recipient_first_name,
         starts_with("q"), starts_with("x"), starts_with("r"), -q291, -q291_1_text, -q292)
  

#TODO: MARIA, confirm -99 (or -55) for missing incarcerated variables
#bind rows then merge with rest of variables
all_incarvars_td <- rbind(bio_incarvars_td, incar_td) %>% 
  left_join(raw_bio_df)

#extract names of variables that were asked of incarcerated participants
names_bio_df <- names(raw_bio_df)
names_incar_df <- names(incar_td)

#extract variables that were not asked of incarcerated participants
vars_not_incar <- setdiff(names_bio_df, names_incar_df) %>% 
  .[-(1:10)]

#extract question text and variable name for metadata
bio_md <- all_incarvars_td %>% 
  slice(1) %>% 
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "Question_Text")

#correct complex data entry errors
bio_df <- all_incarvars_td %>% 
  rename(family = recipient_first_name) %>%
  mutate(
    temp1 = ifelse(family == "P821", pef_1, fev1a),
    temp2 = ifelse(family == "P821", pef2, fev1b),
    temp3 = ifelse(family == "P821", pef3, fev1c),
    pef_1  = ifelse(family == "P821", fev1a, pef_1),
    pef2  = ifelse(family == "P821", fev1b, pef2),
    pef3  = ifelse(family == "P821", fev1c, pef3),
    fev1a = ifelse(family == "P821", temp1, fev1a),
    fev1b = ifelse(family == "P821", temp2, fev1b),
    fev1c = ifelse(family == "P821", temp3, fev1c),
    temp_hr2 = ifelse(family == "HR216", fev1b, pef2),
    temp_hr5 = ifelse(family == "HR216", pef2, fev1b),
    pef3  = ifelse(family == "HR214", 246, pef3),
    fev1a = ifelse(family == "P866", 2.16, fev1a),
    fev1c = case_when(family == "P856" ~ "2.11",
                      family == "P844" ~ "2.11", 
                      family == "HR119" ~ "2.08",
                      TRUE ~ fev1c),
    b27 = ifelse(family == "P803", NA, b27)
  ) %>%
  select(-temp1, -temp2, -temp3, -pef2, -fev1b) %>% 
  rename(pef2 = temp_hr2,
         fev1b = temp_hr5)

#remove excess variables from qualtrics, slice, re-order, rename, and create calculated variables
bio_td <- bio_df %>% 
  slice(-1:-2) %>% 
  mutate_all(~ifelse(is.nan(.), NA, .)) %>% 
  mutate(across(all_of(vars_not_incar), ~ ifelse(is.na(.) & (family == "HR181" | family == "P819"), "-55", .)),
          start_day = as.Date(mdy_hm(start_date)),
          start_time = format(mdy_hm(start_date), "%H:%M"),
          end_day = as.Date(mdy_hm(end_date)),
          end_time = format(mdy_hm(end_date), "%H:%M")) %>% 
  mutate(diff_day = ifelse(start_day != end_day, "Yes", "No")) %>% 
  select(family, start_date, end_date, ends_with("day"), ends_with("time"), bp1a, bp1b, bp2a, bp2b, height_measure:fev1c, fev1b,
         pef2, r1:r12, q1:q14, b1:b29a, starts_with("x")) %>% 
  mutate_if(is.character, ~na_if(., "")) %>% 
  mutate_at(vars(starts_with("bp"), starts_with("pef"), starts_with("fev"), ends_with("measure")), as.numeric) %>%
  mutate_at(vars(starts_with("pef"), starts_with("fev")), ~ ifelse(. == 0, NA, .)) %>% 
  left_join(pulse_td) %>% 
  mutate(bp_sys_avg = ifelse(bp1a != -55 & bp2a != -55, rowMeans(select(., bp1a, bp2a), na.rm = TRUE), -55),
         bp_dia_avg = ifelse(bp1b != -55 & bp2b != -55, rowMeans(select(., bp1b, bp2b), na.rm = TRUE), -55),
         bp_sys_cal = ifelse(bp_sys_avg != -55, ifelse(bp_sys_avg >= 140, 1, 0), -55),
         bp_dia_cal = ifelse(bp_dia_avg != -55, ifelse(bp_dia_avg >= 90, 1, 0), -55),
         bp_sys_pal = ifelse(bp_sys_avg != -55, ifelse(bp_sys_avg >= quantile(bp_sys_avg, 0.75, na.rm = TRUE), 1, 0), -55),
         bp_dia_pal = ifelse(bp_dia_avg != -55, ifelse(bp_dia_avg >= quantile(bp_dia_avg, 0.75, na.rm = TRUE), 1, 0), -55),
         pef_avg = ifelse(all(select(., starts_with("pef")) != -55, na.rm = TRUE), round(pef_columns, 1), -55),
         pef_cal    = ifelse(pef_avg != -55, ifelse(pef_avg <= 319, 1, 0), -55),
         pef_pal    = ifelse(pef_avg != -55, ifelse(pef_avg >= quantile(pef_avg, 0.75, na.rm = TRUE), 1, 0), -55),
         wth_ratio  = ifelse(iliac_crest_measure != -55 & hip_measure != -55, round(iliac_crest_measure / hip_measure, 3), -55),
         wth_cal = ifelse(wth_ratio != -55, ifelse(wth_ratio >= 0.85, 1, 0), -55),
         wth_pal = ifelse(wth_ratio != -55, ifelse(wth_ratio >= quantile(wth_ratio, 0.75, na.rm = TRUE), 1, 0), -55),
         bmi_score  = ifelse(weight_measure != -55 & height_measure != -55, weight_measure / ((height_measure / 100)^2), -55),
         bmi_cal    = ifelse(bmi_score != -55, ifelse(bmi_score >= 30, 1, 0), -55),
         bmi_pal    = ifelse(bmi_score != -55, ifelse(bmi_score >= quantile(bmi_score, 0.75, na.rm = TRUE), 1, 0), -55),
         pulse_avg  = ifelse(pulse1 != -55 & pulse2 != -55, rowMeans(select(., pulse1, pulse2), na.rm = TRUE), -55),
         pulse_cal  = ifelse(pulse_avg != -55, ifelse(pulse_avg >= 90, 1, 0), -55),
         pulse_pal  = ifelse(pulse_avg != -55, ifelse(pulse_avg >= quantile(pulse_avg, 0.75, na.rm = TRUE), 1, 0), -55)) %>% 
  rename(bp1 = bp1a,
         bp2 = bp1b,
         bp3 = bp2a,
         bp4 = bp2b,
         bmi1 = height_measure,
         bmi2 = weight_measure,
         wth1 = iliac_crest_measure,
         wth2 = hip_measure,
         pef1 = pef_1,
         pef4 = fev1a,
         pef5 = fev1b,
         pef6 = fev1c,
         b7c = b7b,
         b7b = b7a_1_text,
         b8c = b8b,
         b8b = b8a_1_text,
         b9d = b9c_3_text,
         b10c = b10b,
         b10b = b10a_1_text,
         b11a = q291,
         b11b = q291_1_text,
         b11c = q292#,
        # b14a = b14b
         ) %>% 
  rename(b12a = 	b13, 
         b12b = 	b14,
         b12c = 	b14b,
         b12d = 	b15,
         b13	 = b16, 
         b13a = 	b16a, 
         b14	 = b17,
         b14a = 	b17a, 
         b15	 = b18,
         b15a = 	b18a, 
         b16	 = b19, 
         b16a = 	b19a, 
         b17	 = b20, 
         b17a = 	b21, 
         b17b = 	b22, 
         b17c = 	b23, 
         b18	 = b24, 
         b18a = 	b25, 
         b18b = 	b26, 
         b18c = 	b27, 
         b18d = 	b28,
         b18e = 	b29, 
         b18f = 	b29a) %>%
  rename_at(vars(matches("^b[0-9]")), ~paste0("hbc", substr(., 2, nchar(.)))) %>%
  rename_at(vars(matches("^r[0-9]")), ~paste0("rhs", substr(., 2, nchar(.)))) %>%
  rename_at(vars(matches("^x[0-9]")), ~paste0("chc", substr(., 2, nchar(.)))) %>%
  rename_at(vars(matches("^q[0-9]")), ~paste0("cev", substr(., 2, nchar(.)))) %>% 
  mutate_at(vars(bmi1, bmi2, wth2, ), ~ round(., 1)) %>% 
  mutate_at(vars(bmi_score, pef5), ~ round(., 2)) %>% 
  mutate_at(vars(pef2, pef3), ~ round(.)) %>% 
  mutate(chc20a = gsub("\\..*$", "", chc20a)) %>% 
  #transform all characters to numbers for survey variables
  mutate_if(is.character, ~ case_when(. == "Yes" ~ "1",
                                      . == "Yes: (Fill in medication name)" ~ "1",
                                      . == "Yes: (Fill in medication)" ~ "1",
                                      . == "No" ~ "0",
                                      TRUE ~ . )) %>% 
  mutate_at(vars(rhs9, rhs10, rhs11, rhs12),
            ~ case_when(. == "Definitely true" ~ "1",
                        . == "Mostly true" ~ "2",
                        . == "Don't know" ~ "3",
                        . == "Mostly false" ~ "4",
                        . == "Definitely false" ~ "5",
                        TRUE ~ .)) %>% 
  mutate_at(vars(hbc13a, hbc14a, hbc15a, hbc16a),
            ~ case_when(. == "a. never" ~ "1", 
                        . == "b. .5-1 hour/day" ~ "2",
                        . == "c. 1-5 hours/day" ~ "3",
                        . == "d. 5 or more hours/day" ~ "4",
                        TRUE ~ .)) %>% 
  mutate_at(vars(hbc17a, hbc17c),
            ~ case_when(. == "a. 0" ~ "1",
                        . == "b. 1-3 cups or cans" ~ "2",
                        . == "c. 4-6 cups or cans" ~ "3",
                        . == "d. 7-9 cups or cans" ~ "4",
                        . == "e. 10 or more cups or cans" ~ "5",
                        TRUE ~ .)) %>% 
  mutate(rhs1 = case_when(rhs1 == "1 - Excellent" ~ "1",
                          rhs1 == "2 - Very Good" ~ "2",
                          rhs1 == "3 - Good" ~ "3",
                          rhs1 == "4 - Fair" ~ "4",
                          rhs1 == "5 - Poor" ~ "5",
                          rhs1 == "6 - Decline to Answer" ~ "-77",
                          TRUE ~ rhs1),
         cev12 = case_when(cev12 == "Johnson & Johnson" ~ "1",
                           cev12 == "Moderna" ~ "2",
                           cev12 == "Pfizer" ~ "3",
                           cev12 == "Not Specified (this option can be used when a participant cannot recall)" ~ "-77",
                           TRUE ~ cev12),
         hbc12a = case_when(hbc12a == "1 cigarette" ~ "1",
                            hbc12a == "2-5 cigarettes" ~ "2",
                            hbc12a == "1 pack" ~ "3",
                            hbc12a == "2 packs" ~ "4",
                            TRUE ~ hbc12a),
         hbc12d = case_when(hbc12d == "1 cigarette" ~ "1",
                            hbc12d == "2-5 cigarettes" ~ "2",
                           TRUE ~ hbc12d),
         hbc18d = case_when(hbc18d == "Mild" ~ "1", 
                            hbc18d == "Moderate" ~ "2",
                            hbc18d == "Vigorous" ~ "3",
                            TRUE ~ hbc18d),
         chc1a = ifelse(chc1a == "Maybe", "-66", chc1a),
         hbc1 = ifelse(family == "HR183", "9:45 AM", hbc1))#,
         #across(c(hbc1, hbc7c, hbc8c, hbc9b, hbc10c, hbc11c, hbc12c, hbc18f), standardize_time)) #format times


#create function to convert time to date/time object for calculating elapsed time
convert_to_posixct <- function(time) {
  strptime(paste("1970-01-01", time), format = "%Y-%m-%d %I:%M %p")
}

#create elapsed time variables
elapsed_vars_df <- bio_td %>% 
  select(ends_with("day"), ends_with("time"), family, hbc1, hbc7c, hbc8c, hbc9b, 
         hbc10c, hbc11c, hbc12b, hbc12c, hbc18f) %>% 
  mutate(across(c(start_time, end_time), convert_to_standard_time),
         across(c(start_time, end_time, hbc1, hbc7c, hbc8c, hbc9b, hbc10c, hbc11c, hbc12c, hbc18f), convert_to_posixct),
         hbc1_raw_elapsed = as.numeric(difftime(end_time, hbc1, units = "mins")),
         hbc7c_raw_elapsed = as.numeric(difftime(end_time, hbc7c, units = "mins")),
         hbc8c_raw_elapsed = as.numeric(difftime(end_time, hbc8c, units = "mins")),
         hbc9b_raw_elapsed = as.numeric(difftime(end_time, hbc9b, units = "mins")),
         hbc10c_raw_elapsed =  as.numeric(difftime(end_time, hbc10c, units = "mins")),
         hbc11c_raw_elapsed =  as.numeric(difftime(end_time, hbc11c, units = "mins")),
         hbc12c_raw_elapsed = as.numeric(difftime(end_time, hbc12c, units = "mins")),
         hbc18f_raw_elapsed =  as.numeric(difftime(end_time, hbc18f, units = "mins")),
         hbc12b_raw_elapsed = as.numeric(ymd(end_day) - mdy(hbc12b))) %>% 
        #manually check negative elapsed times and correct
  mutate(hbc1_elapsed = case_when(family == "P805" ~ 0,
                                  hbc1_raw_elapsed < 0 ~ 1440 + hbc1_raw_elapsed, 
                                  TRUE ~ hbc1_raw_elapsed),
         hbc10c_elapsed = ifelse(hbc10c_raw_elapsed < 0, 1440 + hbc10c_raw_elapsed, hbc10c_raw_elapsed),
         hbc11c_elapsed = ifelse(hbc11c_raw_elapsed < 0, 1440 + hbc11c_raw_elapsed, hbc11c_raw_elapsed),
         hbc12c_elapsed = ifelse(hbc12c_raw_elapsed < 0, 1440 + hbc12c_raw_elapsed, hbc12c_raw_elapsed),
         hbc18f_elapsed = ifelse(hbc18f_raw_elapsed < 0, 1440 + hbc18f_raw_elapsed, hbc18f_raw_elapsed)) %>% 
  rename(hbc7c_elapsed = hbc7c_raw_elapsed,
         hbc8c_elapsed = hbc8c_raw_elapsed,
         hbc9b_elapsed = hbc9b_raw_elapsed,
         hbc12b_elapsed = hbc12b_raw_elapsed) %>% 
  select(-ends_with("raw_elapsed")) %>% 
  select(family, ends_with("elapsed"))


bio_na <- bio_td %>% 
  #merge in elapsed time variables
  left_join(elapsed_vars_df) %>% 
  #specify missing data
  mutate_all(~ ifelse(. %in% c("N/A - Lives Alone", "N/A - Not currently employed", "N/A"), "-55", .)) %>% 
  mutate_all(~ ifelse(. %in% c("Decline to Answer"), "-77", .)) %>% 
  mutate(cev2 = ifelse(cev1 == "0", "-55", cev2),
         cev4 = ifelse(cev3 == "0", "-55", cev4),
         across(c(cev12, cev13, cev14), ~ ifelse(cev11 == "0", "-55", .)),
         across(c(hbc7a, hbc7b, hbc7c), ~ ifelse(hbc7 == "0", "-55", .)),
         across(c(hbc7b, hbc7c), ~ ifelse(hbc7a == "0", "-55", .)),
         across(c(hbc8a, hbc8b, hbc8c, hbc8c_elapsed), ~ ifelse(hbc8 == "0", "-55", .)),
         across(c(hbc8b, hbc8c, hbc8c_elapsed), ~ ifelse(hbc8a == "0", "-55", .)),
         across(c(hbc9a, hbc9b, hbc9c, hbc9d, hbc9b_elapsed), ~ ifelse(hbc9 == "0", "-55", .)),
         across(c(hbc9b, hbc9b_elapsed), ~ ifelse(hbc9a == "0", "-55", .)),
         hbc9d = ifelse(hbc9c != "Other: Please specify", "-55", hbc9d),
         across(c(hbc10a, hbc10b, hbc10c, hbc10c_elapsed), ~ ifelse(hbc10 == "0", "-55", .)),
         across(c(hbc10b, hbc10c, hbc10c_elapsed), ~ ifelse(hbc10a == "0", "-55", .)),
         across(c(hbc11a, hbc11b, hbc11c, hbc11c_elapsed), ~ ifelse(hbc11 == "0", "-55", .)),
         across(c(hbc11b, hbc11c, hbc11c_elapsed), ~ ifelse(hbc11a == "0", "-55", .)),
         across(c(hbc12a, hbc12b, hbc12c, hbc12d, hbc12b_elapsed, hbc12c_elapsed), ~ ifelse(hbc12 == "0", "-55", .)),
         hbc13a = ifelse(hbc13 == "0" | hbc13 == "-55", "-55", hbc13a),
         hbc14a = ifelse(hbc14 == "0" | hbc14 == "-55", "-55", hbc14a),
         hbc15a = ifelse(hbc15 == "0" | hbc15 == "-77", "-55", hbc15a),
         hbc16a = ifelse(hbc16 == "0", "-55", hbc16a),
         across(c(hbc17a, hbc17b, hbc17c), ~ ifelse(hbc17 == "0", "-55", .)), 
         across(c(hbc18a, hbc18b, hbc18c, hbc18d, hbc18e, hbc18f, hbc18f_elapsed), ~ ifelse(hbc18 == "0" | hbc18 == "-77", "-55", .)),
         across(c(hbc18f, hbc18f_elapsed), ~ ifelse(hbc18e == "0", "-55", .)),
         across(c(chc1b, chc1c, chc1d, chc1e, chc1f, chc1g), ~ ifelse(chc1a == "0" | chc1a == "-66", "-55", .)),
         chc1g = ifelse(chc1f == "1", "-55", chc1g),
         across(c(chc2b, chc2c, chc2d, chc2e, chc2f, chc2g, chc2h), ~ ifelse(chc2a == "0", "-55", .)), 
         chc2c = ifelse(chc2b == "-77", "-55", chc2c),
         chc2h = ifelse(chc2g == "1", "-55", chc2h),
         across(c(chc3b, chc3c, chc3d, chc3e, chc3f), ~ ifelse(chc3a == "0", "-55", .)), 
         chc3f = ifelse(chc3e == "-77" | chc3e == "1", "-55", chc3f),
         across(c(chc4b, chc4c, chc4d, chc4e, chc4f), ~ ifelse(chc4a == "0", "-55", .)), 
         chc4f = ifelse(chc4e == "-77" | chc4e == "1", "-55", chc4f),
         across(c(chc5b, chc5c, chc5d, chc5e, chc5f, chc5g), ~ ifelse(chc5a == "0" | chc5a == "-77", "-55", .)), 
         chc5g = ifelse(chc5f == "1", "-55", chc5g),
         across(c(chc6b, chc6b_2, chc6c, chc6d, chc6e), ~ ifelse(chc6a == "0", "-55", .)), 
         chc6e = ifelse(chc6d == "1", "-55", chc6e),
         across(c(chc7b, chc7c, chc7d, chc7e, chc7f, chc7g), ~ ifelse(chc7a == "0", "-55", .)), 
         chc7g = ifelse(chc7f == "1", "-55", chc7g),
         across(c(chc8b, chc8c, chc8d, chc8e, chc8f), ~ ifelse(chc8a == "0" | chc8a == "-77", "-55", .)), 
         chc8f = ifelse(chc8e == "1", "-55", chc8f),
         across(c(chc9b, chc9c, chc9d, chc9e, chc9f, chc9g), ~ ifelse(chc9a == "0", "-55", .)), 
         chc9g = ifelse(chc9f == "1", "-55", chc9g),
         across(c(chc10b, chc10c, chc10d, chc10e, chc10f, chc10g), ~ ifelse(chc10a == "0", "-55", .)), 
         chc10g = ifelse(chc10f == "1", "-55", chc10g),
         across(c(chc11b, chc11c, chc11d, chc11e, chc11f, chc11g), ~ ifelse(chc11a == "0", "-55", .)), 
         chc11g = ifelse(chc11f == "1" | chc11f == "-77", "-55", chc11g),
         across(c(chc12b, chc12c, chc12d, chc12e, chc12f, chc12g), ~ ifelse(chc12a == "0", "-55", .)), 
         chc12g = ifelse(chc12f == "1", "-55", chc12g),
         across(c(chc13b, chc13c, chc13d, chc13e, chc13f, chc13g), ~ ifelse(chc13a == "0" | chc13a == "-77", "-55", .)), 
         chc13g = ifelse(chc13f == "1", "-55", chc13g),
         across(c(chc14b, chc14c, chc14d, chc14e, chc14f, chc14g), ~ ifelse(chc14a == "0", "-55", .)), 
         chc14g = ifelse(chc14f == "1", "-55", chc14g),
         across(c(chc15b, chc15c, chc15d, chc15e, chc15f, chc15g), ~ ifelse(chc15a == "0", "-55", .)), 
         chc15g = ifelse(chc15f == "1", "-55", chc15g),
         across(c(chc16b, chc16c, chc16d, chc16e, chc16f, chc16g), ~ ifelse(chc16a == "0", "-55", .)), 
         chc16g = ifelse(chc16f == "1", "-55", chc16g),
         across(c(chc17b, chc17c, chc17d, chc17e, chc17f), ~ ifelse(chc17a == "0", "-55", .)), 
         chc17f = ifelse(chc17e == "1" | chc17e == "-77", "-55", chc17f),
         across(c(chc18b, chc18c, chc18d, chc18e, chc18f), ~ ifelse(chc18a == "0", "-55", .)), 
         chc18f = ifelse(chc18e == "1" | chc18e == "-77", "-55", chc18f),
         across(c(chc19b, chc19c, chc19d, chc19e, chc19f), ~ ifelse(chc19a == "0", "-55", .)), 
         chc19d = ifelse(chc19c == "-77", "-55", chc19d),
         chc19f = ifelse(chc19e == "1" | chc19e == "-77", "-55", chc19f),
         across(c(chc20a_1_text, chc20b, chc20c, chc20d, chc20e, chc20f, chc20g), ~ ifelse(chc20a == "0", "-55", .)), 
         chc20g = ifelse(chc20f== "1" | chc20f == "-77", "-55", chc20g),
         across(c(hbc1, hbc7c, hbc8c, hbc9b, hbc10c, hbc11c, hbc12b, hbc12c, hbc18f, hbc1_elapsed, hbc7c_elapsed, hbc8c_elapsed, 
                  hbc9b_elapsed, hbc10c_elapsed, hbc11c_elapsed, hbc12b_elapsed, hbc12c_elapsed, hbc18f_elapsed, 
                  pulse1, pulse2, pulse_avg, pulse_cal, pulse_pal), 
                ~ ifelse(family == "HR181" | family == "P819" , "-55", .))) %>% 
    mutate_all(~ ifelse(is.na(.) | is.nan(.), -99, .)) %>%  #last after all conditional are dealt with
    select(family, start_date, end_date, starts_with("bp"), starts_with("bmi"), starts_with("wth"), 
           pef1, pef2, pef3, pef4, pef5, pef6, pef_avg, pef_cal, pef_pal, 
           starts_with("pulse"), starts_with("rhs"), starts_with("cev"), 
           hbc1, hbc1_elapsed, hbc2, hbc3, hbc4, hbc5, hbc6, hbc7, hbc7a, hbc7b, hbc7c, hbc7c_elapsed,
           hbc8, hbc8a, hbc8b, hbc8c, hbc8c_elapsed, hbc9, hbc9a, hbc9b, hbc9b_elapsed, hbc9c, hbc9d, hbc10, hbc10a,
           hbc10b, hbc10c, hbc10c_elapsed, hbc11, hbc11a, hbc11b, hbc11c, hbc11c_elapsed, hbc12, hbc12a, hbc12b, 
           hbc12b_elapsed, hbc12c, hbc12c_elapsed, hbc12d, hbc13, hbc13a, hbc14, hbc14a, hbc15, hbc15a, hbc16, hbc16a, 
           hbc17, hbc17a, hbc17b, hbc17c, hbc18, hbc18a, hbc18b, hbc18c, hbc18d, hbc18e, hbc18f, hbc18f_elapsed,
           starts_with("chc"))





#check to make sure all NA are coded
check_na <- bio_na %>% 
  filter(rowSums(is.na(.)) > 0)

#check dates for elapsed time vars
check_raw_dates <- bio_td %>% 
  select(ends_with("day"), ends_with("time"), family, hbc1, hbc7c, hbc8c, hbc9b, 
         hbc10c, hbc12b, hbc12c, hbc18f)





```

Create RHS subscales

| Variable | Description |
|----------|-------------|
| rhs1     | Item 1      |
| rhs2     | Item 13     |
| rhs3     | Item 14     |
| rhs4     | Item 15     |
| rhs5     | Item 16     |
| rhs6     | Item 17     |
| rhs7     | Item 18     |
| rhs8     | Item 19     |
| rhs9     | Item 33     |
| rhs10    | Item 34     |
| rhs11    | Item 35     |
| rhs12    | Item 36     |



```{r subscale}

#Recoding items
rhs_sub_recode <- bio_na %>% 
  mutate(rhs1_p = case_when(rhs1 == "1" ~ 100, 
                            rhs1 == "2" ~ 75,
                            rhs1 == "3" ~ 50,
                            rhs1 == "4" ~ 25,
                            rhs1 == "5" ~ 0,
                            TRUE ~ as.numeric(rhs1)),
         rhs2_p = case_when(rhs2 == "1" ~ 0, 
                            rhs2 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs2)),
         rhs3_p = case_when(rhs3 == "1" ~ 0, 
                            rhs3 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs3)),
         rhs4_p = case_when(rhs4 == "1" ~ 0, 
                            rhs4 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs4)),
         rhs5_p = case_when(rhs5 == "1" ~ 0, 
                            rhs5 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs5)),
         rhs6_p = case_when(rhs6 == "1" ~ 0, 
                            rhs6 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs6)),
         rhs7_p = case_when(rhs7 == "1" ~ 0, 
                            rhs7 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs7)),
         rhs8_p = case_when(rhs8 == "1" ~ 0, 
                            rhs8 == "0" ~ 100,
                            TRUE ~ as.numeric(rhs8)),
         rhs9_p = case_when(rhs9 == "1" ~ 0, 
                            rhs9 == "2" ~ 25,
                            rhs9 == "3" ~ 50,
                            rhs9 == "4" ~ 75,
                            rhs9 == "5" ~ 100,
                            TRUE ~ as.numeric(rhs9)),
         rhs10_p = case_when(rhs10 == "1" ~ 100, 
                            rhs10 == "2" ~ 75,
                            rhs10 == "3" ~ 50,
                            rhs10 == "4" ~ 25,
                            rhs10 == "5" ~ 0,
                            TRUE ~ as.numeric(rhs10)),
         rhs11_p = case_when(rhs11 == "1" ~ 0, 
                            rhs11 == "2" ~ 25,
                            rhs11 == "3" ~ 50,
                            rhs11 == "4" ~ 75,
                            rhs11 == "5" ~ 100,
                            TRUE ~ as.numeric(rhs11)),
         rhs12_p = case_when(rhs12 == "1" ~ 100, 
                            rhs12 == "2" ~ 75,
                            rhs12 == "3" ~ 50,
                            rhs12 == "4" ~ 25,
                            rhs12 == "5" ~ 0,
                            TRUE ~ as.numeric(rhs12)))

rhs_calc <- rhs_sub_recode %>% 
  select(family, ends_with("_p")) %>% 
  mutate_all(~ifelse(. == -77, NA, .)) 

#check if missing data rule should be applied - no
check_missing <- rhs_calc %>% 
  select(-family) %>% 
  rowwise() %>%
  mutate(perc_missing = sum(is.na(c_across(everything()))) / length(c_across(everything())) * 100) %>% 
  arrange(desc(perc_missing))

rhs_subscales <- rhs_calc %>%
  mutate(rhs_health = rowMeans(select(., rhs1_p, rhs9_p, rhs10_p, rhs11_p, rhs12_p), na.rm = TRUE),
         rhs_phys_limit = rowMeans(select(., rhs2_p, rhs3_p, rhs4_p, rhs5_p), na.rm = TRUE),
         rhs_emo_limit = round(rowMeans(select(., rhs6_p, rhs7_p, rhs8_p), na.rm = TRUE), 2)) %>% 
  select(family, rhs_health, rhs_phys_limit, rhs_emo_limit) %>% 
  right_join(rhs_sub_recode) %>% 
  select(family, start_date, end_date, starts_with("bp"), starts_with("bmi"), starts_with("wth"), pef1, pef2, pef3, pef4, pef5, pef6,
         pef_avg, pef_cal, pef_pal, starts_with("pulse"), rhs1:rhs12, ends_with("_p"), rhs_health, rhs_phys_limit, rhs_emo_limit, 
         starts_with("cev"), starts_with("hbc"), starts_with("chc"))


#internal file
internal_df <- rhs_subscales

#take out identifiable cev and chc vars and rename sequentially for archived dataset
#specify excluded variables
excluded_vars <- c("cev2", "cev4", "cev13", "cev14", "chc1b", "chc1e", "chc1g", "chc2c", "chc2f", "chc2h", 
                   "chc3d", "chc3f", "chc4d", "chc4f", "chc5b", "chc5e", "chc5g", "chc6c", "chc6e", "chc7b", 
                   "chc7e", "chc7g", "chc8d", "chc8f", "chc9b", "chc9e", "chc9g", "chc10b", "chc10e", "chc10g", "chc11b",
                   "chc11e", "chc11g", "chc12b", "chc12e", "chc12g", "chc13b", "chc13e", "chc13g", "chc14b", "chc14e",
                   "chc14g", "chc15b", "chc15e", "chc15g", "chc16b", "chc16e", "chc16g", "chc17d", "chc17f", "chc18d",
                   "chc18f", "chc19d", "chc19f", "chc20a_1_text", "chc20b", "chc20e", "chc20g", "start_date", "end_date")


bio_td_archive <- rhs_subscales %>% 
  select(-one_of(excluded_vars)) %>%
  rename(cev1	=	cev1,
         cev2	=	cev3,
         cev3	=	cev5,
         cev4	=	cev6,
         cev5	=	cev7,
         cev6	=	cev8,
         cev7	=	cev9,
         cev8	=	cev10,
         cev9	=	cev11,
         cev10	=	cev12,
         chc1a	=	chc1a,
         chc1b	=	chc1c,
         chc1c	=	chc1d,
         chc1d	=	chc1f,
         chc2a	=	chc2a,
         chc2b	=	chc2b,
         chc2c	=	chc2d,
         chc2d	=	chc2e,
         chc2e	=	chc2g,
         chc3a	=	chc3a,
         chc3b	=	chc3b,
         chc3c	=	chc3c,
         chc3d	=	chc3e,
         chc4a	=	chc4a,
         chc4b	=	chc4b,
         chc4c	=	chc4c,
         chc4d	=	chc4e,
         chc5a	=	chc5a,
         chc5b	=	chc5c,
         chc5c	=	chc5d,
         chc5d	=	chc5f,
         chc6a	=	chc6a,
         chc6b	=	chc6b,
         chc6c	=	chc6b_2,
         chc6d	=	chc6d,
         chc7a	=	chc7a,
         chc7b	=	chc7c,
         chc7c	=	chc7d,
         chc7d	=	chc7f,
         chc8a	=	chc8a,
         chc8b	=	chc8b,
         chc8c	=	chc8c,
         chc8d	=	chc8e,
         chc9a	=	chc9a,
         chc9b	=	chc9c,
         chc9c	=	chc9d,
         chc9d	=	chc9f,
         chc10a	=	chc10a,
         chc10b	=	chc10c,
         chc10c	=	chc10d,
         chc10d	=	chc10f,
         chc11a	=	chc11a,
         chc11b	=	chc11c,
         chc11c	=	chc11d,
         chc11d	=	chc11f,
         chc12a	=	chc12a,
         chc12b	=	chc12c,
         chc12c	=	chc12d,
         chc12d	=	chc12f,
         chc13a	=	chc13a,
         chc13b	=	chc13c,
         chc13c	=	chc13d,
         chc13d	=	chc13f,
         chc14a	=	chc14a,
         chc14b	=	chc14c,
         chc14c	=	chc14d,
         chc14d	=	chc14f,
         chc15a	=	chc15a,
         chc15b	=	chc15c,
         chc15c	=	chc15d,
         chc15d	=	chc15f,
         chc16a	=	chc16a,
         chc16b	=	chc16c,
         chc16c	=	chc16d,
         chc16d	=	chc16f,
         chc17a	=	chc17a,
         chc17b	=	chc17b,
         chc17c	=	chc17c,
         chc17d	=	chc17e,
         chc18a	=	chc18a,
         chc18b	=	chc18b,
         chc18c	=	chc18c,
         chc18d	=	chc18e,
         chc19a	=	chc19a,
         chc19b	=	chc19b,
         chc19c	=	chc19c,
         chc19d	=	chc19e,
         chc20a	=	chc20a,
         chc20b	=	chc20c,
         chc20c	=	chc20d,
         chc20d	=	chc20f) %>% 
  #remove hbc dates and replace with elapsed variables
  select(-all_of(c("hbc1", "hbc7c", "hbc8c", "hbc9b", "hbc10c", "hbc11c", "hbc12b", "hbc12c", "hbc18f"))) %>% 
  rename(hbc1 = hbc1_elapsed,
         hbc7c = hbc7c_elapsed,
         hbc8c = hbc8c_elapsed,
         hbc9b = hbc9b_elapsed,
         hbc10c = hbc10c_elapsed,
         hbc11c = hbc11c_elapsed,
         hbc12b = hbc12b_elapsed,
         hbc12c = hbc12c_elapsed,
         hbc18f = hbc18f_elapsed) %>% 
  #remove specific prescription drugs from archive data (confidential health info)
  select(-all_of(c("hbc8b", "hbc9d", "hbc10b", "hbc11b"))) %>% 
  rename(hbc8b = hbc8c,
         hbc10b = hbc10c,
         hbc11b = hbc11c) %>% 
  mutate(hbc9c = ifelse(hbc9c == "Other: Please specify", "Other", hbc9c))

check_arch <- bio_td_archive %>% 
  select(family, starts_with("hbc"))

rcheck_bio <- bio_td %>% 
  select(family, starts_with("hbc")) %>% 
  select(family, hbc1, hbc7c, hbc8c, hbc9b, hbc10c, hbc11c, hbc12c, hbc18f) 


#Export times without AM/PM to double check
# check_bio <- bio_td %>% 
#   select(family, starts_with("hbc")) %>% 
#   select(family, hbc1, hbc8c, hbc10c, hbc11c, hbc12c, hbc18f) %>%  #hbc7c, hbc9b, 
#   filter(
#     (!str_detect(hbc1,   "AM|PM|am|pm|Am|Pm|-55")   )|   #is.na(hbc1)) |
#     (!str_detect(hbc8c,  "AM|PM|am|pm|Am|Pm|-55")  )|  #is.na(hbc8c)) |
#     (!str_detect(hbc10c, "AM|PM|am|pm|Am|Pm|-55") )| #is.na(hbc10c)) |
#     (!str_detect(hbc11c, "AM|PM|am|pm|Am|Pm|-55") )| #is.na(hbc11c)) |
#     (!str_detect(hbc12c, "AM|PM|am|pm|Am|Pm|-55") )| #is.na(hbc12c)) |
#     (!str_detect(hbc18f, "AM|PM|am|pm|Am|Pm|-55") ) #is.na(hbc18f))
#   )
#export hbc time variables for checking
#export(check_bio, "check_hbc_times.xlsx")


```

## Export

```{r export}
#export internal file
#export(internal_df, "bio_internal.xlsx")

#export archived file
#export(bio_td_archive, "bio_archive.xlsx")


```


