---
title: "Child Interview"
author: "Jonathan A. Pedroza, PhD"
format:
  pdf:
    toc: true
    toc-depth: 3
    toc-title: Contents
    number-sections: true
    colorlinks: true
editor: visual
---

## Child Interview - Parenting & Pregnancy History Data

```{r}
library(tidyverse)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)

theme_set(theme_light())

interview <- read_csv('C:/Users/cpppe/Desktop/github_projects/tpwdata_fork/jp_files/interview.csv') %>%
  mutate(
    id = assessment_screen_2,
    wave = 'tp'
    ) %>%
  select(-matches('^pct')) %>%
  mutate(
    id = case_when(
      id == 'av' ~ 'P901',
      TRUE ~ id
    )
  ) %>%
  filter(id != 'AG400',
         id != 'K000',
         id != 'F000',
         id != 'P100',
         id != '65973269',
         id != 'P831')

maria_file <- rio::import('C:/Users/cpppe/Desktop/github_projects/tpwdata_fork/jp_files/GLOINFO_DOB.SAV') %>%
  janitor::clean_names()
```

### Removing Columns With All Missing (NA) And Zero Variance In Responses

```{r}
remove_df <- interview[, colSums(is.na(interview)) != nrow(interview)]

remove_df <- remove_df[ - as.numeric(which(apply(remove_df, 2, var) == 0))]
```

### Meaningful Names (Hopefully)

-   commented out columns are to show the names and what they correspond to

-   JP Notes:

    -   bc = biological child

    -   pc_bc = parenting child biological child

    -   sm_sc = stepmothering stepchild/children

    -   other_sc = partner/other stepchild/children

    -   other_kid = any other child/children

```{r}
remove_df <-
  remove_df %>%
  rename(
    times_preg = p00a, #how many times pregnant since last talk
    curr_preg = p00aa, #currently pregnant
    bc1_tc_age_preg = p01a, #tc age
    bc1_preg_attempt = p01c, #trying to get pregnant
    bc1_preg_result = p01d, #what happened to the pregnancy
    # tri_still_preg = p01g, #trimester_current
    bc1_tri_mis_abort = p01g2, #trimester_loss
    bc1_name = p01b, #child name
    bc1_dob = p01b2, #child DOB
    bc1_birth_04 = p01db1, #born before today's date 2004
    bc1_gender_id = p01b3, #child gender identity
    # gender_self_id = p01b3_8_text, # gender identity (self identity)
    bc1_white = p01b4_1, # race - white
    bc1_black = p01b4_2, #race - black
    bc1_amer_ind = p01b4_3, #race - american indian
    # asian_indian = p01b4_4, #race - asian indian
    # other_asian_all = p01b4_5, #race - other asian
    # chinese = p01b4_6, #race - chinese
    # filipino = p01b4_7, #race - filipino
    # japanese = p01b4_8, #race -  japanese
    # korean = p01b4_9, #race -  korean
    # vietnamese = p01b4_10, #race - vietnamese
    # other_asian = p01b4_11, #race - other
    # native_hawaii_all = p01b4_12, #race - native hawaiian/other pacific islander
    # native_hawaii = p01b4_13, #race - native hawaiian
    # guamanian = p01b4_14, #race - guamanian
    bc1_samoan = p01b4_15, #race - samoan
    # other_pacific = p01b4_16, #race - other - entry
    # race_dontknow = p01b4_17, #race - don't know
    bc1_race_other = p01b4_18, #race - other race - entry
    # race_decline = p01b4_77, #race - decline to answer
    bc1_race_tribe_text = p01b4_3_text, #race - tribe text
    # race_pacific_text = p01b4_16_text, #race - other race
    bc1_race_other_text = p01b4_18_text, #race - other race text,
    bc1_latino = p01b5, #latino
    bc1_mexican = p01b55_1, #mexican
    # puerto_rican = p01b55_2, #puerto rican
    # cuban = p01b55_3,  #cuban
    bc1_latino_other = p01b55_4, #other
    # latino_dontknow= p01b55_5, #don't know
    # latino_decline = p01b55_77, #declined
    bc1_latino_other_text = p01b55_4_text, #other text
    bc1_custody = p01b6, #who currently has custody
    # custody_other_rel = p01b6_7_text, #other relative specificed text
    # num_kid_twin = p01mb0, # how many children
    # name_twin = p01mb1, #child name
    # dob_twin = p01mb2, #child DOB
    # bc1_birth_04_twin = p01db2, # child born before 2004
    # bc1_gender_id_twin = p01mb3, #child gender identity
    # gender_self_id_twin = p01mb3_8_text, #self id gender
    # white_twin = p01mb4_1, #race - white
    # black_twin = p01mb4_2, #race - black
    # amer_ind_twin = p01mb4_3, #race - american indian
    # asian_indian_twin = p01mb4_4, #race - asian indian
    # other_asian_all_twin = p01mb4_5, #race - other asian
    # chinese_twin = p01mb4_6, #race - chinese
    # filipino_twin = p01mb4_7, #race - filipino
    # japanese_twin = p01mb4_8, #race -  japanese
    # korean_twin = p01mb4_9, #race -  korean
    # vietnamese_twin = p01mb4_10, #race - vietnamese
    # other_asian_twin = p01mb4_11, #race - other
    # native_hawaii_all_twin = p01mb4_12, #race - native hawaiian/other pacific islander
    # native_hawaii_twin = p01mb4_13, #race - native hawaiian
    # samoan_twin = p01mb4_14, #race - guamanian
    # guamanian_twin = p01mb4_15, #race - samoan
    # other_pacific_twin = p01mb4_16, #race - other - entry
    # race_dontknow_twin = p01mb4_17, #race - don't know
    # race_other_twin = p01mb4_18, #race - other race - entry
    # race_decline_twin = p01mb4_77, #race - decline to answer
    # race_tribe_text_twin = p01mb4_3_text, #race - tribe text
    # race_pacific_text_twin = p01mb4_16_text, #race - other race
    # race_other_text_twin = p01mb4_18_text, #race - other race text
    # bc1_latino_twin = p01mb5, #child latino
    # mexican_twin = p01mb55_1, #mexican
    # puerto_rican_twin = p01mb55_2, #puerto rican
    # cuban_twin = p01mb55_3, #cuban
    # latino_other_twin = p01mb55_4, #other
    # latino_dontknow_twin = p01mb55_5, #don't know
    # latino_decline_twin = p01mb55_77, #declined
    # latino_other_text_twin = p01mb55_4_text, #other text
    # bc1_custody_twin = p01mb6, #who currently has custody
    # custody_other_rel_twin = p01mb6_7_text, #other relative specificed text
    # num_kid_add_birth1 = p01mb0, # how many children
    # name_add_birth1 = p01mb1, #child name
    # dob_add_birth1 = p01mb2, #child DOB
    # birth_04_add_birth1 = p01db2, # child born before 2004
    # gender_id_add_birth1 = p01mb3, #child gender identity
    # gender_self_id_add_birth1 = p01mb3_8_text, #self id gender
    # white_add_birth1 = p01mb4_1,#race - white
    # black_add_birth1 = p01mb4_2,#race - black
    # amer_ind_add_birth1 = p01mb4_3,#race - american indian
    # asian_indian_add_birth1 = p01mb4_4,#race - asian indian
    # other_asian_all_add_birth1 = p01mb4_5,#race - other asian
    # chinese_add_birth1 = p01mb4_6,#race - chinese
    # filipino_add_birth1 = p01mb4_7,#race - filipino
    # japanese_add_birth1 = p01mb4_8,#race - japanese
    # korean_add_birth1 = p01mb4_9,#race - korean
    # vietnamese_add_birth1 = p01mb4_10,#race - vietnamese
    # other_asian_add_birth1 = p01mb4_11,#race - other
    # native_hawaii_all_add_birth1 = p01mb4_12,#race - native hawaiian/other pacific islander
    # native_hawaii_add_birth1 = p01mb4_13,#race - native hawaiian
    # samoan_add_birth1 = p01mb4_14,#race - guamanian
    # guamanian_add_birth1 = p01mb4_15,#race - samoan
    # other_pacific_add_birth1 = p01mb4_16,#race - other - entry
    # race_dontknow_add_birth1 = p01mb4_17,#race - don't know
    # race_other_add_birth1 = p01mb4_18,#race - other race - entry
    # race_decline_add_birth1 = p01mb4_77,#race - decline to answer
    # race_tribe_text_add_birth1 = p01mb4_3_text, #race - tribe text
    # race_pacific_text_add_birth1 = p01mb4_16_text, #race - other race
    # race_other_text_add_birth1 = p01mb4_18_text,#race - other race text
    # latino_add_birth1 = p01mb5, #child latino
    # mexican_add_birth1 = p01mb55_1,#mexican
    # puerto_rican_add_birth1 = p01mb55_2,#puerto rican
    # cuban_add_birth1 = p01mb55_3,#cuban
    # latino_other_add_birth1 = p01mb55_4,#other
    # latino_dontknow_add_birth1 = p01mb55_5,#don't know
    # latino_decline_add_birth1 = p01mb55_77, #declined
    # latino_other_text_add_birth1 = p01mb55_4_text, #other text
    # custody_add_birth1 = p01mb6, #who currently has custody
    # custody_other_rel_add_birth1 = p01mb6_7_text, #other relative specificed text
    # name_add_birth2 = p01mb1b,# child's name
    # dob_add_birth2 = p01mb2b, #child DOB
    # bc1_birth_04_add_birth2 = p01db3, # child born before 2004
    # bc1_gender_id_add_birth2 = p01mb3b, #child gender identity
    # gender_self_id_add_birth2 = p01mb3b_8_text, #self id gender
    # white_add_birth2 = p01mb4b_1, #race - white
    # black_add_birth2 = p01mb4b_2, #race - black
    # amer_ind_add_birth2 = p01mb4b_3, #race - american indian
    # asian_indian_add_birth2 = p01mb4b_4, #race - asian indian
    # other_asian_all_add_birth2 = p01mb4b_5, #race - other asian
    # chinese_add_birth2 = p01mb4b_6, #race - chinese
    # filipino_add_birth2 = p01mb4b_7, #race - filipino
    # japanese_add_birth2 = p01mb4b_8, #race - japanese
    # korean_add_birth2 = p01mb4b_9, #race -  korean
    # vietnamese_add_birth2 = p01mb4b_10, #race - vietnamese
    # other_asian_add_birth2 = p01mb4b_11, #race - other
    # native_hawaii_all_add_birth2 = p01mb4b_12, #race - native hawaiian/other pacific islander
    # native_hawaii_add_birth2 = p01mb4b_13, #race - native hawaiian
    # samoan_add_birth2 = p01mb4b_14, #race - guamanian
    # guamanian_add_birth2 = p01mb4b_15, #race - somoan
    # other_pacific_add_birth2 = p01mb4b_16, #race - other - entry
    # race_dontknow_add_birth2 = p01mb4b_17, #race - don't know
    # race_other_add_birth2 = p01mb4b_18, #race - other race - entry
    # race_decline_add_birth2 = p01mb4b_77, #race - decline to answer
    # race_tribe_text_add_birth2 = p01mb4b_3_text, #race - tribe text
    # race_pacific_text_add_birth2 = p01mb4b_16_text,#race - other race
    # race_other_text_add_birth2 = p01mb4b_18_text, #race - other race text
    # bc1_latino_add_birth2 = p01mb5b, #child latino
    # mexican_add_birth2 = p01mb5bb_1, # mexican
    # puerto_rican_add_birth2 = p01mb5bb_2, # puerto rican
    # cuban_add_birth2 = p01mb5bb_3, # cuban
    # latino_other_add_birth2 = p01mb5bb_4, # other
    # latino_dontknow_add_birth2 = p01mb5bb_5, # don't know
    # latino_decline_add_birth2 = p01mb5bb_77,#declined
    # latino_other_text_add_birth2 = p01mb5bb_4_text, #other text
    # bc1_custody_add_birth2 = p01mb6b, #who currently has custody
    # custody_other_rel_add_birth2 = p01mb6b_7_text, #other relative specificed text
    # name_add_birth3 = p01mb1c, #child name
    # dob_add_birth3 = p01mb2c, #child DOB
    # bc1_birth_04_add_birth3 = p01db4, # child born before 2004
    # bc1_gender_id_add_birth3 = p01mb3c, #child gender identity
    # gender_self_id_add_birth3 = p01mb3c_8_text, #self id gender
    # white_add_birth3 = p01mb4c_1, #race - white
    # black_add_birth3 = p01mb4c_2, #race - black
    # amer_ind_add_birth3 = p01mb4c_3, #race - american indian
    # asian_indian_add_birth3 = p01mb4c_4, #race - asian indian
    # other_asian_all_add_birth3 = p01mb4c_5, #race - other asian
    # chinese_add_birth3 = p01mb4c_6, #race - chinese
    # filipino_add_birth3 = p01mb4c_7, #race - filipino
    # japanese_add_birth3 = p01mb4c_8, #race - japanese
    # korean_add_birth3 = p01mb4c_9, #race - korean
    # vietnamese_add_birth3 = p01mb4c_10, #race - vietnamese
    # other_asian_add_birth3 = p01mb4c_11, #race - other
    # native_hawaii_all_add_birth3 = p01mb4c_12, #race - native hawaiian/other pacific islander
    # native_hawaii_add_birth3 = p01mb4c_13, #race - native hawaiian
    # samoan_add_birth3 = p01mb4c_14, #race - guamanian
    # guamanian_add_birth3 = p01mb4c_15, #race - somoan
    # other_pacific_add_birth3 = p01mb4c_16, #race - other - entry
    # race_dontknow_add_birth3 = p01mb4c_17, #race - don't know
    # race_other_add_birth3 = p01mb4c_18, #race - other race - entry
    # race_decline_add_birth3 = p01mb4c_77, #race - decline to answer
    # race_tribe_text_add_birth3 = p01mb4c_3_text,# race - tribe text
    # race_pacific_text_add_birth3 = p01mb4c_16_text, #race - other race
    # race_other_text_add_birth3 = p01mb4c_18_text,#race - other race text
    # bc1_latino_add_birth3 = p01mb5c, #child latino
    # mexican_add_birth3 = p01mb5cc_1,# mexican
    # puerto_rican_add_birth3 = p01mb5cc_2,# puerto ricna
    # cuban_add_birth3 = p01mb5cc_3,# cuban
    # latino_other_add_birth3 = p01mb5cc_4,# other
    # latino_dontknow_add_birth3 = p01mb5cc_5,# don't know
    # latino_decline_add_birth3 = p01mb5cc_77, #declined
    # latino_other_text_add_birth3 = p01mb5cc_4_text, #other text
    # bc1_custody_add_birth3 = p01mb6c, #who currently has custody
    # custody_other_rel_add_birth3 = p01mb6c_7_text,# other relative specified text
    bc1_drug_preg = p01l, #drugs during pregnancy
    bc1_drug_tri1 = p01n_1, #first trimester drugs
    bc1_drug_tri2= p01n_2, #second trimester drugs
    bc1_drug_tri3 = p01n_3,#third trimester drugs
    # drug_tri_decline = p01n_77, #declined trimester drugs
    bc1_days_drug_preg = p01m, #days using drugs during pregnancy
    bc1_alc_preg = p01q, #alcohol during pregnancy
    bc1_alc_tri1 = p01s_1, #first trimester alcohol
    # bc1_alc_tri2 = p01s_2,#second trimester alcohol
    # bc1_alc_tri3 = p01s_3,#third trimester alcohol
    # alc_tri_decline = p01s_77, #declined trimester alcohol
    bc1_days_alc_preg = p01r, #days alcohol during pregnancy
    bc1_tob_preg = p01v, #did you use use nicotine during pregnancy
    bc1_tob_tri1 = p01x_1, #first trimester nicotine
    bc1_tob_tri2 = p01x_2,#second trimester nicotine
    bc1_tob_tri3 = p01x_3, #third trimester nicotine
    # tob_tri_decline = p01x_77, #declined trimester nicotine
    bc1_days_tob_preg = p01w,

    bc2_tc_age_preg = p02a,
    bc2_preg_attempt = p02c,
    bc2_preg_result = p02d,
    bc2_tri_still_preg = p02g,
    bc2_tri_mis_abort = p02g2,
    bc2_name = p02b1,
    bc2_dob = p02b2,
    bc2_birth_04 = p02db1,
    bc2_gender_id = p02b3,
    bc2_white= p02b4_1,
    bc2_black = p02b4_2,
    bc2_amer_ind= p02b4_3,
    bc2_race_other = p02b4_18,
    bc2_race_tribe_text = p02b4_3_text,
    bc2_race_other_text = p02b4_18_text,
    bc2_latino = p02b5,
    bc2_mexican = p02b55_1,
    bc2_latino_other = p02b55_4,
    bc2_latino_other_text = p02b55_4_text,
    bc2_custody = p02b6,
    bc2_drug_preg = p02l,
    bc2_drug_tri1 = p02n_1,
    bc2_drug_tri2 = p02n_2,
    bc2_drug_tri3 = p02n_3,
    bc2_days_drug_preg = p02m,
    bc2_alc_preg = p02q,
    bc2_alc_tri1 = p02s_1,
    bc2_days_alc_preg = p02r,
    bc2_tob_preg = p02v,
    bc2_tob_tri1 = p02x_1,
    bc2_tob_tri2 = p02x_2,
    bc2_tob_tri3 = p02x_3,
    bc2_days_tob_preg = p02w,
    bc3_tc_age_preg = p03a,
    bc3_preg_attempt = p03c,
    bc3_preg_result = p03d,
    br3_still_preg = p03g,
    bc3_tri_mis_abort = p03g2,
    bc3_name = p03b1,
    bc3_dob = p03b2,
    bc3_birth_04= p03db1,
    bc3_gender_id = p03b3,
    bc3_white = p03b4_1,
    bc3_black = p03b4_2,
    bc3_amer_ind = p03b4_3,
    bc3_filipino = p03b4_7,
    bc3_race_other = p03b4_18,
    bc3_race_tribe_text = p03b4_3_text,
    bc3_race_other_text = p03b4_18_text,
    bc3_latino = p03b5,
    bc3_mexican = p03b55_1,
    bc3_latino_other = p03b55_4,
    bc3_latino_other_text = p03b55_4_text,
    bc3_custody = p03b6,
    bc3_num_kid_twin = p03mb0,
    bc3_name_twin = p03mb1,
    bc3_dob_twin = p03mb2,
    bc3_birth_04_twin = p03db2,
    bc3_gender_id_twin = p03mb3,
    bc3_white_twin = p03mb4a_1,
    bc3_latino_twin = p03mb5,
    bc3_custody_twin = p03mb6,
    bc3_name_add_birth2 = p03mb1b,
    bc3_dob_add_birth2 = p03mb2b,
    bc3_birth_04_add_birth2 = p03db3,
    bc3_gender_id_add_birth2 = p03mb3b,
    bc3_white_add_birth2 = p03mb4b_1,
    bc3_latino_add_birth2 = p03mb5b,
    bc3_custody_add_birth2 = p03mb6b,
    bc3_drug_preg= p03l,
    bc3_drug_tri1 = p03n_1,
    bc3_drug_tri2 = p03n_2,
    bc3_drug_tri3 = p03n_3,
    bc3_days_drug_preg = p03m,
    bc3_alc_preg = p03q,
    bc3_alc_tri1 = p03s_1,
    bc3_alc_tri2 = p03s_2,
    bc3_alc_tri3 = p03s_3,
    bc3_days_alc_preg = p03r,
    bc3_tob_preg = p03v,
    bc3_tob_tri1 = p03x_1,
    bc3_tob_tri2 = p03x_2,
    bc3_tob_tri3 = p03x_3,
    bc3_days_tob_preg = p03w,

    bc4_tc_age_preg = p04a,
    bc4_preg_attempt = p04c,
    bc4_preg_result = p04d,
    bc4_tri_still_preg = p04g,
    bc4_tri_mis_abort = p04g2,
    bc4_name = p04b1,
    bc4_dob = p04b2,
    bc4_birth_04 = p04db1,
    bc4_gender_id = p04b3,
    bc4_white = p04b4_1,
    bc4_amer_ind = p04b4_3,
    bc4_race_other = p04b4_18,
    bc4_race_tribe_text = p04b4_3_text,
    bc4_race_other_text = p04b4_18_text,
    bc4_latino = p04b5,
    bc4_latino_other = p04b55_4,
    bc4_latino_other_text = p04b55_4_text,
    bc4_custody = p04b6,
    bc4_drug_preg = p04l,
    bc4_drug_tri1 = p04n_1,
    bc4_drug_tri2 = p04n_2,
    bc4_days_drug_preg = p04m,
    bc4_alc_preg = p04q,
    bc4_tob_preg = p04v,
    bc4_tob_tri1 = p04x_1,
    bc4_tob_tri2 = p04x_2,
    bc4_tob_tri3 = p04x_3,
    bc4_days_tob_preg = p04w,

    bc5_tc_age_preg = p05a,
    bc5_preg_attempt = p05c,
    bc5_preg_result = p05d,
    bc5_tri_still_preg = p05g,
    bc5_tri_mis_abort = p05g2,
    bc5_name = p05b1,
    bc5_dob = p05b2,
    bc5_birth_04 = p05db1,
    bc5_gender_id = p05b3,
    bc5_white = p05b4_1,
    bc5_amer_ind = p05b4_3,
    bc5_race_other = p05b4_18,
    bc5_race_tribe_text = p05b4_3_text,
    bc5_race_other_text = p05b4_18_text,
    bc5_latino = p05b5,
    bc5_latino_other = p05b55_4,
    bc5_latino_other_text = p05b55_4_text,
    bc5_custody = p05b6,
    bc5_drug_preg = p05l,
    bc5_drug_tri1 = p05n_1,
    bc5_drug_tri2 = p05n_2,
    bc5_days_drug_preg = p05m,
    bc5_alc_preg = p05q,
    bc5_tob_preg = p05v,
    bc5_tob_tri1 = p05x_1,
    bc5_tob_tri2 = p05x_2,
    bc5_tob_tri3 = p05x_3,
    bc5_days_tob_preg = p05w,

    bc6_tc_age_preg = p06a,
    bc6_preg_attempt = p06c,
    bc6_preg_result = p06d,
    bc6_tri_still_preg = p06g,
    bc6_tri_mis_abort = p06g2,
    bc6_drug_preg = p06l,
    bc6_alc_preg = p06q,
    bc6_tob_preg = p06v,
    bc6_tob_tri1 = p06x_1,
    bc6_days_tob_preg = p06w,

    bc7_tc_age_preg = p07a,
    bc7_preg_attempt = p07c,
    bc7_preg_result = p07d,
    bc7_still_preg = p07g,

    bc_parent_num = r0start,

    pc_bc1_white = r01a_c_1_1799, #pc = previous custody
    pc_bc1_black = r01a_c_2_1800,
    pc_bc1_amer_ind = r01a_c_3_1801,
    pc_bc1_other_asian_all = r01a_c_5_1803,
    pc_bc1_filipino = r01a_c_7,
    # pc_bc1_vietnamese= r01a_c_10,
    pc_bc1_samoan = r01a_c_15,
    pc_bc1_other_pacific = r01a_c_16,
    pc_bc1_race_other = r01a_c_18,
    pc_bc1_race_tribe_text= r01a_c_3_text,
    pc_bc1_race_pacific_text = r01a_c_16_text,
    pc_bc1_race_other_text = r01a_c_18_text,
    pc_bc1_birth_04 = r01_screen,
    pc_bc1_latino = r01a_c,
    pc_bc1_mexican = r01a_c_1_1823,
    pc_bc1_puerto_rican = r01a_c_2_1824,
    pc_bc1_cuban = r01a_c_3_1825,
    pc_bc1_latino_other = r01a_c_4_1826,
    pc_bc1_latino_dontknow = r01a_c_5_1827,
    pc_bc1_latino_other_text = r01a_c_4_text,
    pc_bc1_custody = r01g,
    pc_bc1_custody_other_rel= r01g_7_text,
    pc_bc1_lost_custody = r01j,

    pc_bc2_white = r02a_c_1_1833,
    pc_bc2_black = r02a_c_2_1834,
    pc_bc2_amer_ind = r02a_c_3_1835,
    # pc_bc2_asian_indian = r02a_c_4_1836,
    pc_bc2_filipino = r02a_c_7,
    # pc_bc2_vietnamese = r02a_c_10,
    # pc_bc2_native_hawaii_all = r02a_c_12,
    pc_bc2_native_hawaii = r02a_c_13,
    pc_bc2_other_pacific = r02a_c_16,
    pc_bc2_race_other = r02a_c_18,
    pc_bc2_race_tribe_text = r02a_c_3_text,
    pc_bc2_race_pacific_text = r02a_c_16_text,
    pc_bc2_race_other_text = r02a_c_18_text,
    pc_bc2_birth_04 = r02_screen,
    pc_bc2_latino = r02a_c,
    pc_bc2_mexican = r02a_c_1_1857,
    pc_bc2_puerto_rican = r02a_c_2_1858,
    pc_bc2_latino_other = r02a_c_4_1860,
    pc_bc2_latino_other_text = r02a_c_4_text,
    pc_bc2_custody = r02g,
    pc_bc2_custody_other_rel = r02g_7_text,
    pc_bc2_lost_custody = r02j,

    pc_bc3_white = r03a_c_1_1867,
    pc_bc3_black = r03a_c_2_1868,
    pc_bc3_amer_ind = r03a_c_3_1869,
    pc_bc3_filipino = r03a_c_7,
    pc_bc3_other_asian = r03a_c_11,
    pc_bc3_native_hawaii_all = r03a_c_12,
    pc_bc3_native_hawaii = r03a_c_13,
    pc_bc3_race_other = r03a_c_18,
    pc_bc3_decline = r03a_c_77_1885,
    pc_bc3_race_tribe_text = r03a_c_3_text,
    pc_bc3_race_other_text = r03a_c_18_text,
    pc_bc3_birth_04 = r03_screen,
    pc_bc3_latino = r03a_c2,
    pc_bc3_mexican = r03a_c_1_1891,
    pc_bc3_puerto_rican = r03a_c_2_1892,
    pc_bc3_latino_other = r03a_c_4_1894,
    pc_bc3_latino_other_text = r03a_c_4_text,
    pc_bc3_custody = r03g,
    pc_bc3_custody_other_rel = r03g_7_text,
    pc_bc3_lost_custody = r03j,

    pc_bc4_white = r04a_c_1_1901,
    pc_bc4_black = r04a_c_2_1902,
    pc_bc4_amer_ind = r04a_c_3_1903,
    pc_bc4_filipino = r04a_c_7,
    pc_bc4_native_hawaii_all = r04a_c_12,
    pc_bc4_native_hawaii = r04a_c_13,
    pc_bc4_race_other = r04a_c_18,
    pc_bc4_race_tribe_text = r04a_c_3_text,
    pc_bc4_race_other_text = r04a_c_18_text,
    pc_bc4_birth_04 = r04_screen,
    pc_bc4_latino = r04a_c2,
    pc_bc4_mexican = r04a_c_1_1925,
    pc_bc4_custody = r04g,
    pc_bc4_lost_custody = r04j,

    pc_bc5_white = r05a_c_1_1935,
    pc_bc5_amer_ind = r05a_c_3_1937,
    pc_bc5_race_other = r05a_c_18,
    pc_bc5_race_tribe_text = r05a_c_3_text,
    pc_bc5_race_other_text = r05a_c_18_text,
    pc_bc5_birth_04 = r05_screen,
    pc_bc5_latino = r05a_c2,
    pc_bc5_mexican = r05a_c_1_1959,
    pc_bc5_custody = r05g,
    pc_bc5_lost_custody = r05j,

    # pc_bc6_birth_04 = r06_screen,
    # pc_bc6_latino = r06a_c2,
    # pc_bc6_custody = r06g,
    # pc_bc6_lost_custody = r06j,
    #
    # pc_bc7_birth_04 = r07_screen,
    # pc_bc7_latino = r07a_c2,
    # pc_bc7_custody = r07g,
    # pc_bc7_lost_custody = r07j,
    #
    # pc_bc8_birth_04 = r08_screen,
    # pc_bc8_latino = r08a_c2,
    # pc_bc8_custody = r08g,
    # pc_bc8_lost_custody = r08j,
    #
    # pc_bc9_birth_04 = r09_screen,
    # pc_bc9_latino = r09a_c2,
    # pc_bc9_custody = r09g,
    # pc_bc9_lost_custody = r09j,
    #
    # pc_bc10_birth_04 = r10_screen,
    # pc_bc10_latino = r10a_c2,
    # pc_bc10_custody = r10g,
    # pc_bc10_lost_custody = r10j,

    sc_parent_num = spm00,

    sm_sc1_white = spm1b_1,
    sm_sc1_black = spm1b_2,
    sm_sc1_filipino = spm1b_7,
    sm_sc1_native_hawaii_all = spm1b_12,
    sm_sc1_native_hawaii = spm1b_13,
    sm_sc1_race_other = spm1b_18,
    sm_sc1_race_other_text = spm1b_18_text,
    sm_sc1_latino = spm1c_2162,
    sm_sc1_mexican = spm1c1_1,
    sm_sc1_welfare_contact = spm1b,
    sm_sc1_living_with = spm1c_2171,

    sm_sc2_white = spm2b_1,
    sm_sc2_black = spm2b_2,
    sm_sc2_other_pacific = spm2b_16,
    sm_sc2_race_other = spm2b_18,
    sm_sc2_race_pacific_text = spm2b_16_text,
    sm_sc2_race_other_text = spm2b_18_text,
    sm_sc2_latino = spm2c,
    sm_sc2_mexican = spm2c1_1,
    sm_sc2_welfare_contact = spm2d,
    sm_sc2_living_with = spm2e,

    sm_sc3_white = spm3b_1,
    sm_sc3_other_pacific = spm3b_16,
    sm_sc3_race_other = spm3b_18,
    sm_sc3_race_pacific_text = spm3b_16_text,
    sm_sc3_race_other_text = spm3b_18_text,
    sm_sc3_latino = spm3c,
    sm_sc3_mexican = spm3c1_1,
    sm_sc3_welfare_contact = spm3d,
    sm_sc3_living_with = spm3e,

    # sm_sc4_latino = spm4c,
    # sm_sc4_welfare_contact = spm4d,
    # sm_sc4_living_with = spm4e,

    # sm_sc5_latino = spm5c,
    # sm_sc5_welfare_contact = spm5d,
    # sm_sc5_living_with = spm5e,

    other_sc= sp00, #other stepchildren under 17 since last interview
    other_sc_num= sp000,

    other_sc1_name = sp1a,
    other_sc1_dob = sp1b,
    other_sc1_gender_id= sp1c,
    other_sc1_white = sp1d_1,
    other_sc1_black = sp1d_2,
    other_sc1_other_pacific = sp1d_16,
    other_sc1_race_other = sp1d_18,
    other_sc1_race_pacific_text= sp1d_16_text,
    other_sc1_race_other_text = sp1d_18_text,
    other_sc1_latino = sp1d1,
    other_sc1_mexican = sp1d1a_1,
    other_sc1_other_latino = sp1d1a_4,
    other_sc1_latino_other_text = sp1d1a_4_text,
    other_sc1_welfare_contact = sp1e,
    other_sc1_living_with = sp1f,

    other_sc2_name = sp2a,
    other_sc2_dob = sp2b,
    other_sc2_gender_id = sp2c,
    other_sc2_white = sp2d_1,
    other_sc2_black = sp2d_2,
    other_sc2_amer_ind = sp2d_3,
    other_sc2_race_other = sp2d_18,
    other_sc2_race_tribe_text = sp2d_3_text,
    other_sc2_race_other_text = sp2d_18_text,
    other_sc2_latino = sp2d1,
    other_sc2_mexican = sp2d1a_1,
    other_sc2_other_latino = sp2d1a_4,
    other_sc2_dontknow = sp2d1a_5,
    other_sc2_decline = sp2d1a_77,
    other_sc2_latino_other_text= sp2d1a_4_text,
    other_sc2_welfare_contact = sp2e,
    other_sc2_living_with = sp2f,

    other_sc3_name = sp3a,
    other_sc3_dob = sp3b,
    other_sc3_gender_id = sp3c,
    other_sc3_white = sp3d_1,
    other_sc3_amer_ind = sp3d_3,
    other_sc3_race_other = sp3d_18,
    other_sc3_race_tribe_text = sp3d_3_text,
    other_sc3_race_other_text = sp3d_18_text,
    other_sc3_latino = sp3d1,
    other_sc3_mexican = sp3d1a_1,
    other_sc3_welfare_contact = sp3e,
    other_sc3_living_with = sp3f,

    other_sc4_name = sp4a,
    other_sc4_dob = sp4b,
    other_sc4_gender_id = sp4c,
    other_sc4_white = sp4d_1,
    other_sc4_amer_ind = sp4d_3,
    other_sc4_race_tribe_text = sp4d_3_text,
    other_sc4_latino = sp4d1,
    other_sc4_welfare_contact = sp4e,
    other_sc4_living_with = sp4f,

    other_kid = ct0,
    other_kid_num = ct000,

    other_kid1_name = nc1,
    other_kid1_dob = nc1a,
    other_kid1_gender_id = nc1b,
    other_kid1_white = nc1c_1,
    other_kid1_black = nc1c_2,
    other_kid1_amer_ind = nc1c_3,
    other_kid1_other_asian_all = nc1c_5,
    other_kid1_race_tribe_text = nc1c_3_text,
    other_kid1_mexican = nc1c1a_1, #no asking about being latino
    # other_kid1_dontknow = nc1c1a_5,
    other_kid1_decline = nc1c1a_77,
    other_kid1_relation = nc1d,
    other_kid1_welfare_contact = nc1e,
    other_kid1_living_with = nc1f,

    other_kid2_name = nc2,
    other_kid2_dob = nc2a,
    other_kid2_gender_id = nc2b,
    other_kid2_white = nc2c_1,
    other_kid2_other_asian_all = nc2c_5,
    # other_kid2_race_other = nc2c_18,
    # other_kid2_race_other_text = nc2c_18_text,
    other_kid2_latino = nc2c1,
    # other_kid2_mexican = nc2c1a_1,
    other_kid2_relation = nc2d,
    other_kid2_welfare_contact = nc2e,
    other_kid2_living_with = nc2f,

    # other_kid3_name = nc3,
    # other_kid3_dob = nc3a,
    # other_kid3_gender_id = nc3b,
    # other_kid3_race_other = nc3c_18,
    # other_kid3_race_other_text = nc3c_18_text,
    # other_kid3_latino = nc3c1,
    # other_kid3_mexican = nc3c1a_1,
    # other_kid3_relation = nc3d,
    # other_kid3_welfare_contact = nc3e,
    # other_kid3_living_with = nc3f,

    # other_kid4_name = nc4,
    # other_kid4_dob = nc4a,
    # other_kid4_gender_id = nc4b,
    # other_kid4_race_other = nc4c_18,
    # other_kid4_race_other_text = nc4c_18_text,
    # other_kid4_latino = nc4c1,
    # other_kid4_mexican = nc4c1a_1,
    # other_kid4_relation = nc4d,
    # other_kid4_welfare_contact = nc4e,
    # other_kid4_living_with = nc4f,

    # other_kid5_name = nc5,
    # other_kid5_dob = nc5a,
    # other_kid5_gender_id = nc5b,
    # other_kid5_race_other = nc5c_18,
    # other_kid5_race_other_text = nc5c_18_text,
    # other_kid5_latino = nc5c1,
    # other_kid5_mexican = nc5c1a_1,
    # other_kid5_relation = nc5d,
    # other_kid5_welfare_contact = nc5e,
    # other_kid5_living_with = nc5f
  )

remove_df <- 
  remove_df %>% 
  select(-...1:-user_language) %>%
  relocate(id,
           .before = 1)

```

## Creating Long (Not tidy) Dataframes

### Pregnancy Results

```{r}
comb_long_preg <-
  remove_df %>%
  pivot_longer(
    cols = matches('preg_result$'),
    names_to = 'preg_result_name',
    values_to = 'preg_result'
  ) %>%
  mutate(
    preg_result = case_when(
      preg_result == 1 ~ 'still_preg',
      preg_result == 2 ~ 'miscarriage',
      preg_result == 3 ~ 'abortion',
      preg_result == 4 ~ 'birth',
      preg_result == 5 ~ 'multiple_birth',
      preg_result == 6 ~ 'stillbirth',
      preg_result == 7 ~ 'false_pos',
      preg_result == 8 ~ 'decline',
      TRUE ~ NA_character_
    ),
    curr_preg = case_when(
      curr_preg == 1 ~ 'yes',
      curr_preg == 2 ~ 'no',
      curr_preg == 3 ~ 'decline',
      TRUE ~ NA_character_
    )
  ) %>% 
  select(
    id,
    times_preg,
    preg_result,
    preg_result_name,
    curr_preg
  ) %>% 
  arrange(id)

comb_long_preg %>% 
  gt::gt()
```

### Number of Children

```{r}
comb_long_numkid <-
remove_df %>%
  pivot_longer(
    cols = c(matches('name$')),
    names_to = 'kid_name',
    values_to = 'actual_name'
  ) %>%
  drop_na(kid_name, actual_name) %>%
  group_by(id, kid_name) %>%
  count(actual_name) %>%
  ungroup() %>%
  group_by(id) %>%
  summarize(
    total_num_kids = sum(n)
    ) %>%
  ungroup() 

comb_long_numkid %>% 
  gt::gt()
```

### Number of All Stepchildren

```{r}
comb_long_step <-
remove_df %>%
  pivot_longer(
    cols = c(matches('name$')),
    names_to = 'kid_name',
    values_to = 'actual_name'
  ) %>%
  drop_na(kid_name, actual_name) %>%
  group_by(id, kid_name) %>%
  mutate(
    kid_count = n()
         ) %>%
  ungroup() %>%
  select(
    id,
    kid_name,
    actual_name,
    kid_count,
    sc_parent_num
    ) %>%
  filter(
    str_detect(
      kid_name,
      '^other_sc'
    )
) %>% 
  group_by(id, kid_name) %>%
  summarize(
    total_stepkid = kid_count + sc_parent_num
    ) %>%
  ungroup()

comb_long_step %>% 
  arrange(id) %>% 
  gt::gt()

```

### Number of Other Children

```{r}
comb_long_other <-
remove_df %>%
  pivot_longer(
    cols = c(matches('name$')),
    names_to = 'kid_name',
    values_to = 'actual_name'
  ) %>%
  drop_na(kid_name, actual_name) %>%
  group_by(id, kid_name) %>%
  count(actual_name) %>%
  ungroup() %>%
  filter(
    str_detect(
      kid_name,
      '^other'
    ),
    !str_detect(
      kid_name,
      '_sc\\d_'
    )
  ) %>% 
  group_by(id) %>%
  summarize(
    total_other_kid = sum(n,
    na.rm = TRUE)
            ) %>% 
  ungroup()

comb_long_other %>% 
  gt::gt()
```

### Age Each Pregnancy

```{r}
comb_long_age <-
remove_df %>%
  pivot_longer(
    cols = c(matches('age_preg$')),
    names_to = 'kid_number',
    values_to = 'age_preg'
  ) %>%
  drop_na(kid_number, age_preg) %>%
  group_by(id, kid_number) %>%
  count(age_preg) %>%
  ungroup() %>%
  separate(
    col = kid_number,
    into = c('birth_number',
             'tc_remove',
             'age_remove',
             'preg_remove')
  ) %>%
  relocate(
    birth_number,
    .after = id
  ) %>%
  select(
    -matches(
      'remove$'
    ),
    -n
  )

comb_long_age %>% 
  gt::gt()
```

### Children Race

```{r}
comb_long_race <-
remove_df %>%
  pivot_longer(
    cols = c(matches('white$'),
             matches('black$'),
             matches('amer_ind$'),
             matches('samoan$'),
             matches('race_other$'),
             matches('filipino$'),
             matches('vietnames$'),
             matches('other_pacific$'),
             matches('native_hawaii$'),
             matches('native_hawaii_all$'),
             matches('other_asian_all$'),
             matches('asian_indian$'),
             matches('text$')),
    names_to = 'race_name',
    values_to = 'race'
  ) %>%
  drop_na(race_name, race) %>%
  select(
    id,
    race_name,
    race
    ) %>% 
  arrange(id) 

comb_long_race %>% 
  group_by(id, race_name, race) %>% 
  count() %>% 
  arrange(id) %>% 
  gt::gt()

```

### Months From Baseline

```{r}
library(lubridate)

# months from baseline
assess_date <-
  remove_df %>%
  drop_na(assessment_screen) %>%
  separate(
    col = assessment_screen,
    into = c('month',
             'day',
             'year'),
    sep = '/'
  ) %>%
  unite(
    col = 'assessment_screen',
    c(month, day, year),
    sep = '-'
  ) %>%
  mutate(
    tp_assess_date = mdy(assessment_screen)
  )

assess_date_sub <-
  assess_date %>%
  select(
    id,
    tp_assess_date
    )
```

### Names

```{r, eval = FALSE}
# remove_df %>%
#   pivot_longer(
#     cols = c(matches('name$')),
#     names_to = 'kid_name',
#     values_to = 'actual_name'
#   ) %>%
#   drop_na(kid_name, actual_name) %>%
#   group_by(id, kid_name) %>%
#   count(actual_name) %>%
#   ungroup() %>%
#   group_by(id) %>%
#   summarize(
#     total_num_kids = sum(n)
#     ) %>%
#   ungroup() 
```

### Children Date of Birth

```{r}
comb_long_dob <-
remove_df %>% 
  pivot_longer(
      cols = matches('dob$'),
      names_to = 'dob_name',
      values_to = 'dob'
      ) %>%
  drop_na(dob_name, dob) %>% 
  select(
    id,
    dob_name,
    dob
  ) %>% 
  distinct() %>% 
  group_by(id) %>% 
  count(dob_name, dob) %>% 
  arrange(id)

comb_long_dob %>% 
  gt::gt()
```

### Are the kiddos Latino?

```{r}
comb_long_lat <-
  remove_df %>% 
  mutate(
    across(
      .cols = c(matches('^bc\\d_latino'),
                matches('pc_bc\\d_latino'),
                matches('sm_sc\\d_latino'),
                matches('other_sc\\d_latino'),
                matches('other_kid\\d_latino')),
      .fns = ~case_when(
        .x == 1 ~ 'Yes',
        .x == 2 ~ 'No',
        .x == 3 ~ 'Don\'t know',
        .x == 4 ~ 'Decline',
        TRUE ~ NA_character_
      )
    )
  ) %>% 
  pivot_longer(
    cols = matches('latino$'),
    names_to = 'kid_num_latino',
      values_to = 'latino_yn'
  ) %>% 
  drop_na(kid_num_latino, latino_yn) %>% 
  select(
    id,
    kid_num_latino,
    latino_yn
  ) %>% 
  distinct() %>%
  arrange(id)

comb_long_lat %>% 
  gt::gt()
```

### Children Ethnicity (Latino)

```{r}
comb_long_eth <-
  remove_df %>%
pivot_longer(
  cols = c(matches('latino_other$'),
           matches('mexican$'),
           matches('cuban$'),
           matches('puerto_rican$')),
  names_to = 'latino_group_name',
  values_to = 'latino_group'
) %>%
  drop_na(latino_group_name, latino_group) %>% 
  select(
    id,
    latino_group_name,
    latino_group
  ) %>% 
  distinct() %>%
  arrange(id) %>% 
  filter(
    !str_detect(
      latino_group_name,
      '^bc\\d'
      )
  )

comb_long_eth %>% 
  group_by(id) %>% 
  count(latino_group_name)
```

### Children Gender

```{r}
comb_long_gender <-
  remove_df %>%
  pivot_longer(
    cols = matches('gender_id$'),
    names_to = 'gender_name',
    values_to = 'gender_id'
  ) %>%
  mutate(
    gender_id = case_when(
      gender_id == 1 ~ 'cis_fem',
      gender_id == 2 ~ 'female',
      gender_id == 3 ~ 'cis_male',
      gender_id == 4 ~ 'male',
      gender_id == 5 ~ 'trans_fem',
      gender_id == 6 ~ 'trans_male',
      gender_id == 7 ~ 'non_binary',
      gender_id == 8 ~ 'self_id',
      gender_id == 9 ~ 'decline',
      TRUE ~ NA_character_
  )
  ) %>% 
  drop_na(gender_name, gender_id) %>% 
  select(
    id,
    gender_name,
    gender_id
  ) %>% 
  distinct() %>%
  arrange(id)

comb_long_gender %>% 
  # group_by(id) %>% 
  # count(gender_name, gender_id) %>% 
  gt::gt()
```

### Custody of Children

```{r}
comb_long_custody <-
  remove_df %>%
  pivot_longer(
    cols = matches('\\d_custody$'),
    names_to = 'custody_name',
    values_to = 'custody'
  ) %>%
  select(
    id,
    custody_name,
    custody
  ) %>% 
  mutate(
    custody = case_when(
      custody == 1 ~ 'tc',
      custody == 2 ~ 'bio dad',
      custody == 3 ~ 'tc bio dad - living',
      custody == 4 ~ 'tc and bio dad - shared',
      custody == 5 ~ 'tc and partner',
      custody == 6 ~ 'grandparent(s)',
      custody == 7 ~ 'other relative',
      custody == 8 ~ 'adopted',
      custody == 9 ~ 'state',
      custody == 10 ~ 'don\'t know',
      custody == 11 ~ 'decline',
      TRUE ~ NA_character_
    )
  ) %>% 
    drop_na(custody_name, custody) %>% 
  arrange(id)

comb_long_custody %>% 
  gt::gt()
```

## Additional Files

```{r}
child_history <- readxl::read_excel('C:/Users/cpppe/Desktop/github_projects/tpwdata_fork/jp_files/full_pregnancy_child_history.xlsx') %>%
  janitor::clean_names()

assess_date_sub <-
  assess_date %>%
  select(
    id,
    tp_assess_date
    )

child_sub <-
  child_history %>%
  mutate(
    family = fam_id
    ) %>%
  select(
    dob,
    total_number_of_children:number_of_other_children,
    preg_num:child_num,
    child_dob:child_n,
    date0,
    family
  )
```

```{r}
combined <-
  maria_file %>%
  left_join(
    child_sub
  )

combined <-
  combined %>%
  select(
    family:dob,
    date0
  ) %>%
  rename(
    first_assessment = date0
  )

```

```{r}
comb_long_age <-
  comb_long_age %>%
  rename(
    family = id
    )
```

### Joining

```{r}
jp <-
  left_join(combined, comb_long_age)

jp <-
  comb_long_numkid %>%
  rename(family = id) %>%
  right_join(jp)

jp <-
  comb_long_other %>%
  rename(family = id) %>%
  right_join(jp)

jp <-
  comb_long_preg %>% 
  rename(family = id) %>%
  right_join(jp)

jp <-
  comb_long_step %>%
  rename(family = id) %>%
  right_join(jp)


jp <-
  assess_date_sub %>%
  rename(family = id) %>%
  right_join(jp)

jp <-
  comb_long_race %>%
    rename(family = id) %>%
    right_join(jp)

jp <- 
  jp %>% 
  rename(tc_dob = dob)

# issue
jp <-
  comb_long_dob %>%
  select(
    -n
  ) %>%
    rename(family = id) %>%
    right_join(jp)

# need to include custody
jp <-
  comb_long_custody %>%
    rename(family = id) %>%
    right_join(jp)

# need to include ethnicity
jp <-
  comb_long_eth %>%
    rename(family = id) %>%
    right_join(jp)

jp <-
  comb_long_lat %>% 
  rename(family = id) %>% 
  right_join(jp)

jp <- 
  comb_long_gender %>% 
  rename(family = id) %>% 
  right_join(jp)

jp <-
  jp %>%
  distinct(
    across(
      .cols = everything()
    )
  )

# this will get rid of the three missing births, don't run this until you find out
# why they don't have first assessments (P828, P829, P847)
# jp <- 
  # jp %>%
  # drop_na(first_assessment)

jp <-
  jp %>%
  relocate(
    first_assessment,
    .after = family
  ) %>%
    relocate(
      curr_preg,
      .before = preg_result_name
    ) %>%
    relocate(
      total_stepkid,
      .before = total_other_kid
    ) %>%
    relocate(
      nfam,
      .before = first_assessment
    ) %>%
    relocate(
      cohort,
      .before = first_assessment
    ) %>%
    relocate(
      dob,
      .before = first_assessment
    ) %>%
    relocate(
      glptx,
      .before = first_assessment
    ) %>%
  relocate(
    age_preg,
    .before = total_stepkid
  ) %>%
  relocate(
    birth_number,
    .after = age_preg
  ) %>%
  mutate(
    birth_number = case_when(
      ((preg_result %in% c('stillbirth', 'abortion','miscarriage')) &
         !is.na(birth_number)) ~ NA_character_,
      TRUE ~ birth_number
    )
  )

jp <-
  jp %>%
  mutate(
    month_compare = lubridate::interval(
      first_assessment,
      tp_assess_date
      )
  )

jp$month_diff <- jp$month_compare %/% months(1)

jp <-
  jp %>%
  arrange(family)

# jp_sub <- 
#   jp %>% 
#   select(
#     family:tp_assess_date,
#     times_preg,
#     wave:month_diff
#   )
```

```{r}
rm(comb_long_age, 
   combined,
   maria_file,
   comb_long_numkid,
   comb_long_dob,
   comb_long_custody,
   comb_long_gender,
   comb_long_eth,
   comb_long_lat,
   comb_long_race,
   comb_long_other,
   comb_long_preg,
   comb_long_step,
   interview,
   remove_df,
   assess_date,
   assess_date_sub,
   child_history,
   child_sub)

gc()
```

## Calculations

### Pregnancy Results

-   For each Family/ID

```{r}
jp %>%
  distinct(family, preg_result_name, preg_result) %>% 
  group_by(family, preg_result_name) %>% 
  count(preg_result) %>%
  ungroup() %>% 
  drop_na() %>% 
  gt::gt() 
```

-   Pregnancy Results Summarized

```{r}
jp %>% 
  distinct(family, preg_result) %>% 
  count(preg_result) %>% 
  drop_na() %>% 
  gt::gt()
```

-   Cumulative Number of Births

```{r}
jp %>% 
  distinct(
    family, 
    preg_result_name,
    preg_result,
    curr_preg
    ) %>%
  group_by(family) %>% 
  count(
    preg_result_name,
    preg_result,
    curr_preg
    ) %>% 
  ungroup() %>% 
  drop_na() %>%
  filter(preg_result == 'birth') %>%
  summarize(
    total_preg = sum(n,
                     na.rm = TRUE)
  ) %>% 
  gt::gt() 
  
```

### Kiddos

-   Numbered Kiddos

```{r}
jp %>% 
  select(
    family,
    preg_result_name, 
    preg_result
  ) %>% 
  distinct(
    family,
    preg_result_name, 
    preg_result
           ) %>% 
  drop_na() %>% 
  gt::gt()
```

-   Kiddo (Biological, Step, Other Step, Other) Race

```{r}
jp %>% 
  select(
    family,
    race_name,
    race
  ) %>% 
  distinct(
    family,
    race_name,
    race
  ) %>%
  group_by(family, race_name) %>% 
  count(race) %>% 
  ungroup() %>% 
  drop_na() %>% 
  gt::gt()
```

-   Kiddo Ethnicity (Latino) If they are NA then they responded No to the kiddo being Latina/o.

```{r}
jp %>% 
  select(
    family,
    latino_group_name,
    latino_group
  ) %>% 
  distinct(
    family,
    latino_group_name,
    latino_group
  ) %>% 
  drop_na() %>% 
  gt::gt()
```

-   Kiddo Gender

```{r}
jp %>% 
  select(
    family,
    gender_name,
    gender_id
  ) %>% 
  distinct(
    family,
    gender_name,
    gender_id
  ) %>% 
  drop_na() %>% 
  gt::gt()
```

-   Kiddo Custody

```{r}
jp %>% 
  select(
    family,
    custody_name,
    custody
  ) %>% 
  mutate(
    custody_yn = if_else(
      custody %in% c('tc',
                     'tc and partner',
                     'tc bio dad - living'),
      'Yes',
      'No'
      )
  ) %>% 
  distinct(
    family,
    custody_name,
    custody,
    custody_yn
  ) %>% 
  drop_na() %>% 
  filter(
    str_detect(
      custody_name,
      'pc_'
      )
    ) %>% 
  group_by(family, custody_name) %>% 
  count(custody, custody_yn) %>% 
  ungroup() %>% 
  gt::gt()
```

-   Total Number of Step, Other, and Biological Kiddos

```{r}
jp %>% 
  select(
    family,
    total_stepkid, 
    total_other_kid, 
    total_num_kids
  ) %>% 
  group_by(family) %>% 
  count(
    total_stepkid, 
    total_other_kid, 
    total_num_kids
  ) %>% 
  drop_na(total_num_kids) %>% 
  ungroup() %>% 
  arrange(family) %>%
  select(-n) %>% 
  gt::gt()
```

### Months From Baseline

-   

        Differences between the first assessment date and the TP wave assessment date. Dates are included for double-checking. 

```{r}
jp %>% 
  select(
    family, 
    first_assessment,
    tp_assess_date,
    # month_compare,
    month_diff
  ) %>% 
  distinct(
    family,
    first_assessment,
    tp_assess_date,
    month_diff
    ) %>% 
  drop_na() %>% 
  gt::gt()
```
